\chapter{Beautiful Lost Nebula}

“Hope” is the thing with feathers –
That perches in the soul –
And sings the tune without the words –
And never stops – at all –

And sweetest – in the Gale – is heard –
And sore must be the storm –
That could abash the little Bird
That kept so many warm –

I’ve heard it in the chillest land –
And on the strangest Sea –
Yet – never – in Extremity,
It asked a crumb – of me.

Emily Dickinson

\simpleline

\DatePlace{The Chamber of Secrets\\
1185 C.E.}

“I grow old, Nagina. My hope of evading death is becoming a distant memory. It is clear that in my lifetime, it shall not come to pass.” Salazar spoke slowly to his basilisk.

“Issss sssssorry, masssster. I truly wisssh that I had ssssspoken true to you that day, ssssso many yearsss before. But Heracliussss–“

“Herpo. Herpo the Foul. His true name must be lost to time.”

“Yesss, massster. He taught me and mine little beyond what you already know or have disssscovered on your own. But ssssstill, have you not reconssssidered? There are ssssso many, sssssurely you can find one that no one would missss, one who does not desssserve their gift.”

“No. That is one thing I still cannot sacrifice.”

“It need not be frequent…. Perhapssss oncccce a cccccentury. Our mindssss are bound, your lore isssss my lore. If you were to passsss unexxxxxpectedly, I could teach you that which you had losssst….”

“Again, no. Even one innocent life is too much.”

At the word ‘innocent’, Nagina made a skeptical gesture with her eye; if she had eyebrows, she would have cocked them.

“I have an exxxxcccccellent and capacccciousssss memory… “

Salazar held up a hand to silence her. “No. But I have a solution. One that requires no sacrifices of others. We are here in our chamber, this chamber of secrets. I have left clues and hints so that one day my rightful heir can pick up the sword that I will lay down, and rid the world if its demons, rid the world of death.” As he spoke, he moved his hands in a gesture that Nagina recognized.

“Massssster…”

“It is my time, for now. But one day, one day we shall reawaken.”

Nagina’s heart began to beat quickly as she felt the oppressive prickles of magic begin to caress her scales. She understand what he was doing, and why he must do it, but the prospect of loss stung her nonetheless. A single tear of liquid stone dripped from her eyes, which she always kept shut as a gesture of respect, peace, and submission.

“Goodbye, for now, Nagina. AVADA KEDAVRA!”

His wand was pointed at his own chest, so the bolt of light did not need to travel far. Nagina had darted forward to catch his body in her coils so that it would not be damaged as it fell. They physical aspect of her body momentarily glowed a soft green, and she could feel his spirit bind itself to her flesh. It would lend her a degree of permanence beyond even her own impressive natural lifespan.

When the ritual was complete, she gently flicked his eyelids open with her forked tongue. His body was still warm, she could at least do this much in remembrance for him. She opened her golden, multifaceted eyes, needing to adjust to the touch of light which she had blocked out for the better part of a century. Once objects came into focus, she stared into his eyes. His soul was gone, but the biological component was still there. Magic flowed from the connection, and slowly turned his body into stone, the enchantment creeping out from the extremities, through to the limbs, up to his chest, until finally the aged lines of his face solidified into permanence, into stone.

From time to time over the coming centuries, she could feel his mind reaching out, testing the waters, calling to the students of Hogwarts, trying to determine if the time was right. Until that time, she spent many long years waiting, alone, waiting for the chosen one to solve the riddle of the Chamber of Secrets and awaken her master at last.
\simpleline
\DatePlace{London\\
1202 C.E.}
Matthew Ravenclaw read the scroll again, still trying to decipher its meaning. It had been willed to him by his grandmother, Rowena, who had passed away shortly after his mother, Helena, who in turn had been slain shortly after he was born. It was enchanted so at to only open when he had graduated from Hogwarts. It was written in true Ravenclaw fashion, filled with riddles and hidden meanings, both of which he had little patience for.

“When your mother was born, I learned that my life’s greatest creation, crafted in pursuit of truth and knowledge, was in fact, built on a foundation of lies.

‘Wit beyond measure is man’s greatest treasure.’

I had thought myself clever, with such dual meaning. The wisdom locked behind the shackles of the Interdict, which I wished to overthrow, I truly thought that would be the salvation of our kind.

I discovered a magic much greater. You never knew your mother, but nonetheless, you must honor her, pass on her name. Helena. She was meant to be a light in the darkness, the moon to balance the dark of night. But now that sky is empty, and you must carry the torch.

Your mother discovered that great magic with you, and she would stop at nothing to protect you from this world. I had learned where my true treasure lie, and gave her my Diadem. With it, she sought to follow the Path to find the Grandmother Witch, hoping to steal her heart.

Honor your mother; pass down her name, and seek our treasure. When you find it, you will find that you no longer need it. And if you wish to find it, look to the prayer of the faithful, beyond the Crux and beyond the Hallowed name.”

He sighed. He hated Riddles.
\simpleline
\DatePlace{Hogwarts\\
1202 C.E.}

Helga sat in her office, rubbing her temples. She was so lonely, so, so lonely. Rowena had passed away shortly after the death of her daughter. Salazar had fled Hogwarts shortly afterwards, presumed dead as well. It was just her and Godric.

She had burned through so many minds, names, and faces through her countless centuries of life. So much had been taken from her. Her life’s ambition had been stolen, twisted. She slid a sword through the heart of the one man who could possibly understand her journey through life, and she turned herself over to the cause of hatred, almost throwing away her own life just to see him burn. And the one man who could possibly represent hope, a new life, a new light for her, was broken beyond repair.

The wind rattled the windows of her chambers, a low whisper which gained in intensity. “You can take his place, you know.”

She looked up. The voice was unmistakable. It was him. And yet it came from nowhere. “Enough games. Show yourself.”

The air cooled, and mist began to form in the slow currents of air that wafted through the room. As the mist grew thick, it began to take shape, swirling in fractal patterns that built up to something far beyond the sum of their parts. Like a butterfly emerging from a cocoon, Merlin unfolded from the empty air into his full glory. His green eyes glimmered with the reflection of the fire, still containing a hint of youthful twinkle, despite carrying an eternity of experience and heartbreak. The lines in his face did not make him seem frail, only more powerful, more wise, more experienced.

“You cannot Apparate within Hogwarts,” she spoke at last.

“Yes, well, being me has its privileges.”

“What do you want?”

“To keep a promise that I made. It was never my intent to hurt you so. The windmill was his plan, his doing.”

“You let it happen, you knew it would happen. So I blame you. I know that this was your plan. It was never about Hogwarts. You wanted to sweep us off of your game board.”

He shook his head sadly. “Not quite.”

“I just don’t care anymore. You’ve won. You’ve broken us all. So again, I ask. Why are you here?”

“To simply make you an offer.”

‘To what? Rule the world by your side? How cliché. No, I will not be your proxy , only to be disposed of like you did Constantine and Meldh. I decline.”

“I told Meldh that I would fulfill your heart’s desire, and I am here to offer that.” He held out his hand. “Rise,” he commanded her.

She moved from behind her desk. With his right hand, Merlin took the silver cross from around her neck and wrapped his fingers around it. With his left hand, he gently held her hand. He closed his eyes, and they were gone.

\simpleline
\DatePlace{Elsewhere\\
Elsewhen}
The stars were so beautiful, with nothing but Nothing between them. Some were so distant as to be mere pinpricks, others formed groups and shapes too many to count. She had no corporeal form, but her being was there in its entirety, unbound by Time or Space. She felt him, her Meldh, and so she moved, flitting across the multiverse.

He was staring at a small proto-star, shaping it, forming it. “It is called a Bok Globule, my love. Cold, small, ephemeral. But it can be our world, just you and me. We can shape it in our image.”

“Where are we? When are we?”

‘We are beyond. After the war. After our victory. We have won. This world, all worlds, are free for us to command, to command us. You and I, together in eternity. You have ancestors, you know. Not just Garrick, but the countless more Heirs of Gryffindor and Hufflepuff. Even Godric is here, somewhere, building his own world, a world of Phoenix fire and righteousness.”

“But how? How did we win?”

“The Crux.”

“But who?”

“They are simply the Crux.”

She pondered this for a moment. “But this isn’t real.”

“It isn’t. But, it is. Don’t you see? That is Magic.”

“Yes, but…” Suddenly, she understood. “Magic– “

“–isn’t magic.”

This wasn’t real. It was real to her, but it wasn’t really Real. Anything was possible with Magic. But possibility was not Reality. Not yet, at least.

She directed her attention at his form. “You cannot stay.”

“I know.”

“The battle still must be fought, in reality. It still must be won. And I am no warrior.”

“I know.”

“And you are.”

A long period of silence followed. Their star, their world, it was brilliant with cold fury. It was so small in comparison to everything else in that great beyond, but that was fitting. Their love was not some all-consuming inferno that dominated the universe. It was theirs, and this would be enough.

“You cannot stay. Go, Heraclius. I will wait for you here.”

She could sense the bonds that held him in this place beyond time, that chainehim to this star, this beautiful, lost world of their own. As she became one with the structure, Meldh could sense his connection to the world of Reality return. The infinite, unbound space of possibility was now forged into a single point of silver, which unfolded into a line, and then a cross. Finally, he felt a warm, rough, loving hand encircling him.

He whispered his goodbyes, and opened his eyes.
\simpleline
Merlin was watching him, holding the small silver cross in his right hand.

“Welcome back, friend.”

Meldh looked around. He was standing in Hogwarts, in her office. “How long?” he asked.

“Only about a century. You have done well. The world has turned on them, as we knew it would. Godric is the only one left, and he is not long for this world. When he passes, the school will be ours.”

“Are there more like her?” He stared at the ceiling, his mind on the stars in the night sky above.

“Yes, countless more.”

“‘The fires of the soul burn as brightly as the stars.'” Meldh quoted.

“Yes, and there will come a day when the Crux will tear apart the very stars in Heaven.” Meldh winced at Merlin’s words, but he continued. “You always knew the stakes, the price if we lost. But,” Merlin took the cross in his hand and pressed it against Meldh’s chest. “Keep her there, and one day you will find your treasure.”

Merlin turned to leave. Meldh did not follow, not yet. “Where do we go from here?”

“It is time to become The Three once more.”

\simpleline

\DatePlace{St. Brutus’ Hospital for Incurably Infirm Wizards\\
1202 C.E.}
The colors of Gryffindor house used to be black and white, trying to represent Godric’s view of the world. He knew now that this was the easy way out. It was too simple, cowardly even, to try to paint the world with such broad strokes. It took no bravery to mindlessly condemn one’s foes, throwing away one’s own life as a weapon against another. He realized that at last, and although he saved the woman he loved from making that same mistake, it was too late for him.

He had turned away his Phoenix’s call. He had failed himself, but he would not, could not fail his House. He could still rescue them. From that day forth, he clad himself and his House in red and gold, to remind them all of the price of the Phoenix. To remind them that they must discard their childish notions of simple, black-and-white morality. His house would go on to honor his name, and indeed some of the bravest and most celebrated Gryffindors were ones who had to make some of the most terrible choices.

Godric was on his deathbed, scribbling notes, trying to pass on some final bit of wisdom in his admittedly short autobiography.

It takes a great deal of courage to stand up to one’s enemies. But it takes a great deal more to stand up to one’s friends.

Hm. No, it wasn’t quite right. It didn’t fit. He rest his hand on the hilt of his sword, imbued with the powers of all the various creatures it had slain. He looked out into the night sky, to the stars above. He wondered which one of those stars was his nameless Phoenix, and if he would ever see her again. Somewhere in the distance, a single point of light, billions of years away, twinkled impossibly.

He smiled, and began to write.

No rescuer hath the rescuer.
No Lord hath the champion,
no mother and no father,
only nothingness above.

He laid down his quill, and laid down his sword, and closed his eyes for the last time, with an uncharacteristic smile on his aged face.