\chapter{The Goat and the Ram}

\DatePlace{Earlier}

\lettrine{M}{aksimillian} Koschey watched the seconds tick by, as the world died around him.\\Even the end was unbearably anticlimactic.
\SmallVSpace
\emph{I wonder how long I can wait before I truly die? That might be interesting. Then again{\el} Maybe something interesting is on the other side. Might as well give it a shot. After all, I can die whenever.}
\SmallVSpace
He requisitioned the necessary mass\mbox{--}energy, created a suitable vessel for himself, and bound it to one of the countless power crystals he had surreptitiously (and quite illegally) stowed away for himself. After all, he figured this day would come sooner or later.
\SmallVSpace
With but a flicker of his Will, the entirety of his being transmuted, and traversed all barriers.
\SomeVSpace
And with that, Maksimillian Koschey awoke somewhere new.
\simpleline
\DatePlace{Seconds later}

Adnan Nejem was roused, unceremoniously, from his game.
\SmallVSpace
\emph{Shit. What a fucking waste of an hour. Almost there, too.}
\SmallVSpace
These kinds of power spikes were rare, but not unheard of. He started to reboot. While he waited, he glanced briefly over at his work terminal and\mbox{---}
\SmallVSpace
\emph{Shit shit shit shit shit shit shit shit shit shit shit shit shit}
\SmallVSpace
He ripped the inputs out of his arms and temples, and with a swift kick, propelled himself in his rolling chair across the polished metal floor of his flat. It had to be a false positive.\\What he was seeing was just{\el} “Impossible” doesn’t even really begin to cover it.
\SmallVSpace
A few quick keystrokes. Some regression analysis.
\SmallVSpace
\emph{Shit.}
\SmallVSpace
Adnan’s code was spaghetti. It always was. But it worked. It worked in ways that other people couldn’t fathom, which is what made Adnan so singularly valuable. But it all so made him a liability. He always told himself that he would eventually rewrite everything, make it extendable, add some documentation, all that stuff that he would get around to some day if only he weren’t too busy doing more important shit.
\SmallVSpace
Well, didn’t he feel stupid, now?
\SmallVSpace
The system had begun to fail almost a full two minutes earlier. More specifically, his module had begun to fail almost a full two minutes earlier. The code was fine. It had to be. But, it was failing. And no one across the whole of Humanity was capable of troubleshooting it except for him. And he had waited an entire two minutes. It was over. Even if he had been there when it started, it still may have been over.
\SmallVSpace
It was like a waterfall. Layers of failure, rippling, crashing against the rocks. The weight of it was heavy, too heavy to bear. His fault. It had to be. The system was inviolate. He was the weak link. Everyone dead, all his fault.
\SmallVSpace
Adnan was already preparing. He looked at the various prototypes and experiments in his flat. No. It wouldn’t do. He needed to be anonymous; that ruled out the majority of his options. No, he wouldn’t be coming back from backup. It would be him, in the flesh.
\SomeVSpace
\emph{Hmmm{\el} Options, options, options{\el}}
\SomeVSpace
His eyes stopped on Dinsdale. He had been experimenting with this particular variety of Chol for centuries. Fire was the constituent element, but that was just another kludge. It was so much easier to just complete the metaphor than to do the hard work of explicitly defining the connections: the Chol judged intent, and the fire purged and purified. Of course, Adnan wasn’t a monster: the fire didn’t do any lasting harm, it was just a means of transport.
\SmallVSpace
He looked at the bird-like creature, perched on the thin glass shelf. As he stared into his creation’s eyes, he formed the question in his mind. Dinsdale looked back at him, and cocked its head, quizzically.
\SmallVSpace
“Caw?”
\SmallVSpace
Judgment was issued. And the conflagration began. A fiery menagerie stampeded into the room, purging and purifying, whipping around with angry lashes, surrounding Adnan and Dinsdale. He was being judged, and he had failed. The fire burned, and burned, and burned; it burned until there was nothing left of Adnan. The sound and the fury had ceased as quickly as it began.
\SomeVSpace
The immolation was complete. And with that, all that was of Adnan Nejem had been burnt away.
\SmallVSpace
Dinsdale idly pecked at his feathers, feeling a distant sense of loss. But for what? It couldn’t quite recall. It seemed so far, so far away. After all, time is the shortest distance between two places.
\simpleline
\DatePlace{Seconds later}

Natalie Kyros was always amazed at the propensity for the religious to fold modern advances into their belief system rather than update their belief system to account for modern advances. But, people had always been that way, and trying to fight it was a fruitless endeavor. Many of her friends and colleagues had tried. For centuries. And they were perpetually frustrated.
\SmallVSpace
Natalie, on the other hand, had realized early on that some flaws in human cognition weren’t worth fixing; it was better and easier to simply use them to your advantage. That was how the central node of her network had come to take its current form: a three-meter tall cross, crafted of a metal that outwardly appeared to be iron.
\SmallVSpace
\SmallVSpace
The geometry was actually quite convenient for its intended purpose. It could have been a tesseract, but unfolding the cube before extending it into four\mbox{--}dimensional space had quite the same effect, but with a few advantages. The infrastructure was actually more modular and extensible, but that came with a few key drawbacks as well. Namely, it was also more corruptible.
\SmallVSpace
She remembered her conversations with her colleague, Gus. They always argued with each other, but in a respectful way. There was an implicit understanding between them that having a constant Devil’s Advocate was exceedingly useful, despite being exceedingly frustrating. Their coworkers, of course, did not have this understanding, and simply wondered when they were going to get it over with and finally start dating.
\SmallVSpace
\emph{Technically speaking, \textbf{every} structure is a four-dimensional structure}, he would always remind her. Which, sure, it’s true, from a certain point of view. But it’s an asinine point of view to take, because by that logic, every structure is an infinite\mbox{--}dimensional structure. \emph{Yes, and that’s quite the point, isn’t it?}
\SmallVSpace
He had an obnoxious habit of being smug and cryptic like that. She never really had patience for the riddles though. The point was that the True Cross was deliberately extended, by conscious design. It was that conscious intent, in her mind, that truly gave weight to a structure.
\SmallVSpace
And it was with conscious intent that she incorporated several elements of the standard mythologies into her design, just to make it more palatable for the masses. If she only had more time, she could have come up with a suitable spin for the events unfolding around her. \emph{Apocalypse. Revelation. Rapture.}
\SmallVSpace
But she had no time. Her followers would not be saved. Gus wouldn’t be saved. It was hard to tell which was more sad. No time to think though. Action. She spoke the phrase:
\SmallVSpace
‎‎\textbf{``}\begin{cjhebrew}'br' kdbr'\end{cjhebrew}\textbf{''}
\SmallVSpace
As the Cross began to unfold itself in that unseen dimension, its physical form in this Time and Space diminished. The Cross was reducing itself to a point, a single, one\mbox{--}dimensional vertex: massless and volumeless. Natalie’s corporeal form was already gone, her Life and subsequent Death Burst both channeling through and powering the machination.
\SomeVSpace
And with that, Natalie Kyros and her True Cross were gone: nothing but myth and legend.
\simpleline
\DatePlace{Seconds later}
Christopher Chang stared at his reflection in his mirror. The mirror was the answer after the answer. Reaching eternity was one thing, but once you answered the Last Question, there was still one more: what next?
\SmallVSpace
He hadn’t completed it. Of course he hadn’t. How could he? The risk was so untenable that it did not even need to be articulated. The project itself was, in the parlance of the 21st century, “open source”. Anyone could build upon it, improve it, perfect it. Which of course, meant, that few did. Some things never changed. The producers of the world were far outnumbered by the consumers, in every facet of life.
\SmallVSpace
Which is why it had been so important to cultivate those less productive than oneself. Teach them to become producers. Of course, it didn’t matter now. Well, it wasn’t supposed to matter. But something was wrong. Something hadn’t worked. He could feel it, like some fundamental flaw in the generating function of the universe.
\SmallVSpace
There was nothing that could be done, of course. This was John’s problem to fix. And he didn’t mean that in the defeatist sense: it was just a matter of pure logistics. Even if Christopher had been capable of affecting any sort of real change, he was full minutes away, and that was assuming he used the fastest possible transportation protocols.
\SmallVSpace
So, he stood in front of his Mirror, and allowed it to reflect his deepest, most profound volition. The image of Christopher and the classroom behind him vanished, and in its place, the Mirror displayed \emph{Question.}
\SmallVSpace
He provided the answer. And with that, Christopher Chang was gone.
\SomeVSpace
The golden oval stood, inviolate, in this world, in all worlds.
\simpleline
\DatePlace{Seconds later}

Constantine Atreides rushed manically around the lab. The anchoring rods were uniquely equipped to handle, channel, and redirect the absurd amount of power coursing through the system from the network of L.E. lines. Calling them “Low Energy” lines really was a bit of a misnomer. Certainly with the correct state of mind and the proper knowledge, one could access that energy without the aid of tools. But the whole point of Constantine’s rods was to harness the energy from something wild, dangerous and mind-bendingly powerful into something tame, usable, and above all, safe.
\SmallVSpace
For a brief moment, Constantine thought that he might save the world. If he could force everything to channel through the cluster of rods, it could be dispersed safely. He’d have to direct it. He’d have to use it to create something. He’d make{\el}
\SmallVSpace
\emph{Damn it.}
\SmallVSpace
He never really was the creative type. He spend whole moments pondering, then realized his folly, and simply let his mind drift towards a random series of fractal patterns, maybe that would work?
\SomeVSpace
It did not.
\SomeVSpace
Of course it did not. The rods required intent of some kind.
\SomeVSpace
Even if his mind was capable of containing a structure grand enough, complex enough, even if he had taken the time beforehand to plan all of his movements and thoughts to the microsecond, it simply would not have been enough. There was too much. But Constantine did not know this. The system was flitting through failure modes faster that he could keep track of them. He continued to look for an answer. No time, no time.
\SomeVSpace
Nat.
\SomeVSpace
Not enough time. He couldn’t save her. He couldn’t save anyone. What now? Save himself. Save himself. The one grand, complex structure his mind was capable of containing was, of course, itself. Clever self\mbox{--}referencing hacks wouldn’t cut it in this use case. Were he performing a simple transform, he would be fine; the mind would provide the Form ad\mbox{--}hoc as the Substance was being assembled.
\SmallVSpace
But this was a clean write, which meant it had to be done in one fell swoop. That left no room for anything else. Unless{\el} Yes, that actually would work. Before the operation, he sacrificed a small portion of who he was, of his being, kept in reserve to hold on to that one idea, that one hope, that one dream:
\SmallVSpace
\textbf{\emph{Her.}}
\SomeVSpace
And with that, Constantine and his hope were gone.
\simpleline
\DatePlace{Seconds later}

Dexter Charles giggled. As the lead Seer, he was privy to secrets, knowledge, information. Oh yes, he was privy. Things that no one else knew. Things that no one else \emph{could} know. Yes, of course he knew this day would come. All paths led to it.
\SmallVSpace
All paths led to him, through him. He was the gate. Of course he was. He knew the gate, he was its key and guardian. Past, present, and future were one. His past, the world’s past, a fixed line. The present, a hot white point that encompassed this world and all worlds. And the future, a diffuse web of background noise for as far as the mind could fathom.
\SmallVSpace
But of course, he knew what lay beyond that. He knew. Of course he knew. How could he not? Past, present and future were one. Even as the world died around him, he giggled as he watched the future loop back upon itself, over and over and over and over and over spiraling out and up and down and out and up and down and out of control until all that was left were two paths, and it all went through him, which was so silly, so sad, but so, so silly that he couldn’t help but giggle.
\SmallVSpace
Needless to say, one of the occupational hazards of being a Seer is that it’s not exactly conducive to preserving one’s mental health. Dexter’s mind had been shredded by the enormity of what he was trying to encompass: he had walked down both paths, just to see how it all would end. But, what he saw could not be comprehended by a finite mind.
\SomeVSpace
One path could not permit the finite.
\SmallVSpace
The other path could not permit the mind.
\SomeVSpace
No matter. It didn’t matter, couldn’t matter. For all he knew, all paths led to him. Why wouldn’t they? He was the gate. So, he simply opened the gate, and exited the world.
\SomeVSpace
And with that, Dexter Charles entered the world.
\simpleline
\DatePlace{Seconds later}

Janus Tucker knew that this was the end. But he also knew that there was a loophole. There always were loopholes.\\The scales as a metaphor for justice had persisted from ancient times even to today. But it was done now, it served no further purpose. What use was Justice in a dead world? He reached into the metaphor, pondered for a moment, and removed the two cups from the scale.
\SmallVSpace
As long as there were people, things, structures that obeyed the laws, in whatever form those laws would take, the metaphor would hold. Justice. Balance. It was written into the very fabric of Creation, it was the canvas on which the tale of the world was spun.
\SmallVSpace
The question now, was what to do{\el} Ah, yes. He simply inserted himself into that fabric, into the tale. The will of the world was being Bound, regardless, regardless of his own actions. So why not Bind himself to it? Yes, it was a moment of darkness for the world. But it was said that the darkest hour of midnight came just before the dawn. And he would be there for that dawn, to see what we be born.
\SmallVSpace
He grasped the two cups, and smiled for a brief moment as he struck a suitably dramatic pose. If he was to be a God, he may as well play the part.
\SomeVSpace
And with that, the tale of Janus Tucker was written.
\simpleline
\DatePlace{Seconds later}

Kayla Rahl examined the three boxes. There were only a few moments left, but she had designed the Box for this very purpose. A surprisingly effective failsafe.\\It was an exercise in pushing things to their limits. An arbitrarily large extendable space. An arbitrarily long connection. In this case, though, about 26,000 light years sufficed.
\SmallVSpace
She knew when she created it that she could never open the Box. The very notion of her opening the Box was a paradox unto itself. And yet, here she was. That small fraction of her mind that did not exist, the part that would permit itself to open the Box, suddenly was there. Just popped into existence, five minutes prior.
\SmallVSpace
She immediately felt it. And she immediately went to check on the Box. And that’s when she saw there were three. It was, in reality, a single Box. The Box in the present. The Box in the past. The Box in the future. Each was its own distinct physical entity. She had heard once that the cells in our bodies were completely replaced every seven years. It was nonsense, of course, that’s not how biology works. But even still, she was always fascinated by Theseus’ Ship. She suspected that is why the Box presented itself as three rather than one.

But, most importantly, she was able to open the Box. For eons, the very nature of the world prevented the Box from ever being opened. But it had changed, everything had changed. This meant only one thing; the world had already passed its own event horizon. The world was already going Beyond.
\\
Which meant there was no harm in going Beyond along with it.
\SmallVSpace
So she willed the Box open. The three aspects obliged, unfolding themselves. Kayla gazed into the gaping maw of the Beyond, and entered.
\SmallVSpace
Once she was truly locked Beyond, the boxes snapped shut.
\SomeVSpace
And with that, Kayla Rahl and the world were gone.
\simpleline

And with that, the new world was born.
\SomeVSpace
The world unfolded, like a fully grown adult emerging from the womb. The new Gods of the new world emerged, as well, shaking off the afterbirth, their eyes sensitive to the intense, penetrating waves of this new sun.
\SmallVSpace
Each knew there were others, for they each knew that they were not the oldest, or the cleverest, or the most knowledgeable. And if they were able to do it, someone older, someone cleverer, someone more knowledgeable would have been able to do it too.
\SmallVSpace
But at the end of it all, someone had to be the best, the oldest, the cleverest, the most knowledgeable, and that person, whoever he or she was, would be a God amongst Gods.