\chapter{Crab Canon}

The Mirror stood, inviolate and whole. The Professor watched Dumbledore patiently through the Mirror of Volition. It stirred echoes within his mind of an ancient time, in an ancient place, when he was younger so, so much younger.

“Why, look at that,” he spoke, mimicking history. “I don’t seem to have a reflection any more.”

From inside the mirror, a voice cried out. “No,” said Albus Dumbledore. “No, no, NO! ” Into the hand of Albus Dumbledore flew from his sleeve his long, dark-grey wand, and in his other hand, as though from nowhere, appeared a short rod of dark stone. Albus Dumbledore threw these both violently aside.

The Professor stood ready, catching the Line of Merlin as it passed over the threshold of the Mirror. In the meantime, the scene shifted to a conflagration of fire and light. For a timeless moment, the boundaries of the End of Time felt malleable. As the star was torn apart, a voice from behind the mirror spoke up.

“Well, I guess that’s my cue. I’ve got a lot of work to do, huh?”  Harry stood up and sighed.

“I’ve never been one for protracted goodbyes. Besides, it will be much, much longer for you than it will be for me.”

“Yes… And I don’t really know how to describe it. You’d think that we should value the lives of our alternate selves as equally as we value our own. But, that’s not quite right, is it? For every decision I make, there’s a path untaken. If there’s a version of me who takes that path, well… By definition, that’s not me.”

“And yet, you did make that decision. The fact that we’re here is proof of that.”

“No, not me. Myself in the future. That version of myself who makes that decision, he’ll be locked away, forever.”

“And Ironically, in doing so, he’ll have achieved immortality, true immortality. He’ll have cheated his way to the end of the quest that you and I are only beginning.”

“Technique,” Harry corrected with a wry smile. “But yes, in a way, yes. Not just for him, but for that whole world.”

“A world we’re about to destroy. Which, I think I better get along with now. I’ll see you in a few moments.”

“Well… I’ll see you in another 26,000 years. Or something like that.”

And with that, the Professor stepped through the Mirror, into Atlantis.

\DatePlace{London\\
February 1, 27999}

The system was procedurally generating humans as fast as it could churn them out. It started with the thousand or so genetic patterns it had recovered from the first aborted payload attempt. The rest, it built from patterns. Ten million and change.

Questions, questions, questions. All the answers would be there, eventually: Who was the old man? How did he get a copy of The Line? Is it even a copy? How will I recover the payload? How much of the system would survive? How useful would it be? How will I destroy it? What would this new world look like?

He didn’t have time. He’d have to do that part later. He’d have time later, but not now. It was time to run. He didn’t know what the old man was capable of, and none of this was rehearsed. He committed to the decision, and it was done. It was out of his hands now, so he had time to think, wonder, and speculate.

No. No time.

Flight. It was done. There would be no climactic fight to save the world or its people.  It didn’t matter what the old man’s motivations were, how he got there, anything.  Any time spent thinking about it was time wasted. There was no option left but to run, and to rebuild. He’d have to destroy the entire system, every last remnant though, to fully rebuild. He began to–

No, No, No, no, NO.

The old man was holding The Line.

This was his doing. There was no question. In pure reflex, he activated his Battle forms. He had even practiced this, fighting against countless unseen enemies. But, what good would it do? What to do? Fight or flight? What would he be fighting? What was the man doing? Those hand gestures were ancient. A past architect? A back door? No, the system was sacrosanct. Besides, the man had a tool. It was–

He was old. Old. No one was old anymore.

And that’s when he saw him. The man who was out of place, out of time.

He’d saved the people. He didn’t save the world. The world was done for, but a world could be recreated easily. No. Not easily, of course. Nothing would be easy at this point. The system had failed at three separate junctures. This was not chance. Something, someone, was responsible.

The payload was already constructed. It existed conceptually, in abstract. Now he needed to realize it. The Line was the most secure object in the known universe, and it had more than enough capacity within its buffer. He did more calculations. It would cut into its capabilities significantly. Maybe six hours, tops? It didn’t matter.

Yes, there was noise. There was too much noise. Every signal was being garbled. Warped beyond recognition. There was interference coming from… Somewhere? Only about 1,000 identities were piped through, and of those, the only thing left was raw DNA.  Change of plans.

John made the snap decision. He couldn’t save the world by himself, someone knew that, and someone had stopped him, and he could either keep pushing,  or he could recant, relent, retreat. With pleading eyes, he looked up at the stranger, conveying a silent cry: Help.

The stranger smiled a wicked grin. “Mr. Potter. Have you finally learned to lose?”

“Mr. Potter?” John asked, slowly. The name was familiar, intimately familiar, and yet…

“Yes. Mr. Potter. I said once, a very long time ago, that there are gates you do not open, there are seals you do not breach. I can tell you with absolute certitude that if you make the wrong choice, you will be responsible for the greatest tragedy that will ever be perpetuated against mankind. I am living proof of that fact.” The Professor held up his own copy of the Line.

John nodded. He did not waste time with questions that he knew would be answered soon enough.

“Take the Line.”

John Merlin did as he was instructed. He silently screamed the moment his hand closed around the second Line, as 26,000 years worth of memories returned in a torrent. The Professor. Hermione. Draco. Neville. Fred. George. Meldh. Perenelle. The Old Ones. Pip. Cedric. Percy. All of them. They were all here. They were all alive. He was here. He was alive.

Harry’s face was heavily seamed with care, and he looked up at the Professor with his green eyes.  Ancient, ancient green eyes.

There was only one thing left to do. He moved three fingers: thumb poised against forefinger and middle finger…

…and snapped.
