\chapter{The Tragedy of Light}
The curtain opens on a large, wizard-sized chessboard. The pieces are represented by actors, all of whom are sitting down except for THE ROOK who is at the back of the board. After a time, he moves across the board to the front of the stage. 

THE ROOK: 

O blindness of the great.
They go their way like gods.
Great over bent backs.
Sure of hired fists.
Trusting in the power
Which has lasted so long.

ALL:

BUT LONG IS NOT FOREVER.
O CHANGE FROM AGE TO AGE!
THOU HOPE OF THE PEOPLE.

Enter LIGHT AUGURREY. He is wearing a dark CLOAK, and carrying a STONE in his right hand, and a WAND in his left hand.

THE ROOK: 

Up, great sir, deign to walk upright.
From your place the eyes of many foes follow you.
And now, you don’t need an architect. A carpenter will do.
You won’t be moving into a new palace
But into a little hole in the ground.
Look around you once more, blind man!
Does all you have please you?
Between the Easter Mass and the Easter meal
You are walking to a place whence no one returns.

ALL: 

WHEN THE HOUSE OF A GREAT ONE COLLAPSES
MANY LITTLE ONES ARE SLAIN
THOSE WHO HAD NO SHARE IN THE GOOD FORTUNES OF THE MIGHTY
OFTEN HAVE A SHARE IN THEIR MISFORTUNES.

LIGHT: The plunging wagon drags the sweating oxen down with it…

ALL: INTO THE ABYSS.

“The Tragedy of Light”, by S. Leigh, as staged in the 1989 London production.
\simpleline
\DatePlace{June 13, 1334, C.E.\\
Hogwarts}

\emph{“Egeustimentis.”}
Nell looked around the hall of mirrors. Every surface was reflective, every move she made echoed perfectly through eternity.

Except for one.

Somewhere in the distance, there was one, one who didn’t mimic her moves, who had a life of her own. It traveled through the reflections, one mirror at a time until it reached her, and began to speak.

“Seriously? Did you seriously think that was going to work?”

From the moment the incantation was spoken, she had an inclination that something was wrong, the the plan went awry. Wherever she was now, she was not inside the mind of a millennia-old wizard/witch, and she was definitely not in control. In fact, she felt decidedly trapped.

She had lost.

She had lost. She knew the risk: her likelihood of success was miniscule. But when weighed against the value had she succeeded, it would have been the most tremendously immoral thing she could have done to simply let the opportunity slip. Even if it was a one in a thousandth, even one in a million chance, there were far more people than that in the world, and that was just at this point in time, not to mention the future. She couldn’t fathom a number high enough to make the risk not worth it.

She had a chance to end Death forever, she took it, and she failed.

Her reflection interrupted her thoughts, “Did you really think that the Cup of Dawn, a relic plundered from Atlantis itself, would operate on such a baroque interpretation of its instructions? Even f you were right, even if you had succeeded, what was your plan? I can see quite plainly that you have never used the Lethe Touch in any serious capacity before.

Nell opened her mouth to speak, but it was unnecessary. Her mind was laid bare, vivisected.

“That’s an admirable sentiment. But so flawed, so naive. Still. I can see why he wants you.”

“Who?” Although she had lost, the game was clearly not over. Her only choice was to respond and react, and hopefully provide her opponent what she was looking for.

“You wanted to get the attention of God. Well, you succeeded. And in a way, you will have won our little game. You will have won on my terms, and your victory will serve my ends, but you will win nonetheless.”

It may as well have been a monologue. There was nothing Nell could contribute to this conversation. But even still, she had the sense that the right thing to do was to simply shut up and and serve as the audience to whatever was happening now, to this information dump.

“You are one of the chosen ones, one of the Cruxes of the world, the world upon whose choices fate hangs in the balance. They have been shepherding mankind since the beginning of time, using people like me as pawns, who in turn use people like you. I was sent here to do two things: to collect you, and to die. But I was given the freedom to do so on my own terms, as long as it coincided with his.

“He has his plan for the world, and for that plan to work, I need to be gone.”

Who is ‘He’? What is his plan? Why does he want me? So many questions. Too many questions. 

“Even if I had a year to sit down and explain things to you,  I doubt it would make sense. There’s just too many entangled timelines, too many plots, too much going on for any one person to really grasp it. Sometimes, I question whether even he truly grasps the enormity of what he is attempting.

“Nonetheless, he is the father of this world. He created it from Nothing because our world was dying, and I strongly suspect it was dying because of his actions. But in creating this world, he not only bound our world, but every world. 

“Yes, the Fall of Atlantis. Much like you, he thought that he could end Death forever. Much like your choice, the risk was great. I doubt you could fathom a number high enough to quantify the risk. He saw the chance, and he took it. You gambled with your own life, which some may say is noble. He, on the other hand, gambled with the life of humanity. He gambled with the multiverse. 

“None of that, of course, has any practical meaning to you in the here and now. You are a creature of this world. You’re bound to live by the rules of this world. Your thrashing, organic sack of flesh is bound by the laws of time and space. Your means of experiencing the world around you are inherently tied to a single point of continuity. These higher level concepts are largely irrelevant to you.

“You see these reflections? They are you. They are you, gone down different paths. None of them made any choices that you would not have made yourself. They are you, and yet, for all intents and purposes, from your perspective they are different people.”

The reflection snapped her fingers, and a cacophony ensued. Each reflection was now living its own life, making its own way through the world. Each reflection acted like Nell, said things Nell would say, doing things Nell would do. They were her, without a doubt. And yet, they were not. She was the only one.

“Do you see?”

She snapped her fingers again, and the action quickened. Decades passed in the span of a few seconds. Nell watched herself grow old and gray a thousand different ways, watched herself die a thousand different ways. She saw blackness, so much blackness, so much Void, and yet, off in the distance, like the twinkling pinpricks of light against the night sky, she saw life.

She exerted her Will, and that life was now reflected across from her. It didn’t look much different, even though centuries had obviously passed. She looked a little bit older… No, not older. More mature.

That reflection turned to her and spoke. “As you have seen, preventing Death is not a particularly difficult problem. There are enough of us ‘immortals’ to serve as living proof of that. Reversing Death is even possible to a limited extent, provided one has taken proper precautions beforehand. You are one of the lucky ones. You did not have to look too far to find the shadow of yourself who had successfully avoided the clutches of Death.

“Lights out.”

The reflection disappeared, and it was darkness. There could have been an entire universe in front of her, but she would have been blind to it. She knew, however, that there was light somewhere. She searched through the blackness, finding nothing. It was there; it was just hidden. So there was nothing else to do besides keep searching.

“How long would you be willing to keep searching in order to find that light? How long would you continue to look? For that matter, how would you even find it in the first place? How far does the Void extend? If you believe, as many do, that the Void is infinite, then you could spend an eternity searching, and having nothing to show for it. Incidentally, the ancients called this ‘Information-Theoretic Death’.

“Now, on the other hand…” The lights returned, and the reflection was holding one of the mirrors, grasping a corner delicately with each hand. Gently, she bent the mirror so that it curved, and bent it further and further until the two corners touched each other. She repeated the same process with the other pair of corners, then smoothed the surface into a sphere. “Imagine, instead of extending on forever, it looked more like this,” she continued as she released the sphere.

It gently floated towards Nell, who peered at it curiously, and waited for the reflection to continue.

“Now, I would like to see if you are worthy of the role you are about to accept. Tell me, what are the consequences?”

Nell was silent for some time, considering the question. “You could… It’s finite. So long as you were determined enough, as long as you spent enough time, you could find the light. Not just yours, but everyone’s. No one… no one would stay dead.”

The reflection smiled. “Good, good.”

Nell, however, was frowning. “But, that’s not all.”

Still smiling, the reflection urged, “Go on.”

She gestured to a point on the sphere, and a pinprick of light revealed itself. “That’s me.” She gestured to another point, which lit up as well. “That’s you.” She continued, “And that’s Helena and that’s Babette, and that’s mum, that’s dad.”

More names, more pinpricks. “And this… this is everyone.” The pinpricks were so numerous that they blurred together, covering the sphere in a dim glow. “That’s today.”

The sphere glowed brighter, fractionally. “That’s tomorrow.”

The sphere glowed significantly brighter. “That’s a century from now.”

She shielded her eyes as the sphere began to glow an intense, blinding white. Before long, the light was as overwhelming as the darkness was a few moments before. There could have been an entire universe in front of her, but she would have been blind to it.

“And that’s it. It’s finite, you said so yourself. It has an end, and after that end is Death. True, permanent Death.”

“Yes, indeed. This man who  you seek, he created a world where countless millions, countless millions of millions, would be created, and subjected to that true, permanent Death. Every day, hundreds of thousands of tragedies are born. Weak, baseline humans destined to die after less than a century, and once this tiny little sphere runs down, they will stay dead forever.

“The fate of all worlds are now bound to this one. Neither can live while the other survives. That is the crime he is trying to repent for, that is the wrong he is trying to right.”

Nell was nodding. “So he is trying to save the world, all worlds, from Death. Why would I say ‘No’ to that?”

“Twenty minutes ago, you were prepared to do so. Had you succeeded in pilfering the secrets you sought from my mind, you would have learned one of the paths to immortality, and with my power you would have embarked on a grand quest to save the world. You would find, however, that a shadowy villain lurked in the background, stymying you at every turn, preventing you from achieving your ends. That villain would whisper into the ears of fools, speaking of the necessity of death, of the circle of life, telling people that to oppose death is a craven, sick urge. You would have devoted your life to stopping this destroyer.

“But it’s more than that.  I do realize that you have the propensity to consider yourself the smartest person in the room, despite your protestations. I don’t just mean outwardly, I mean the comforting lies you tell yourself.

“When it came down to it, in your heart of hearts, you believed yourself more clever than an Ancient with thousands of times your age and experience.”Nell tried to do some quick mental math, but was interrupted. “52,000 years, give or take. Think about that.

“You believed that you were more clever than I. And you saw to what end that brought you. Now, tell me, what do you make of the fact that you, a girl of a mere sixteen years, could see the folly of his plan? I might add that I can say with certainty that he is more clever than I.”

Nell paced around restlessly while she spoke. “It wasn’t a miscalculation or a mistake. If it were possible to miscalculate, I wouldn’t take that kind of gamble. He wouldn’t take that kind of gamble. The risk would be too great. To gamble with your own life, as you said, is noble. But to risk the lives and future of all? No. He wouldn’t do that.”

She paused.

“No, wait.”

Silence.

“Yes, I would. He would. He knew there was a risk, and he probably would have taken as many precautions as necessary to minimize the risk, but… But you said it yourself. He’s more clever than you, and you’re more clever than I am. I am supremely overconfident in my own abilities, in proportion to my cleverness.

“From what I’ve seen, you too are supremely overconfident in your abilities, in proportion to your own cleverness. Which means…” she spoke more slowly now. “He thought… He thought he’d be clever enough. He thought that if disaster did strike, he’d be clever enough to solve the problem.”

The reflection nodded, grimly. “Indeed. And that is why he seeks the counsel of others. He has learned what it means to lose, and he does not wish to repeat that mistake. That is why he needs you.”

Nell returned the grim nod, “I understand. And I am still willing.”

“Good. Now the only thing left to discuss is how we shall manage your ascendance. There is one assumption you made that was accurate, and that is that the vast majority of your classmates are blithering fools, and as such, will accept whatever titillating, ridiculous story we throw their way.

Nell grinned at this. “Yes. One of my fallback plans was to convince Hogwarts that we had slept together.”

“Yes, I’m quite aware. In fact, I have made arrangements such that your diary will, by this point, already be in the hands of Headmaster Gagwilde. He will, no doubt, be making his own arrangements to have me removed from my post as Battle Magic professor. Finding that I have unceremoniously fled in the dead of night, will all but confirm the suspicion.”

“Fled?”

“That is what you will make it look like, after you have killed me,” the reflection spoke pleasantly and matter-of-factly, as if discussing the yield on this season’s batch of puffskeins. “He will find that I have fled, and that you are in my chambers in a… shall we say… compromising position.”

“But that won’t be enough, will it?”

“No, of course not.”

“People love a good conspiracy theory, so we’ll give them one. A lie wrapped in the truth: I did, in fact, kill you and steal the object of your power. When I fail to return to Hogwarts and instead resurface as a nigh-immortal Goddess, this story will satisfy those who think one level above everyone else.”

“And what of those who think one level above that?”

“They’ll either join us, or they’ll die.”

The reflection nodded, grimly. It was time to begin.
\simpleline
LIGHT laughs uncontrollably. He is caught, defeated.

LIGHT: Yes, I am Keira. But, Keira is bigger than me. She is what keeps order in the rotten, broken world. You speak of wars? What wars? Crime? Thugs flinch at the very idea of committing a crime for fear of Keira’s righteous retribution. I know that killing people is wrong, I’m not a monster. Do you think I wanted this? But there’s no other way to fix this world, other than to purge it. No one else wants to do it, no one else CAN do it. If you kill me, you might save the world as it stands, but you sacrifice the future. Kill me, and the world of Good dies with me.

NEAL: No. You are nothing more than a murderer, a murderer who possesses the Deathly Hallows, the most sophisticated weapon of Death our world can imagine. You are not Keira; you are simply a killer, a sad, pathetic murderer.

LIGHT laughs again. He is thinking.

LIGHT: Say, Neal. Here’s some food for thought. The Hallows that Isaac had recovered, how do you know those are the real ones? There’s only one way to find out, you know. You’ll have to kill me with them. Only then can you be sure if they’re real…

LIGHT makes a quick gesture with his hands, and spins around to face the AURORS.

LIGHT: OR FAKE!

ISAAC: He’s hidden a piece of the Wand!

The AURORS whip out their wands, but MONICA is the first to draw hers. She fires a curse at LIGHT’s hand, blasting him off his feet. He pulls himself up, clutching his ruined hand.

LIGHT: Monica, you idiot! You stupid bitch, what are you doing, what the hell do you think you’re doing?

MONICA: You! It was you! What was it all for? Your father… You led him to his death, and for what? What did he even die for?

LIGHT: He was a fool! They all were! They cared more about the system of justice than they cared about justice itself. Can’t you see that? People like him, people like them, they don’t care about the good that I’ve done, all they can see is that I haven’t followed the rules! Do you really want to leave the world to fools such as them?

MONICA: Now that he’s dead, you call him a fool?

LIGHT: It’s not too late. You understand, I know that you do. You’re a good person, you know that what I’ve done is a good. We can still build a new world, free from darkness. It’s not too late, Monica, just KILL THE OTHERS!

The command rings with unnatural force. MONICA stands silent, shaking, not moving otherwise. After a long moment, LIGHT realizes she will not help him, and his posture relaxes. The stage lights dim, imperceptibly. He makes another sudden movement.

ISAAC: HE’S USING WANDLESS MAGIC!

Indistinct shouting. They all begin to fire curses, with MONICA leading the charge. She viciously whips her wand back and forth, advancing on him.

MONICA: (wildly) I HAVE TO KILL HIM, HE HAS TO DIE!!

LIGHT collapses. In the commotion, MCNAMEE struggles with ISAAC and grabs his wand. ISAAC twists his arm, forcing the point of the wand into MCNAMEE’s stomach. ISAAC pins his arm in place. Slumping his shoulders in defeat, MCNAMEE raises his head, and shouts a word.

MCNAMEE: SECTUMSEMPRA!

Blood pours out in liters. ISAAC and MAURY turn to MCNAMEE and try to start healing him. While the Aurors are distracted, LIGHT stumbles up and awkwardly shambles offstage, clutching his wounds. The stage lights come up, bathing the entire scene in white. Everyone freezes, except for LIGHT, who stumbles up the stairs to the top of the stage balcony.

THE ROOK is standing, waiting for him.

THE ROOK: Well Light, it looks like you’ve finally lost. Remember how I told you in the beginning, one day I would claim you for my own? You see, that’s part of the agreement between an Angel of Death and the one who claims the Hallows.

THE ROOK walks down the stairs to ISAAC, who is still frozen, and removes the CLOAK, the WAND and the STONE.

THE ROOK: It was good while it lasted. We eased each other’s boredom for quite some time.

Holding the STONE in one hand, he traces a name in the air with the WAND. The name reads, “LIGHT AUGURREY”.

THE ROOK: Goodbye, Light.

“The Tragedy of Light”, by S. Leigh, as staged in the 1989 London production
\simpleline
\DatePlace{June 13, 1989, C.E.\\
London}
Draco had been waiting for this question, and he had been long considering his answer. Why did father take him to see this play? Light was a brilliant role model, a perfect example of a Slytherin who used the true power of his cunning. So he wanted Draco to be more like Light. But Light was always thinking one step ahead, anticipating the moves of even his friends and companions…

So Father would want him to think one step ahead.

What would Father say, or do, in response, and how should he respond to that? He had been narrowing his eyes in thought the entire walk from their box seat to the private, exclusive, and wildly expensive restaurant. Think. Think. What would Father do? What would he say? Father was so clever, always so clever.

If he were Father, he would ask to see an example to ensure that the lesson sunk in. It was perfect. Father would want to see an example of Draco thinking one step ahead, and so Draco would oblige and tell Father what he was expecting.

“You wanted to teach me to be as cunning as Light and Lawliet when I grow up. But more than that, you wanted to see the principles in action. So here I am, thinking one step ahead,” Draco spoke with a self-satisfied smile.

“You couldn’t be more wrong.”

Draco’s smile froze.

“Light and Lawliet are dead. Is that what you mean by clever?”

“I, uh…”

“Do not feel ashamed, Draco. It’s an important lesson. When trying to come up with the correct answer, you most likely found yourself asking, ‘What would Father say?’, is that correct?”

“Yes, Father.”

“But instead, you answered the question, ‘What would I do if I were Father?’, is that also correct?”

In response, Draco wrinkled his nose, trying to understand the distinction.

“Take your time, Draco.”

After a few moments, Draco spoke hesitantly, “Yes… And that was doomed to failure because I am not you. If I wanted to be one level above you, I would need to… I’m not sure how to say this. I would need to have all of you inside of me?”

“That is a reasonable enough way to phrase it. To put a finer point on it; you would need to be more clever than myself. Which you are not, nor would I expect you to be. Perhaps one day. What you would do if you were me is not the same as what I would do. Now, imagine if you were to write a play about me. How clever would this false Lucius Malfoy be?”

Draco took a few more moments to consider. “He would only be as clever as myself.”

At this, Lucius smiled. “Correct. And if Mr. Leigh was as clever as he imagined Light and Lawliet, if he had actually known what someone that intelligent would do, he would have found the Deathly Hallows for himself and ruled the world, instead of just writing plays about it.”

“But they aren’t actually real… are they?”

Lucius waved his hand. “They may be, they may not be, it is of no real importance. I have another question for you. What was Lawliet’s biggest mistake?”

“I… Well. I was going to say that he was not as clever as Light, and so he lost. But I understand what you are saying. They are, in fact, equally as clever, which is to say, they are only as clever as the playwright. So his error must have been a tactical one. But…” He paused as he tried to think.

“That’s not strictly true. A brilliant author may very well write a character who is deliberately flawed. In fact, without such flaws, in all likelihood there would be no story. Perfect people rarely have reason to quarrel. But, it is quite easy for an author to blame their own lack of cunning on their characters.”

Draco was going to respond, but he got the strange sense that Father was not just talking about a play.

“Lawliet’s mistake was that although he had cleverly concealed his face, there was no good reason for him to tell Light his name. In fact, there is little reason for him to have interacted directly with Light in the first place, especially if he truly suspected Light of being Keira. Now, Draco, can you tell me what Light’s biggest mistake was?”

He tried to follow the same pattern as Lawliet’s mistake. “He should have continued to operate in secrecy. He should have simply used the power of the Hallows to kill anyone who stood in his way?”

Lucius smiled. “Close, very close. But his goal was not simply to kill people. He wanted to purify the world of evil. But Light, to his credit, knew that he could not do that simply by killing one criminal at a time. In order to truly rid the world of evil, people would have to police themselves.”

Lucius gestured dismissively to a waiter, pointed to an item from the wine list, and the waiter bowed his head in acknowledgement. Lucius continued, and Draco’s eyes grew wider and wider. “A war requires the participation of both sides. Just because someone calls for war against you does not mean you are obligated to reply. In fact, it is most often advantageous not to, for typically people do not launch themselves into battle until they are relatively sure of their chances of victory. ”

The waiter returned, more quickly than he would have if it were any normal patron, carrying a bottle of Tokaji. He poured a small amount into a glass and offered it to Lucius, who instead inclined his head towards Draco.

“Me?”

Lucius nodded. Draco cautiously reached across the table, and took the glass. His hand was shaking slightly. He felt like his father was on the verge of revealing something very important, but he could not fathom what that might be. The topaz liquid reached his lips, and Draco was very determined not to make the face.

“It’s… sweet?” Draco offered. The server’s eyes flashed briefly with terror, and Draco quickly corrected. “But it is supposed to be, I think. I like it.”

Lucius was silent as his own glass was filled. The server poured Draco’s glass quite slowly, constantly looking back to the Lord Malfoy for an indication as to what was enough. After less than a finger’s worth, he inclined his head, and the server hurried away. Silently, Draco and Lucius clinked glasses.

Draco thought that Father had taken a much larger sip than usual.

“Light’s folly was, when the Aurors declared war upon him in the first Act, he rose to the challenge. And that was unnecessary, there was no benefit to doing so. By going so far as to murder some of the Aurors, he galvanized not only the Ministry, but much of the public, against him. Had he simply continued to kill evildoers, the Aurors would have turned against each other. Keira would have been hailed as a savior rather than an anti-hero.”

“I… I see. That’s brilliant, father.”

“Now, can you think of another example of this, but in real life? A brilliant, cunning individual in possession of great power who sought to reshape the world and purify it of evil? One who was eventually brought down by an over abundance of his own perceived cleverness combined with the inexplicable propensity to wage senseless war against the public rather than to court them?”

The edge in Lucius’ voice was pronounced, and it scared Draco. He knew the correct answer, there was no doubt in his mind. But if that were not the answer Lucius was looking for, it would be a terrible mistake to utter it out loud. Was this Father testing him, seeing if he learned the lesson? Was this the challenge? Even if it was not deliberate, Draco stood nothing to gain by saying what he truly thought, so instead he invented a plausible lie.

“Lord Grindelwald? He sought to bring the Muggles under our heel for the greater good, but in doing so he tore through Europe, making enemies as he went?”

Lucius paused, and then a wicked smile graced his lips. “I see you’ve learned the lesson well, Draco. But we both know that you’re wrong. I will spare you the deliberation of whether you should say it or not, and simply do it for you. Tom Riddle.”

Despite himself, Draco gasped at hearing the name, the crude, vulgar, Muggle-given name of the Dark Lord.

“He was indeed brilliant, and he was indeed cunning, and he was indeed powerful beyond measure. He could have given us the world we sought. A world where Magic no longer fades, a future where our wands will not break in our hands, where the line of Merlin never ends, the blood of Atlantis never fails. He could have saved us all.”

Lucius downed the rest of the wine, and continued. “But instead, he took it upon himself to wage war against the first foe he considered worthy. Him. Dumbledore. Before the Dark Lord began attacking Wizarding families, the public secretly admired the Death Eaters. Those who didn’t admire us were scared. They were scared, and more importantly, they were policing themselves, for fear of our righteous retribution.

“Dumbledore spoke out against us, and he put together his Order of the Phoenix, this is true. But their voices would have been drowned by the cheers for the Death Eaters if the Dark Lord had simply ignored them!” Draco noticed from the corner of his eye that Father’s knuckles were white around his cane. “The Order would have been the villains! They would have been the ones fighting to preserve a system that allows evil to flourish. They would have been the enemies of progress. The Ministry would have stopped them, and if the Ministry didn’t, then the public would have overthrown the Ministry.

“But that was not to be. Instead, many good people died. Many good people were corrupted. Many good people were turned away by our perceived brutality.”

Draco closed his eyes. The meaning was unmistakeable. Mother. Aunt Bella. Aunt Andromeda.

“Think about that, Draco, before you decide to take an enemy for yourself. And more importantly, do not play the game simply for the sake of playing the game. Light and Lawliet, they played the game because the playwright thought that playing the game is what clever people do. But the Dark Lord… He…”

“He was playing a different game entirely?” Draco offered.

Lucius nodded in satisfaction. His son was young, still so young, and yet so clever, so cunning. He wondered what would become of his son, with a note of regret, wishing only to live to see it.
\simpleline
\DatePlace{June 13, 1334, C.E.\\
Hogwarts}
“You BITCH!”

Her world was ice. Her world was crystal. Her world was fire, burning through every metaphor until nothing existed of her but the abyssal depths of her dark side.

“Crucio!”

She felt nothing.

“CRUCIO! CRUCIO! CRUCIO!”

Her breath came in ragged pulls and she poured all of her magic into the pain. Still, nothing.

“YOU FUCKING BITCH!”

She reached for the nearest heavy object, a candlestick on the nightstand. She was still naked. They both were. Normally when she was exerting herself, her hair would come loose, cover her face, obscure her vision. But today, it was slick with sweat and blood, and stuck to her back and chest.

She swung the candlestick, hard.

“This is for my mother!”

She swung again.

“This is for my father!”

CRACK.

“THIS is for Babette!”

The candlestick finally snapped. At this point, what she was swinging at was an unrecognizable, pulpy mess.

“YOU KNEW. This entire time, you KNEW! This entire time you could have done SOMETHING. ANYTHING!”

She choked out a sob. With no convenient weapon, and almost no magic left in her, she resorted to her fists.

“God damn you. GOD DAMN YOU.”

Impossibly, the breaths still came. She knew there was one last thing to be done, and she had held a small part of her magic in reserve. She hoped it was enough. With an angry cry of effort, she plunged her fist, augmented by a small flow of magic, into the chest of her victim. With a wet sucking sound, she pulled out what she sought.

A green, fist-sized chunk of crystal. The Heart of Koschei the Deathless.

She had a speech written in her mind, about the millions of deaths that Koschei was responsible for, and the blood on its hands and the good that it could have done and the choice of inaction and the path of evil and her own grand dreams and ambitions and how she would change and save the world. But she could not form coherent words, only vitriol.

“You… fucking.. BITCH.”

She held up the Heart. It was poetic in a way. She would use its own power to destroy both the Heart and its owner. It would, of course, be diminished. It would be a sacrifice. But it would be more than sufficient for what she hoped to accomplish.

She used the final mote of magic left in her to transfigure the Heart into something lesser. It was smaller, the size of an egg, and it was no longer the brilliant, iridescent green that reflected an infinite multitude of colors while still maintaining its own identity. Now it only reflected what was on her mind: dark, ruddy, sticky blood. She tapped into the power of the Heart.

Its form was Changed. As too, was the God beneath her. An instant before, it was a broken, but living, breathing person. An instant later, it was a corpse. It was over.

At that moment, on cue, she heard the clipped scream of Helena, who had seen the entire thing. Helena was no gossip. She would keep Nell’s ‘secret’ safe, from everyone throughout her life except for a handful of trusted confidantes. No one would have any reason to doubt her veracity or motives. And those confidantes would preserve the secret, except for a handful of trusted confidantes of their own… And thus the legend would spread.

Shortly thereafter, as expected, the Headmaster showed up to find Nell still mostly undressed, halfway wearing her favorite emerald-green dress. The scene was set: the window was open and most of Baba Yaga’s personal collection of lore, including the Goblet of Fire, was gone.

Also according to plan, the Headmaster performed a clumsy attempt at Legilimency, and saw exactly what he expected to see: confirmation of his theory. Nell was underaged, and therefore the victim, so he did not blame her. In fact, he would immediately begin making arrangements to provide her with as much support as possible during this difficult time.

That support would be for naught, however, as moments after he left her to her own devices, a thick white mist precipitated into the air near Nell, eventually coalescing into the form of a middle-aged man, a little out of shape, with a small paunch. Taller than average, but somewhat stooped.  A face heavily seamed with care, and green eyes.  Ancient, ancient green eyes, and disheveled black hair.

“Are you him?” Nell asked.

The man smiled, softly.  He had a kind face.

“Yes, Perenelle du Marais,” he said, in a voice that was mellow, and deeper than Nell expected. “I am Merlin.”






