\chapter{A Song For You}
\DatePlace{Hogwarts, 12 Months Later
June 13, 1334, C.E.}

It was the scandal of the century. It had happened plenty of times before. Hogwarts was a hotbed of pheromones and poor decision-making. The penalty, of course, was instant termination, and they had lost a handful of Herbology professors, Potion masters, and Care of Magical Creatures professors just in the six years that Helena had been there. But a Battle Magic professor? This was unprecedented. The victim, though, was still officially unnamed, as of right now. It was Hogwarts policy, and because it was Hogwarts, Helena figured it would be roughly two days before the entire school knew. Until then, she was content to simply wonder, just like everyone else. As Helena wandered past the portrait of Barnabas the Barmy, she narrowed down the list in her head.

Baba Yaga was a woman, which suggested that her paramour was a man. But, the boys of Hogwarts were notoriously puerile, and she was almost certain that some amount of bragging would have taken place if this were the case. Then again, she wondered if her own preferences were causing her to weigh too heavily the probability of a sapphic affair. But Nell had pointed out several times before that most ancient wizards were notoriously pansexual. They had discussed the subject before, and it made sense. Who knew how old Baba Yaga really was? Boredom had to take its toll at some–

CRACK.

What?

It sounded like someone was slapping a steak against a wall. Over and over. She was on the seventh floor, and it was coming from behind a door that she had never noticed had been there before.

“You… Fucking… BITCH!”

What… The…. Hell?

The door was slightly ajar. Her curiosity was too much. She peered inside and instantly regretted it. It was something beautiful, something she had longed for, and it was ugly, terrible, and horrifying.

Nell was naked.

Covered in blood.

Holding a stone?

Despite the rumors, their physical relationship never advanced beyond that single, drunken kiss. She wanted more, for certain, but she did not want it like this. She wanted it on Nell’s terms, with Nell’s consent, she wanted Nell to want it.

She felt like a pretender. A disgusting, cheap voyeur. Objectively, the sight was beautiful, titillating. The curves of Nell’s body were slick and glistening, the light from the fire playing delicately across the fine traceries of her taut muscles. Her backed was arched in such a way that emphasized the fullness of her breasts. Despite the clearly apparent rage, her movements were measured and precise, like a moving sculpture of reflective marble. The violence with which Nell was swinging her fists against the figure beneath her did not undermine her femininity.

No, what undermined the beauty was the undeniable horror: the blood, the bits of ruined brain and bone and flesh, the wanton disregard for life. Nell was a healer, not a murderer. There would have been no need for forgiveness if this were a simple sexual escapade: Nell did not belong to Helena, she was her own woman, free to do as she pleased with her body. But this was a betrayal of the soul.

Helena couldn’t help herself. Like a stupid character from one of those stupid plays, she let out a sob, and immediately clasped her hand over her mouth. Nell’s head whipped around and her eyes widened as they stared at each other.

Helena ran. And ran. And ran. She didn’t stop running until she reached her room, and saw the note tucked under her pillow.
\simpeline
\DatePlace{Hogwarts, 9 Months Earlier
September 3, 1333, C.E.}
Festivus pushed the bag of gold across the table. “Nell, my dear, you insult our honor.”

“We should be paying YOU for this wondrous opportunity,” Ollie exclaimed.

Nell took the sack of gold. She knew it was a token gesture. They knew it was a token gesture. She knew they knew it was a token gesture, and they knew she knew it was a token gesture. Had they accepted the gold, Nell would have felt no ill-will. Nor would Festivus and Ollie had Nell not offered to pay them. Nonetheless, the dance was appreciated by all parties, as it was the dance of trust and friendship.

Nell spoke. “I’m not an expert at plotting or pranks–”

“–Neither are we.” Festivus cut in.

“We are masters.” Ollie completed.

“Well. Okay then. I’m not master at plotting or pranks. But I do have enough clout to where I can make sure that there won’t be any consequences.”

“Not for us, at least.”

Nell nodded. “Well, there won’t be any lasting consequences for her, either. I’m just trying to… Ah… Prove a point.”

Ollie and Festivus glanced at each other. “I won’t even ask.”

“Good. As usual, I’ll pay for any supplies or expenses.”

“And as usual, we shall be honest beyond reproach.” Ollie held his hand to his heart.

“It’s so delightfully lurid. Who should the other victim be?” Festivus inquired, half to himself, and half to Nell. Ollie and Festivus had a quick sidebar conversation and suggested a few names between the others.

“I’m sure you’ll have a score of volunteers. I mean, you’ve seen her.”

“I know for sure that I wouldn’t mind!” Ollie grinned.

“Me neither. You know what they say about Dark Witches…” Festivus nodded as his imagination wandered. Nell rolled her eyes, sighed dramatically, and smiled inwardly.
\simpleline
\DatePlace{
Hogwarts, the Previous Day
September 2, 1333, C.E.}
She was unearthly beautiful. A perfect, symmetrical face with pale, icy eyes flecked through with veins of violet. Snow white skin, smooth, taut, and unmarred. A figure both voluptuous and athletic, hugged suggestively by the multilayered, flowing dress, leaving just enough to the imagination, but revealing enough to give the imagination a place to start from. She was entrancing, and it was almost enough to make Helena forget.

Baba Yaga stood at the front of the class, arms folded behind her back, waiting patiently for the final students to trickle in. Of course, the last two were Ollie and Festivus. The twins sauntered in with that casual, smirking look about them that telegraphed to the world that they simply did not care where they were supposed to be or when they were supposed to be there. That attractive, carefree confidence, charming by virtue of its sheer naïveté.

The moment they sat down, Baba Yaga began to speak without preamble. “Good morning, class. You are in your sixth year of Battle Magic, which means you have reviewed and presumably mastered tactics, strategy, wandwork, footwork, and martial arts. You have learned offensive spells, defensive spells, crowd control spells, anti-personnel spells, and utility spells. Out of all this, who can tell me what is the most important lesson of Battle Magic?”

An anonymous Ravenclaw boy raised his hand, “Never use a complicated way of dealing with an enemy when you can just Avada Kedavra them?”

Baba Yaga considered. “A valuable lesson, indeed. However, observe. AVADAKEDAVRA!”

The class screamed. The Ravenclaw boy ducked as the bolt blazed towards him. Students behind him dived out of the way, and the curse smashed into the wall behind them, leaving a black scorch mark and a shower of green sparks.

What the fuck what the fuck what the fuck??

“Please elaborate on the error I made, class.”

“Are you insane??” Nell shouted.

“Child, do you really think–”

“I don’t CARE if you THINK you have things under control! Things can go wrong! Things DO go wrong! What were you thinking??”

“Child, come to the front the class. Now.”

The class was silent. This wasn’t the first time that a Battle Magic professor had done something fabulously dangerous, with the potential to go horribly awry. But Avada Kedavra?

Nell did not move. Festivus whispered under his breath, “Nell…”

“Child. Now.”

Nell did not move.

Baba Yaga rolled her eyes. She sighed, annoyed, and with a single thought, Nell flew up out of her desk. In an instant, she was carried by some unknown force to the front of the room, and came to stop in mid-air, a few feet away from Baba Yaga, her arms and legs splayed like a grotesque Vitruvian Man. As soon as she stopped, Baba Yaga drew her wand. “AVADAKEDAVRA“.

A bolt of green light shot into Nell’s chest. The class screamed again. Three-fourths of the Gryffindors had drawn their wands. Festivus and Ollie had both fired defensive spells which were obviously neither fast enough or powerful enough to stop the curse. Several Hufflepuffs had ducked behind chairs. Slytherins watched, amused, and considered how to play the situation to their advantage. Only a few of the Ravenclaws had enough presence of mind to notice that Nell was still alive and breathing.

“The terms laid down by the Cup of Dawn, which you have all agreed to, prevent me quite forcibly from harming any of you. Even the Killing Curse has no effect. Even if my first Killing Curse had hit, no harm would have come to her.” As Baba Yaga was speaking, she idly gestured towards Nell who floated back to her desk. Once she was positioned over her chair, the spell’s effects ended and Nell collapsed unceremoniously to the floor.

Damnit, she told herself, Damnit, Nell. That was costly.

“But, the spell would not have hit. The most important lesson of Battle Magic is not to simply indiscriminately cast Avada Kedavra. Avada Kedavra is slow. Avada Kedavra is obvious. Avada Kedavra takes entire moments to cast. Everyone knows Avada Kedavra and its distinctive incantation and green light. Every knows to dodge, and only the slow, the infirm, or the stupid are unable to dodge. Off the top of my head, I can think of at least half a dozen curses that would easily cause instantaneous death, all of which could be cast in half the time, with half the wand motion, and move at twice the speed. So now, we shall have a brief side lesson. What then, is the purpose of Avada Kedavra?”

A random Gryffindor chimed in, “Because it can’t be blocked?”

Silence.

The class would quickly learn that silence meant your answer was so stupid as to not merit a response.

“It’s a tool. A means to an end,” Nell had resituated herself by this point. A bit humiliated, for sure, but she still held her head high.

“Correct, Ms. du Marais–”

“–you can just call me Nell, all my friends do.”

“But I am not your friend. I am your teacher. You are correct, It is a tool. Now, how did you come to this conclusion?”

“Avada Kedavra terminates the life of the victim. But it also has the unique effect of reliably creating a Death Burst, which suggests that this effect is intentional. Thus, given the sheer redundancy of a spell solely designed to kill people, this suggests that the creation of the Death Burst is its primary purpose.”

“Correct, more or less. Avada Kedavra, stemming from the Hebrew ‘אברא כדברא’, which roughly translates as ‘What I say shall be’. Which in turn is a derivation of the ancient Latin phrase of power, ‘Et quod dicitur erit quod’. It is a Transfiguration spell, of sorts. It transmutes the victim’s Life into a different Form, free of any earthly binding. Pure Life is powerful stuff and can be made to do powerful things, if harnessed correctly. However it is very unstable without a physical binding and typically lasts no longer than the span of a few moments before dissipating, lost to the Beyond.

“This is why only fools use Avada Kedavra in combat. It is akin to bringing a butcher knife to a sword fight. Crude, and effective in a pinch, but ultimately lacking. Yet, it was the first thing that came to mind, simply by virtue of the fact that it is called the ‘Killing Curse’. Now, class, knowing this, can you tell the most important lesson of Battle Magic?”

Silence.

“Know that with which you deal. I was able to subdue and manipulate one of the more powerful witches of this year, and I expended no more than a thought. I would ask if anyone knows the nature of the spell I used for this purpose, but I do not make a habit of questions of which I already know the answer. And that, children, is the point. You do not know what I am capable of. If any of you were to attempt any sort of attack on me, you would be eviscerated before you even had a chance to blink.

“I say this not to brag. I say this because all spells have their counter. In fact, there is ample evidence in Magical Theory to suggest that the more powerful and complex the spell, the more trivial the counter. The Touch of Truth, the most perfect means of mind control that Wizardkind has devised, is dismissed by a mere syllable. You can see now why those with great power rarely deign to share their secrets. The world would be a very different place if ‘Egeustimentis Ba’ were not common knowledge.

“If you do not know the weapons in your opponents’ arsenals, you cannot hope to win. If you do not know the proper counters to the weapons in your opponents’ arsenals, you cannot hope to win. I am not the greatest Dark Lady of a thousand generations because of my reflexes or my aim. No, it is because I know spells and rituals whose very names, let alone their counters, have been lost centuries before this castle was ever built.

“Now. Based on this, what is the most important question you should be asking me right now?”

Nell spoke, immediately. “Why are you teaching us?”

“Why indeed? If you know enough to ask the question, you should know enough to divine the answer. And if you know enough to divine the correct answer, you should know that you will not need me to confirm that it is correct. Now, let us begin our lesson in the practical application of specialized spells and their counters.”

\simpleline
\DatePlace{Hogwarts, Near Midnight
September 2, 1333, C.E.}

Nell knocked on the door, tentatively at first. “Enter.” Baba Yaga’s voice rang from the other side, and the door swung open of its own accord. The Cup of Dawn flickered ceaselessly on the table, casting undulating shadows across the room. Nell did not even have to touch the Goblet to know that it would be impossible for her to remove it, much less steal it.

“So late in the evening, Ms. du Marais? I assume students need a chaperone at this hour to be wandering the halls.”

“I can go a lot of places, Professor. Look. I’m pretty sure, no, I’m certain that I know the answer to your riddle. But I can’t stand unsolved puzzles. Can I just tell you the answer, and you can tell me if I’m right?”

Baba Yaga stared at her, amused.

Nell took a few steps closer. “Look, I know we got off on the wrong foot, but it’s not often someone gets a chance to pick the brain of a Dark Lady who’s a hundred thousand years old.”

An unspoken conversation, one filled with assumptions upon assumptions upon assumptions, had already taken place.

It was a clumsy attempt at fishing for information, at its face. But Nell was too clever for that, and Baba Yaga knew this, and as such, the question was not the payload, it was the medium. But the unspoken question was too easily answered, given sufficient thought, which meant that it too, was a medium for yet another question, which Baba Yaga would not lightly answer.

After a moment, the ageless Witch spoke, “Well then, what is your guess?”

“You’re bored.”

“That is a facile answer. You’ll need to elaborate further if you want to have any sort of conversation with me.”

“You’re playing solitaire. You’re obviously powerful enough to have and do anything you want. Clearly there’s a reason why you aren’t living some hedonistic dream in a cabin in the woods somewhere. Judging by the rumors, and for as old as you are, however old it may be, that you already have. But you abandoned that. And now you’re spending your time teaching impudent sixth years like myself.

“Frankly, I feel the same way. I own this castle. I can do more than just walk around the halls at night without a teacher. I could have you fired. In an instant. That’s not a threat, I have no intention of doing so. It’s simply the truth. And I don’t even have to try hard. I look at these ridiculous Slytherins, with their convoluted plots, vying for power, trying to jockey their way into a better position on the game board. Frankly, it’s just depressing. I own the game. I am the game board.

“I know what it’s like to amuse yourself with tittles and jots. I know what it’s like to challenge oneself with ridiculous constraints just to prove to yourself that you can do it. I have friends my own age, sure, but it’s not really accurate to say they’re ‘friends’. They’re my wards. I protect them. I protect everyone. That’s why power has always come naturally to me. I have the ability, yet not the desire, for power. And so power seeks me out. But I have no peers here.

“There’s a question that I should be asking you. But I know you won’t answer it, not now. Not until I’ve proven myself. But until then, if I could ask you any question, it would simply be this. Why haven’t you killed yourself? Because I can’t imagine dealing with this, for thousands upon thousands of years. I would ask you, what have you done to give your eternal life meaning?”

A long silence followed.

Please buy it please buy it please buy it please buy it please buy it

“You amuse me. But you’re lying.”

Ice water, running down her spine. Shit.

“And yet, you truly believe much of what you said. You genuinely think you could outmaneuver me, and it is not the idle, overconfident boast of a bully. I confess, this, I would very much like to see.”

The chill withdrew. In its place, well, Nell wasn’t sure what to think. Her mother had always taught her that the best way to bluff was to make sure that everything you say is true, from a certain point of view. She didn’t actually feel all superior and bored like that. She’d certainly considered the notion, but she had dismissed as summarily as she dismissed the idea of becoming a tyrannical despot. But even still, it wasn’t too hard to just continue that line of thinking, and apparently, it was convincing. To an extent.

“OK… So?”

Baba Yaga stood. “I propose a wager. One enforced by no magic, other than our own honor. You have me terminated from my position before the end of the year, and I will grant you one wish, anything that is within my considerable power to grant. Should you fail, I will take something from you, anything that I may ask, anything that is within your power to get.”

“And what is it that you would take?”

“I believe that I have all year to decide. And what wish would you have me grant?”

“I would have you answer my true question.”

At this, Baba Yaga stared into Nell’s eyes. The Cup of Dawn prevented any sort of Legilimency or similar violation into the sanctity of her mind, but Nell wore the question openly on her face, and the question was clear.

Who? Who roused you from your life of ceaseless boredom and pleasure-chasing? You, likely the most powerful being to ever step foot into Hogwarts, who are you afraid of? To whose will do you bend? That person, the one with the power to make God cower with fear, yet does nothing with that power. They are my true enemy, and I will destroy them.

Baba Yaga smiled. “Very well.” She stepped closer and extended her hand across the desk. She clasped Nell’s hand. They were both beautiful. Baba Yaga, unearthly so. A vision of manufactured perfection, almost cruel in her beauty. She was the result of eons of calculated creation, a marble statue. Nell, by contrast, was a majestic landscape. Organic, natural, breathtaking, and awe-inspiring. The random emergent byproduct of a thousand generations of patterns mixing, combining, persisting, mutating, evolving. Beautiful not by conscious design, but simply by virtue of what it is: a reminder, that even from the crudest conditions of disorder, beauty can and will emerge. On the most fundamental, statistical level, if patterns can emerge, they will. And if patterns can persist, they will. Life will always prevail over death because that is simply how things are, and Perenelle du Marais was the living embodiment of the noble spirit of Life.

They were two visions of perfection, touching flesh, staring into each other’s eyes, each trying to size up the other’s soul. Baba Yaga had gone by a thousand names. Koschei the Deathless. Ma’krt of the Rock. And in a time before Time, an even more ancient name: Max Koschey. He was an electrical engineer, of sorts. He specialized in matter, energy, and the manipulation and conversion thereof. He designed, created, and maintained the System’s power crystals. And although many of his colleagues had developed rudimentary sentient structures, that was hardly Max’s area of interest, much less his expertise. He had no interest in stewardship. Lesser beings were boring to him.

So it was that after the disaster, all that remained of Max Koschey was a single power crystal that had been Bound with his life force. He was forced to use a brain as his template for consciousness. Specifically, a human brain. The human brain has flaws. The human brain can be physically manipulated. The human brain can be swayed by something as simple as an influx of testosterone and oxytocin in response to a physical stimulus.

Unconsciously, Baba Yaga’s pulse quickened, ever so slightly. Her pupils dilated, imperceptibly. Nell was not consciously aware of this reaction. But she did know enough about unscrupulous old people to know that most of the time, there was always a certain… something in the back of their mind. So she let their handshake linger ever so slightly longer than most would consider appropriate.

“You’ve got a deal.”





