\chapter{Things Fall Apart, The Center Cannot Hold}

Dearest Louis,

The taste of victory is sweet. I would have never guessed in a century that at the end of it all, Severus Hortensius would be our greatest ally. This is a new and treacherous game board, for certain, but it is certainly preferable to waiting patiently for our forebears to pass so that we may take their seat on the Council.

Even in the few short days since the Edict, alliances are being formed within the ranks of the Hogwart’s Governors. My father chuckled at the very notion. In my younger days, he used to tell me that trying to keep my in light was like trying to cage a bolt of lightning. It has been many a long year since he told me that, but he said as much with regards to the Founders: ‘They are bolts of lightning that you wish to cage, son. Take care.’

The Founders truly care about their mission. They are devoted to the school, which means they will be easy to control. They are not experienced in the games of power and intrigue, and as long as we take care to keep the best interests of the school in mind at all times, they will be in our catspaw. Although Hogwarts is young, I do suspect in the years to come that our Board of Governors will wield a power even greater than that of the Wizard’s Council.

Of the matter regarding blood, that I think we should discuss in person. You and I do not always see eye to eye on this subject, and it would hurt me greatly if you misinterpreted my words as carrying anything but the utmost respect and friendship. Our means may be different but we still strive for the same end. The blood will run cold in my veins before I allow the blood of Atlantis to fade from the world. Of that, we are of the same mind.

Until our next meeting, I wish you the best of health.
-Excerpted from the private correspondence between Richard Potter, Son of Henry, and Louis Malfoy, son of Armand.

\simpleline

\DatePlace{The Keep of Mysteries
Westminster, London
1107, C.E.}

\lettrine{“C}{ivility}, I will have civility!” Severus Hortensius shouted. He held the Line of Merlin, the symbol of his station, in his left hand, and it whispered to him ideas, suggestions, paths. “I remind all of the members of the Wizard’s Council that Godric Gryffindor, Helga Hufflepuff, and Salazar Slytherin are here as our guests and should be treated as such.” He stared at Godric. “And in turn, I expect that our guests will afford us the level of respect that we are due. Now, that said, Master Longbottom has a fair and valid point. You requested special dispensation to circumvent the military authority of this Council in order to fight Lord Foul yourself. We granted that, and not only did you fail, but Lord Foul’s whereabouts are currently unknown.”

Septimus Longbottom added, “And this trophy you brought back for us, this Archway, we know nothing of its nature. For all we know, Lord Foul and his army may be dwelling just on the other side of that veil.”

“Master Longbottom, I can assure you that I have thoroughly inspected and researched this artifact,” Salazar Slytherin provided. “It is no dark portal to realms unseen, it is something much more eldritch than that. You should be thanking Godric for ensuring its safety within the hallowed halls of the Keep.”

“Yes, and further to the point, Longbottom, we have our best Unspeakables working around the clock to further decipher its mysteries.” Hortensius spread his hands. “But Godric, the fact stands that our world has grown close, perhaps too close. And your past few… escapades have not ended satisfactorily.”

“You speak of Dark Evangel. The Apostle of Darkness, she is dead, is she not?” Godric replied.

“Yes, and it practically put us to war against Shafiq and his regime in the process. Look around you at the world. The Muggle pontifex has called for war against Shafiq’s people. The Muggle king sends soldiers. Our world is fragile, and you have upset the game board too many times.”

“And what would you have me do, Severus? Stand idly by and watch as Longbottom’s Aurors flail blindly?”

Longbottom scoffed at the insult. “If we are blind, Godric, it is due in no small part to the fact that you and the others horde much-needed lore in your fortress that you call a ‘school’. Severus, the time for reform is here. Hogwarts needs to be recognized as an official branch of the Wizards’ Council. There is much we can share, much good we can do each other. You would have access to resources that I know for a fact you are currently struggling with.”

“And at what price would that come?” Godric demanded. “I am unwilling to sacrifice the neutrality of our school, to trade it away for a handful of coins. In this new era, knowledge is far, far more valuable.”

“Is it knowledge you crave? Or power?” Longbottom asked, the accusation ringing clearly.

Helga stepped in. “As distasteful as the idea of administrative oversight may sound, Longbottom is correct. There is much we have struggled with in the early days of our school. We can put limits in place as to the degree with which our affairs may be interfered.” She cast a sidelong glance at Godric. “I for one am comfortable with putting limitations upon the… military wing of Hogwarts.”

Salazar Slytherin nodded in agreement, and Godric voiced his displeasure, “And what limitations did you have in mind?”

William Umbridge looked down over the top of his glasses, “Yes, and I am curious what limitations you had in mind with respect to our influence.”

“Yes, I think that it is only fair and proper to demand that we are consulted when matters of international or interspecies relationships may be significantly impacted.” Albert Dumbledore spoke loudly from the back of the room.

Longbottom spoke up again “Yes, that fiasco with your sword has given the Goblins much reason to rally against us. They, like we, were not entirely in favor of such an accord.”

Severus Hortensius stepped in, before the matter could escalate. “We shall discuss the issue of Goblin insurgency in due time. And make no mistake, it is something that absolutely must be discussed. But we must come to an accord as to how Hogwarts will operate in the future. And another matter that needs attention in this regard is the attendance of Hogwarts.

“If you are to be granted a degree of privilege above and beyond that of a private institution, you must be aware of how your policies may be interpreted as an extension of the policies of the Council. Acceptance of those of mixed lineage by Hogwarts could, for example, be seen as tacit acceptance by the Council, perhaps even a mandate, to water down the blood of Atlantis.”

“Water down?” Godric exclaimed. “I thought that we were above this sort of arrogance and hubris.”

“There is no need to preach. We have heard the lecture many times, but you seem not to have heard our rejoinder. It is not a matter of intolerance, it is simply that we wish to proceed with caution for now. It is simply the fact that, as of yet, we still do not know the impact of diluting the blood of Atlantis.” Slytherin retorted.

Helga rolled her eyes. It was the same argument, but this time they had an audience. They went through the motions of appearing to argue with each other. Helga, and for that matter, everyone else in the room, knew full well that Godric and Salazar were arguing for the benefit of the crowd, not each other. Typically, Helga and Rowena could respectively calm Godric and Salazar, but Headmistress Ravenclaw was at Hogwarts; politics or no, there was still a school to run.

“Yes, and as we discussed previously, it is observable fact that the strength of one’s blood has no impact on the power that they may wield. Some of our best students are half-blood or less, and could easily out-magic those in your own house.” Godric added.

‘Yes, and as we have also discussed, it is an observable fact that the purity–” Salazar hesitated and reworded himself. “That the strength of one’s connection to Atlantis has measurable environmental impacts. One need only compare the Slytherin common room to that of, say, Gryffindor’s, to see the difference.”

Godric paused for a moment. His voice no longer carried the self-assured fire of before, and he proceeded hesitantly. “Are you so sure that is a good thing? I agree that magic flows more freely within your halls than my own. But with that power comes… danger.”

Salazar narrowed his eyes, “You have danced around this point for weeks, ever since returning from Azkaban. It is not a concern that you have ever brought up in our long years together.” He looked Godric in the eyes, who instinctively cast them downward. Slytherin growled, emphatically. “What did you see there?”

“What I saw…” Godric faltered, but then like a climber unexpectedly finding solid purchase, continued with renewed fervor, “What I saw was the danger and devastation that one person can wield. Lord Foul has inflicted a terrible evil upon not just our people, but the entire land as well. As we have seen, he is experimenting with magics that are dangerous even to the most reckless among us. And that is coming from me,” he added with a rare tone of self-deprecating humor. It seemed to work, as several members of the Wizard’s Council were smiling.

Longbottom seized this opportunity. “You see? They cannot agree, even among themselves! Yes, we should be mindful of the danger that one man may possess, Godric. Not only did you drive a rift between the Goblin communities, but you then massacred an entire regiment of them. They are a threat to our country, now. Even those who were on your side, they did not look kindly upon that spilled blood.”

“Damn them, and damn anyone who served Lord Foul. I taught you myself when you were at Hogwarts, Longbottom. You were renowned for your bravery. Have you truly fallen so low as to cower beneath such little feet?”

A few members of the council laughed. Longbottom turned red, “I would not underestimate them, were I you. They are, more and more, becoming armed. They have lost their lore, and in response have taken up wands. Combined with their mastery of artifice, they present a a very real threat.”

Hortensius was growing exasperated with the several different directions the conversation was taking, but had given up trying to corral it. After all, they had time to cover all points, even if it were not in the original order Severus had envisioned. “Yes, and you propose a limitation on their access to Wizard-made wands?”

“At the minimum, yes. They must be regulated, monitored. To say nothing of the matter of the dwindling supply of wands since Madame Ollivander’s absence.” He offered an olive branch to Godric, “What Godric had done with Ragnuk the Rampant, was, in its own way, brilliant. I propose that we can enforce similar such limitations upon them, under the guise of such mutually beneficial relationships?”

Godric clearly did not see the olive branch as a peace offering, “Limitations such as those you wish to enforce upon Hogwarts?”

Longbottom smiled, placatingly, “Godric. You are a wizard, not a Goblin. Although we are concerned that you may upset the game board, we are quite certain that we all play with the same color pieces. I do not share that same certainty with respect to the Little.”

Godric harrumphed, but Helga stepped in, changing the subject slightly, “But there is the matter of logistics… I am unsure as to whether Madame Ollivander would take kindly to such impositions upon to whom she can and cannot sell her wares.”

“Yes, well, Madame Ollivander is not here, is she?” William Umbridge piped up.

Hortensius rapped the Line of Merlin on the stone podium to demand silence. “The matter of what we do with the Goblins is a discussion for members of the Council, not the Founders of Hogwarts. We have called you here to discuss one specific aspect of the Edict, not all the points in their entirety. I suggest that we finish that discussion so that the Wizard’s Council may deliberate on their own matters.”

The council reluctantly nodded their agreement and began discussing anew the regulations that would be placed upon Hogwarts. It was over the span of several hours that the finer points of the Edict of Hortensius were hashed out and debated. When they had finally finished discussing Hogwarts, they bade the Founders to make their exit.
\simpleline
“I don’t like it.” Godric said, departing the meeting chamber with Salazar and Helga, looking up at the Archway. After the battle at Azkaban, representatives of the Aurors and several members of the Council had answered his urgent calls. He stayed there until enough of them arrived, but in the meantime he made sure to clean up much of the gruesome mess that had been made as he battled his way to the lowest floor. If they had seen the true extent of it, it was unlikely that the last meeting would have been as amicable as it was.

It took the group several hours, but they had successfully removed the entire inner core of the triangular tower, leaving it with a hollow center that extended up to the top through which the Archway was levitated up, up, and away. As Godric walked through the spiral staircase back to the top of the tower, the effect was chilling. He could see into almost all the rooms in the tower from any vantage point on the staircase.

There was a small note of confusion that he had trained himself not to ignore. This layout did not make sense. Why would a tower be designed in such a way? From a rough glance, it seemed that several of the chambers were previously inaccessible prior to the removal of the inner core. It didn’t make sense. Although he was not an expert in magical architecture, he had picked up a thing or two in the many long nights spent designing and building Hogwarts castle.

The triangular shape was not optimal, architecturally. The original plan was to simply blast the hole out the side and remove the Archway through the opening. But a few cursory charms to inspect the structure of the tower revealed that any such attempt would, in all likelihood, cause the entire tower to collapse upon itself.

How was it that the tower would have such an obvious architectural weak point, but that it was further built in such a way that the entire center could be removed with no ill effect? There was only one conclusion to be drawn, and it was chilling: this was deliberately designed. Whether Lord Foul had built Azkaban himself was unknown, but whoever did, it seemed clear that what Godric saw now was its intended final shape.

He voice these concerns to the other Founders, who personally visited the tower and scrutinized the Archway. Rowena Ravenclaw concluded that the tower was built to temporarily house the Archway. Further, she deduced that the curious metal ring with which the Goblin leader had escaped, was somehow linked to the Archway.

They had done all manner of experiments. Passing inanimate objects through the veil seemed to have no effect. Similarly, mundane living creatures could pass freely. Magical creatures, however, reacted very differently. No creature seemed willing to enter the Archway of its own volition. At first they tried immobilizing Cornish Pixies, and floating them through with magic. But the creatures resisted so intensely that they managed to break the bonds of the Immobulus charm.

After a few similarly failed attempts, they used magically reinforced leather straps to tie a Pixie down to a long length of rod, which they extended through the Archway from a distance. The sprite hissed venomously as they hoisted it into the air, but as it drew closer and closer to the veil, that hiss became a shriek. It shook violently within its bonds, trying desperately to escape, and eventually the shriek gave way to a wail of terror. Salazar held the rod, and continued to dispassionately proceed despite the fact that Rowena was visibly distressed.

As it past the threshold, the struggling immediately ceased. The light left its eyes. It was dead.

Helga Hufflepuff walked to the other side of the Archway, “Same over here. Dead. And Godric, you are certain that Lord Foul walked through the archway and simply ‘disappeared’?”

“Yes. Absolutely certain.”

Further experiments showed a certain magical resonance occurring between the Archway and the ring whenever living creatures passed through the veil. No matter what variables they manipulated, the end result was always death. The one thing they had not tried, however, was a creature of true sentience. A human. However, the need to decipher the Archway’s mystery did not seem to be so great that it justified the monstrous cost.

It was Salazar that suggested experimenting on prisoners, those who were already sentenced to death for their crimes. It was a notion that none of them were particularly comfortable with, and required the explicit consent of the council. But the Council seem far less concerned with the ethical implications, and far more concerned with simply solving the mystery. And a few less criminals in the world was no skin off their backs, because after all, the members of the Council were not criminals.

In the end, the result was the same. The first three prisoners, all dead. But the  curious observation was made that there was no Death Burst of any kind. They would have been able to detect if the Burst had simply been channeled through the Archway. To be fair, not every sudden death of a wizard or witch resulted in a Death Burst; it was roughly one in two deaths. As such, Rowena pointed out that there was still a one in eight chance that this would happen by pure random chance. The Wizard’s Council helpfully pointed out that they had several more prisoners that could be experimented upon.

A brief debate ensued concerning what their limit would be. After all, you can send one hundred men through, and even if there were no Bursts, it could still be nothing more than dumb luck. How many men were they willing to sacrifice before being satisfied? On this, Godric and Salazar were of the same mind: if they were to die anyway, what was the harm? So they agreed: five more prisoners. And if the same result was observed, they would have their conclusion.

Five prisoners walked through the Archway, five more died. No Death Bursts.

Besides the most obvious sign of death, the cessation of all activity associated with life, there were none of the other telltale indicators that the victims had passed. It was almost as if it simply transported the life force of its victims to someplace else entirely. But that still didn’t explain how Lord Foul had simply disappeared, unlike the others. There was another hypothesis to be tested: being a tremendously dark wizard and the very inventor of the Horcrux ritual itself, it was overwhelmingly likely the Lord Foul was in possession of one, if not several of the phylacteries.

Sacrificing a prisoner for the sake of science was already walking the very darkest edges of the grey area of morality. But overwriting their very life force in order to create a Horcrux? Even Salazar Slytherin was unwilling to go that far. By happy coincidence, however, Dark Evangel, a witch whom Godric had personally defeated half a century prior, had left behind a Horcrux of her own. Like most dark witches and wizards, she was prone to folly, and wore the Horcrux openly around her neck: a glittering silver pendant which now rest safely within the Keep of Mysteries.

More than willing to be rid of the terrible artifact, Severus Hortensius authorized the Unspeakables to remove it from its protective chamber. A veritable army of Aurors led by Lord Longbottom himself was gathered in the chamber that contained the Archway, ready to strike in the event of some unforeseen dark magic.

Godric did the honors, and flung the pendant through the Archway. In retrospect, that particular experiment was quite foolish. For all they knew, the spell could have triggered a blast which knocked the entire room unconscious. Although they had safeguards in place, levels and levels of safeguards, Magic is unpredictable and doesn’t always follow the rules. In fact, it rarely does.

Nonetheless, nothing particularly sinister happened. Save for the prone, childlike, unconscious form of Dark Evangel hurtling through the other side of the Archway, following the flight path of the pendant, which was nowhere to be found. Immediately, a dozen or more bolts of light, concussive waves, fans of ice and pillars of stone shot from the wands of the assembled group, stunning, sapping, imprisoning, and in one unfortunate case, eviscerating her.

That was unexpected.

She was kept on the cusp of life, and all manner of detection charms and rituals were used upon her, which revealed that her spirit was anchored. There was no trace whatsoever of any Horcrux connection. Satisfied that she did not pose the threat of revival, one of the Aurors snuffed out her remaining life, and a brief pulse of energy shockwaved through the room as the veil rippled softly.

“Lock it down, now.” Rowena demanded. She immediately went to work upon sealing the portal, and prepared a charm that spread as a diffuse, barely visible mist that blanketed the room. “It goes without saying that the results of this experiment should not leave this room. I have placed a Trace upon us all, and so if it does, I shall know. And more importantly, Godric shall know, and as you all are well aware, he does not wear the crown of restraint or ethics as heavily as I do.”

The Aurors in the room looked uncomfortably at the diadem on her head and the sword in Godric’s hands. The threat was effective, although uncomfortable. Although there were several paths to reconstructing a bodily form using a Horcrux, this one was surprisingly simple. They did not relish the prospect of being under constant attack from erstwhile servants of previously fallen dark lords.

Presently, the archway now sat, unused, for several months within the Keep of Mysteries before the day that the Wizards’ Council had convened to discuss the Edict of Hortensius. As Godric walked from the room, he could hear whispers from beyond the veil, calling to him. They all could, and they all heard something different.

Godric heard the slow, sad wail of a Phoenix’s cry.
\simpleline	

\DatePlace{Elizabethan Tearoom}

The eight men sat in the cozy room, whose exposed oak beams and soft, velvet covered furnishings provided the perfect atmosphere in which to relax before venturing out into a strange, timeless world. Presently, they were playing Dragon poker. How else would they pass the time? Although, time was perhaps a bit of a misnomer. They were on their hundred, thousand, millionth hand? They couldn’t keep track. They were on some hand of dragon poker when they heard voices from beyond the unopenable door to the north. They had tried, of course, to leave. But such a strong feeling of dread overcame them that they found themselves incapable.

Although they couldn’t leave the room through the door, there was a Judas window installed through which they could view the outside world. They rarely bothered; it was quite boring, to be frank. But now there were sounds, which was new, so one of them stood up to investigate the disturbance., and opened up the porthole to see the source of the disturbance. As soon as he did, a silvery pendant was flung unceremoniously through, hitting him square in his face.

“Oi! That was rude!” He cried.

The other men looked up. “What is it?” one asked.

“Something shiny, I reckon. Give it here.” The man closest to the pendant grabbed it, and another lumbered over trying to get a closer look, and tugged on the chain in an attempt to take it. “Oi, gerrof!”.

The other men rolled her eyes and watched the two wrestled bawdily for control. One of the men who was still playing laid his cards down on the table, “Read ’em and weep, boys. Straight flush!”

“Not so fast, Gilesbie.” Travers grinned as he laid down the Dragon card, and paired it with the deuce. “Reverse-o!”

Gilesbie groaned, and began collecting the cards to shuffle for the next hand.
\simpleline

The Edict of Hortensius, although remembered later in history primarily for its restriction of wand ownership, was rightfully hailed at the time as a brilliant political masterpiece. Its original intent was to settle the long-standing concern over the growing autonomy of Hogwarts by establishing an independent Board of Governors that, although did not explicitly answer to the Council, was nonetheless influenced by them.

It maintained Hogwarts’ neutrality by ensuring that no member of the Wizards’ Council could simultaneously be a member of the Hogwarts’ governing board. But it had also satisfied the Council’s desire for a degree of oversight by granting board positions solely to the heirs of the various most prominent members of the Council.

In doing so, it also addressed a growing but unstated problem: the heirs of those on the Council were well of age at this point, and many had heirs unto themselves. They were growing restless, hungry for power, but their fathers and mothers had no plans on dying anytime soon, and creating additional seats on the Council was not a desirable option.

It even managed to address the ever growing concern of wand supply. Ever since Madame Ollivander’s son had graduated from Hogwarts and taken over the family business, the production of new wands was vastly limited. Ollivander the Elder had clearly not passed her expertise down, and she rarely made appearance at the store. Each year, their vast supply of wands she had created over the centuries began to dwindle precipitously, and unless Ollivander resumed production or passed on her lore, there would be none left within the span of a few decades.

In a move would satisfy both the prudent and the purists, the Edict of Hortensius demanded that all Ollivander wands in the civilized world be returned to the Wizard’s Council within one year’s time. Those wands would be registered and then returned to their owners, provided they could demonstrate an appropriate knowledge of magical safety. For the vast majority of wizards, this meant either having attended Hogwarts themselves, or having a living heir who is attending or had attended the school.

The move drew out the few Methuselahn, heirless wizards that the Council knew existed, and had long wanted to keep tabs upon. Those who did not present themselves were greatly weakened, for in a shocking, rare public appearance, Madame Ollivander gave her support of the Edict, and pledged to enact a grand ritual at the end of the yearlong deadline, which would render her creations useless were they not subject to the registration process.

In one deft stroke, Severus Hortensius had eased the tensions between three powerful and disparate groups of interest, and had further consolidated power in the civilized world in the hands of the Council and its heirs.

But alas, every river of good intentions must eventually terminate, flowing out into a sea of unintended consequences.
\simpleline
\DatePlace{The Urgod Ur\\
Ackle\\
1107 C.E.}
“Do not be so hasty to deny this opportunity, Surdod.” Godrod spoke, emphatically.

“I agree. Let us not show the same ignorant intolerance as the humans and reject him out of hand simply because he is not Goblin.” Haddad agreed.

Surdod slammed his first upon the table. “It is because of him that Ulak the Unconquered has fallen. Ulak and his kin chose to follow the Archon, and paid for it with blood. I wish to see no more goblin blood on this man’s hands, or any man!”

“Yes, but let us not forget whose sword actually drew that blood. That man is the one upon whom the Archon proposes war.” Bilgurd offered amicably.

“Need we escalate this cycle of death? Say we win, what then? Do you truly think that humans, in their perpetual bloodlust and ignorance,” He nodded his head at the Archon Heraclius Hero, who sat in the guest chair at the table. “Present company excluded, of course. Do you really think they will let such a blow go unreturned? Of course not! They will wage war.” Surdod retorted.

“Then war they shall have!” Haddad roared. “They seek to take our wands, they seek to remove the ability with which we may defend ourselves from their ever encroaching advances. Somehow they have bamboozled or coerced Madame Ollivander, who was a friend to all of our kind, and I believe her when she says that our wands will turn to sticks in our hands if we do not submit to their slavery. We must strike before that happens.”

Surdod sighed. “And what good will that do? We cannot control Madame Ollivander: our wands will still be useless, war or no. What do you suggest, that we send our younglings to that human school to have their minds filled with rot and poison? Do you propose that we take over the school, and teach humankind our secrets? Or do we simply refuse entry to all but Goblins?

“At the end of all these paths lie ruin. The covenant that the Four Founders and the Board of Governors signed, bound by the Cup of Dawn itself, dictates that all parties much reach a supermajority on any matters which ‘significantly impact the course and direction of the curriculum or administration of Hogwarts’. Such an agreement cannot be coerced, it must be entered into freely. In their spite, the humans would never agree to allow us our wands.”

Godrod nodded. “Then it is they who send us into the cycle of death, not us. We cannot simply sit idly by while they trample our people. I speak to you now as a friend, Sodrod. I know that you have been hesitant to send our people to war, and with good cause. Your voice of reason has been much appreciated and greatly valued. However, we stand now at the precipice of a new era. Already, our magic wanes. Wizards wish to crush us beneath their heels. It is often more brave, more honorable, more difficult to stay one’s hand than to strike. But now is not one of those times. If we stay our hand, it will be cut off. If we put down our spears, they shall be stolen. We are stuck between the hammer and the anvil, forced into a choice not of our own making. It is a terrible choice, yes, but one that we cannot afford not to make. This is the future of our very race at stake, and sadly now we must fight for that future!”

An overwhelming majority of the goblins at the table cheered loudly at this. Bilgurd, Sodrod and a few others looked at each other, dubiously exchanging meaningful glances, and eventually nodding amongst themselves.

After a time, Sodrod spoke. “Very well. Let us decide then, on whether to ally with this man who proposes war against Wizards.”

Archon Heraclius Hero, who had been silent up until this point, raised his open hand, and the room grew quiet. “Before you decide, I would like to speak. Because I do not wish you to enter into such a decision lightly. You must understand that, although I disagree with Sodrod’s hesitance to fight, he is correct in that it is unlikely that Lady Ollivander will change her course. By allying with me, you embrace a new era, but it will be a darker era. Many magicks will be lost, and must one day be rediscovered. I can help you with this, I can help you to shine a light in the darkness, but darkness will come, make no mistake.

“Those who knew Ulak, they should know that I did not view him as a subordinate, but truly as equals. If you ally with me, you do not take on a master, but rather, an advisor, a general to fight under your banner. But make no mistake, this will be not be a battle, it will be a war over the span of centuries. Many of you in this room will die. Many of your children will die. Many of your children’s children’s children will die as a result of the seeds we sow in the coming year. If we win, it will not be a happy victory, but it will be a necessary one.

“I know that this likely will dampen your ardor, I can see that many of you are still reluctant, and my warnings will make more of you so. But I respect your people too much to try to win you over with honeyed words and clever rhetoric. I speak to you plainly, so that you may truly know the risks in which you are about to engage.”

The surrounding goblins nodded grimly, understanding. A long moment of silence passed, as they considered and weighed his words. Eventually, the vote was called, and the goblins began to raise their hands. The decision was unanimous.

Meldh smiled to himself.

\emph{All too easy…}