\chapter{Egeusly Stare}
\lettrine{T}{he} man placed his hand on Meldh’s shoulder and replied. “But there are still more to be fought. You are a worthy leader. But I fear you may not yet be strong enough for the battles to come. \emph{Egeustimentis}”
\simpleline
\begin{flushright}
Meldh existed as an abstraction, his mind existed as a physical structure. The space that Meldh currently occupied, however, was a crude facsimile.\\It was fuzzy and low fidelity, like a sketch of an artist painting a portrait of a beautiful landscape.\\The broad strokes of his being were there, open and laid bare for manipulation. But the subtle interweaving of connections that truly made up his being were lost in the amongst the sludge, and as such the intruder did not have complete control. Meldh sensed this, and the intruder responded.
\SmallVSpace
“I do not need to forcibly change your mind, Heraclius Hero.”
\SmallVSpace
\emph{What manner of magic is this\mbox{--}}

“It is the Aletheia Touch, the Touch of Truth. It lays the victim’s mind open in its entirety. Exceptionally powerful magic, yes. But trivially dismissed.”
\SmallVSpace
\emph{Who are you?}
\SmallVSpace
“I am the one who runs this world. That is to say, I set the world in motion. All of the events that you have witnessed in your lifetime and will ever witness in millennia to come are my doing.”
\SmallVSpace
\emph{Then what use do I have to you?}
\SmallVSpace
"You are but a mere child to me. A mewling babe. But what I have learned from watching this world spin and dance is that wisdom can be found in the most unlikely of places. People are resources, you must never forget that. Like a shepherd, one must cultivate and husband the flock, or you will see no yield. If you let your flock stagnate, they will do nothing for you. If you do not protect them, they will wither and die."
\SmallVSpace
"The world grows large, Hero{\el} or shall I say, Meldh? An old word, of questionable origin, yet an undeniable meaning. Yes, I rather like that. You asked who I am. I have gone by many names, but you may call me Merlin. Yes, this world grows large, and it is a world that will be shaped by your vision, not mine. The world will and must be ruled by man and reason, not by old gods and whispers, or shamans with their totems of power."
\SmallVSpace
“I can no longer be the only shepherd of this world. Every era, the world doubles upon itself. No, the world requires an entire flock of shepherds. And someone must herd that flock, Meldh. No matter how much power I can obtain on my own, people are always necessary. Two people will always have more absolute potential than a single person. And, as it were, it appears that I am operating under a rather strange and very peculiar set of constraints. So to put it simply: I need help.”
\SmallVSpace
\emph{How? And why}?
\SmallVSpace
"Inspiration can come from the strangest of places. There are an infinite number of possible ideas and concepts. New ideas can be refactored upon old ideas, and recombined with newer ideas in ways newer still. Those combinations can be further refactored, et cetera, et cetera, ad infinitum. A mind can contain but itself, and as the arrow of time progresses, the possibilities in the world grows exponentially faster than any one person’s capability to understand them all."
\SmallVSpace
“A simple solution to this is to limit the scope of possibilities, to move the world in the direction of one’s choosing. Which I have done. This is the world of my imagination. But that is precisely the problem: it is an echo chamber. It is time for new input to be introduced. Somewhere in the swirling miasma of possibility, something useful lurks, and I intend to find it.”
\SmallVSpace
\emph{You have answered neither the How nor the Why.}
\SmallVSpace
"I am not proud to say this, but I simply lack the empathy to properly deal with the masses in the manner that I would prefer. They seem so{\el} Alien to me. Imagine, trying to comprehend the mind of a mere insect, trying to empathize with a gnat, to the point where you can predict its behavior, understand what it will do next. I understand human nature, yes. Far too well, some may say. I can tell you as surely as the sun rises the direction that civilization will take, and how to shape it in the direction of my choosing."
\SomeVSpace
"But ultimately, really how useful is it to point to the sky and say, ‘The sun will rise tomorrow’? That yields no wisdom or knowledge. The sun is a mighty force, it burns with the fury of a God, and so a fool may be inclined to see himself as powerful because he can shade himself from that sun. There is delicate work that must be done in the future, delicate work far more subtle than mere shade. It needs a delicate hand. Someone who{\el} Understands the insects."

“For example, this spell, if executed with sufficient empathy, would yield a perfect, inviolate reflection of your mind. But as it were, my rendition of it merely produces{\el} Ah, how did you put it? ‘A picture of a picture of a landscape’?”
\SmallVSpace
\emph{No. ‘Like a sketch of an artist painting a portrait of a beautiful landscape.’}
\SmallVSpace
“You see? Executed perfectly, I would be able to pluck those thoughts from your mind before they even had a chance to form for your self to experience them. Your mind, any mind, is simply information. Patterns reflecting patterns, folding in upon themselves endlessly. And yes, you are precisely correct in assuming that this is the basic principle behind your ‘Horcrux’ ritual.”
\SmallVSpace
\emph{It is called the öρóσταυρóς.}
\SmallVSpace
"Forgive me for using the Latin rendition. Although I do think it’s catchier. Less of a mouthful. Regardless, you will find that there are, in fact, many ways of extending one’s life, of achieving functional immortality. Some of these means are likely as far beyond your comprehension as your Horcrux is beyond that of an ant’s. Others are so simple that it feels like cheating. Others still are simply esoteric and bizarre."
\SmallVSpace
"It is enough for you to know that as long as you are allied with me, your Form shall be perfect. In exchange for this, I request, not demand, your loyalty and assistance. I expect that you will be able to make far better use of the Aletheia Touch than myself. And I further expect you to make some very strange advances in the world of herpetology. But most importantly, you must be one to fulfill a rather crucial prophecy."
\SmallVSpace
\emph{Prophecy is Delphic nonsense, designed to impress nobility by telling them half what they want to hear and half what they already know.}
\SmallVSpace
The voice of the interloper took an abstract form as a quizzical smile. “Oh?”
\SmallVSpace
\emph{If our destinies were in any way predetermined, it would be incompatible with my observations. I observe that I can make decisions, that I am a Prime Mover. If I choose to say Fire is my favorite element rather than Water, that is my choice.}
\SmallVSpace
“If I asked you then, to tell me the airspeed velocity of an unladen swallow{\el} Let’s say, African, for argument’s sake. Could you *choose* to tell me?”
\SmallVSpace
\emph{That’s pedantic. That is information which I do not possess. That is not a decision of choice.}
\SmallVSpace
“You are precisely correct. You cannot simply make the decision to know something you do not know, just as you cannot simply make the decision to walk through solid stone without the use of magic or tools. Just as you cannot simply make the decision to disobey the will of prophecy.”
\SmallVSpace
\emph{That is unfalsifiable.}
\SmallVSpace
“Is that so? Then open this box.”
\SmallVSpace
A black box, darker than dark, deeper than the pitchest black, unearthed itself from beneath the flow of time and instantiated within Meldh’s mind. Its presence was the absence of presence, it’s entire form a negative, defined by the razor\mbox{--}sharp hole that it appeared to make in the world.

He knew that with a simple exertion of his will, he could open that box.
\SmallVSpace
“I swear that no harm will come if you choose to open that box.”
\SmallVSpace
As surely as he knew that he was capable of opening the box, he also knew that he would not. He knew, somewhere, somehow, that opening the box with irrevocably destroy this world, and all worlds. To open the box would bring about the End of All Things. He could not open the box; he would not open the box.
\SmallVSpace
“I have told you that no harm will come to you or yours should you choose to open the box. And yet, you hesitate.”
\SmallVSpace
Meldh considered opening the box simply to prove a point, but he knew this was an idle boast. He knew beyond reckoning that the box would stay closed until the end of Time.
\SomeVSpace
"You see? There is nothing preventing you, in the laws of nature or physics, from opening that box. In your mind, you are bound only by your free will: you would not make that choice. In reality, you are bound by prophecy. You \emph{cannot} make that choice."
\SmallVSpace
"The world must be consistent with itself. And therein lies the heart of my trouble. As you have been so impatiently thinking throughout this discussion, I have still yet to tell you why I require your assistance. All prophecy is true. But there will come a day when prophecy will no longer be able to guide us. The choices we make now are 10,000 threads woven through 10,000 needles, and each one must be woven expertly in order for us to continue down the path of life."
\SmallVSpace
"When that day comes, there is but a single choice that is the crux of the matter, a single decisions, the fundamental decision for all things: life or death? All worlds ultimately narrow to those two. The paths that lead to death are nearly infinite. The paths that lead to life, on the other hand, are few and precious. The irony of that is not lost to me."
\SmallVSpace
"My entire life, I have been trying to shepherd this world, all worlds, down that path. There was a time, many ages ago, that I made a crucial mistake, and was fooled by own power. I gave in to the temptation to believe that because I was a good person, that my actions were in the right. I have had the rest of eternity to contemplate that mistake."
\SmallVSpace
"Magic binds this world to all others. Using nothing but a small bit of your magic, you can pierce the veil of this universe and reach into another world and bring forth your Will. This provides for possibilities beyond your wildest imagination, but it comes at the expense of salvation. Magic is part of the answer, but it is not THE answer. All paths that travel solely down the road of magic end with death, and that is why you must join me. That is why you \emph{will} join me."
\SmallVSpace
\emph{I do not understand. I suspect you know more about the true nature of magic than any of the scholars of Greece and beyond. So you should know that Magic has been used to defeat death}.
\SmallVSpace
“Magic connects this world with all worlds. But the path of life, it must be inviolate. Life can tolerate no death. Life is a potion in a cauldron, and death is the poison. There can be no compromise; in any compromise, only death can win. Either must destroy all beyond a remnant of the other, for those two spirits cannot exist in the same world. Through the bonds of Magic, we are but a veil away from that world of death. Observe.”
\SmallVSpace
The entirety of the night sky illuminated the interior of Meldh’s mind. An ethereal centaur comprised of stars drew from its back a glittering bow, and let loose an arrow across the night sky. It flew directly into the heart of a great, bejeweled scorpion, and travelled farther, farther away, beyond to the center of something.
\SmallVSpace
“We walk down that path of the Scorpion and the Archer. It points us to a place Beyond Time, beyond reckoning. Every improperly used bit of magic draws us further close to that realm of death, allows it passage into our world. You are familiar with the Ritual of the Subtle Knife?”
\SmallVSpace
\emph{I have heard whispers of it from the Necromancers who dwell beyond Carthage. A rope that has hanged a man and a sword that has slain a woman, among other things. It is said to be able to summon a Specter of Death. I had assumed, until now, that it was simply a myth, a legendary retelling of some old bit of lore lost to time.}
\SmallVSpace
“It is no myth. In a universe of endless possibilities, it is only inevitable that we encroach into a world that has death as its final endpoint. These are wounds in this world, and with each day we open more. That ritual simply provides a Form to those wounds, a Form that our minds can comprehend. The Specters, you see, they are horrifically dangerous. But in other ways, they are useful, for that which has a physical form can be defeated. Observe.”
\end{flushright}
\simpleline
\DatePlace{Another Britain\\
Another Time\\
Another Place}
The end had come without noise or notice. One by one, he individually visited his Death Eaters, revealing his return. He spoke of power beyond reckoning, and a new era for Wizardkind. His most loyal lieutenants, he bestowed great gifts upon. His more erstwhile followers were set to other tasks, such as serving as permanently transfigured simulacra of various political figureheads; Scrimegeour, Bones, Thicknesse and the like were as easily replaced as they were murdered.

Alastor Moody was only slightly more difficult to deal with. The following morning’s Daily Prophet read: \headline{“THE DARK LORD RETURNS:  Dumbledore, Boy who Lived Dead”}  Beneath the menacing headline was a picture of Not\mbox{--}Amelia\mbox{--}Bones and Not\mbox{--}Alastor\mbox{--}Moody kneeling at the foot of Lord Voldemort who was giving the Hand of Benediction. The message was as clear to the true Moody as it was inscrutable to everyone else: \emph{No one can be trusted. You are not safe. Recant. Relent. Retreat.}

Moody had long ago learned the tactical value of a complete and hasty retreat. You did not live to tangle with as many Dark witches and wizards as Moody if you made it a regular occurrence to charge headlong into almost\mbox{--}certain death. So with a dull pop, the true Alastor Moody disapparated to a safe house whose location was known only to him, and was never heard from again.
\simpleline
Tom Morfin Riddle was the master of life and death. His True Horcrux gave him mastery over life, enabling him to travel freely from vessel to vessel, body to body, soul to soul. His Deathly Hallows gave him mastery over death: The Spirit Stone, rightfully passed from heir to heir. The Elder Wand, forcefully wrested from the hand of his foe. And the True Cloak of Invisibility, bequeathed to him by his mirror self, his shadowform. He was truly king, and God, and as such had abandoned his previous moniker of Lord Voldemort, and chose the simple epithet: \emph{The God King.}
\SmallVSpace
The majority of the Wizarding public simply counted themselves lucky: although the God King was quick to mete out punishment, he was also quick to bestow favors, and as long as they kept their heads down and toed the party line, life was actually not so bad. In fact, it was better in many respects. Gone was the bloated, impotent Ministry of the past, whose sole purpose was to maintain the outdated hegemony, not to better the lives of its subjects. The God King did not need to resort to mean, petty politics in order to extend his reign. Any challengers were simply killed. As such, there were no challengers. But also as such, it freed the Ministry to actually do some good every now and then.
\SmallVSpace
More shrewd members of the Wizarding public recognized Voldemort’s change of identity and methods as a brilliant political gambit: history has taught us that tyrants rarely rule longer than a generation or two before being replaced by an ostensibly less tyrannous tyrant. Furthermore, history has also taught us that hope is like a virus, and will take root in the most unlikely of places, breeding and growing until it can no longer be contained. A lesser tyrant will try to quash all hope, and thus allow hope to proliferate: the hope of revolution. A shrewd ruler knows that hope must be accounted for and allowed to fluorish in a controlled fashion. A brilliant ruler will be the very person who provides hope to his subjects. The God King was cruel, yes, but he also brought great wealth to Britain, and His advancements in the realms of health and medicine were staggering. His subjects could live in hope that one day the God King would bestow His blessing upon them.
\SmallVSpace
No one in the Wizarding public knew the true method behind the madness. The truth was that the God King was a man obsessed. Obsessed with a small prophecy he had heard from the lips of a sherry\mbox{--}soaked Divination professor. A prophecy that upon further research was The Prophecy, the one prophecy upon which all others hinged. A prophecy whose fulfillment was the crux of everything. The God King spent most of his days deep within the Department of Mysteries, trying to salvage what he could from the ruined Hall of Prophecy. He sought out and met, under many disguises, with many students of deep, hidden knowledge.
\SmallVSpace
After years of collecting lore, and countless days spent poring over the ancient text, \emph{The Transmygracioun}, the thought of a ritual began to grow in the mind of the God King, the Ritual of the Starfire, a ritual by which prophecy could be fulfilled and the world be saved.
\SmallVSpace
There has always been a Crux upon which the web of prophecy circles itself around. However it is not strictly accurate to say that there is only one Crux. In every world, the Fate of All Things hinges upon a single choice. Who makes the choice? What is the nature of the choice they must make? Only those Outside Time know for certain. But what is known is that the Choice must be made, and the mere death of one possible vehicle of prophecy would not stop things. The God King knew this much, and he knew that the mantle of the Crux had been passed to him.
\SmallVSpace
What he did not know was that there was another named by prophecy, one who was Fated, in a time of great strife, when all worlds narrow to two, to bring down a great house. A Slytherin boy who had read tales of The Boy Who Lived, who combined the Muggle knowledge of science with the Wizard knowledge of magic and whose legacy was cut tragically short by the God King himself. A Slytherin boy who, emboldened by being Named by Prophecy, took it upon himself to experiment in secrecy, utmost secrecy, with the deepest laws of magic and nature, just like his idol Harry James Potter\mbox{--}Evans\mbox{--}Verres. He made great strides in the field of transfiguration, and had such a fine command that he could manipulate the Form of things on an atomic, even subatomic level. A boy who was desperate enough to overthrow the God King that we would resort to desperate, even insane means.
\SmallVSpace
He was, however, alone, unlike his idol. He had his companion, but unlike his idol, he chose not to seek her counsel. She knew as little of Muggle physics as he did: that is to say, she studied a pair of purloined physics books for a few weeks. She grasped the broad strokes of quantum mechanics without any true understanding. However, she could have been what he needed: a staying hand, someone to shape his curiosity, someone to guide his intellect, someone to tell him, for the love of Merlin and all that is holy, \emph{\textbf{do not try to find out what happens when you transfigure a cubic millimeter of up quarks, just the up quarks, without any down quarks to bind them!}}
\simpleline
“Lawrence, I’m not so sure about this.”

“I am. What would Harry Potter have done? He knew science. WE know science. He gave his life to fight the God King so that we don’t have to.”

“But you don’t even understand what it is you’re doing. You don’t even know what these things really are.”

“Sure I do. They’re the lightest of all elementary particles. They form the basis of neutrons and protons. They have mass, and as such can be Transfigured.”

“No, I don’t mean{\el} Look, I can recite an encyclopedia entry, too. But I mean, you don’t really understand what these things will do.”

“Don’t be silly. I’m taking adequate precautions. How much damage could a few cubic centimeters of ANYTHING really do?”

“I still have a bad feeling about this{\el} You really should have been sorted into Gryffindor, you know.”

He gave her a quick peck on the cheek, held her hand, and directed his wand at the Knut that lay on the table.

Annabeth and Lawrence were instantly consumed, as was the whole of Hogwarts and most of Scotland. The world itself screamed in pain as it warped beyond recognition, consumed in its entirety by the Void that was created.
\simpleline
In the brief instant of time before his mind was lost, Meldh recognized the Void, or more specifically, recognized the ways it was different. There was no control, no safeguards, no finesse. It was purely unfathomable. It was madness.
\SmallVSpace
The notes of the universe’s song stretched interminably, seamlessly shifting from reality to a musical harmony to a single note sustained infinitely. The note slowed, lowered in pitch, lowered, lowered until the individual frequency of the periodic wave became discernible. The frequency stretched further, further. The waves were fewer and fewer between. At some point, there was nothing, no change, no fluctuation, no vibration, nothing.
\SmallVSpace
And somewhere between that nothing and The Nothing, the true horror of Death crashed into Meldh’s unprotected mind like the fist of God.
\SmallVSpace
If the reflection of his own mind that the interloper had generated was but a picture of a picture, what he saw now was like he was like he was given new eyes, eyes that could see beyond the veil of time with a clarity so crystalline that it was physically painful for his mind to behold.
\SmallVSpace
What he saw was beyond terrifying. There were no expectations for the force to conform to in order to protect him. It was new, to him and to the majority of mankind. As such, it was unknown: there was nothing for his mind to flinch towards or away from. He was simply hit head on with the full impact of that horror beyond horrors.
\SmallVSpace
It was Death, pure, glorious, powerful, terrible Death. The point at the end of all paths. He saw the universe run like some clockwork automaton, powered by a cosmic spring, tick tick, tick tock, tock tock. He saw the spring slowly wind down, and he saw the brave, the intelligent, the cunning, the diligent, all fighting with the entirety of their being to no avail, like a stone falling from a cliff. All the motion, the action, the vibrancy of life, fighting against the anticipation, hurtling towards that inexorable end.

He could live to be 10,000 years, 10,000 times over, and it would be of no use. That end could come. That end would come one day. The hopelessness of it all consumed him. His brain, in sheer reflexive self\mbox{--}defense, began throwing as many happy memories as possible into that void: the less happiness he clung on to, the less brutal the sting of loss would be.
\SmallVSpace
It was betrayal, which made the sensation all the worse. His own mind, willingly turning against his own values, in exchange for an infinitesimal bit of respite against an elemental force that did not care to bargain. It was the dark center that dwelled at the heart of all mankind. He would commit any crime, sacrifice any virtue, defile anything holy, for no atrocity could even be a speck of dust in comparison to the darkness he was approaching.
\SmallVSpace
Somewhere in Meldh’s mind, an idea lurked. It was hidden, out of sight, but it was there, waiting to be uncovered, if he only knew where to look. His mind did not want to look. His mind wanted to die. His mind begged for death. Death would be preferable to this Death.
\SomeVSpace
\emph{\textbf{\underline{Kill me.}}}

\emph{\textbf{Please.}}
\SomeVSpace
Gone. Gone. The abstraction layer stripped away. Bare metaphor, unplaced structures, synaptic connections. Separate. Separate. Regroup. Fight. Fight. Fight.
\SmallVSpace
A hasty retreat. The king was in check. Sacrifice the knight. Sacrifice the rook. Save the king. Retreat. Relent. Recant. Pawn to E7. Sacrifice. Regroup. Sacrifice. Reclaim control. Take your position, no matter how small. Take it.
\SmallVSpace
Meldh fought his own mind, fought the instinct of sacrifice, partitioned away the truly important parts of his mind and used the rest as a buffer. It afforded him a few precious moments. His memories, his thoughts, his happiness, they were all being stripped away, burned through at an alarming rate, but Meldh was still intact, for the time being.
\SmallVSpace
\emph{Fight.}
\SmallVSpace
He thought back to all the things he had learned, from all the people he had met, from the simpletons in the asylum all the way to the Old Gods themselves. He thought back to the hope of which they spoke. The hope. The hope. He fought for that hope.
\SmallVSpace
He focused that hope, harnessed it, and looked towards Death with new eyes. He saw Death, feasting upon his very soul: a tiny ball of light that was floating towards its{\el} Mouth?
\SmallVSpace
Its gaping mouth? Surrounded{\el} Surrounded by a black, tattered cloak. A rasping hiss. Beneath the cloak, a tall, thin, naked man, obscenely painful to behold{\el} But alive. Tangible. Something almost human. Something that could ultimately be defeated.
\SomeVSpace
\textbf{ENOUGH.}
\SomeVSpace
He had already seen Death. He had already beaten Death. He had died before, he would die again, and he would not give up. And although this was more than just the mere death of his body, although this was the Death of All Things, he would still fight. And with his Steel and his Magic and his Will and his Life and his Time, he flung his weapons against his foe, his final adversary.
\SmallVSpace
\emph{I{\el}}
\SmallVSpace
The light built up within him. He directed it downward, looking upward, always upward, always to the stars, never looking back. He would not look back. He could not look back. Close the box. Ever upward.
\SmallVSpace
\emph{I will{\el}}
\SmallVSpace
He had wings. He was Wing. He flew to the sun, and beyond. Even as his wings melted, he flew higher, ever higher, never looking down, never looking back.
\SmallVSpace
\emph{I will never{\el}}
\SmallVSpace
He was a single point of light in a dead, uncaring, clockwork universe. As he hurtled past the infinite darkness of space, he saw the others stars like him, the other points of light, shining brightly, fighting ceaselessly against the void, giving meaning to an otherwise meaningless collection of symbols, rules, laws, and patterns.
\SmallVSpace
\emph{I will never stop{\el}}
\SmallVSpace
Some of the lights were dim, some of the lights were dimming, they were the ones in danger. To them, he gave a measure of his Life, his Light. He found that the more he gave, the more he had to give, so he gave more. He gave more, and more. He gave his fire, and that fire grew, he burned through everything he had and more.
\SmallVSpace
\textbf{\emph{I will never stop fighting.}}
\SmallVSpace
He directed that inferno outward, in all directions, in a single direction: backward, downward, behind. He directed it against the stagnation and the death that chased him, that chased everyone. He directed it at the hideous, all\mbox{--}consuming beast that lived beneath that tattered black cloak. The beast greedily and happily consumed the fire, but Meldh would not stop fighting, would not stop burning.
\SmallVSpace
It was not just his star that burned, that raged against the beast, it was every star in every universe, every star that ranged with hot, angry resolve, and burned, burned, burned to live.
\SmallVSpace
\textit{\newline You are not invincible, I have beaten you once.}%\SmallVSpace
\textit{\newline You are not inevitable, so long as we have a choice.}\SmallVSpace
\textit{\newline You may one day claim me, but I will return, as I have before.}
\textit{\newline You may claim others, but I shall see to it that they too return to fight.}
\textit{\newline I fight you with the power of my mind, with all of my life.}\SmallVSpace
\textit{\newline I am Heraclius Hero, and I will fight you.}
\textit{\newline I am Alexander, Protector of Mankind, and I will fight you.}
\textit{\newline I am Meldh, descendent of the Ancient Gods, and I will fight you.}
\textit{\newline I am Man, every man, woman, child and beyond, who has ever thought to shine a candle into the darkness.
}
\SmallVSpace
\textbf{\newline\emph{And I will never stop fighting.}}
\simpleline
\begin{flushright}
Somewhere in the distant corners of a distant universe, the sound of wings: a tattered black cloak, drifting away into nothingness.
\end{flushright}