\chapter{The Fall}

\DatePlace{XXXXXX\\
XX,XXX X.X.}

\lettrine{M}{erlin} emerged on the back end of eternity, his Will nearly broken, his Life nearly lost. He desperately reached out backward across the span of Time, but he knew what the result would be. Nothing. What he created should have been Paradise. Instead, it was Hell. They were gone, all of them, and he had no one to blame but himself. No one was left to blame but himself.
\SmallVSpace
He looked forward into the depths of Time, and what he saw horrified him further. So many were already dead at his hand, but there were to be more. Countless more. Billions more. With every day that passed, the Curse that now bound this world and all worlds would grow. New lives would be created, lives so unbelievably, horrifyingly, tragically short. There was nothing he could do to save them.
\SmallVSpace
Not yet, at least.
\SmallVSpace
He had looked through Time once more, and in that instant of calculation, he embraced all possible futures and saw only one. The world must be unbound. The world must be sacrificed for the sake of all other worlds. There was no other way. How could there be? This was his burden, and every moment wasted, a new tragedy was born.
\SomeVSpace
He would soon find that there were others, those who had foreseen the cataclysm and taken steps to ensure their safety. Tragedies. More tragedies. They were anchored to this world, thus they too must be unbound. Nog\mbox{--}Nandh of the Flame, Yanotuk of the Cups, Ma’krt of the Rock, KriXiang of the Glass, Shiggoth of the Spire, Neirkalatia of the Cross, Gom’Jorbol of the Rod, Kari of the Cube, and a handful of others.

And himself, Merlin of the Line. He too must be unbound, this he knew. It was a sacrifice he would be proud to make when the time came: one life for infinite lives. It was a sacrifice that all of his kind should be proud to make, twelve lives for infinite lives. It was a sacrifice the entire world should be proud to make, billions of lives for infinite lives.
\SmallVSpace
Over the eons, he met with them, when this new Earth was still young and wild. Some had woken, and wandered the world. Some appointed avatars to be their proxies. Others still lay slumbering. Most, however, clung desperately to their lives, and waged mean and petty wars against each other for dominance over a child’s playground. He left these sad creatures to their own punishment, for he knew they would either end each other, or be ended by the new masters of this new world.
\SmallVSpace
Shiggoth was the first to fall. He left behind, (as the others would as well), his point of anchoring to this world. The Spires of Shiggoth were fearsome, powerful, and dangerous. But they were useful.\\Such things do not last long in this world or any world before they are discovered, abused, and eventually destroyed. He would let the universe take its natural toll.
\SmallVSpace
The others, however, were more problematic. Merlin was powerful, but not omnipotent. He was knowledgeable but not omniscient. He devoted much of his early days to searching, gathering lore and knowledge and power and puissance in the process. After a time, he came into a plan. He needed their powers, and once he claimed them, he would set to his work of saving the world.

And he need not waste one more minute.
\doubleline
Nog\mbox{--}Nandh slept. Nog\mbox{--}Nandh dreamed. It dreamed of death, of horror, of bodies and teeth and limbs, in their countless trillions. It dreamed of the death it felt responsible for. This horror, this oblivion, was preferable to waking to face what it had wrought.

So Nog\mbox{--}Nandh slept. It slept for countless eons, dreaming the same dreams. Of course, had it so chosen, it could have dreamed joy, hope, and love. But it did not want peace. It wanted absolution. That absolution would be born in pain and loss.
\SmallVSpace
When Nog\mbox{--}Nandh dreamed of something different, it knew its day of reckoning had come. It dreamed of a man, so unfamiliar. It dreamed of a man, an old friend. It dreamed of lined faces and green eyes and strange robes and strange hair strange eyes strange face strange teeth the teeth the teeth the teeth\mbox{--}

\simpleline

\DatePlace{On the shores of the lake of teeth,\\ where the black hills end.}

\mbox{---}the teeth. The landscape of Nog\mbox{--}Nandh’s nightmares had coalesced into distinct geography. In the sky was rain, for it always rained from eternity into eternity. Today, the rain took the form of mist. A light fog of milk wafted through, collecting dew upon the jagged frozen rocks at an outcropping of the lake.
\SmallVSpace
This world, this living nightmare, stared into the eyes of the strange man who existed as nothing but fractal shadows. And undefined period of silence followed. Nog\mbox{--}Nandh’s nightmare-world finally spoke.
\SmallVSpace
“Merlin{\el} Please.”
\SmallVSpace
At that, the new lords of this land arrived: the people of Danu. When the last of them came, Merlin wove all of Nog\mbox{--}Nandh’s will into the fabric of permanency, ensuring that as long as Nog\mbox{--}Nandh endured, so too would this new land. And as long as this new land endured, so too would Nog\mbox{--}Nandh. It was not absolution. It was Purgatory.
\SomeVSpace
Tírr i’nna n\mbox{--}Óc endured.