\chapter{Minor Fall, Major Lift}

\DatePlace{London}

\lettrine{N}{eville} was tired. He was always tired when he came home from work. His job was physically and mentally draining, and he was glad to be home. From the other side of his flat, he could hear the tinny sounds of music; he left his radio on. He did that, from time to time. He made a beeline for his study as the music wafted slowly through the air.

\song{…Pass me that lovely little gun,\\my dear, my darling one,\\
the cleaners are coming, one by one,\\you don’t even want to let them start…}

He thumbed through several bottles in his cabinet, and decided on brandy. He uncorked the bottle, and briefly considered the jigger measure in the drawer. Naw. He’d just eyeball it. He started pouring the liquor into a glass which had dutifully filled itself with ice. Glug. Glug. One finger. Two fingers. Three fingers. Four.\SmallVSpace

He reckoned that it wouldn’t do to just drink it straight, so he added a little splash of fizzy water. He didn’t want to bother cutting up a lemon, so he fished a cherry from a jar in the icebox and plopped it into the cocktail. He stirred the drink with his finger, and sat down in his armchair.

\song{…they’re knocking now upon your door,\\they measure the room, they know the score\\
They’re mopping up the butcher’s floor,\\of your broken little hearts…}

He was already almost halfway done with his drink before he was really even consciously aware of it. His mind was elsewhere; he was thinking about his path and where he would go next. What do you do \textit{after} you’ve won?

No one ever told him that vengeance didn’t feel like it does in the books. In stories, all you get to see is that moment of beautiful catharsis. You pump your fist and cheer as justice is meted out, and you feel nice and warm inside. The stories don’t show you how things end after the ending. They don’t show you the ‘happily ever after’. Neville wondered if he would ever have his own ‘happily ever after’.

\song{…O’ children….\\Forgive us now for what we’ve done,\\it started out as a bit of fun\\
Here, take these before we run away;\\the keys to the gulag…}

He didn’t feel nice and warm inside. It felt good, for a moment. She deserved what she got, despite everything Harry had said. The fact that she used to be such a sweet, nice girl didn’t change anything. No tragic origin story would change anything. She did what she did, and for that, she deserved to die. It was as simple as that. But her death, that didn’t make a difference either.
\SmallVSpace
His parents were still dead.
\SmallVSpace
He envied Draco. The memory of Lucius Malfoy had been preserved, whole and uncorrupted, written somewhere in the underlying fabric of the world. Frank and Alice Longbottom persisted, their old, pure selves overwritten by these broken, damaged shells. Draco was lucky enough that his father actually died. Draco put his faith in Harry, and Harry delivered.

\song{…O’ children, lift up your voice, lift up your voice…}

He was finished with his drink by this point. He was crunching the ice and pondering why the world was the way it was. Why did it have to be this way? He walked over to the wet bar, and fished for a different bottle to refill his glass. No pretenses this time, just straight vodka, poured over the melted ice, sloppily filled to the brim. He stared at himself in the mirror mounted behind the bar.
\SmallVSpace
The alcohol was dulling his senses, but somewhere in the recesses of his mind, two independent, disparate ideas joined together to synthesize an entirely new concept. It was a small spark, but one that caught Neville’s attention, and he would not let it be extinguished. As he watched himself, he saw tears begun to fill his eyes and break free to drip down his cheek. But these were not tears of woe, or self-pity. They were the angry, hot tears of resolve.
\SmallVSpace
Why did the world have to be this way?
\SmallVSpace
Something about Harry’s endless, pedagogic lectures had clicked into place. Harry and Hermione had challenged everything that Neville knew about the notion of death. When Hermione returned to the world of life, it shattered all the rules. But for some reason, Neville had just invented his own arbitrary rules to replace the previous ones. But why those rules?

There really was no reason the world had to be the way it was. There was no reason why he couldn’t reach back into the depths of Time and recover his parents the way they were, \textit{the way they should be}. That would be his true revenge; he wouldn’t be content with merely striking down a bishop. He would mate the Black King himself.

\song{…O’ children, rejoice, rejoice ….}

He dumped out his drink, and turned on his heels. He didn’t even pause to turn off the radio or wash the ice out of the sink. He had work to do, and there was not a minute to be lost.
\simpleline
%\SmallVSpace
\DatePlace{Malfoy Manor}

Draco sat in his study, alone, scribbling notes on a parchment. The room was illuminated by a few torches, sunk into the walls, and the flickering silver light of his Patronus, idly slithering around his desk. The war was over, and they had all but won. The rest was just a formality. A few political maneuverings, but it would be done. This chapter in their tale would be over and they could rebuild a world, united.

It felt late, even though the night was only just beginning. The Muggle radio program detailing the day’s news had ended. It told tales of terror and war across the world, a world driven temporarily mad, but a world restored. They were rebuilding, just as Draco was. The news had given way into a selection of various pop songs, but Draco didn’t bother turning it off.

\song{…Here comes Frank and poor old Jim,\\they’re gathering round with all my friends\\
We’re older now, the light is dim,\\and you are only just beginning….}

Something Harry told him once had stuck in his head for years. It was when he was retelling the story of his final confrontation with Lord Voldemort. Something that Albus Dumbledore had told Tom Riddle: “Anyone who can bring themselves to act the part of Voldemort, is Voldemort.”

He had been playing the part of a monster for almost half a decade now. He’d played the part of someone who was actively opposed to life, someone who championed stagnation, entropy, and death. The mask he wore was not false, it drew upon true emotions that lurked deep within him, emotions that he had to actively seek to repress. He could not lie to himself; there was a strange sense of freedom when he let those feelings run rampant as part of his act.

\song{…O’ children…\\We have the answer to all your fears,\\it’s short, it’s simple, it’s crystal clear\\
It’s round about and it’s somewhere here,\\lost amongst our winnings…}

This was why he enjoyed the company of his Patronus. It served as a reminder, an assurance, a touchstone of sorts. The happy, life-affirming memories still existed. There was enough Good inside of Draco to be able to produce the soft, silvery light that now cast an otherworldly shadow across the desk as the radio continued to hum across the otherwise silent room.

He knew what Harry would say. Harry would tell him that you can’t be your own barometer of goodness. Harry would say that everyone is the hero of their own story, and of course you are going to think \emph{you} are doing the right thing. Otherwise, why else would you do it? Draco knew that this was true, of course. But the Patronus comforted him nonetheless.

Draco looked up at the torches on the walls. He snapped his fingers, one by one, and the torches extinguished. The only light left in the room was from his Patronus, which slowly reared her head up to look at him. It was like staring into a crackling fireplace; the swirling, fractal forms of mist and shadow that undulated beneath the form of the snake… It was almost hypnotizing.

“Am I a good person?”

\song{…O’ children,\\lift up your voice, lift up your voice\\
O’ children, rejoice, rejoice…}

He knew it was a silly thing to ask. But no one was around to hear him. The Patronus seemed so… sentient, as it looked up at him. Draco knew, though, that it wasn’t his own judgment that mattered. Because Harry was right. He needed someone on the outside, someone to serve as a sounding board, not an echo chamber. He lay his head down on the desk.
\SmallVSpace
After a time, he raised his head back up to face his Patronus, who was still looking at him in that odd sort of way. As Draco’s mood shifted, the Patronus began to flicker and dull, then dissolved into a mist that hung in the air. No. He would not let it extinguish. Not now. This was too important. His eyes welled with tears; these were not tears of woe or self-pity. They were the angry, hot tears of resolve.

He grit his teeth, and he fought, he thought about everything good, everything happy, everything worth living for, and fighting for. The mist did not dissipate, but it did not regenerate. He continued to pour his heart and soul into that mist, desperately trying to keep what it represented alive. After a time, the mist began to coalesce back into a corporeal form.
\SmallVSpace
It had regenerated itself… as an \emph{otter}?

\song{…The cleaners have done their job on you,\\they’re hip to it, man, they’re in the groove\\
They’ve hosed you down, you’re good as new,\\they’re lining up to inspect you…}

That was… Odd. He had never seen it do that before. It was not unheard of; people’s Patronuses often changed forms in response to their masters’ emotions. The otter swam playfully through the invisible water that was the air in the room. It darted around Draco a few times, and then swam up to eye level, and whispered a single word.

“Draco…”

Draco’s heart stopped. That was not the voice of his Patronus. That was… It was her? His Patronus darted forward, into Draco’s chest, filling him with a beautiful, ethereal light. He didn’t understand what was happening. But then again, did he need to? Somehow, although he didn’t know what it was, or how it would work, somehow he knew that this silver light would take him to the place that he needed to be.\\

He stood up, embraced the light, and disapparated with a dull POP.

\song{…O’ children, rejoice….}
\simpleline
\DatePlace{The Tower}

Harry was type, type, typing away at the terminal. His eyes were sunken and bloodshot. He had been at it for almost twelve hours straight. There was so much work to be done. He had returned, of course, as Hermione knew he would. He and the Professor had accomplished much, but they needed some sanity checks, some way to ensure that the results were reproducible outside of their sandbox.

There were so many projects, both near-sighted and far, so many weak links that needed to be strengthened, so many crossroads that still terminated with him at their crux. There was the physical aspect, the biological, the mental, the metaphysical, the logical, and countless more. There were so many facets of this gem that needed polishing.
\SmallVSpace
Currently he was working on the problem of self-contained recursion. He had cracked it years before with respect to a relatively simple system. Magic was simple at its heart, although it had grown to something mind-numbingly obtuse. It was easy enough to simulate a large physical system. You could track the path of a thrown ball, or the behavior of water through a pipe under pressure, or the melting of ice, and so on, and so forth. But simulating physics, true physics, with enough precision to accomplish his goal? It just wasn’t conventionally possible. He needed to cheat.

But it seemed like the universe did not want him to cheat. It wanted him to die, the good old-fashioned way. To keep running until everything ran down and then fold up into a great, empty Nothing.

He would not do that, of course. He would continue to fight.

He fought for hours today, and didn’t even notice as morning rose into midday, and midday waned into evening. He didn’t notice the sounds of the radio in the corner, or the sharp pop that reverberated from the Receiving Room moments earlier, or the soft rapping at the door to his office.

\song{…Poor old Jim’s white as a ghost,\\he’s found the answer that we lost\\
We’re all weeping now, weeping because,\\there ain’t nothing we can do to protect you…}

The rapping grew more insistent. “Enter,” he spoke.

The door opened, and Hermione walked inside. “That’s a rather rude way to greet your guests, don’t you think?”

Harry was distracted, and he didn’t look up. He was still staring at the innumerable lines of code that filled his screen. “Huh? Oh. Yeah. Sorry. Uh… Hi Luna.”

Hermione coughed. “Hello, Harry.”

He looked up, embarrassed. He stammered a weak apology, and turned back to the computer. She looked around the room, distantly considering everything. She had a soft, peaceful smile on her face as she watched Harry work. He continued to type, type, type away as she stood, silent. Eventually, he became self-conscious of her presence, and the typing slowed, and eventually stopped, as Harry turned around, expectantly.

Hermione said nothing. She walked to where Harry was working, leaned over, and turned off his computer monitor.

“Hermione, wha\mbox{---}”

She took his hands, and pulled him up from his seat. Even though the gesture was purely symbolic, it did have an effect. Harry felt, in some distant way, like he was carrying a great weight around his neck. With the monitor switched off, he felt that the weight had been temporarily lifted. He looked at Hermione.

She still said nothing. Harry looked tired, so very tired. So very tired, and so very alone. He had been in a solitary prison of his own making, both literally and metaphorically, for many long years. Hermione smiled distantly at the soft music echoing from the radio.

“This song does seem out of place, doesn’t it?” She remarked.

\song{…O’ children, lift up your voice, lift up your voice…}

She held both his hands, and took a step backward. She started to sway her shoulders back and forth in time with the music.

\song{…O’ children, rejoice, rejoice…}

She cocked her head at Harry, who reluctantly joined in. They held each other’s hands, moving in an awkward little dance. It reminded him a bit of the bumbling fourth-year students that he watched at the Yule Ball so long ago during his first year at Hogwarts. Harry didn’t dance, no one ever taught him, and he certainly had no experience or occasion to practice.

Hermione didn’t seem to mind. She lifted one of his hands up, and spun him.

\song{…Hey little train, we’re jumping on,\\
the train that goes to the Kingdom\\
We’re happy, Ma, we’re having fun,\\
and the train ain’t even left the station…}

He laughed, silently, as they waltzed around the room, sometimes falling completely off-beat with the music which had started to pick up in tempo a bit. He felt guilty, though. This was time he could be spending working, but he was wasting it on frivolities. Hermione seemed to sense this shift in Harry’s emotions, and pulled him closer.

\song{…Hey, little train, wait for me!\\I once was blind but now I see\\
Have you left a seat for me?\\Is that such a stretch of the imagination…}

He couldn’t abandon his quest to save the world. But then again, wasn’t she part of that world? The enormity of it all, of the path that lay before him and the path that he had already walked down, seemed to crash in on him all at once.

What was he going to do?

He did the only thing he could think to do, and buried his head in her shoulder and began to cry, softly. They weren’t tears of woe or self-pity. They were the angry, hot tears of resolve. He felt Hermione’s hand on the top his head, patting his hair gently. He was a soldier in the war. An important soldier, but a soldier nonetheless. And no soldier can fight on the front lines twenty-four hours a day.

\song{…Hey little train, wait for me!\\I was held in chains but now I’m free\\
I’m hanging in there, don’t you see?\\in this process of elimination…}

He gave in, temporarily surrendered himself to this brief moment of respite. He knew, in his heart of hearts, that he would never give up the battle, that taking one break to have one silly dance would not be the end of the world, and that, it might, in fact, make the world better in its own special way.

\song{…Hey little train, we’re jumping on,\\the train that goes to the Kingdom\\
We’re happy, Ma, we’re having fun,\\it’s beyond my wildest expectation…}

They continued to shuffle back and forth to the music, their heads on each other’s shoulders. They held each other as the music and began to slowly fade away. The tears were gone.

\song{…Hey little train, we’re all jumping on,\\the train that goes to the Kingdom\\
We’re happy, Ma, we’re having fun,\\and the train ain’t even left the station…}

The music faded out, and Harry and Hermione separated, looking at each other, so much unsaid, so much that did not need to be said.

“Hermione, I… Uh… Thank you for that. I feel better. I really do.”

She smiled. “I know, Harry.” She leaned forward and planted a kiss on his forehead. “That’s what friends are for. Don’t you ever forget that.”