\chapter{A Million Same}
\DatePlace{Alderney\\
June 13, 1334, C.E.}
\lettrine{N}{ell} cackled, despite herself. Was it really this easy? It was, wasn’t it? All it took was a bit of theater, a cheap trick to smoke that fat oaf out of his hiding spot. Well, not that cheap. It had taken the assistance of a pair of ridiculously powerful pair of artifacts, but still. It was amusing: the Elder Wand was, in terms of raw power, the most powerful of the Hallows. But offense can only take you so far. How can you kill a ghost? How can you spot what remains unseen?

The church was laden with counter-jinxes and dark detectors. Had she cast any sort of magic within their radius of effect, it would have immediately revealed her location along with removing a large majority of the protection provided by the Cloak. But she didn’t need magic: she had a thick, leather sap filled with lead which would do the trick just fine. And it did, quite handily. A sharp crack to the base of the skull dropped “Hugues de Payens”, along with his defenses, in an instant. The Elder Wand clattered to the floor, and sparing no time for dramatics, she quickly scooped it up and Apparated away.
\simpleline
\emph{…Ignotus was sad. She was young, too young to understand the mantle that had been thrust upon her. He saw the unbroken chain of causality that stretched from eternity into eternity, illuminating the path that she must follow. He saw her, awash with sadness, grief, and the weight of the world. He saw the sadness, clarified into white hot anger. He saw her slashing, thrusting angrily, violently against a foe much older than herself, much more powerful than herself. He saw her dismantling defenses, only to have those defenses rebuilt. He saw her gain no purchase-}
\simpleline
\DatePlace{Minutes earlier}

Cadmus cackled, despite himself. Was it really this easy? It was, wasn’t it? He was still relatively young by the standard of functionally immortal wizards and witches, but he was startled by how reliably people tended to play to expectations. And this girl, this child had done so marvelously. Cadmus had long known that he needed to pass it down to a new owner, and he had already done so with the Cloak and the Stone. But the Wand could not be gifted, it had to be earned. And who more worthy to possess it than the next Master of Death?

After all, only one who had claimed the Cloak and understood its properties could pass through his wards, unaffected. And only someone who had claimed the Stone and understood its properties would be capable of sending the proper message via the proper messenger. Ignotus had laid down in the Keep of Mysteries his contribution to the Great Prophecy; he spoke of the Path of the Scorpion and the Archer, the road that the two-faced God must walk. And now Ignotus existed only in that place beyond Time, a place where all prophecy was true.

The Master of Death had sought him out, and he had deemed her worthy.
\simpleline
\emph{…Ignotus watched the young woman’s duel with the witch in the green dress with curiosity. It was a strange thing. Curses fell useless against the witch’s shields, which barely glowed a gentle silver as they absorbed one curse after another. And the ancient witch’s attacks found no purchase, for the Elder Wand moved of its own accord, assisting its true owner, obliterating magics as if they were a child’s whisper-}
\simpleline
\DatePlace{Minutes earlier}

Ever since a young age, Nell had exhibited quite a knack for recognizing just how good was “good enough.” Like most disciplines, you could learn much of what any given magical subject had to offer in a very short period of time if you only directed your studies appropriately and actually applied yourself. Most people did not, and so Nell was able to quickly outpace “most people” at just about anything.

After her first year or two at Hogwarts, when she had risen meteorically through the academic ranks, she had simply thought that everyone around her was stupid. And indeed, if you equated intelligence with winning, then most people certainly were. But that was a rather antisocial attitude, one that tripped up many of her Ravenclaw classmates. No, it wasn’t that people were inherently stupid or irrational, it was just that their potentially was yet to be tapped.

She had thought that she should become a teacher, but she considered the fate of Elijah Solomon, the old professor at Hogwarts who taught the N.E.W.T.-level class, “Existential Threats”. It was a class that attracted little interest these days, for the world was in its prime. Most of the students were those who already followed his teachings: he had dedicated much of his life to spreading the gospel of Rationality.

He was a modern-day Prometheus, and what was his reward? His peers left him to drown in an ocean of derision. A sneer, it seemed, was equally as damning as a well-reasoned argument. The world, it seemed, did not wish to stand tall, for when you do, that is when you are most visible, most vulnerable.

Nell knew a lost cause when she saw one and determined that teaching was simply not for her. Instead, she would lead by example and simply serve as a living role model. To reach that point, she simply got as good as she could get at as many disciplines as possible. Once she reached the point of diminishing returns, she would move on to a new subject.

Although initially, she was merely a jack of all trades and a master of none, as time went on she was able to weave her skills and knowledge in with one another, producing unconventional yet highly effective solutions to problems that a more singularly focused expert would never consider.

Part of what made this process so easy was that, although magic was highly opaque, it was also highly functional and robust. One could spend the better part of a decade researching and examining the True Cloak of Invisibility, determining how to was created, how each material and fiber lay with relation to the other, and so on and so forth.

Or, she could spend the lesser part of an afternoon messing around with her best friend and figure out 90% of what she needed to know in order to take down one of the most powerful wizards in recent history. Knowing “why” something worked was exponentially more difficult and exponentially less useful than knowing “how” something worked.

It was with that in mind that she set about trying to determine the properties of the Spirit Stone. She had made it a point, when doing research of this nature, to attempt the most hopelessly optimistic outcome first, just in case it worked. For example, if the Spirit Stone could truly call forth a sufficiently high fidelity reproduction of any person who had ever died, ever… Well, that would basically make her a God, and today would be Judgment Day.

Although things were sometimes that easy, this time, it wasn’t. It seemed that she needed to precisely identify who she was attempting to call forth. So she tried several iterations of summoning, attempting to determine precisely where the outer boundary began. But she knew in the back of her mind that she was simply stalling the painful but necessary test that she would have to perform at some point.

Rather than flinch away from it, she embraced the pain, and rolled the Spirit Stone over in her hand thricely, summoning forth the spirit of young Elizabeth du Marais.

Even though she was prepared for it, she still felt it as a blow in her gut, a visceral, heart-rending pain as the perfect, unbroken spirit of her little Babette coalesced from the ether and looked her.

“Nell?” She was disoriented and rubbed her eyes.

Nell had told herself that she wouldn’t cry, which was stupid, because how could she not? Her vision was already blurry. “Babette. Babette, love, it’s me.”

“Nell? Where are we? What happened?” She ran towards Nell and tried to hug her, but she passed through Nell’s body and was able to hold nothing. Elizabeth’s eyes widened. “Oh, no. No, no. No, no, no, no, no…”

“Babette…”

“No, no. NO, NO, NO! Nell, no! Am I dead? I don’t want to her dead!” Her voice grew panicked, frantic. “Where are mama and papa? I want to see them. Please, Nell, help me! Please don’t let me be dead!”

Nell couldn’t respond. The tears had choked her words and clouded her vision and her mind.

“Help me, please. Please! I don’t want to be gone. Take me back. Bring me back. Help me, please, please, please, please!”

Nell didn’t know what she expected. Of course it would be this hard. She needed to take back control. She needed her protection against the sadness of this broken world. She surrendered her mind to all the things that made her angry, that made her rage, that made her hate. She thought about the world’s cavalier acceptance of death, about the indifference that humanity showed to this wholesale tragedy, how mankind was so terrified that they would rather embrace death as a friend than fight it until the bitter end.

Waves of hot anger rushed over her, dulling her senses, forcing out all other emotions. The world crystallized in front of her, and she saw her delicate, pure, perfect sister falling victim to the same fear, the same cowardice.

“BABETTE. LISTEN TO ME!” She shouted. Babette stopped crying. She was on the ground now, curled up, still sniffling, but at least she was silent. Nell continued. “I am going to save you. I’m going to save you and Mama and Papa and everyone. But I need you to help me. I need you to be brave. Can you do that for me? Can you be brave?”

Babette nodded with a weak sniffle.

“Good. I need to know the last thing you remember.”

She thought for a moment. “We were playing. Playing near the river, the one that Mama had warned us about. I fell in…”

“Yes, but how? I was climbing our tree and didn’t see you, or hear you fall in. What were you doing when you fell in? What happened?”

Babette’s spirit screwed up her face in thought. “I… I don’t remember. I think I was dipping my toes in the water… But I’m not sure. Why don’t I remember? Nell, what’s happen–”

Babette was starting to lose it again. “Hush, it’s okay. That’s normal,” Nell lied. She thought quickly, she needed something to verify her hypothesis, something to confirm her fear. After a moment, she had it. “Okay. Your diary, do you remember that?”

“Mm hmm.”

“You told me that you had given it a name, but that name was a secret. You said it was a silly name, and that one day you’d tell me and I’d laugh, but that it was your secret for now. Do you remember that?”

“Yes…”

“What was the name?”

“Oh! It–” Babette’s eyes widened. “I… I can’t remember. It’s right there, on the tip of my tongue but…”

“Never mind that. Think of the last thing you and I were apart. When I was at Hogwarts. Tell me something, anything you remember, when it was just you and Mama and Papa.”

“I can’t. Nell, I can’t. I don’t remember any of it.”

Nell sighed. This was confirmation enough. She didn’t know how much more she could take. She immediately dismissed Babette’s spirit. It wasn’t her, not really, so she didn’t want to inflict the pain of a long goodbye upon herself.

Okay, so, at face value, the Stone produces a Ghost. Whatever it called forth was shaped by the owner’s memories, expectations, and thoughts. But somehow, it was linked to the world of Life and Death, for it would only call forth the spirit of someone who was truly dead. She tried to call forth the spirit of fictional characters, or those she knew for a fact were alive, and nothing came.

That alone represented a treasure trove of information. She could verify the historicity of any person from history, or determine the precise moment of death of any live person. But that aside, the stone clearly drew from a source of information outside of Nell’s own mind. If the Stone fit the pattern, as so many magical things did, there was a fighting chance that the knowledge was somehow linked to the previous owners of the stone. Unfortunately, she didn’t know much of the Gaunt family tree, so she decided to go straight to the top and try to summon the spirit of Cadmus Peverell.

Huh. Nothing.

That was strange, though not altogether shocking, that the Peverell Brothers were simply a myth. Even though the legend was still fairly young, stories had a way of spreading out of control over the span of a few generations. Unless…

She focused her mind on the name of Antioch Peverell, and called him forth from the abyss.

“That’s my brother’s ring,” the spirit spoke, immediately.

Nell was cautious. There were a lot of implications here. “Yes, yes it is.”

“Taken, or given?”

“Given.”

He grunted. “Yet you are no blood of mine.”

“No, I am not. It was loaned to be by the descendent of Celia Peverell Gaunt, by way of her cousin, from the Ollivander-Nott family.”

At this, Antioch’s ghostly expression softened. When he spoke, it was almost wistful. “Little Celia. She was barely a few months old when I had passed.”

“Oh? Would you like to see her? I can call her forth…”

“No need, I just did.”

“You– ah.” Nell faltered. “Yes, you’re dead. Space and time, I’m guessing they don’t mean much to you.”

“No, they don’t.”

“Well, as long as you’re here, do you mind telling me how you died? Legend has it that you slew a wizard with whom you once quarreled, and that night your throat was slit by someone who sought to claim the wand for themselves?”

Antioch considered this and smiled grimly. “Yes, I suppose that is true.”

“Who was it? Who now possesses the Elder Wand?”

“I’ll tell you no more than I already have, and if you knew what was best, you would ask no more, either.”

She ignored the veiled threat. “Tell me about your brother, then. Cadmus.”

At this, Antioch jerked reflexively, but immediately composed himself. “What of him?”

“He was real?”

“Of course he was real. What are you playing at?”

“He’s alive.” Silence. Long silence. Both their minds were racing. Antioch’s lack of a response was damning, and Nell connected the dots, coming to a realization that she probably should have come to long before. She began to speak, slowly. “Your family… You came from Alderney, didn’t you? Small place. It’s where I’m from, you know. You know, I think I might just take a little trip home. Visit the sites, you know? You enjoy your rest, now.”

With a flick of her hand, the white mist that made up Antioch’s spirit dissipated immediately, as did the form of Nell, who had Apparated to away to her native home of Alderney, to confront Cadmus Peverell.
\simpleline
…Ignotus watched, trying to remain impartial as the battle raged on beyond the veil. They were both glorious in their puissance and beauty; one a vision of natural beauty, keen intelligence, an almost childlike innocence. The other was an earthly Goddess. He saw how the girl-child closed the distance, and they fought. Spells fell on shields. Spells fell on wand-wards. The duel was a storm without wind.
\simpleline
\DatePlace{Minutes later}

The power that was coursing through her was palpable and begged for release. The Wand had glowed reluctantly and dimly in reluctant recognition of its new master. She had been taught that wands had personalities, and if this was the case, she had a distinct impression that this particular wand would be rolling its eyes and sighing dramatically, as if to say, “You? I’m stuck with you?”

Only for a little bit. I have a job to do. After I’m done, I won’t need you anymore, and you’ll be free to seek out a new, more bloodthirsty master.

“Fair enough. Then you should Apparate, that would be the fastest way to get there.”

What, like, to the front door? You can’t Apparate into Hogwarts.

“Don’t be stupid. Use the Cloak. Apparate right into her room.”

Umm… Are you sure that the Hogwarts’ wards won’t–

“One of us is a 16-year old witch, and another is the intelligent, anthropomorphic representation of a centuries-old object of immeasurable power. Of course I’m right.”

Yeah, but she’ll be waiting for me.

“Yes, I know that. You may as well have written a letter telling her when, where, and how you’d be going after her.”

So how do I get the drop on her?

“She won’t be expecting you to just appear right in front of her. Once you do, just leave the rest to me.”

I don’t want to kill her, you know that, right? Her powers, her information, they’re no good to me, dead.

“Yes, I know that, idiot girl. I’m a projected figment of your imagination, how would I not?”

I thought you were an intelligent, anthropomorphic representation of a centuries-old object of immeasurable power.

“Look, I… You know what? Times up. Let’s do this.” The Elder Wand screamed into action, dragging her almost unwillingly through time and space, directly into the office of Baba Yaga.
\simpleline
The quality of the air changed slightly. Nothing altogether noticeable, but when you were this old, there was just something about the underlying pattern of the universe that seemed different when a specific volume of air is replaced by an equal quantity of an invisible, unseen intruder.

Perenelle.

The intruder was not just invisible, but truly hidden. There were only one or two extant objects of power in the Wizarding world capable of doing this, one of which was conveniently located here at Hogwarts. It didn’t take much of a leap of faith the deduce the identity of the intruder.

Baba Yaga knew that Perenelle would not dare attempt an outright attack unless she was protected, and unless she had a weapon. If she possessed one Hallow, it was not unreasonable to expect that she now possessed the others. The only unknown was how she planned to handle the protection of the Cup of Dawn. Would she try to bait out an attack so as to force Baba Yaga to forsake its protection? Or would Perenelle simply go on the offensive, abandoning her own protection?

The latter was simply suicide, and because the two courses of action were mutually exclusive, it was simply more prudent to wait than to strike first. Baba Yaga’s magic radiated outward, passing unperturbed, for the most part, through Perenelle. However, because Baba Yaga had the well-founded suspicion that she was somewhere in this room, a small fraction of her magic returned to her with useful information.

With that information, the well-founded suspicion became an educated guess, which in turn increased the power of her magic, which in turn confirmed that educated guess, and within moments, she could sense precisely where Perenelle was hiding, invisible.

It was right behind her.

An invisible hand reached out. Baba Yaga had an eternity to practice the concealment of her emotions, her thoughts, her suspicions, and to the outside world, it appeared that she was doing nothing more than reading the notes on her desk. But she was ready.

somebody shouts a word

In an instant, she felt a hand on her shoulder and heard the first breaths of a syllable. Faster than what should have been possible, she slapped the hand away from her shoulder, and with a concussive burst of magic, sent Perenelle flying across the room.

New calculations were made, scenarios simulated, probabilities weighed. This child was seeking to incapacitate, to plunder her mind for secrets, rather than to kill. Nell had charged, wand raised, already casting. Baba Yaga sneered, raising her own hands, and lighting surged between them.

The Elder Wand took it from the air.

The song of the Wand was a hymn of worship in reverent supplication to the holy purity of battle, purging the wrongs from the world and extracting the rights by force, if necessary. It led her to that one singular goal: close the distance.

The battle was a storm without wind. Nell would have been dismantled in an instant, if not for the protection of the Elder Wand, augmented by the knowledge provided by the Spirit Stone. An important lesson of Battle Magic was that even the greatest artifact can be defeated by a counter-artifact that is lesser, but specialized. And indeed, that was the purpose of the Deathly Hallows, specialized tools designed to neutralize, overpower, and overcome the anchors of the Old Gods, those last remaining representatives of Death that needed to be cleansed from this world in order for it to be saved.

Merlin had known when he led the Peverell brothers down this path, that one day even he would fall to this weapon, and he was prepared for that. He would be the last, of course, but he too was made of Magic. He was Magic, and Magic was him. The Line must be broken eventually.

But for the time being, those tools were being turned against Maximillian Koschey, the last remaining Old God that still possessed any capacity for meddling.

Adnan Nejem, Nog-Nandh of the Flame, had willing surrendered in his grief, and now endured as the binding essence of Tír inna n-Óc. When the time was right, that place would be unbound. And Dexter Charles, Shiggoth of the Spire, the Gate that Knows the Gate, he was an impotent, sleeping God who was omniscient yet impotent. His only remaining power was derived from his mortal servants, who were crippled by the Interdict. Soon enough, in a few centuries time, he would be gone for good.

The Battle of Olympus had taken care of most of the rest. Natalie Kyros and Constantine Atreides, the star-crossed lovers and lab partners, had willingly banished themselves, leaving the tools of their craft for the ants to play with. And Janus Tucker, Christopher Chang, and Kayla Rahl had eliminated each other in a stand-off, sacrificing portions of their anchors. The Cup of Midnight was lost, leaving only the Cup of Dawn. The Mirror of Volition had shattered, leaving only its reflection. And the past and the future were lost, leaving only the present Box of Orden. These artifacts had been scattered, but conveniently now were consolidated within the confines of Albion.

That left only Maximillian Koschey, Ma’krt of the Rock, Koschei the Deathless, Baba Yaga, and a thousand other names. With his Stone of the Endless Song, his Emerald Heart, he could arbitrarily change the form and substance of anything within its sight. But even that ultimate power was disrupted by the combined effects of the Deathly Hallows, when wielded by a Master of Death.

And so Baba Yaga was forced to fight Perenelle du Marais using mere mundane Magic; not the deeper, true magic of Atlantis, but the absurd, arbitrary, nonsensical Magic of Merlin’s Line. She was a master swordsman forced into a knife-fight. The same principles applied, but much of her superlative experience was inapplicable.

But she would not be overcome. Spells fell on shields. Spells fell on wand-wards. But Nell could gain no traction against the witch in the green dress, who evinced neither strain nor dismay.
\simpleline
\emph{
“Foolish monkey,” said the witch, her words punctuated by the wordless thrusts of her hand which sent green light and burning flame and sharp crystal cascading into the Goddess’ Wand-borne defenses. “Didn’t you know there was only ever one outcome, here?”
}
\simpleline
“Foolish monkey,” said the witch, her words punctuated by the wordless thrusts of her hand which sent green light and burning flame and sharp crystal cascading into Nell’s wand-borne defenses. “Didn’t you know there was only ever one outcome, here?”
\simpleline
“I did,” said the Goddess, panting. “And so now would be good, gentlemen.”

She lashed out at the witch with every ounce of belief and faith and grief, and the enemy’s wand glowed bright under duress. The Goddess’ other hand landed like a titan’s hammer immediately afterwards, a crushing blow dealt with a troll’s strength.

At the same instant, there were two sharp cracks, almost simultaneous. Twin gunshots, fired from above.

The first rifle shattered the witch’s shield. The second passed through her stomach.

Perenelle du Marais screamed, and it was loud, at it was long.
\simpleline
“I did,” said Perenelle, panting. “And so now would be good, M’lady.”

And without another word, Nell dropped her defenses. The crystals lashed across her face, spraying droplets of blood onto the floor, and in that instant, Baba Yaga understood Perenelle du Marais’ gambit and understood that she had lost.
\simpleline
It was time. After an interminable moment, the ancient witch in the green dress, gutshot and dying, succumbed to her wounds. Her spirit, previously so fuzzy and indistinct on the other side of the veil, was now crisp, sharp and clear. She shook off her disorientation.

“Is it time?” she asked Ignotus.

“Yes, I think so.”

Together, they watched another scene, this time, of a seventeen year-old Perenelle, fiddling awkwardly with the Spirit Stone, outside the abode of Cadmus Peverell. They stared intently as the hole in the world began to open, and waited as she reached into this Timeless place, under the protection of Ignotus’ cloak. She was blind to her future-ghost. She was blind to everything that the future held for her. They were Hidden by something much more powerful, much more fundamental than a mere trinket.

She called to Ignotus, and he was compelled to follow, carrying with him the eternal words of prophecy.
\simpleline
The flames in the Goblet of Fire roared, overtaking the room. In a blinding instant, Nell had charged forward, and Baba Yaga, stripped of even her mundane magical defenses, could do nothing as Nell reached out, touched her shoulder, and shouted a word.

Egeustimentis

The world shuddered.
