\chapter{The Battle of Hogwarts}

MORPHEUS: I am a world, space-floating, life-nurturing.

CHORONZON: I am a nova, all-exploding… planet-cremating.

MORPHEUS: I am the Universe — all things encompassing, all life embracing.  

CHORONZON: I am Anti-Life, the Beast of Judgment. I am the dark at the end of everything. The end of universes, gods, worlds… of everything. Sss. And what will you be then, Dreamlord? 

Neil Gaiman, The Sandman: Preludes and Nocturnes

\simpleline

\DatePlace{Hogwarts\\
1107 C.E.}

\lettrine{T}{here} was no hope.

How could there be? Lord Foul had thought of everything. Although Ελαολογος was older, she was no warrior. She was an artist, a creator of things. She was Life, and at the fabric of her world was woven in such a way that all life must end.

He, on the other hand, was Death, destroyer of worlds. He commanded vast, terrible armies. He cast visions into their mind of the Tarrasque razing the beautiful city of Estremoz, making sure that every exquisite scream echoed within their souls. The wail of every mother, watching their children’s broken bodies chewed and crushed by an unfeeling, dispassionate beast. The shrieks of anguish as men lived their last moments in abject, blinding pain and misery. An unending windmill of horror sliced through their minds, blade after blade after blade.

And they had not even battled him yet; they were still fighting their way through his creatures, his pawns, his proxies. The king was well protected. It was only through barest of chance, dumbest of luck that they managed to turn away the dozens of snake-creatures he had at his command, creatures that could seemingly turn men into stone with but a glance.

Scores of armored defenders had been turned into statues by the gaze of these unknown beasts, but even in death, their stone form had been put to use. With a quickly improvised ritual, Rowena Ravenclaw imbued the statues with a small measure of her life force, then animated them:

“Piertotum Locomotor!”

Hogwarts was under attack, and they rose to defend it. But even then, the only tactic that seemed to be of any effectiveness against the creatures was distraction. Once they realized that their gaze could not affect the stone defenders, they simply stopped engaging them and slithered past to attack the defenders behind them. The golems continued their defense, but it had little effect.

In desperation, Professor Kaspersky sent out a burst of light and sound in order to distract them, draw their gaze away. It seemed to work, momentarily; the basilisk could not initially differentiate between the harmless lights and the bolts of deadly magical force. As such, the Professor continued the assault, burning through memory after memory, drawing on every experience in his past in order to distract them, forcing them to divide their attention between the true and false attacks.

He was reaching the point of diminishing returns. With each successive burst, it held their gaze for a shorter and shorter period of time. It would not be long before they ignored it entirely and resumed their attack with full force. Had it not been for Rowena Ravenclaw’s keen eye, all may have been lost. With one burst of sound, the basilisk reacted differently. For a moment, they froze, and she could see a brief flicker of fear in the language of their movement.

It was a panoply of sound that the Professor had drawn upon his days on the farm as a youth in order to produce: cows mooing, horses whinnying, donkeys braying, pigs squealing, roosters crowing.

“Do it again, now!” Rowena commanded. The sound echoed forth with doubled intensity, and she began her experimentation. One sound at a time.

Nothing.

Nothing.

Nothing.

Something.

When she broadcast the sound of the rooster crowing, the basilisk vocally shrieked in fear, seizing backward and whipping their coils around to look for the source of the unknown threat. They were confused.

“Daerovan!” She shouted to a nearby Fae, who was casting his glamours outward in pink, crystalline bolts. He and his kind had bound themselves to serve the house of Hogwarts, exchanging their vast, unknowable power for a home and protection, in accordance with the laws of their kind. “Summon the kitchen staff, now!”

He nodded, and with a snap of his fingers, half a dozen Fae appeared. Because they were rarely presented to the public, they did not bother maintaining their physical glamours. They appeared in their natural form: short, lanky creatures with bulbous eyes and floppy, leathery ears. Most were wearing rags or improvised outfits made of tea cozies and such. Rowena shouted, “Do we have roosters in the henhouse?”

Charky, the head of the kitchen staff nodded. “Would it pleases Mistress for me to bring them forth.”

“Very much, Charky.”

With a smile, he waved his hands in an arc, and the roosters immediately instantiated. They were confused, and ruffled their feathers, clucking angrily. The nearby basilisks winced in pain. No longer were they acting in confused fear, they were reacting with abject terror. The ones that were closest spun around, and began to slither away as quickly as their scales would carry them.

Catching on, Salazar Slytherin amplified the sounds of the roosters, throwing the basilisks into disarray. Realizing that the roosters needed more stimulus, he cast a false sun into the night sky, temporary illuminating the battlefield.

The carnage was horrifying. Broken bodies of all manner of magical creatures lay strewn about, discarded. Every surface was slick with the vital fluids of men, goblins, snakes, giants, and other unknown creatures. The grass was matted, compressed. The air buzzed with the sound of chizpurfles, feasting upon the enhanced blood and remnants of magic in the air.

The sun pulsed with power, casting long, ominous, undulating shadows. In response, the roosters began to crow, their calls amplified by Slytherin’s magic. The basilisks were now apoplectic. They wrenched and twisted in pain, shrieking and hissing. They were dying.

“Pleasssssse….. Sssssstop.”

What?

Slytherin had been experimenting for some time with a language that would allow him to lend some measure of his own sentience into a serpent to allow for speech. But his results had largely been in vain.

“Pleasssssee…. Do not wisssssh to die.”

One of the great snakes was talking to him, beseeching him. It had wrapped its coils around its own head in an attempt to drown out the sound. Slytherin responded in the tongue of snakes:

“Tell me, ssssnake. Why do you ssssserve him?”

“Wassss born to him, sssserve him for he threatenssss our young. Pleasssssse.”

“Do you underssssstand me? Are you truly a living mind?”

“Pleassse, ssstop thesssse creaturessss… Do not wisssh to die, have lived ccccenturies, have much lore I can teach you.”

Salazar considered this. It could be a workaround, for the time being. The beast was clearly ancient, possibly even ageless. If it was sentient, and he passed his knowledge down to it, bound it to him….

“Lore like ssssecret to true Horcurxxxxxx…..”

He stopped in his tracks at this. In an instant, he made his decision, whipping his wand in vicious slashes, quickly transfiguring the creature into a rough-hewn emerald, and bade it upward and into his robes.

Rowena stared, open-mouthed at what was unfolding around her. None of this made sense. He could talk to snakes? Snakes are sentient? And why in the name of Merlin would a rooster’s crow be fatal to these beasts? Even by the admittedly lax standards of Magic, this defied reason. How is it that they just happened to stumble upon these invulnerable creatures’ one random weakness. And how is that someone whose last name just happened to be “Slytherin” could speak to snakes?

Waves of terror crashed over her. How could they win? And what if they did? What good was any of this? If nothing in the world made sense, if nothing followed the rules, there was no point. Why not just descend into madness if the rest of the world was mad, too?

“What good is any of this?” She shrieked, roughly grabbing the robes of Godric who was standing near to her. “The world is mad!”

“No, he is driving the world mad. He has been my enemy since my youth, there is something about him, something that brings out the madness in people. Stay strong, there is still a battle to be fought.”

“Why? Why do we fight? Why is this so? He is your fated foe? There are prophecies that brought us together? It’s too convenient! This isn’t a story, this is life!”

“Pull yourself together, woman!” he barked, roughly.

She started cackling. “Pull yourself together! Pull yourself together!” She stared around: fear was thick in the air, the basilisks writhing in their death throes, Salazar looking white in the face as he backed away slowly, clutching the fat green emerald. “You pull yourself together! This is not our world! It can’t be! It’s too convenient! This is a story, a fantasy, a fiction!”

She cackled again, and began gesturing with her wand. “Can you hear me?” She screamed at the reader. “Did you write this?? Is this your doing? Or are you just watching??” She screamed incoherent curses, and with a rapidfire movement of her wand and thricefold repetition of the trigger word, “Az’reth”, she summoned forth a great and terrible raven crafted of dark, bloody fire.

Drops of the living flame dripped from its wings as it bore itself into the air, beating in circles above them. “This world is insane, this story is insane, and I will burn it down! Do you hear me?? I’ll give you a story of ash, and fire, and emptiness! Enjoy your tale of Nothingness!”

At that, she cast the raven upward, and it beat its wings, sending wave upon wave of burning Fiendfyre in all directions, igniting the ground and the air alike. The flame stopped at a certain point in the sky, as if it was meeting resistance. She grinned, “The fourth wall?” she called to no one in particular. She directed all of the fiery raven’s force against the barrier, until it stressed, bent, cracked, and eventually shattered under the force, causing waves of destructive magical backwash to spray back onto them.

As the shield that cloaked the left wing of Lord Foul’s army fell away, they could see something in the distance: three dozen dark, hooded figures, floating, watching them all intently. It was like a dam had burst: the shield had been concealing them, but it had also been restraining them. With nothing to keep them held back, and their master’s promise of countless souls heavy on their dead minds, they charged. They opened their mouths and inhaled the living flame, which flickered weakly and died.

Slytherin stared up at them. “Specters…” he whispered. He turned to his companions. “Summon your Patronuses, now!” Godric blinked a few times. He had never been able to muster enough happiness to summon forth a corporeal Patronus. But Helga Hufflepuff immediately leapt into action, summoning forth a vast, angry badger to join the Lord Slytherin’s bright, silver serpent.

The defenders lifted their heads and watched as the shadows passed from their hearts. The hooded creatures were turned away by the pure life force that stood between them and their victims. The madness was gone from Rowena’s eyes, but she was still shaken. “That… that fool. We shall turn his creations against him.” She attempted to summon her own Patronus as well, but Salazar turned to her.

“Lord Foul is no fool, that much I know.”

Godric nodded with a frown on his face as he studied the battlefield. Basilisks lay slain, their corpses contorted into coils. The Hogwarts Tarrasque was vanquished, imprisoned beneath the Black Lake and left to drown. The Dementors circled high above, kept at bay by the Patronuses of the survivors which had joined the serpent and badger, a menagerie of mist, shining brightly in stark contrast to the darkness above.

The students had long before been hidden within the Room of Requirement, which had expanded to the size of the Great Hall to accommodate their numbers. Portkeys had been arranged for each student, suspended in unreality for so long as the four founders maintained their hold on their magic. If they were slain, rendered unconscious, or deliberately relinquished control, the Portkeys would instantiated, and the students would be transported to safety.

That said, Hogwarts was the safest place in the civilized world, second only perhaps to the Keep of Mysteries. They did not know to what lengths Lord Foul would go to end the perceived threat of Hogwarts; it was entirely possible that he would simply hunt down the students at their homes, where they were defenseless. For now, it was easier to protect the students if they were in a centralized location. If that layer of protection were to fail, they would be dispersed.

There was a lull in the battle. Lord Foul’s shock troops, the disposable magical creatures, the muggles, the Goblins, had put a significant dent in the ranks of the defenders. Although each individual wizard was more than capable of handling multiple threats at once, there were just so many, so many of them. And the true battle had not even begun, for Lord Foul still had his army of men, and behind them, a battalion of wizards.

There was no hope.

And yet, all five of them knew that they were fated to win.

By the ancient laws of combat, the four generals strode to the front lines, having been granted an audience with Lord Foul in person. He stood tall, proud, passionate. His Asiatic features wore his eternal age well. He was not young, but he was not aged. He looked exactly as he should.

For their part, the founders wore their age well. They were all at least a century old, which was basically middle aged by the standard of the time. They stood, defiant, bolstered by the confidence of prophecy and fate, as the Lord began to speak.

“You four, you have been bound together by prophecy. You know as well as I that you will win this battle. And you may have asked yourself, why would I wage such a senseless campaign, knowing that it can only end in defeat. The answer should be clear: in defeat, I shall find victory. It is your choice, however, whether that victory will be over you, or our shared enemy, the last enemy.

“I have seen your heart, Salazar Slytherin, and it is mine, for we share that same enemy. Your face to the world speaks of spreading magic, spreading knowledge, but you simply seek one thing: you do not wish to die. Why must you hide this desire deep within your heart? Why must this be your craven, secret, sinful indulgence? Your desire is heroic. I see how you have studied and pored over ancient lore, and you have even unknowingly sought out me and mine in order to glean the secrets of the Horcrux.

“Yes, you have rightfully identified the key weakness of its common form, and further, you have rightfully deduced that there is a more advanced ritual, the knowledge of which, I am in sole possession. You revealed your true heart when you attempted to tame my creature instead of slaying it, in order to tap into her mind. It was in vain: she knows as much of the secret of the Horcrux as you do. But it seems that she shares your aversion to death, along with your cunning. She fed you a clever lie, and you spared her life.

“You struggle with the reality you are faced with. You hoped that by spreading the light of knowledge, someone would shine a candle into the darkness and burn away the specter of death that looms over you. I tell you now that I am your light. I am that candle. If you end me today, you snuff out the wick, you extinguish your only source of hope. End me today, and my secrets die with me.”

Capture the rook, the King is in check.

“You, Rowena Ravenclaw, you know of what I speak. You know more than any of them the price of knowledge lost. ‘Wit beyond measure is man’s greatest treasure’, indeed. You share a craven desire of your own, one you wish to keep hidden away: to overturn the Interdict. Perhaps that is why you and Salazar shared such a bond… such…. passion. You thought a daughter would be the perfect vessel for preserving your lore, and Salazar, for his part, thought he could train her, put her on the righteous path so that one day she may rise up and conquer the final enemy.”

Slytherin was already reeling from his blow, and Rowena was too numb to react to the exposure.

“Now, now, don’t be prudish. Your companions shared the same passion, but for much less noble reasons. All the same, your heirs not walk the world, and yet you are no closer to achieving your ends. But you have correctly deduced that no magic is without its counter, that no incantation is so binding as to never be undone, that no sacrifice… is permanent.” With a hand gesture, a speck of the air turned pitch-black, and began to coalesce into a single red droplet of liquid, which floated towards Rowena and entered her.

“I return to you a single drop of blood, the price you paid to reveal the Specters of Death. You seek, one day, to return that which Merlin sacrificed, in order to undo his Interdict. End me today, and that secret too will be forever lost.”

The move is forced, the bishop is captured. The king remains in check.

“And you, Godric, I too have seen your heart. I, who have traveled between worlds on the tongues of fire. You know the path of righteousness, your heart is good. You can be redeemed. It might be as simple as thinking of a flame…”

At this, Lord Foul looked into the sky. A star flashed in the night. A faint star whose brightness was slowly, visibly waxing, seeming to grow as well as brightening. It looked closer, suddenly, no longer so far away… A lighted form whose shape you could actually see…

A bird.

A piercing cry split the night, echoing from the rooftops of Hogwarts. Great shining wings, red like a sunset, and eyes like incandescent pearls, blazing with golden fire and determination. The Phoenix’s beak opened, and let out a great caw that Godric understood as though it had been a spoken command.

JOIN US.

Godrich stood paralyzed. This was it. This was his choice. Should he follow the Phoenix? Or…

“…solve the riddle…” Helga Hufflepuff whispered. She looked at Meldh. “And what of me?”

The knight must retreat, the king is still in check. The queen is in danger.

A slow, sad smile spread across his face. “Oh, I believe you know all too well the price.”

She took a step forward, and started directly at him. Ollivander and Meldh stared at each other, the raging Fiendfyre burning around them as the Dementors swirled overhead. He whispered to her, “The choice is yours, as it always has been. You must make your decision, now rise up and do so.”

With tears in her eyes, Ollivander embraced her Hero. It started with a tight, passionate hug, and they separated briefly to look into each other’s eyes, and she kissed him, hard, deeply. Godric watched, as he always had. Hot with anger, he watched, as he always had, as they embraced with lurid passion. He grit his teeth and gripped the hilt of his…

…His sword was gone.

Her left hand was encircled around Meldh’s waist, her right hand running through his hair, roughly. The pointed, patchwork hat atop her head had an oddly shaped lump in it. When she reached the top of his head with her hand, the reached up into her hat, and pulled from in the Sword of Gryffindor, forged by the Goblins from the form of pure War.

“I’m sorry, my love.”

His eyes grew wide, as she reared the sword up in one swift motion and pulled it roughly across his throat. Immediately, blood poured down from his neck as he stared in shock. She followed through with her right arm, pulled back, and slid the sword through his heart. The light left his eyes, immediately.

The connection to life is severed, now to contain the soul.

She was ancient, she had visited the Necropolis at Carthage, she had heard whispers of the Specters of Death, she knew the basic premise of their operation. They conformed to expectations, they were drawn to death. And so, she opened the dark doors within her heart, the ones she had worked all her life to slam shot, under lock and key, rejecting with all of her being. She now embraced that dark heart, that small spark inside of her that relished the prospect of revenge, allowing it to grow into a raging inferno, a terrifying blaze of hatred and death.

Feast, she commanded wordlessly. The Dementors circling above swooped down, and before his soul could escape to one of his many countless vessels, they began to inhale. White points of light seemed to draw from all directions, all corners of the Earth. Their vortex of death was so strong that white wisps were drawn forth, even from the flames of the Fiendfyre. They coalesced into a single white ball of light, centered around the small, silver cross around her neck, and then began to float upward towards the mouth of the Dementors.

The Phoenix that had been waiting expectantly for Godric’s decision looked distastefully at what was unfolding. It was objectively vile, repulsing the Phoenix on a fundamental level. It stared accusingly at Godric, hissing a disappointed ‘Caw’, and with a burst of flame, disappeared.

Godric watched the Phoenix depart with a sickening ache in his heart. He always wanted to be brave. He spent his life raging from one battle to the next, viewing the world in black and white, risking his life time and time again. He knew in his heart that this was not true bravery, for he had never made the hard choice, never considered the shades of grey.

And here was his opportunity. And he let it slip. He turned away his Phoenix and he knew beyond a shadow of a doubt that he would never see that Phoenix, or any Phoenix again. The pain of it broke him in a way deeper than his heartbreak.

He stared at Helga, who was lost within her hatred. It had consumed her to the point where all she wanted was to see Meldh’s soul irrevocably destroyed, to see his being banished into the Abyss, sacrificed to no end other than the sake of sacrifice. She was falling, falling, falling, and with each moment, she gained velocity. She had given herself over to hate, and once she had done so, it became easier and easier to justify, which in turn made her numb. The horrible things he had done, the crimes he had committed against man and nature, the ways he had violated her…

She was beyond the event horizon. There was no turning back now. She was broken beyond repair, and she would break Meldh along with her.
“NO!” Godric shrieked. “Expecto Patronum!”

White light, tinged red with holy fury, hurtled out of his wand. It had no discernible shape, it was war, it was fire, it was passion, it was love. Like a battering ram, it crashed into the seething mass of the Dementors, spreading far and wide, buffeting them backwards, causing them to retreat in fear. The light threatened them in a way that the mere animal forms of the badger and snake could not. They knew what the light could become, and they fled from it, fleeing far, far away to the place where their master told them they would be safe.

The ball of light floated downward, slowly, settling back into its singular resting place within the silver cross that hung around Helga Hufflepuff’s neck.

Godric’s magic had been broken. He knew that he would never summon a Patronus again, and would never see the Phoenix that had come to him. He had given everything he had to rescue his love from the brink, and her place in that Abyss.

Salazar stood, dumbstruck, as he watched the forces of the Lord Foul fall into disarray at the death of their master. He could hear the pops of wizards Apparating away, the thunderous roar of flame as great chariots of fire carried away entire regiments of goblins.

He caressed his hand over the fat emerald, and peered into the still, unconscious mind of the basilisk. Lord Foul had spoken true: the creature had lied. But, Salazar had spared her, and the basilisk was, after a fashion, bound to him.

Rowena, for her part, was still staring at her chest, where the sacrificed drop of blood had reentered her. She could feel it, she had grown all too familiar with the touch of the interdict, the jagged edged tears in the fabric of her mind. Her Diadem, created with the aid of Lady Hufflepuff, assisted her with this, for more often than not she could discern the form of lost knowledge by following the edge of that boundary, tracing the shape of the negative space.

But as she explored the Sacrifice, there was no shape; it was a line, a line that extended indefinitely in either direction. There was no shape to discern, it was simply the terminus. She railed in vain, pounding, trying to break through, but of course she knew it was to no avail.

Ollivander looked from Rowena to Salazar, reeling with their losses, and turned to Godric’s broken face. His sunken eyes stared beyond her into some great Nothing. It was him, but it was not him.
\SmallVSpace
She knew that day that she had lost both of the men that she could ever possibly love, lost in a way that they could never be returned. For death was temporary, but change is forever.
\simpleline
MORPHEUS: I am hope.