\chapter{Rosencrantz and Guildenstern}

\playScript{
\setlength{\vleftskip}{15pt}

\dialogue{HAMLET.} Why then it’s none to you, for there is nothing either good or bad but thinking makes it so. To me it is a prison.\\
\dialogue{ROSENCRANTZ.} Why, then your ambition makes it one. ‘Tis too narrow for your  mind.\\
\dialogue{HAMLET.} O God, I could be bounded in a nutshell and count myself a  king of infinite space, were it not that I have bad dreams.\\
\dialogue{GUILDENSTERN.} Which dreams indeed are ambition; for the very substance of  the ambitious is merely the shadow of a dream.\\
\dialogue{HAMLET.} A dream itself is but a shadow.\\
\dialogue{ROSENCRANTZ.} Truly, and I hold ambition of so airy and light a quality that  it is but a shadow’s shadow.\\
\dialogue{HAMLET.} Then are our beggars bodies, and our monarchs and outstretch’d  heroes the beggars’ shadows.
}
{Why, then your ambition makes it one.}

\simpleline
\pagebreak
\lettrine{M}{eldh} was fighting for his life. Which is to say, he was simply fighting. He had died once before, and he was quite sure that he would die again. Perhaps not today, but at some point. He thought back to that first moment; it was after he had proven himself to his old masters, having demonstrated sufficient skill, wisdom, and kindness to be appointed as the regent of Neirkalatia of the Cross. As part of that induction, he was to die and be reborn, which he assumed was a metaphor. He stood in front of the cross, surrounded by the Coalition and their inner circle.
\SmallVSpace
A bolt of green light. A phrase of what seemed like Hebrew origin? And he was no more.
\SmallVSpace
He had no eyes to open when he awoke. His mind simply emerged, unfolded into consciousness, like those wine\mbox{--}fueled excursions of his youth, when consciousness faded slowly into subconsciousness into unconsciousness, and the line between the three was blurred beyond recognition. He simply awoke, a new person. He could feel the bounds of this world. Who he was, his mind, could reach from one corner of the universe to another, but it could find to purchase, no vessel by which to enact its Will. His mind existed in but a single dimension, it was written indelibly into the world line, but it could not escape. He knew that at any moment, he could relinquish control, and he would be no longer. But he did not want to truly die, if that was even possible.

He also felt the magic of the Cross, even in his death. Once he felt it, it gave his being weight, his spirit a connection back to the universe at large. In his current state, he could see the Cross in its true structure: grandiose, perhaps even infinite. Through it, he was able to sense the traceries of energy that pervaded through this world, all worlds. Magic.
\SmallVSpace
When he was a child, a child in the true sense of the word, he was riding in a chariot outside a palisade. He was fascinated by the fact that, as they moved quickly, the gaps in the palisade blurred together to form an entire coherent vision of what was behind those walls. It made him feel powerful. But when the chariot slowed to a halt, it ceased, and again he could only see the posts of the fence.

This reminded him of that; he had lived his life flitting through space and time, unable to see the fine structures that held up and bound the world. But now that he had slowed to a true halt, it was clear to him. So he picked a point on the web at random, and followed a meandering path towards it, darting through one world and another.
\SmallVSpace
He happened to look back, and he saw that the webs did not extend in all directions as he had once thought. He looked back and he saw the line of the world as it was, and the point in time that was the present, and from there, the webs exploded outward. He was exploring branches of possibility, and had to skip farther and farther ahead into order to avoid the webs collapsing as they were folded into the line, into the path.

The further forward, backwards, sideways he travelled, the more fuzzy and diffuse the details. He cast his mind out farther, into the realm of possibility that lived beyond possibility. The circumstances that could only arise by the barest of coincidences layered on top of coincidences. He travelled further still. After some amount of time, he reached a deep void of nothing, like when the calm gradient of a sunset eventually gives way to the burning flame of the sun itself. Beyond there lie possibilities so impossible that his mind could not distinguish them from the truly Impossible.

He sensed, somehow, that he could travel farther beyond that still. But he sensed, rightfully so, that he should be frightened. He had no anchoring, no point of connection, and if he continued into that Nothing he may never find his was back to the Path.\\So he returned.
\SmallVSpace
After an undefined amount of time, it could have been a year, a decade, or it could have been but a fraction of a moment, he felt it. Structure. Rules. Laws. The delicate traces of energy condensed into something more substantial, like threads of flexible glass. It contained his mind, yes. But it also gave him freedom, power. There was an object of sorts, he could not discern its nature, that represented these bounds.
\SmallVSpace
At first, he had no means of truly experiencing reality, much less interacting with it, and for a few eternal moments, he was impotent, trapped in a prison with only his thoughts. But he quickly learned the subtle language of his new form: the shifts in its constituent matter in response to light and vibration, and perhaps more importantly, the resonance with other nearby minds. He had no time for it now, but he knew that he could learn to reach out, to caress those minds, to tempt them.
\SmallVSpace
But after another eternal moment, he awoke, this time in a true body. His eyes snapped open. His soul was interfacing with a fleshy bowl of seething organic matter, all switches and synapses and simple reactions, which together allowed him entry into the world of life. He was on a stone altar, still surrounded by the members of the Coalition and their regents. He had literally died, and was literally reborn.
\SmallVSpace
Throughout the years, he had an inkling of a hope that this was possible. How else could the Old Ones persist as they did? But at the time it seemed like a foolish hope, an opiate to dull his resolve, to calm him, to keep from the fight of his life, all lives. An empty promise of eternity if in turn, he would only just \emph{believe.}
\SomeVSpace
He saw now that it was no empty hope. But that knowledge, that hope, it was hoarded, stowed away for only the most elite of elites. He could already hear the arguments, the justifications, the rationalizations. Those damned deathist scholars that made up his peers had been rattling them off ever since they had a sense of their own mortality:
\SmallVSpace
“What would happen to the world if everyone were to live forever?”
\SmallVSpace
“Death is a natural part of life.”
\SmallVSpace
“You cannot have the light without the dark.”
\SmallVSpace
“You cannot spend your life forever running from death.”
\SmallVSpace
And so on and so forth, all spoken with the smug superiority of someone who thinks that to sneer at Death is to defeat it, as if whispering some tired platitude would save them from that horror of horrors. But this, this was worse. They would twist these sentiments, which ultimately existed to provide some measure of solace to dying old men, and use it to enable the tyranny of that dark lord.
\SmallVSpace
He could not stand by this. He understood its structure, the basic theory. He was already reverse engineering the principles of operation. Either everyone could have this gift, or no one could. His current masters were tyrants, and it fell on him to recreate this world in the image of Man, not of God.
\SmallVSpace
His secret experimentation proved that the implementation was far more difficult than he had anticipated. But it was encouraging as well. It was possible, he had proven as much, and that was what mattered. His first iteration was functional, but flawed. It required an untenable, unconscionable sacrifice. He couldn’t understand the recursive aspect of the True Cross’ infinite structure, but that would come in time. But still there were those who wanted to die, there were those who deserved to die, and they could serve as fuel until he could perfect his grand creation. So for now, his öρóσταυρóς (although it would later become more famously known by its Latinization) would have to be sufficient.

Emboldened by this, he sought to overthrow his masters. The path seemed inexplicably easy. His rousing speeches turned the right ears. His pleas for support went both noticed and unnoticed by the right sets of people. And when it came time to move openly, support for his cause swelled quickly, so quickly. Often times he had to remind himself that, although most of the time, life isn’t like a play, sometimes it is. Sometimes it is.

And so it was that he, in blissful ignorance of the fact that he had simply exchanged one set of masters that operated in the open with another who operated in the shadows, he assembled his forces, put together an army, and led them against the Coalition.

They had battled their way into the heart of the Stronghold of the Coalition, and they were very close to the chamber in which he had died. He had no delusions that they would be able to kill the Gods; his goal was simply to destroy the Third Spire of Shiggoth. Without an anchoring point to harness and multiply their power, their hold and influence would be severely weakened. They would be forced to flee to other lands, easier targets. And if they chose to stay, well, they would be vulnerable, and he could continue to fight.

Currently, Meldh was equipped with his close quarters battle armor and weapons. Unlike Magical Warfare, Magical Combat all but required the wizard to be on the front lines. Their attacks were far too widely destructive to be of any use from the rear; there was typically insufficient time or space to maneuver such long\mbox{--}ranged weapons of death. You could hurl Greek Fire from a distance, but only a fool would dare use the same in close quarters.

As with all things in life, the art of war could be mapped out onto a board of the Game of Kings. The Queen, in the beginning, must be protected. You must establish your position, ensure her safety. But she cannot stay in hiding forever. At some point, she most go on the offensive, she must emerge and unleash devastation. But with insufficient preparation, the Queen will quickly be cut down or sacrificed.

And as with Magical Warfare, more often than not, the wizards fought the wizards and the humans fought the humans. You could certainly focus your magic on cutting down large swathes of the enemy, but this would leave you open to swift and sure counter attacks, from both the enemy wizards and their warriors. Furthermore, and perhaps more importantly, you would leave your own men vulnerable to similar destruction.

Meldh was equipped with his close quarters battle armor, and he wielded two wands embedded into the hilt of twin swords, in the manner of a διμάχαιρος. Few were as skilled in such arts as Meldh, and like a well\mbox{--}positioned Queen, he was able to cut down a number of pawns while still posing a formidable defense.

They adopted an inverted\mbox{--}claw formation, with Meldh in the recessed center. His men on either side curved outward, engaging the edges of the enemy forces in the wide hallways. The enemy adopted a similar defense, and Meldh exchanged volley after volley of curses with the enemy wizard.

Their goal was penetration; the chamber of the Spire was but a few corridors away. Meldh carefully chose each spell to have a physical component that, even if countered, would force the enemy backwards. Walls of ice were a popular choice in Meldh’s day; they were easy to construct, robust, and impervious to most elemental defenses, except of course, fire. And in this case, that fire could then be transformed from a defensive play into an immediate offense, which would lose him the initiative.

Instead, he drew from the ground jagged, thick spikes of woven branches and thorns, weaving around each other and jutting out towards the enemy forces. Yes, they could be cut down by physical attacks, but that was time consuming. And they could certainly be burned, but the ensuing fire would do more damage to the enemy troops than Meldh’s own. No, the easiest defense was fairly trivial: simply fall back, yield ground. It rendered the attack moot, wasted your opponent’s magic, and took no magic of your own. So this is what the enemy did: if Meldh wanted to continue to waste his magic on such structures, they would allow him. They could continue to fall back, deep into the Stronghold, as there were many advantageous positions and potential traps they could lure him into.

But Meldh was not trying to rout the enemy forces. In fact, the fewer casualties, the better, in his mind. Of course, he was not opposed to dealing death when necessary, but he would not slaughter them simply because they held the same set of misguided ideals that he once did. So he was more than content to fire up spike after spike, forcing the enemy further and further backwards. They were closer to the chamber now, perhaps one hallway away.

The enemy soon realized Meldh’s intention, and took steps to slow the advance. The Butterball Charm that they employed had been expected; it was a fairly standard method of delaying an enemy’s assault when on rocky terrain. But Meldh had already prepared the surface, coating the stone floor with a thin layer of unyielding glass, which supported the weight of his troops even as the stone beneath turned to muck.
\SmallVSpace
Because he had already prepared the floor in such a manner, he was free to devote all of his energy into his counterattack. He transfigured most of the air in the room into a single, tiny, incredibly dense stone. The vacuum and subsequent lack of air disoriented them all, friend and foe alike. An instant later, he cast the rock into the churning liquid.

With a concussive pop, air filled the vacuum in the room, and at that moment, Meldh released his hold on the transfiguration. The rock instantly reverted back to its original, true Form: a room’s worth of air. The liquid stone beneath the glass floor had nowhere to go but up and out, towards the enemy. The result was not so much deadly as it was absurdly disorienting, like being splashed in the face with a massive bucket of mud.

The enemy wizard was unfazed and was already mounting his counter\mbox{--}attack, a volley of diagonally\mbox{--}oriented blades. It would serve the dual purpose of cutting down both Meldh’s troops, and his walls of brambles and thorn.
\SmallVSpace
This proved to be quite the mistake.
\SomeVSpace
Wizarding Combat almost always hinges on one simple factor: who can most cleverly turn their defense into an attack? For example, an elemental attack would have to be elementally countered, dodged, or swept aside: it could not simply be Finited. Granted, \emph{Finite Incantatum} was rarely an effective tool in battle, as it is a spell of pure magical brute force, and 99 times out of 100, a more efficient tool can be used to achieve the same ends.\\In this unique case, however, Meldh’s mass Finite was powerful enough to dissipate the incoming blade attack instantly. It had been tremendously costly, but it had the ancillary benefit of also dispelling all the charms in its path.
\SmallVSpace
Including the Butterball Charm.
\SmallVSpace
The enemy soldiers had been soaked with the liquid stone from Meldh’s prior counter. And that liquid stone immediately transmuted back into solid form, encasing the entire front line in prisons of rock, and severely hobbling the lines behind them. It simultaneously neutralized their offensive capacity and prevented the men behind them from engaging in any sort of effective counter\mbox{--}attack.
\SmallVSpace
The enemy wizard was naked, bereft of protection. He tried to retreat back behind his line of men, but it was to no avail. Meldh and his men charged forward, and the enemy wizard desperately tried to hurl blasts of Ventus to repel them. There were only a small number of effective counter\mbox{--}attacks he count have mounted, and Meldh was prepared for them all. In this case, he simply created Void, and sent it upwards so the ensuing vacuum pulled the gust of wind harmlessly away. At that point, it was over. The enemy wizard could not defend against Meldh’s ceaseless attacks and the ensuing rush of troops. He was unceremoniously cut down, and the enemy men, now with no wizard to protect them, were done for.
\SmallVSpace
Not wishing for unnecessary death, Meldh raised his hands upward, this time using wandless magic, and lifted the imprisoned men, turned them on their side, then blasted them backwards. The effect reminded him of a time when he saw a shipment of logs fall off the back of a merchant wagon and roll down a hill, knocking down an entire group of merchants that were behind it. The soldiers who weren’t physically knocked down had the good sense to beat a hasty retreat. A few mass \emph{Somnium}, and the path to the Spire was cleared.

As he charged into the room, he did not know how much time he would have, so there were no dramatics; he simply launched straight into the ritual. His hand slashed to the left and he cried \emph{“Khorne!”} Then his hand pointed below him, and \emph{“Slaaneth!”}, above him and \emph{“Nurgolth!”}, and then to his right, \emph{“TZEENTCH!”}

The room started rumbling.

\quotePoem{
“Darkness beyond darkness,\\
deeper than pitchest black,\\
Buried beneath the flow of time{\el}\\
From darkness to darkness,\\
your voice echoes in the emptiness,\\
Unknown to death, nor known to life.

You who knows the gate, you who are the gate,\\
you who is the key and guardian of the gate.\\
Past, present, future, all are one in you.\\
You who knows where the Old Ones broke through of old,\\
You who knows where They shall break through again.\\
You who knows where They have trod earth’s fields.\\
You who knows where They still tread them.\\
You who knows why no one can behold Them as They tread.

Ogthrod, ai’f\\
Geb’l-ee’h\\
Shiggoth-y’wrd\\
‘Ngah’ng ai’y\\
ZHRO!\\
ZHRO!\\
ZHRO!”}{}

Meldh did not question the source of the scroll that contained the ritual. He had seen darker, more Eldritch incantations, found in much more sinister places. It had been given to him by one of the nine Muses, when he had found her bathing in a spring on Mount Helicon. He had discovered the location to this particular spring in a piece of parchment that was hidden within an innocuous book in an arcane library. The whispers of this hidden parchment had been reported back to him by the beasts of the woods, who heard two dark magicians speaking of it in hushed tones. Further research determined that the two magicians were agents of the Coalition, tasked to inventory and shore up their weak points.

What Meldh did not know was that he was simply a pawn masquerading as a Queen. He had been led, like a rat following a piper, to find that scroll and that ritual. Every move he had made was planned out, the product of a grand design that he was not only unaware of, he was convinced the grand design was his own. The surest path to manipulation, indeed, is to convince your victim that a brilliant idea is their own.
\SmallVSpace
Merlin had wanted the Coalition toppled, and so they would be toppled.

Merlin wanted Christopher Chang and Constantine Atreides out of the picture, and so they would be gone.

And Merlin wanted the Third Spire of Shiggoth, the third “Tower of Atlantis”, to fall, so it would fall.
\SmallVSpace
As Meldh continued repeating the final word of the incantation, the power of the phrase reverberated within the chamber, waxing in power until the very words themselves took on some otherworldly resonance, and the Tower began to vibrate. The very Stronghold began to vibrate.

The fall began.

\simpleline

%\begin{quote}\small ROSENCRANTZ: Whatever became of the moment when one first knew about death? There must have been one. A moment. In childhood. When it first occurred to you that you don’t go on forever. Must have been shattering, stamped into one’s memory. And yet, I can’t remember it. It never occurred to me at all. We must be born with an intuition of mortality. Before we know the word for it. Before we know that there are words. Out we come, bloodied and squalling, with the knowledge that for all the points of the compass, there’s only one direction, and time is its only measure.\end{quote}


\playScript{
\setlength{\vleftskip}{15pt}

\dialogue{ROSENCRANTZ:} Whatever became of the moment when one first knew about death? There must have been one. A moment. In childhood. When it first occurred to you that you don’t go on forever. Must have been shattering, stamped into one’s memory. And yet, I can’t remember it. It never occurred to me at all. We must be born with an intuition of mortality. Before we know the word for it. Before we know that there are words. Out we come, bloodied and squalling, with the knowledge that for all the points of the compass, there’s only one direction, and time is its only measure.}
{Why, then your ambition makes it one.}


\simpleline	
\DatePlace{Moments Before}

Kari of the Cube, Yanotuk of the Cups, and Kri’Xiang of the Glass stood in detente. One could control the world. One could destroy the world. And one could create the world. Rock, paper, scissors. The first to act would be the first to lose, and so no one took action.

\nopagebreak{Kari and Yanotuk held each other’s hand, a hint of desperation in their posture.  As if to say, “Not like this. It’s too soon.” They did not know Kri’Xiang other from Before. They had never met, despite their many long years of life. After all, there were so, so many people. As such, they did not know the other’s hopes, each other’s dreams, each other’s wishes. They did not know that, perhaps, if they really, truly, thoughtfully considered each of the other’s information and conclusions, they might discover they were all three allies.}

But they did not. They simply knew each other’s power, and they knew that this was a standstill that would never be broken. There would be no climactic fight, two Gods with the twin powers of Destruction and Control, against a God wielding the might of Creation. There would be no pithy speeches, glib comebacks, no denouements or monologues. They were simply three unimaginably powerful beings that knew on some level, that they were all about to die, and that the fate of the very world hinged, in part, on this moment.

When they felt the shudder of the Tower, they knew it was time, and they all acted at once.
\SmallVSpace
The all\mbox{--}consuming darkness of the Cup of Midnight erupted forth, filling the room with a void whose darkness could only be matched by the true form of the Boxes of Orden. Any mere mortal would have been driven instantly insane, their minds unable to comprehend the manifold and conflicting commands that spewed forth at random.
\SmallVSpace
The Boxes of Orden contained that darkness, however, and folded them in to their own all\mbox{--}consuming power. The three forms condensed into one: past, present, and future, for all the world’s past had led to this single point in the present that would dictate the future. The Boxes unfolded, the Box unfolded, and in that instant, infinity was in the room, infinity \emph{was} the room.
\SmallVSpace
The world would have been consumed in that moment. The world was consumed in that moment. There was no past, there was no present. There was only void.
\SmallVSpace
Presently, the only thing reflected by the Mirror of Volition was that empty void. If one gazed into it, they would see perfect, a unyielding, golden nothing.

Presently, the only thing reflected by the Mirror of Noitilov was an empty chamber. If one gazed into it, they would see a perfect, unyielding reflection of itself and the empty room surrounding it, a room which contained only a single, plain, wooden Cup, and a single, plain, jet\mbox{--}black Box.
\simpleline	
\quoteBook{ROSENCRANTZ: How sweet! I once had a fish… Francis. He was very dear to me. One afternoon, I came downstairs and… it vanished. Poof.\\
GUILDENSTERN: That’s very odd, isn’t it?\\
ROSENCRANTZ: Yes, doesn’t it? But that’s life! I suppose, you\mbox{---} you go along with and suddenly… poof.\\
GUILDENSTERN: Poof.\\
HAMLET: Poof.}{}
\simpleline	
\DatePlace{Moments before}

A long period of silence passed.
\SomeVSpace
“Long time, no see.” Constantine Atreides finally spoke.
\SmallVSpace
Natalie Kyros laughed. “Long time, no see? THAT’s your line?”
\SmallVSpace
Constantine smiled, sadly. He had thought, dreamed, hoped for this moment, so much so that it was written into the very fabric of its being. And here it was.

And all he could say was, “Long time, no see.”
\SomeVSpace
“I don’t understand it, Gus. Why are you allied with him? You know how close we had been. We were \emph{so close}. I could practically taste it. A few more centuries. Tops. But he was reckless. Impatient. And we all paid the price. Maybe the final price. You, me, everyone. And now, you’re{\el} What? On his side?”
\SmallVSpace
“Don’t be like that. Yes, we lost a terrible battle, that day. But the war isn’t over. It’s never over. And right now, he’s our only hope.”

“He’s \emph{not}. You’ve seen what we’ve built. In just an eye blink of time, we’ve shepherded these people, and look what they’ve done. Just think about what they could do in a thousand years. Or ten thousand years. This here, this is the future.”
\SmallVSpace
Constantine rolled his eyes. “You’ve created a society, divided. A society ruled by our Descendents. They don’t know the truth about who they are, who they were, what their birthright is, what their role is{\el} We have to start over. We have to limit them, or else\mbox{---}”

“Or what? They blow themselves up with ‘Magic’? We’ve been through that already. He put us through that already. What he did was orders of magnitude worse than anything they could ever do.”

“It’s not just that. It’s… Look, as long as they’re around, as long as \emph{we’re} around, we’re all bound to that dead world. All worlds are bound to that dead world.”

“So, what, we sacrifice them? Everything we built? Sacrifice this world so that he can create a new one in his own image?”

“It’s not a true Sacrifice. They’ll still exist. In memory, in hope.”
\SmallVSpace
Natalie scoffed. “Hope?”
\SmallVSpace
“Yes, hope. It’s powerful,” Constantine replied, indignantly.

“For God’s sake. Listen to yourself.”

“You weren’t around for the really old days. You weren’t\mbox{---}”

“You’re not THAT much older than me.”

“Yeah, but it was different back then. You can’t imagine what it felt like. The not knowing. We were close, sure. But, seeing people die at what, 200? 300? Being almost that old yourself and just \emph{not knowing}. Hope was all we had. Hope that \emph{something} would happen in our lifetime.”

“You don’t think I know how that feels? You don’t think we all know how that feels? Don’t be so self-centered. I knew what was at stake, the price if we lost, if we lose. I still know that price. But I’m not\mbox{---}”

“No. It’s not the same. Knowing that you can fight until the end, the real end, that’s empowering. It’s life affirming. But knowing that you have 30, maybe 40 years left, and then you’re gone? Think about it. I mean, really think about it.” He gestured angrily at the cross. “Why do you think \emph{this} has persisted across worlds? I can’t even imagine what it must be like for \emph{those} people. Hope is all they have. It’s all they can have. You know it’s true. There’s a reason you chose this inverted cube design rather than a tesseract. Somewhere, you know the power of hope.”
\SomeVSpace
Natalie paused, and considered this. “Ok. I can see your point. But what of it?”
\SomeVSpace
“They have to build their own path. We can’t help them.”

“How? And why?”
\SmallVSpace
“We did.” Constantine pause, and corrected himself. “Well, not ‘we’. Those that came before us.”
\SmallVSpace
“No, that doesn’t answer my question. What I’m saying, and what you’re not making sense of, is why we can’t help, why we have to be out of the picture. That’s what’s never made sense about any of this.”
\SmallVSpace
Constantine didn’t have an answer. “Well?” Natalie pressed.
\SmallVSpace
“I{\el} I don’t know! Because he says so.”

“Are you kidding me? You don’t even know?”

“You don’t{\el} You don’t understand. You and me, we play at being Gods. All of us do. But he{\el} Everything we do, it’s because of him. We only exist at his forbearance. He is God, and King. He’s the thing we merely pretend to be.”

“Are you listening to yourself? You sound like, I don’t know, like you’re trying to be a character out of one of your video games. Just, stop being ‘Gom’Jorbol’ for a second, and just be Gus.”
\SmallVSpace
Gus smiled at the anachronistic happy memory. After a time, he spoke. “I don’t know how, or why, but this is his world. He knows too much. It’s like he’s had an eternity to contemplate every possible move we might make, every possible path we might go down. If he wants this world to end, it will end. I’d rather shape the things that come, than pointlessly fight to try to stave off the inevitable.”
\SmallVSpace
Natalie considered this. Despite the act, despite the ruse, despite the masks, this wasn’t some work of fiction. He wasn’t just some character arbitrarily representing the hopelessness of the situation, some messenger to convey to the audience just how powerful their enemy was. He was a real person, he was her Gus. And if he had come to this conclusion, it was not lightly.
\newpage
She thought on this further. She wished they had reunited ages ago. She wished he would have sought her out the moment he came to this realization. She wished so many things. Above all, she wished things could have been different.
\SmallVSpace
“Then let’s run. We escaped once before, we can do it again.” Natalie spoke with steely resolve.
\SmallVSpace
“Don’t you think I’ve considered that? Where would I run, and how would I stay there? All worlds are bound to this one.”

“Not ‘I’. ‘We’. He plans to unbind this world. That means he plans to unbind us, too, eventually. So we’ll just do it for him.” She was clearly getting to something, and so, although she paused, Constantine did not speak. “You know, I took what you said to heart. Technically, every structure is an infinite\mbox{--}dimensional shape. I incorporated some of that into the design. This,” she gestured at the cross, “is just a single facet. A shell, if you will.”
\SmallVSpace
New information. Interesting. It was modified. Improved. Thoughts, calculations, estimations. Yes, this did change things. “I see,” Constantine nodded.
\SmallVSpace
“And with your Rod{\el}”

“And the power of the Line{\el}”

“Yes. We leave this world behind. We leave the world to him. He will exert his will upon the world and its people.” She looked up at him. They both paused.
\SomeVSpace
‘We will be together, though?”

“Yes, we will be together. ”

“Then everything will be all right.”

“Yes, it will.”
