%% TODO: Chapter tittle doesn't match the rest of the document
% Current style looks better than previous, but is still inverted
% Index entry in TOC doesn't match style

\chapter*{Strange Loops}
\begin{center} \chapnumfont PROLOGUE \end{center}
\addcontentsline{toc}{chapter}{Prologue: Strange Loops}
\SomeVSpace
\SomeVSpace
\SomeVSpace
\textbf{\textit{The Dark Lord had won.}}\par
\simpleline


\DatePlace{June 13, 1992. 20:43:24 \\
Hogwarts Castle}

The Stone instantiated in Lord Voldemort’s hand, glistening coldly in the reflected light of the mirror, free from any imperfection.
\SmallVSpace
A quick flick of the wrist.
\SmallVSpace
A swift twitch of the finger.
\SmallVSpace
A deafening crash of a pistol firing.
\SmallVSpace
Harry’s eyes barely had a chance to widen before the bullet entered his forehead.
\SomeVSpace
The Boy Who Lived was dead.
\SomeVSpace
The entirety of his being; his mind, unprotected by Horcrux or ritual or saved state, was currently settling onto the ground, a red mist of gore, bone, and brain. The remainder was stuck to the walls behind the Mirror, (the Mirror itself being perfectly unblemished), or still clung desperately to the inside of his ruined skull. The chamber still echoed with the discharge of the weapon, but Lord Voldemort was already gone, willing to take no chances with what might happen upon the Boy’s death.

\simpleline

\DatePlace{Sagittarius A* \\
Now, Before, Later}

Dumbledore emerged from the tunnel. His world was all worlds. His world was fire. His world was void. His world was formless nothing. His world was stagnant death. He focused all his being onto the two worlds that mattered. In one, the star burned, rendering the world insane, its very soul raging with white plasma that rendered such abstract notions as space and time irrelevant in the face of the heat.
\SmallVSpace
He looked across the span of eons into the other world, wherein the Boy Who Lived was dead.
\SmallVSpace
He had all of eternity to rehearse the ritual, and yet, he still felt the slightest bit of nervousness. He began, using the Line of Merlin to harness the magic of all worlds into this one final act. He was Dumbledore, destroyer of worlds, creator of life. Everything that ever was and everything that ever will be in the universe had led him to this moment. This moment that must come to pass because it already has.
\SomeVSpace
All worlds had narrowed to two, and from those two all worlds would be born. When the Line of Merlin could bear the strain no longer, it glowed white, and began to fray apart at the edges. Dumbledore could feel the eyes of prophecy in the heavens upon him, about to be torn apart by the ritual of Harry’s creation. The Headmaster connected the nodes in his mind, and it was done.
\SmallVSpace
Sagitarrius A* collapsed in less than a second. It folded in upon itself, and distorting the very fabric of reality as it did so. In the final moments of its life, the Headmaster flitted through some dimension that only exists in the minds of addled physics professors, and emerged to the place Beyond Time, where he was connected by the power of the ritual.
\SmallVSpace
In the world he left behind, a galaxy was born. A galaxy where the balance of the world was held in place by a single thread of time, a universe where the only means by which the Crux could succeed was to seek the path of the Scorpion and the Archer. The fires of prophecy would burn with the white light of truth; they had come to be because they had come to be.
\SmallVSpace
He entered a world that was already born, a world where the balance of the world was held in place by a single thread of time that had, until now, been snipped. It was at this very moment that he emerged. He was outside the Mirror. No, he was inside? It was a curious sensation, experiencing time backwards. He took a brief moment to consider the runes that had once been incomprehensible to him. He smiled.
\SmallVSpace
Inside and outside the Mirror, the world was hazy, a confounded miasma of abstraction, like some sort of halfway lucid dream that someone had pressed the rewind button on. His brother took the stone from him. Not from him.\\From his shadowform. It was not him?  He was talking to his brother. But it wasn’t him. He was saying the war was over. They had won. That was true, no? It was Time. Time to stop holding on to the stone. Give away the stone. Yes.
\SmallVSpace
You could change the past, you just had to think about it at the right time.

As he moved further backwards in time, he considered the tools of his craft that he still had upon his person. The Line of Merlin. The Stone of Permanence. The Elder Wand. A curious glass bottle.
\SomeVSpace
A curious glass bottle of viscous black ichor.

\simpleline

\DatePlace{Mid-Fall, 1999 \\
Wilbraham, Massachusetts}

“Everett, was that you?”

Sarah Snipes was cleaning dishes in the kitchen when she heard the crack. Or was it a pop? It was probably just her husband playing around in his lab. He was a compounding pharmacist, and owned his own store, so he often experimented with different formulations of various creams or pastes to sell.
\SmallVSpace
As it were, Everett Snipes was not in his laboratory. Rather, he was in his study. “Yes, dear. One of my vials popped a cork,” he yelled a blatant lie back to her.
\SmallVSpace
“Okay, well make sure to clean it up before you let Lily in there. She’s at that age, you know?”
\SmallVSpace
As if on cue, Lily burst in through the study door, her hair all fire and curls, her eyes an angry emerald-green. She had all the energy of a five-year old, and all of the precociousness as well. She stared at her dad who was sitting on the Comfy Chair, and the strange man sitting on the Chair That Mom Yells At Me When I Climb On. “Hi Daddy. Hi Mister Man. Guess what? I learned what a Quine was today in school. I bet you don’t know what a Quine is, Mister Man.”
\SmallVSpace
She glared at the stranger. He considered for a moment, then replied, “If I did not, then this statement would be a lie.”
\SmallVSpace
She paused, thought for a moment, then giggled. “You’re funny, Mister Man. But you’ve got a girl’s hair.” At this, he self consciously adjusted his ponytail. To break the ensuing silence, he reached over and grabbed the thick glass bottle filled with viscous black ichor, and placed it into his suit pocket. It created an awkward lump in his figure.
\SmallVSpace
“I hope that you know, ah, ‘Everett’\mbox{---}”

Lily cut in, “His name’s Daddy, you know!”

“Well, I hope that you know, ‘Daddy’, that I truly understand the gravity of this intrusion. And I hope that you understand that my need is proportionate.”
\SmallVSpace
Everett nodded.
\SmallVSpace
The stranger spoke again, “I would tell you that what you have done today would honor my mother’s memory more than anything else you’ve done in your life. But,” he looked at Lily who had already grown bored, and was splayed out on the floor, playing idly with the rug. He smiled, widely, “I see that this is not true.”

Everett smiled, genuinely. “Thank you.”
\SmallVSpace
“Besides, I have a gift for you in return. A bottle of my own magic that will hopefully aid you in your life’s quest,” at this, the stranger produced a plastic bottle from an extendable space within his robes, and handed it to Everett, who looked at the label.
\SomeVSpace
\textit{Head and Shoulders}
\SomeVSpace
Everett laughed. “Drop dead.”
\simpleline

\DatePlace{Early Fall, 1999\\
The Tower}

Harry had informed the Shichinin that, especially considering to whom they were delivering the message, that they were to not under any circumstances, read its contents. Which of course, meant, especially considering to whom they were delivering the message, that they absolutely were going to be reading its contents. In fact, they didn’t even wait to leave the Tower before they ripped open the envelope.

It had been quite some time since they had a good old fashioned, film noir\mbox{--}esque missing person search. And the person that they were looking for? Oh, this was going to be spectacular. Unfortunately, they were slightly underwhelmed (although a bit intrigued), at the contents of the message.
\begin{writtenNote}
“Bahl’s Stupefaction. 1 week.”
\end{writtenNote}
\simpleline
\DatePlace{King’s Cross\\
Outside Time}

“No,” said Albus Dumbledore. “No, no, NO! ”
\SmallVSpace
The building sense of power rose to an unbearable peak, and then disappeared.
\SmallVSpace
And then, there was nothing.
\SmallVSpace
He lay facedown, listening to the silence. He was perfectly alone. Nobody else was there. A long time later, or maybe no time at all, it came to him that he must exist, must be more than disembodied thought, because he had a sense of touch, and the thing against which he lay existed too.

He sat up. His body appeared unscathed. He touched his face. He was not wearing glasses anymore. His beard was gone. As were the wrinkles.
\SmallVSpace
Albus turned slowly on the spot, and his surroundings seemed to invent themselves before his eyes. A wide\mbox{--}open space, bright and clean. He was the only person there, except for\mbox{---}

He recoiled. He spotted him sitting on a bench, idly reading a curiously thick book. Tom Riddle. He seemed thoroughly unconcerned with the situation.
\SmallVSpace
“He cannot hurt you.” He spun around. Harry James Potter-Evans-Verres was walking towards him, sprightly and upright, wearing sweeping robes over a Muggle suit.  “Prophecy has proven true. I have come to rescue you, Headmaster.”

“Harry. You have{\el} You have aged. How long has it been?”
\SmallVSpace
“Oh, about 20,000 years, objectively. Subjectively? Well, for you, it’s been but a few seconds, has it not?”
\SmallVSpace
“It has, but I am trapped outside of Time. I would fear for you, but you are The Crux, the Once and Future King. You do not carry the look of sadness about you, which lightens my heart greatly. Dare I ask if you have succeeded? Did you tear apart the very stars in heaven to save its people?”
\SmallVSpace
“Ah{\el} Well{\el} Not quite.” Harry tittered on his feet a bit, “In fact, we’re not really out of the woods just yet.”
\SmallVSpace
“I confess, I do not understand. But then again, that is more than fair turnabout. Would you do an old man the honor of explaining what I must do?”
\simpleline
\DatePlace{King’s Cross\\
Later}

The Headmaster’s head was still reeling from the enormity of the plan. But, then again, it fit with all the prophecies. For the first time since Nicholas Flamel had bequeathed upon him the Words of the First Enchanter that unlocked the keys to the entire Web of Prophecy, things began to make sense.
\SmallVSpace
“We have a final pair of gifts to give you, that I suspect you will greatly need.” Harry removed from his robes a thin stone rod, “The Line of Merlin Unbroken.” Harry handed the Headmaster the wand with reverence.
\SmallVSpace
Tom Riddle stood up from the bench, put down his book, and strode forward. “And, Headmaster, my old enemy and future friend, I also have a gift for you.” He produced a thick glass bottle filled with viscous black ichor, and handed it to Dumbledore.
\SmallVSpace
Dumbledore understood.
\SmallVSpace
“Headmaster,” Harry spoke, “You need to understand something. You have a choice at this moment. All worlds, ultimately, have narrowed down to this one choice. Although I am, as you say, the Crux, you still must make this choice of your own volition. You would be sacrificing your Life, and your Time. Truly.”
\SmallVSpace
“Harry. You know my views on this matter. I have already sacrificed my Life and my Time once for your sake, for the sake of the world. Besides, you are the Boy Who Lived. I’m sure you’ll find a way to rescue me again.” He smiled with a twinkle in his eye. “Now, how do I leave this place?”

“Oh yes,” Harry smiled at him. “We are in King’s Cross, are we not? I think that if you decided to move on, you would be able to{\el} Let’s say{\el} Board a train.”
\SmallVSpace
“And where would it take me?”
\SmallVSpace
“Beyond.” said Harry simply.
\SmallVSpace
Silence again.
\SomeVSpace
“Goodbye, Headmaster. And thank you, truly.”

“Do not pity the dead, Harry James Potter\mbox{--}Evans\mbox{--}Verres. Pity those who live without love.” And with that, he boarded a train, and disappeared into the tunnel.
\simpleline
\pagebreak
\DatePlaceInv{eltsaC strawgoH\\
72:34:02 .2991, 13 enuJ}

\begin{flushright}
The Boy Who Lived was dead.
\SomeVSpace
Harry’s eyes barely had a chance to widen before the bullet entered his forehead.
\SmallVSpace
A deafening crash of a pistol firing.
\SmallVSpace
A swift twitch of the finger.
\SmallVSpace
A quick flick of the wrist.
\SmallVSpace
The Stone instantiated in Lord Voldemort’s hand, glistening coldly in the reflected light of the mirror, covered in a viscous black ichor.
\end{flushright}
\simpleline

\textbf{\textit{The Dark Lord was laughing.}}