\chapter{The Battle of Hogwarts - Prelude}

But where shall wisdom be found? And where is the place of understanding? Man knoweth not the price thereof; neither is it found in the land of the living… for the price of wisdom is above rubies.

Job 28:12

\simpleline

\DatePlace{Hogsmeade\\
1107 C.E.}

\lettrine{“D}{id} you not think that I, the one who would be most likely to see the rightness in your cause, would be offended that I was the last of the Four that you approached?” Helga Hufflepuff took a sip of tea, watching her friend’s reaction closely. “It is fair to say that I and my brethren are known for little, save for our tenacity. But I dare say that hard work often beats a faster path to Truth than cleverness, cunning, or courage.

“I have seen what our students have done. I have seen what we have wrought. I know what we are capable of. And yes, I have heard the prophecies. Even The Prophecy.” At this, Heraclius Hero arched an eyebrow.

Helga continued, “Friend, I have often considered walking the same path as yourself. I have often considered abandoning my companions, walking away from what we have built. The others, they do not see the extent of the danger as clearly as I do.”

“So then, you will aid me, when the others have rebuffed me?” Heraclius asked.

Helga began to speak, but her regretful smile communicated everything Heraclius needed to know.

“You’re a fool! All of you are!” He slammed his fist into the table, causing the other people in the pub to look over in irritation.. “You’re so damned clever, every last one of you. You only believe the best because you want it to be true! But has it ever occurred to you that sometimes, the simplest solution is the correct one? I am well aware of the manifold interpretations. Rending asunder the fires of the sky. Tearing open the eyes of heaven. Tearing apart the very stars in heaven. They all speak to one thing: destruction, death, the end of all things! And you, you cursed deathists, you wish to let it happen, in the misguided hope that The Prophecy means something other than the obvious!”

At this, Helga’s phoenix, Howard, cawed softly, and Helga interjected. “Do you not think that out of death, can come rebirth?” Heraclius cut her off, “Not this again. I have heard this enough from the others, but from you as well? No. I do not accept this. Death is never good. Death is never right. And I for one, will not stand idly by and watch as you march this world towards oblivion, made worse by the fact that you think you lead us into salvation.”

Heraclius stood up to leave. “SIT.” The command seemed unsuited for Helga’s lips, but it was spoken with such force, anger, and determination, that he was almost bound to comply. “You have insulted me and mine enough. It is fortunate that I did love you, once. You have little idea of the sacrifices I have endured for the sake of you and your wretched companion. The lies he told me. I had made beautiful, terrible things. My power was growing. I was to be The One, to lead us to a new era.

But he came to me, with honeyed words and promises. He came to me as he came to all of us, and I gave him an audience because of you, because of our love. He told me the plans he had for my Cup, the ways he would channel our power to create the ultimate creative force. He told me LIES, and now all I have to show for my life’s work is THIS!” She angrily shook her teacup at him. Fortunately, it was empty. Not that it would have mattered.

“He shackled me, he shackled all of us, Meldh. And you allowed it to happen. You knew. You allowed this, this monster, to become masters of all of us. Even yourself. You began this march, this inexorable spiral into stagnation. Despite this, I never sought to strike against you, but you would be well to know that you only live by my grace. We have watched the passage of time for a millennium, you and I, and I do not end such friendships lightly. But the tools of my will are spread wide, every man, woman and child wizard in the whole of this part of the world uses a piece of my Will. And through them I command a great power. See to it that you do not give me cause to turn that power against you.”

Meldh considered his response. “You call me by my True Name, It is a word I have not heard in centuries. I shall return the favor, Ελαολογος. But know this. You do not absolve me of blame out of some misguided loyalty to our centuries together. You know as well as I do that I had been Bound. You know that I would not have deceived you otherwise.”

A pause.

A long pause.

She said nothing.

“Not under my own volition, so to speak, but nonetheless, I am Bound, forever more.” This made matters considerably more complicated. After a time, she spoke.

“Would you move against us all the same, were you not Bound?”

“I would. But I would not have lied to you. I would do as I do now, moving openly.”

“And have you spoke with Godric?”

“I have not. His pride would not permit it. Nor would mine,” his words were tinged with bitterness. At this, she finally laughed.

“To think. All of history, all of fate, the future of all our kind, will be altered by the pride of two jealous men, quarreling over a woman.”

He smiled in return. It was genuine. “More significant events have been precipitated by less.”

Helga began to speak.

“Then there will be war.” At this, Meldh nodded.

“And you know that we will win.” At this, Meldh nodded.

“And yet you still will move against us.” At this, Meldh nodded.

“Because you truly, deeply, believe that what you are doing is right.” At this, Meldh nodded.

Helga closed her eyes. No one is the villain of their own story. She stood.
\simpleline
\DatePlace{Estremoz\\
1107 C.E.}

The first thing that Adelberto noticed was the oppressive heat; Évora was known for being warm, but this was bordering on unnatural. These were strange times, but God worked in strange ways. It was a stroke of fortune that this stranger, who was no Christian or Moor, was willing to pay such a handsome sum for such strange cargo. Adelberto was a poultry farmer by trade, he lived a simple life and had simple needs, but in the last six months, he had fallen on difficult times. Even when every last galo came down with the febre vermelha, his Faith never waivered, for the galinhas were unaffected. This gave him at least a few months time. He was confident that the Lord would provide, and He did.

The man was waiting, as promised. He stood near a circle drawn in the ground with chalk. There were five buildings nearby that looked new’ in fact, they looked like cages, but Adelberto could not think of any beast large enough to warrant a prison that large. He then thought about his cargo, and what would happen if it were discovered. The local authorities were friends of the Lord, it was doubtful they would care about some leftover weapons from the Reconquista. Crates of scimitars. Piles of nooses. They were tools of the Lord; their victims were simply Moors.

The man spoke. “Ola amigo. Leve o seu ouro, deixar o vagão, em seguida, partem. Egeustimentis.” The man shook Adelberto’s hand, and Adelberto shuddered for a moment, but complied. Quickly.

The man removed the tools from the wagon. He breathed in deeply, then began the chant.

“…Eu dar-lhe um Nome, eo Nome é perdido . Eu dou-lhe o sangue de fora da minha veia , e uma pena eu puxei de asa de um anjo . Eu chamo -lhe nomes, de meu senhor, meu senhor . Eu convoco com veneno e chamar de dor. Eu abrir o caminho e eu abrir os portões. Vem. Vem…”

He closed his eyes, and felt the heat from the five caged dragons begin to dissipate, counterbalanced by an unnatural chill. Well. That had worked.

In his mind, he retreated to a comforting mantra, the one that had guided him for so many centuries, his battlecry. With intense effort, he whipped his wand out and enveloped the darkness with light.

The chill lifted. Soon enough, he would ensure that the counterspell was lost forever, but he still had much work to do. He pointed his wand at one of the cages containing the Welsh Green, and fired off a spell at each cage in rapid succession.

\emph{“AVADAKEDAVRA AVADAKEDAVRA AVADAKEDAVRA AVADAKEDAVRA AVADAKEDAVRA!”}

He was preparing for war, and he was building his army.