\section{Omake – Trump Card}

Author’s note:
A large portion of this dialog is borrowed from HPMOR, starting with “When I had devised my great creation…” and ending with “…from where he stood by the cauldron.”

Igbo-Ukwu 
Present Day

She-Who-Calls-The-Dead and her nameless daughter fluttered through the sky, following the elder human and younger human, who walked hand-in-hand towards the Dead Place. Here and there, they pecked at holes in the ground that they thought might contain worms, or perhaps a nice, fat bug or two. After some time, the two humans stopped.

“The elder one will be greeted by Grandmother Death shortly, youngling.”

“How do you know this, mother?”

She-Who-Calls-The-Dead lifted her beak in the air, and ruffled her wings. “There is a smell about the air, a feel to the wind. You will learn it in time, dear. For now, you can simply trust me.”

“I’m scared.”

“As you should be, but you will be safe. The spirits of human-kind are big, and they are frightening, but they cannot harm you. We must do as we have always done. We will call to them, mimicking the voice of their ancestors. Their ancestors will call to them as well. And they must choose which call to follow to the Sunless Lands.”

“And if they choose to follow us?”

“Then you shall gain a Spirit, daughter. And you shall gain your name.”

“But what of them?”

“What happens to the humans when they pass into the Sunless Lands, I do not know. We birds hear much, but that is beyond even our reach.”

“How many Spirits do you have, mother?”

She-Who-Calls-The-Dead cocked her head. “You will learn in time that is not a question you should ask aloud. The truthful answer is, I do not know. I lost count around one hundred and seven.”

Her nameless daughter cawed in surprise. “What are they doing now?”

“They are telling their stories. They are people of stories, of tales, like we are. They are telling the tale of the All-Conqueror, who created his own twin in order to help him rule the world. His twin then rose up and imprisoned him. Despite this, the All-Conqueror still offered his counsel from beyond the walls of his prison. Together, they flew to the Sunless Lands and conquered Grandmother Death.

“The women of the tribe tell a different version of the story altogether. In their story, the All-Conqueror creates his own twin without intending to do so. The two are mortal enemies from the very beginning, and after many long seasons of war, the twin finally defeats the All-Conqueror, whose mind has grown frail with the rot of evil.”

There was silence for a time as She-Who-Calls-The-Dead pecked at the ground, idly. After a bit, her daughter spoke.

“Which one is the true tale?”

“Ah, my daughter. Well, we birds have our own tale as well. Come, roost. We have time to wait before we must make our calls. I shall tell you our story.”

Hogwarts Castle
June 13th, 1992
Another Time, Another Place

“My original plan this evening was to retrieve the Sorcerer’s Stone from the Mirror, and then dispose of you. However, I was visited by a prophecy a few short hours ago, which has significantly altered the course of my plans. Something about the words and the images they invoked indicated that the very threads of time are tangled and looped, which makes this prophecy all the more dangerous, even moreso than the one that marks you as the destroyer of this world.

“Simply put, new information was revealed to me, and I see that there is something far greater at stake than this world: all worlds. It seemed that I have a choice. The particulars of the prophecy, I shall not share, but there is one portion that I believe is for the ears of both Tom Riddles.”

The Professor closed his eyes, and when he spoke, it was not his own voice, it was a hollow, clipped imitation, and the echoed syllables carried with them meaning far beyond the words themselves.

“YOU MUST CHOOSE TO FOLLOW THE PHOENIX OR SOLVE THE RIDDLE”

He opened his eyes. “It seems that fate has a sense of humor when it comes to wordplay. There are several levels of meaning to that, some more obvious than others, and in due time you will discover that meaning for yourself.

“The most surface level interpretation, and thus the one most generally applicable, is the choice I face tonight: do I follow the Phoenix or do I solve the Riddle? Every problem, every great catastrophe that has befell our world has a cause and an effect. Are you familiar with the tale of Estremoz?”

“No.” Harry responded flatly.

“Estremoz was once a grand and glorious city, where wizards flourished in peace. Many great magical innovations were made there, and it was a hub of culture and art. A great wizard known only to the world as Lord Foul was concerned with the fate of this world, much as I am, and was convinced that the four founders of Hogwarts were misguided in teaching such terrible, dangerous magics to young students who could barely contain their powers. And so he threatened war upon them.

“He summoned a great and terrible beast, thought by many to be indestructible, from the depths of the underworld, and he set this beast upon the city of Estremoz. And so, the four founders had a choice: they could band together and protect the city, or they could band together and fight the wizard who summoned the threat and prevent it from ever happening again.

“It is a variation on the trolley problem, which given your Muggle upbringings, I am quite sure you are familiar with.”

Harry nodded.

“And so, when presented with a problem with a clear cause and clear effect, do you address the effect immediately, saving a handful of lives in the short term? Or do you address the cause, allowing the effect to go unchecked, but hopefully saving many more in the long run?”

“Both. You always strive for both. It doesn’t have to be a choice. You cheat. You win.” Harry’s reply was more passionate than he intended.

The Professor laughed. “Are you so sure you were not a Gryffindor? That was Godric’s response as well. But he learned, as you will one day learn, that one person simply cannot do everything, that hard choices must be made, that you cannot always have your cake and eat it too. That being said: you are forced to pick between the two. Which do you pick?”

“If I had to choose, well, you do what saves the most lives in the long run. That’s what you have to do. That’s with any sane, rational, good person would do.”

At this, Quirrell smiled. It was a cruel, condescending smile. It carried no hint of mirth. “Yes, yes indeed. And that is with the founders did. And so they ended Lord Foul’s reign of terror. His great beast, the Tarrasque, it razed the city of Estremoz. Left unchecked, it rampaged through the beautiful marble buildings, and killed every man, woman, and child, before it went to hunt those who had escaped.

“How the Tarrasque was contained is unknown, and there are several legends that attempts to explain this. A popular tale that is tangentially relevant to our current situation is that one of the escapees was in possession of the true Cloak of Invisibility. With it, he was able to hide from the Tarrasque, who was bade with the task of extermination. Absent a master to call it down, it would not rest until it had completed its goal. And so it wandered the world in search of its final quarry.

“The legend says that the sons of that man laid the Cloak over him on his death bed, and that he passed me on this world of life from underneath that shroud. And thus his passing went unnoticed by the beast. So to this day the Tarrasque still wanders, searching in vain.

“The loss of Estremoz was a terrible tragedy, and the wizarding world blamed the founders. Despite doing the right thing, they were cursed for it, hated for it. It is amusing how they were cursed by virtue of their ability. No one cursed the common simpleton who had neither the strength nor will to fight such a beast. No, they cursed the only people who could possibly protect them. If Dumbledore were not intercepting your mail, refusing the petitions of countless hundreds from every corner of the globe, you would see how people curse your name, how they hate you for doing nothing to solve their mean, personal little tragedies.

That is the curse of competence, that you are forced to make those choices, between ‘right’ and ‘more right’. And so that brings us to now. When I had devised my great creation and come into the fullness of my magic, I thought the time had come for me to take political power into my hands. It would be inconvenient, certainly, and take up my time in ways that were not enjoyable. But I knew the Muggles would eventually destroy the world or make war on wizardkind or both, and something had to be done if I was not to wander a dead or dull world through my eternity. Having attained immortality I needed a new ambition to occupy my decades, and to prevent the Muggles from ruining everything seemed a goal of acceptable scope and difficulty.

“It is a source of continual amusement to me that I, of all people, am the only one really taking action towards that end. Though I suppose it would make sense for the mortal insects not to care about their world’s end; why should they, when they are just going to die regardless, and can save themselves the inconvenience of trying to do anything difficult along the way?

“But I digress. I saw how Dumbledore had risen to power from his defeat of Grindelwald, so I thought I would do the same. I had long ago taken my vengeance on David Monroe – he was an annoyance from my year in Slytherin – so I bethought to also steal his identity, and wipe out his family to make myself heir of his House. And I conceived also a great foe for David Monroe to fight, the most terrifying Dark Lord imaginable, clever beyond reckoning; more dangerous by far than Grindelwald, for his intelligence would be perfected in all the ways that Grindelwald had been flawed and self-destructive. A Dark Lord who would do his cunning utmost to disrupt the alliances who would fight him, a Dark Lord who would command the deepest loyalty from his followers through his oratical skills. The most dreadful Dark Lord who had ever threatened Britain or the world, that was who David Monroe would defeat.”

Professor Quirrell’s mallet struck a bellflower and then a different pale flower with two more thuds. “But then, while I had sometimes played the part of Dark Wizard in my wanderings, I had never adopted the identity of a full-fledged Dark Lord with underlings and a political agenda. I had no practice at the task, and I was mindful of the story of Dark Evangel and the disaster of her first public appearance. According to what she said afterward, she had meant to call herself the Walking Catastrophe and the Apostle of Darkness, but in the excitement of the moment she introduced herself as the Apostrophe of Darkness instead. After that she had to ruin two entire villages before anyone took her seriously.”

“So you decided to try a small-scale experiment first,” Harry said. A sickness rose up in him, because in that moment Harry understood, he saw himself reflected; the next step was just what Harry himself would have done, if he’d had no trace of ethics whatsoever, if he’d been that empty inside. “You created a disposable identity, to learn how the ropes worked, and get your mistakes out of the way.”

“Indeed. Before becoming a truly terrible Dark Lord for David Monroe to fight, I first created for practice the persona of a Dark Lord with glowing red eyes, pointlessly cruel to his underlings, pursuing a political agenda of naked personal ambition combined with blood purism as argued by drunks in Knockturn Alley. My first underlings were hired in a tavern, given cloaks and skull masks, and told to introduce themselves as Death Eaters.”

The sick sense of understanding deepened, in the pit of Harry’s stomach. “And you called yourself Voldemort.”

“Just so, General Chaos.” Professor Quirrell was grinning, from where he stood by the cauldron. “You, the destroyer of worlds, I could trivially end your threat. In doing so, I would save this world. But it may come at the price of losing everything. In those hours between hearing the prophecy and now, I have done a great deal of thinking, and have devised a plan. Either way, I suspect it shall end in my favor.

“Despite everything, you still see the good in people. You still trust the democracy of idiots. I plan to disavow you of that trust. I will use the Stone to revive myself to my full glory as Lord Voldemort. And, I shall further use it to revive your friend, Miss Granger. The world can ill afford another wizarding war, and so I will enter the world of mundane politics. Cornelius Fudge has six years left on his term, at which point coincidentally, according to our ancient customs, Miss Granger will be of age to oppose me in my bid to become Minister for Magic.”

Harry could already see where this is going, and interrupted, “That’s a rigged game. I will not play it. People would vote for you out of fear, they would remember the last war, they would not vote for you because they truly thought it was right.”

“Of course you are correct, Mr. Potter. That is why I would publicly take the Unbreakable Vow, I would bind myself to not extract any sort of revenge or harm upon any of those who may choose to vote against me.

“You will have six years to groom her, The Girl Who Revived, to battle for the souls of this country against He Who Must Not Be Named. Six years to employ all your tools of reason and persuasion to oppose me while I appeal to the dark heart of humanity. You know that I am not a good person, Potter, and I will not attempt to disguise that fact. I will openly display my vileness. I will call people to me with my cries of intolerance and wanton displays of ignorance. And you, Mr. Potter, will see the folly of trust.”

Igbo-Ukwu 
Present Day

“But how, mother? Why? Why did the people choose evil over good? How can this be true?”

She-Who-Calls-The-Dead cocked her head, and flapped her wings gently towards her daughter. “No one believes what they are doing is evil. When doing wicked deeds, one believes that one is choosing from the lesser of two evils. Or worse still, the greater of two goods.

“And furthermore, I did not say the story was true. We are Drongo birds. We are tricksters, for every truth we tell, we tell ten falsehoods. It is our nature.”

“But tell me mother, I must know. Is this a true tale? Or is this a falsehood?”

Her mother cawed. “That is the curse of the Drongo bird. We may never know. Now, come. They are standing, it is almost time.”