\chapter[The Sudden Stop]
\DatePlace[The Palace at Arcadia]
903 C.E.

\lettrine{“K}{night} to C3.”
“Clever. Now, tell me more about this woman. Bishop to C5.”

“We are kindred spirits. She was chosen by one of yours: Gom’Jorbol of the Rod. She is an artificer. She… creates things. Rook to E8, check.”

“Ah yes… Little Gus. That problem has taken care of itself. King to F1. And this is why you are enamored with her, because of her, ah, creative potential?” He trailed off with a smile.

“Don’t be crude. Yes, she is beautiful. But beauty is cheap. We are all beautiful,” Meldh gestured at Merlin and the glittering palace of glass in which they currently sat. Even their Shatranj board was of such superlative quality that to disturb it seemed somehow profane. “Bishop to E6.”

“Bishop to B6. Your queen is captured. And, she has sent word to you, I hear. We had bade her to make her leave of Greece centuries before, to attempt to recover the Cup of Midnight. From my understanding, even though it was lost, she has been pining over it for ages.”

“Bishop to C4, check. Yes, she has. She has been attempting to recreate it. I suspect she has succeeded.”

A pause. Considering the moves…

“King to G1. And if she has?”

Another pause.

“Knight to E2, check.”

“King to F1.” Another pause. “And if she has?” Merlin repeated.

“She is useful.”

“I never said she was not.”

“I… I have brought this up before, as have you. We have sought to make our union a Triumverate for some time. Have you reconsidered–”

“Make your move.”

“Have you reconsidered your position?”

“Make your move.”

He sighed. “Knight to D4.”

“Thank you. She must prove herself to us, not the other way around. Until that happens, no I have not reconsidered. King to G1.”

“Knight to E2, check.”

“Testy, testy. King to F1.”

“Knight to C3, check.”

“King to G1.”

“Pawn to B6.”

“My, my. Have I struck a nerve? Queen to B4.”

“Don’t be ridiculous. Rook to A4.”

The banter had slowed; Merlin was actually paying attention to the game, now. “Queen to… B6.”

An immediate response: “Knight to D1.”

A pause. “Pawn to H3.”

Meldh actually laughed. “Rook to A2.”

“King to H2.”

“Knight to F2. If she has succeeded, what are your plans?”

“Rook to E1. Just ask me if I plan to kill her.”

“My Rook to E1, thank you for that. Do you plan to kill her?”

“Queen to D8, check. No, I do not.”

A slight hint of relief. “Bishop to F8. Then what are your plans?”

Merlin studied the board for a moment. The moment stretched into a beat, and the beat stretched into a pause. “Damnit.” He swept his hand across the board and knocked the pieces to the floor. The White King shattered when it struck the floor. “Knight to E1, Bishop to D5, Knight to F3, Knight to E4, Queen to B8, Pawn to B5, Pawn to H4, Pawn to H5, Knight to E5, King to G7, King to G1, Bishop to C5, check, Knight to F1, Knight to G3, check, King to E1, Bishop to B4, check, King to D1, Bishop to B3, check, King to C1, Knight to E2, check, King to B1, Knight to C3, check, King to C1, Rook to C2, checkmate, you win. Go, and speak to your lady, find what you can, and meet me upon the Shores once you have news.”

“Yes, master.”

“And, Meldh?”

“Yes?”

“Brilliant game.”

“Thank you.”
\simpleline
In a world rife with possibilities, such as one containing Magic, it is no small wonder that many clever individuals have discovered the secret (or one of many secrets) to what some might call “immortality”. A clever theorist would come up with at least half a dozen means of achieving this goal, without even trying particularly hard. And yet, there are so few to ascend to the ranks of the deathless. This speaks to something; perhaps the stolid devotion of Wizardkind to their outmoded ideals of “light” and “dark”. Or, perhaps it speaks more to those who glibly remark on what should be possible in theory, without paying any heed to the world at large around them.

Regardless, there are those who have ascended. There is an upper limit to what one can accomplish by oneself before simply growing bored; this is a fact that applies to the immortal even more so. So it is only natural that like would seek like, for companionship, guidance, wisdom, a different perspective, or simply for entertainment.

Further, in a world where knowledge is tantamount to power, those who are driven by curiosity, and have the means to pursue that curiosity for as long as they wish, have an undue amount of influence on the course of events in the world. Short-sighted scholars of Magical history have suggested that Greece was once the location of “Atlantis” (whatever that might mean), and that the blood of the ancients flows most strongly there, and this must be why Greece has played such a central role in history.

The reality of the situation, (as reality often is), happens to be far more arbitrary and capricious. A handful of Ancients once made a particular mountain their home, eons ago, and over the ages they attracted more of their kind like a lightning rod. They were not always discrete with their secrets, and so their numbers and influence only multiplied.

Thomas Malthus would not be born until nearly a millennium later, so perhaps their slightly blasé attitude towards population growth may be excused. But in spite of their numerous peccadilloes with mere mortals, among them was one rule that seemed to go unspoken yet universally understood: it does not do for a God to fall in love with a God.

Trust is delicate and finite. It is the ultimate expression of entropy. Trust is a delicate menagerie of spun-glass sculptures, resting precariously upon the shelf of one’s psyche. All it takes is one careless hand, and the world comes toppling down, never to be recovered.

A life can be reconstructed, the fractured pieces of one’s soul picked back up and stitched together, placed in a new vessel to persist. One can pierce the veil of the worlds, like an arrow shot into the ether, peeling back the layers of time in order to reach back into a distant era where the mind and the being was still intact. But that arrow shoots in both directions, for what is done is done, has been done, and always will be done. If an entire life can be reconstructed from the faintest echoes of time and space, so too can a memory of one single mistake.

And unfortunately, immortality provides one with an eternal lifetime of opportunities to make mistakes.

\simpleline

\DatePlace[Glen Nevis, Scotland
903 C.E.]

“I know that it’s unbecoming to gush over one’s own creation, but this could change everything.” Helga Hufflepuff grinned widely at her companion, Hankerton Humble.

“The Cup of Midnight…. I know that you — Wait. How certain are you that this room is secure?”

“Quite certain. Godric has quite the talent for such charms.”

Humble winced at the name. “Yes. Godric. And where is he now?”

Helga cocked her eyebrow. Her eyes were suspicious, but her face was smiling. “Do I detect jealousy?”

He barked out a laugh, just a fraction of an instant too quickly. They had known each other for a long time, perhaps too long. She immediately knew from the clipped tone and the just-too-quick reaction that it was a forced laugh. She knew. And he knew that she knew. Attempts to dissemble would be pointless. “Yes. Obviously. He is young. He is objectively attractive; I have seen him when he bathes at the river.”

At this, Helga laughed, and this time it was genuine. “It’s not even midday, and already you put such ideas in my mind.”

Hankerton smiled at this, as well. “The lady of the house having a lascivious tryst with the virile servant boy… Well, clichés are clichés for a reason”.

She ran her hand through his hair. “Please. Yes, they are clichés because they are so blindingly obvious that one would have to be a fool to fall into their trap. Now, stop being silly. Will you be a dear and animate this for me? I don’t think the effect will be quite as spectacular if I demonstrate on something of my own creation.”

“Expecto Patronum”, he whispered. Hankerton Humble’s life force, a very small measure of it, shot from his wand and into the clay golem that Helga Hufflepuff held in her hand. It twisted back, sleepily, stretched out its arms, and looked up expectantly. He could see from its body language that it was a bit annoyed. The thin slit on its face split open and it spoke.

“Lovely. I suppose I should not get too attached to this life. It won’t be much of a loss, I can barely think properly with such a rudimentary form.”

“But you are sentient, yes?” Humble asked his alternate self.

“Yes, although that is exactly what a non-sentient golem would say, now, isn’t it? So to that end: 927 πατάτα.”

He mentally noted the code, and would not use it again. “Yes, he is sentient.”

Helga watched the proceedings with interest. “Perfect. Now, observe.” She delicately cradled her jeweled teacup. It did not look like the original Cup of Midnight, which was deliberately grandiose, meant to serve as a stark contrast to the plain wooden Cup of Dawn. But its essence was unmistakable. The thick black Nothing contained within its bonds poured out slowly, a single drop flowing through the air.

There was enough Void within the Cup to bind the entirety of life, both now and forever. Used in such a fashion, it would render the cup useless forever afterwards. But there was also enough Void within the Cup to selective bind one person at a time for as long as once cared to do so.

The Void was diffuse, almost transparent, and settled upon the golem. It looked up, quizzically. It felt different.

The man who called himself “Hankerton Humble” was, in no uncertain terms, the world’s most foremost expert in the subject of mental magic. He could see the subtle shift in behavior even in something as rudimentary as an animate clay statue. “There is… a degree of flexibility to the control you can exert, correct?”

“Yes. It is similar in function to the Unbreakable Vow.”

Yes, that made sense. The field of mind control was either achingly simple, or absurdly complex, depending on whether you were considering the ends or the means. If one is simply concerned with extracting a specific behavior from a specific subject, once scarcely needs magic at all. Criminals from all walks of life, magical or not, are quite familiar with a shockingly effective spell whose incantation sounds something like, “Do what I say or I will torture and kill your family.”

Humble had performed experiments to this effect, examining the inner workings of a person’s mind when put under duress. Like the limbs of an animal exposed to an electric current, the mind would instinctively flinch and react in response to certain stimulus. The “Lethe Touch”, as it had come to be known, operated on this basic principle, albeit on a more granular level. Further, it lent those changes a degree of permanency with its magic.

Spells such as Legilimens or concoctions such as a Love Potion, worked on a different premise entirely. They created a compulsion within the subject’s mind, as difficult to ignore as a loud bang or a bright flash of light. The greater the magic of the caster, the more intense the stimuli. The greater the will of the victim, the easier it is to ignore. But because this is an outside intrusion, the mind actively works to resist it, to eject it, and as such the magic required to sustain such a compulsion grows exponentially over time.

The Unforgivable curse, Imperio, operated in a different fashion as well: the connection between the victim’s mind and body was, to an extent, severed, and replaced by the will of the caster. Such bonds between the soul and body are not permanent, they are in fact regenerated on a moment by moment basis, so without a sustaining flow of magic from the caster, the victim’s minds would regain complete control within an hour or so. This meant that for Imperio to be truly effective, it required the conscious attention and direction of the caster, rendering it impractical in many and most cases.

The old adage, “It is easier to create than destroy”, is actually quite untrue when it comes to Magic, and especially so in the realm of mind control. The mind is quite capable, (perhaps too capable), of visualizing abstract concepts; it’s the fine details it struggles with. Tell a person to think of a loved one, and they’ll have no trouble picture their face. They’ll them to draw that same face from memory and they’ll likely fail miserably.

One of the most simplistic explanations of Magic is that it simply completes these mental images from their patterns. It’s a very neat and tidy explanation, (which is why it fell into such favor during the Muggle Dark Ages), and it conveys in simple terms one of the key limitations of Magic: Form requires Substance. Magic can take the imaginary Form of a cat, and make it real. An imaginary cat may run like a cat, purr like a cat, stalk like a cat. After all, this is what truly makes a cat a cat. And yet, it does not bleed like a cat, or digest like a cat. The chemicals in its brian do not interact like that of a cat. All of the mechanical automation that powers the rules and symbols behind a “cat” are fundamentally lacking. There is no Substance to power the Form, and as a result, such creations are rarely long for this world.

The realm of the mind, however, is one of pure Form, and so it is not subject to the same limitations. Creating an idea is trivial. Destroying one is nearly impossible. Even Oblivate does nothing more than sever the connection between a memory and the mind that created it. The memory still exists, it is merely hidden in the mind. A few years, or decades, and those connections will eventually be rediscovered, like a message in a bottle that eventually washes back ashore. But the Unbreakable Vow…

Sacrifice has always been a subject that has fascinated and stymied practitioners of Magical Theory since the dawn of Magic. Something Sacrificed simply cannot be reclaimed. The mechanics of this are hotly debated and not well understood. The end result, however, is inarguable. The Unbreakable Vow quite literally sacrifices the portion of the mind which allows for a certain course of action to even be contemplated. A person Bound in such a way is truly bound for all time. And if this Cup of Midnight operated on the same principle…

“You could destroy the world with this device. You could obliterate the minds of every living being. The Cup would be broken, afterwards, but so too would the world,” Humble said, in quiet awe.

“Yes, I suppose that’s true. But then again, there are countless devices of power of which the same could be said. Even without an artifact, I could think of half a dozen ways to cause mass death without even really trying hard… Transfigure a bit of poison into a town’s water supply… Let loose a hint of Fiendfyre in the middle of a crowded village… Use Salinos to salt the ground and destroy a region’s food supplies… Transmute–”

“Right, right, I get the point. And of course, you would not use it in such a way. But, I do not understand how it functions beyond the scope of a single victim, or perhaps a handful.”

“Ah, yes, the recursion. It took centuries to finally achieve the necessary breakthroughs, and no small Sacrifice. You see, the Cup contains itself, and within it, a piece of my being that powers the recursion.”

Hankerton’s eyes widened. “And so… Unless you were to pass on its secrets to another, you would be unable to recreate another.”

Helga Hufflepuff’s eyes narrowed, “I sense an ulterior motive to that question, but I was never one for plotting. Tell me why you ask, and be truthful.”

Hankerton replied swiftly and truthfully, “You know that I am deeply concerned with the fate of this world, and the threats that we may pose to it. Such a device in the hands of someone malevolent, or even someone foolish, could spell disaster. But you know this. And because you cannot be coerced to make another, the only two points of failure are the Cup itself, and your knowledge of its secrets.”

“Yes, dear.” She walked over to him, and stood close behind him. The back-and-forth, the assumptions and completing of each other’s thoughts, she enjoyed this. She ran her hands through his hair. “Go on.”

“You would have safeguards in place. The same safeguard for both the Cup and its secrets. Something preventing them from being taken by force, or coercion, or duress.”

“Yes,” she spoke. She was in front of him now, her hands wrapped around his waist, her lips softly brushing his ear as she whispered, “Tell me more.”

“A trap, something triggered either by a word, a thought, or a deed. Or, more likely, any of the above. You are powerful enough to resist the majority of attacks, but in the event of the unknown, anyone who accesses the Cup, or the knowledge of its creation, without your explicit consent would trigger the trap.” He thought for a moment, “It would Sacrifice both, to put them safely out of reach, but to what end..? Simply killing the intruder would not be sufficient. Ah, yes… It would Sacrifice the intruder as well. At that point, what is summoned forth by the Sacrifice is inconsequential, no?”

“I wouldn’t say that. It’s an alarm, of sorts. It would alert me,” she slid her hands down his chest as he spoke, “Me and those that I love.” At that word, Humble inhaled sharply. “Would you like to see it? Would you like to… Enter me?”

He let out a soft moan of pleasure, “Oh god, yes. Egeustimentis”

Her mind was a towering castle, a picturesque landscape, a fractal pattern beautiful in its simplicity and infinite in its complexity. He was there as a guest, not as an intruder. Sometimes seeing something from the inside out was far more effective than simple words at communicating a concept. Further, in here there was no need for aliases or secrets. No need for “Helga Hufflepuff” or “Hankerton Humble”. They were simply Meldh and Ollivander.

Their physical forms were, of course, perfect. Because why would they not be? But their mental avatars were beyond perfect, they were the very Platonic ideal of Perfection itself, made real. They strode hand in hand through the glittering palace of her mind. As they walked the halls, he saw libraries, laboratories, factories, workshops, vaults.

Vaults. Hidden things.

Secrets.

Not now. They continued to what was obviously a throne room, the Crown Jewels of her being. He was looking at the Holy Grail. The complexity of it stretched even his own comprehension, a comprehension honed by centuries of study. As ancient as he was, she was older, and her mind could contain entire concepts that he still struggled to simply understand. She sensed his struggle, and obligingly condensed the concept of the Cup into something more manageable.

The Cup was endlessly pouring itself onto its victims. Not pouring its contents but actually pouring itself. Over and over, slowly making its way around the world of life.

“I don’t understand, why the limitation? If it truly contains itself why can it not duplicate? Why can it only fully Bind life once, before being rendered unusable?”

“Simply physically reproducing it is insufficient. Does your reflection have a mind of its own?”

“It depends on the mirror. “

“True.” A pause. The number Three began to pop up in the room countless times. Hundreds of times. The room began to be filled with Threes. “How many Threes are there?”

Instinctively he tried to count and then roughly estimate, but he knew that this was a riddle of words. He stared at the numbers. After time he spoke: “One. There is only one ‘Three’.”

“Correct. Writing down the number “Three” a thousand times does not change its properties, nor does it give the concept more significant or weight or meaning. Three is simply Three. And the Cup is simply the Cup. Another could create a Cup of their own, certainly, but it would be theirs and theirs alone; it would have powers unto itself. But such secrets are ones I shall not pass down.”

The Vaults of her mind were locked with the absence of chains. There were simply no doors, no latches, no surface with which to gain purchase. He could see the intricate webs of magic meant to masquerade as such, webs which would not only destroy the intruder, but further destroy the secrets they sought.

He also saw, beyond the Vaults, a number of lesser compartments, ones which contained secrets no less powerful, but far less guarded. There was one that caught his attention, a fluid room of portraits and memories. He would have been able to resist, if not for a single face he saw, reflected from deep within the folds of the room.

Godric.

She had given him permission to enter her, and so she did not at first detect his absence. It was not until she spoke and heard no response that she realized the violation.

She instantiated next to him, as he roughly pawed through the volumes of memories, all related to that one face, that haughty, insulting, proud young face. It reminded him of himself, in his youth, his true youth. Perhaps it reminded her as well, perhaps that is why–

–The concussive wave of power that forced Meldh from her mind shattered windows, rattled dishes off shelves, and forced the door to the kitchen off of its hinges. It was enough to physically knock him backward into a table, which splintered from the blow.

“You stupid, stupid bastard,” she hissed.

Meldh matched her gaze with anger. “Yes, I suppose I am. To give my heart, to make myself vulnerable to–”

“No, NO, you stupid child. THINK. Think about what you saw, tell me what you saw, you unforgivable… IDIOT!”

Silence.

“Tell me!”

Her words carried with them a palpable hint of power, magic made manifest as needle sharp shrapnel that flew across the room. Meldh instinctively raised his hand in front of his face. The impact was not severe, but it was enough to draw blood. “I saw passion, I saw feelings, I saw the undeniable loops and whorls of Love. The Touch of Truth is inviolate. What I saw I can’t be faked, you can’t tell me that – –”

“What did you see?! Did you see action? Did you see deed?” She advance on him, hotly. He briefly faltered.

“I–”

“You saw nothing. What you saw were the idle fantasies of someone who has lived twice your span, and nothing more. Do you mean to tell me you hold no unacted lust in the dark heart of your mind?”

He saw the opportunity to seize the high ground and he made his move. “Yes. Yes, that is what I mean to tell you. I open my mind to you, lay myself bare. Look. Look inside me.” He roughly grabbed her hand, and placed it forcefully on his shoulder. “Say the words. Say them! Look, and tell me what you see.”

She tried to pull her hand away, but he held it firmly. “And you think your chastity gives you the right to violate me? You think that gives you the right, you think that that justifies– Unhand me, child.” She pulled hard again, and he yanked roughly pulling her close to him. She glared at him, and the temperature in the room dropped several degrees. “I could tear you apart with the flick of my wrist.”

“Could you? Could you really?” With his free hand he shoved her backward, and then slapped her. Hard. “Go on then, do it. Tear me apart.” They stared at each other for a hot moment. The air was electric. Frost formed on the windows and the metallic silverware that lay unused on the table.

Nothing.

“Well?” He demanded. When he received no response, he raised his free hand up again, and grab the braid of her hair. He yanked it back, and pulled her body against his.

As he turned away she spit squarely in his face. He reared his hand back to slap her again, but with the flick of her finger he was hurled backward. He crashed hard into the wall, and the shelves behind him collapsed. He briefly considered a magical counterattack. But from the corner of his eye he glimpsed a copy of one of Godric’s research journals on the desk. He grabbed the book and roughly tore a few pages from them, used them to wipe the saliva from his face, and then spit the blood that had pooled in his mouth. He crumpled the ruined paper, threw it in her face, and turned on his heels to leave. “Give Godric my regards.”

As he took a step, the door slammed shut, and the icy chill that had previously washed the room now dissipated with a THUMP and waves of oppressive heat coursed across Meldh’s body. Ollivander spoke, angrily: “You enter my house as a guest. You entered my mind as a guest. You defiled my house, you defiled my mind. You insulted me, you attacked me, and you think you can just leave? With no consequences?” She grabbed him roughly by the collar of his robes. “I would have given you everything. But you couldn’t just trust me.”

“Would have? You would have given me everything? I did! I did give you everything. I left my kingdom, my country. I gave you everything I have to give. My love. My soul.” He gestured angrily and the simple leather thong around her neck that wore a small silver cross. “Why wasn’t that enough? Why was I never enough for you?”

The anger still hot in her voice, she replied, levelly. “Because you are weak. Look at you, you petulant child. I do not even need to enter your mind to see the tears forming in the corner of your eyes, you boy, you eunuch. I don’t need to violate your trust to see the way your shoulders shake at the insult, to see your fragile male ego come crashing down at the very thought of a woman having an independent desire. Look at you. You are weak. You’re disgusting.”

He angrily pulled her towards him again, “And I don’t need to enter your mind to see your heavy breathing, your dilated pupils… The slick sheen of sweat, the elevated pulse…” He gripped the back of her dress and twisted, ripping them, and then he forced his hands into the tear. “There are certain signs that are unmistakable.”

His slid his hands into the tear in the dress, and caressed her sternum, down to her stomach, down–

With a shuddering moan, she pulled his mouth to hers and they kissed, passionately.
\simpleline

He knew that he should turn away. He knew that if he had courage and integrity, he would turn around, walk away from the window, and go back to his chores as if he saw nothing. What was her business was her business. He had certainly seen the two argue more heatedly than this on more than one occasion. He knew the man was not good enough for her. He knew he should stop them. But he also knew he should walk away and leave her to her own business. Oftentimes, the bravest thing a person can do is to make a difficult choice, knowing that neither one may be right.

Instead, Godric Gryffindor did neither. He stayed at the windowsill, and he watched.
\simpleline

\DatePlace[Knockturn Alley
903 C.E.]

Rupert Scabior gazed nervously into the darkness of Knockturn Alley. “I’m here, sir, I have him,” he called to no one in particular. He thrust forward the unconscious body of the prisoner, with a sack over his head and his arms tied behind his back. Not that it would have mattered, as the prisoner was fully unconscious.

Rupert was no saint, by any stretch. But this whole arrangement made him deeply uncomfortable. Even though he had to verify, firsthand, the horrific nature of his victims’ deeds, even though he personally took no part in the enacting of their punishment, he still felt a twinge of guilt and regret.

But, the pay was good, and he had a family. The only dream he had left in his small, miserable life was that his daughters would be able to rise up beyond their station and make something of themselves and their family name. And this man, his mysterious employer, had seen to it that they had the audience of the greatest tutors in the land.

Inky black shadows writhed in the darkness, and a man in a billowing black cloak stepped into view, surveying the scene. “Good, good. And you are certain, completely certain of his crimes?”

“Yes, master.” Scabior produced the vial containing the silvery, undulating wisps of memory tainted by oily black slicks of Nightmare. “His own niece, sir. This is plucked straight from her unknowing mind.”

The man in the the cloak kneeled down and put a hand to the prisoner’s shoulders, whispering a few words. He nodded with satisfaction. “Yes, this will do. Did you heal her afterwards, erase the traces of this Nightmare?”

Scabior looked around, nervously. He never understood this part of their process, but he had done it dutifully, nonetheless. “Yes, master. She will remember nothing. She slept with a smile for the first time in many seasons.”

“Good.” The man removed the sack from the prisoner’s head and reached his hand into the prisoner’s mouth, who began to awake groggily. Reflexively, still mostly asleep, he tried to speak, but, with several fingers probing roughly inside his mouth, he of course could not. The man’s forefinger and thumb found their way to the back molar, and with preternatural strength, he yanked the tooth roughly from the prisoner’s head. The shock and pain immediately roused him from his stupor, and he began to scream as blood filled his mouth and poured onto the street. The cry was clipped short by–

“AVADA KEDAVRA!”

The green light shot out and illuminated the alleyway briefly, until the entirety of the light was drawn into the single tooth he held in his fingers. When the green glow subsided, he turned towards Scabior. “You may go.”

Scabior needed no further prompting, and quickly made his leave.

Meldh holstered his wand, and with a swift gesture, plucked one of the eyes from the socket of the murdered man. He poured the vial of the child’s nightmare onto the lump of flesh, and it continued to pour, effulgently. As it touched the ruined eye, it reacted, turning a bright flaming red, and it continued overflowing, liquid flame splashing onto the ground, flame which flickered but produced no heat. It poured and poured, grew and grew, and slowly poured itself into the form of a chariot drawn by a horse. Still clutching the tooth, Meldh stepped into the chariot and was carried away.

\simpleline

\DatePlace[On the shores of the lake of teeth, where the black hills end
Tír inna n-Óc]

The lake of teeth was quiet at this time of daynight. The bilious, sulphurous stench that emerged from the archway that stood on the Isle of Woe would not begin to belch forth until at least Midnight. The archway and the forgotten statue of Adrienne the Witch, a hero from a bygone era, were the only two signs that any sort of intelligent life had consciously touched this place.

The archway cast a shadow, although from what direction the void-sun shone was unknowable. Not unknown: unknowable. Within that shadow were more shadows still, and within those further more. From somewhere within the fractal reflection deep within the fractal reflection, a shift occurred, which reverberated exponentially out into this constructed world. The shadows which contained shadows swirled, accommodating their new host.

The black shadow of the first figure stood in stark contrast to the white mist that comprised the second figure. The black shadow held a tooth in his finger, turning it over, inspecting it before flicking it casually into the lake.

“I bring news.”

The second figure waited, expectantly, and gave no acknowledgment.

“The Cup of Midnight is at last recovered. She has recreated it. I’ve seen to it myself.”

The white mist nodded in satisfaction.

“But, please. See that no harm comes to her. I– ”

The white mist held up a single hand, silencing the shadow. After a few tense moments of consideration, the mist spoke: “No harm will come to her. In fact, I will give her her heart’s desire.”

The black shadow shuddered at this, as very rarely did such a promise end well. “Thank you. Please, just… Be kind. She is a good person. She is on our side, whether she realizes it or not.”

“I do not know what you take me for, but I am no monster. She will come to no harm under my hand. Where I you, I would hold yourself to the same standard.”

“I, that’s not–”

But the white mist had already dissipated, for midnight had come sooner than expected. The plumes of sulfur belched forth from the arch, casting aside the last wisps of mist, leaving the inky fractal shadow alone with its thoughts.

Tír inna n-Óc endured.

\simpleline

Diagon Alley
903 C.E.

He was running in circles. He was bound by a rope, stretched beyond its limits. Or, was it a Line? The rope, or the Line, it was staked into the ground. He was a dog, chained. The Line was staked into something important, terribly important, the most important thing. And yet. It eluded him. It was always eluding him.

Maybe. Maybe if you run fast enough. So he ran. He ran faster. He ran fast, so fast, so fast. Around, and around, and around. He ran so fast that he ceased to simply be a point attached to a Line. He was a blurred circle, jagged around the edges but if you screwed up your eyes it looked like one solid shape. A circle, an endless, strange loop of frustration and exasperation. Twice per go-around, he would cross that… that thing, that the Line was staked it. A Path? A Path that stretched backwards into eternity and forward into eternity. But the Line. The Line took the path to a dark place. A dark eternity.

When he crossed the path the first time, he could see them. Her flowing hair. His strong jaw, a family of his own. He saw happiness. And behind the happiness, only a slight fear, the fear of some great Death that was eons away. But that fear was bolstered by hope. Not the empty wish of a dreamer, but the assured hope of an entire civilization fighting together, gladiators. Fighting the Titan, with hope as their weapon, made sharp by the knowledge that from now until the End, if that End came, they would fight, they would fight, they would fight with all of their soul and all of their being and everything they had and would ever have.

But then they were gone. They were so close. But he only saw them for a brief instant as he ran by them. He could reach out and touch them. He did. But they disappeared as he ran, and he kept running, desperately, to see them again, the feel that hope. But each time, he would cross the Path again. And in that world, it was a desolate, empty place. Stagnant. It didn’t smell like Death because there was nothing to smell. An empty, horrifying Nothing. And he wanted nothing than to run away from that Nothing, horrified.

So he did.

He ran and ran and ran until he reached the Path again, until he could feel that brief instant of hope. He kept running. He had to. He was Bound by that Line. The Line. It was always the Line. He knew, somehow he knew. There was no intuition, it was pure reason, but that reason worked from a premise that was lost to Time. Nonetheless, it was true. True but impossible to prove. As true as this is a lie is false. If he could break free of the Line, he could make everything whole, make everything right. The Line took something precious, something valuable, something of the utmost important, something that was lost. He knew that if he just ran faster, the line would diminish, would eventually disappear.

So he ran faster. Faster. And faster. He poured his entire being into running. He sacrificed everything, everyone, just so he could run, faster and faster. He ran until the Line grew smaller. He ran until the line diminished. He ran, and ran, and ran in circles and circles and loops and loops and circles and loops, and ran until all that was left was a fragment of silver, a fraction of a Line.

(black robes, falling)

…blood spills out in litres, and someone screams a word.

Suddenly, without warning or notice, the line began to lengthen. It grew, and grew, and he ran, and ran, but still, it grew, strengthened, bolstered. It could not stop. It wouldn’t stop. It was out of control.

This couldn’t happen. How could it happen? The equation was too perfect. He had seen to it, he had controlled the inputs to thousands of degrees of precision, had guided the thread through every possible eye of every possible needle, but it went wrong, it all went wrong, how could it go wrong? Input, output, functions, decision trees, logic maps and neural nets flicked through his mind, streaming an infinity of possibilities into the span of a single instant. How?

But, the one inexorable truth of the universe, something deeper than any law of “magic”, held him back, stymied his efforts. There is no infinity. If permitted, a pattern will persist, and persist, and persist. If allowed, the digits will keep repeating. The irrational pattern of the numbers will continue and continue as long as you care to generate them. At some point, there has to be a point where you take action, where you decide the the map matches the territory enough to where you can start your great adventure. At some arbitrary point, you have to decide that you have enough significant digits.

It wasn’t enough.

Those forgotten numbers, that endless stream of numbers forever lost, stuck on the wrong side of that arbitrary termination point. They add up. And after millions upon millions of inputs and outputs and combinations and permutations, they all added up, added up to one choice, one crux. Like a fist with a limitless number of fingers, closing one at a time, until all that remained were the two choices, a finger and a thumb, poised to snap. If they did, all would be lost. The Path would never be made whole. From outside, a woman screamed, long and loud. The scream of a dying woman.Within a moment, another cry joined with the first: the sound of a hundred phoenixes, their call like the birth of a new world.

He turned.

And heard the snap.

Merlin awoke, screaming

