\chapter{If Only In My Dreams}

\DatePlace{Outside Time\\
Outside Time}

The Mirror stood, inviolate and whole. Harry watched Dumbledore patiently through the Mirror of Noitilov. It stirred echoes within his mind of an ancient time, in an ancient place, when he was younger so, so much younger.

A voice from behind the mirror spoke up. “Why, look at that,” the Professor spoke, mimicking history. “I don’t seem to have a reflection any more.”

From inside the mirror, a voice cried out. “No,” said Albus Dumbledore. “No, no, NO! ” Into the hand of Albus Dumbledore flew from his sleeve his long, dark-grey wand, and in his other hand, as though from nowhere, appeared a short rod of dark stone. Albus Dumbledore threw these both violently aside.

The Professor stood ready, catching the Line of Merlin as it passed over the threshold of the Mirror. In the meantime, the scene shifted to a conflagration of fire and light. For a timeless moment, the boundaries of the End of Time felt malleable. As the star was torn apart, Harry stood up and sighed.

“Well, I guess that’s my cue. I’ve got a lot of work to do, huh?”

“I’ve never been one for protracted goodbyes. Besides, it will be much, much longer for you than it will be for me. In fact, in some ways, this is goodbye, forever.”

The exchanged tittles and jots, but Harry wasn’t really fully engaged; his attention was diverted elsewhere. He was watching his friends through the mirror, knowing that for many of them, it would be the last time he saw them as they were.  But most of all, he watched Hermione.

“Well… I’ll see you in another 26,000 years. Or something like that,”

And with that, he stepped through the Mirror, and into the Tower.
\simpleline

\DatePlace{The Tower\\
December 25, 1999, Twelve Hours Later}

As the hours waned on, he typed away at the computer terminal, making the final preparations. He needed to make sure that after the Transmigration, he was well-equipped to continue the problem at hand. He was still the Crux, the Once and Future King, and memories or no, he was still responsible for the fate of the world. He didn’t notice the sounds of the radio in the corner, or the sharp pop that reverberated from the Receiving Room moments earlier, or the soft rapping at the door to his office.

…Poor old Jim’s white as a ghost, he’s found the answer that we lost

We’re all weeping now, weeping because, there ain’t nothing we can do to protect you…

The rapping grew more insistent. “Enter,” he spoke.

The door opened, and Hermione walked inside. “That’s a rather rude way to greet your guests, don’t you think?”

Harry was distracted, and he didn’t look up. He was still staring at the innumerable lines of code that filled his screen. “Huh? Oh. Yeah. Sorry. Uh… Hi Luna.”

Hermione coughed. “Hello, Harry.”

He looked up, embarrassed. He stammered a weak apology, and turned back to the computer. She looked around the room, distantly considering everything. She had a soft, peaceful smile on her face as she watched Harry work. He continued to type, type, type away as she stood, silent. Eventually, he became self-conscious of her presence, and the typing slowed, and eventually stopped, as Harry turned around, expectantly.

Hermione said nothing. She walked to where Harry was working, leaned over, and turned off his computer monitor.

“Hermione, wha–”

She took his hands, and pulled him up from his seat. Even though the gesture was purely symbolic, it did have an effect. Harry felt, in some distant way, like he was carrying a great weight around his neck. With the monitor switched off, he felt that the weight had been temporarily lifted. He looked at Hermione.

She still said nothing. Harry looked tired, so very tired. So very tired, and so very alone. He had been in a solitary prison of his own making, both literally and metaphorically, for many long years. Hermione smiled distantly at the soft music echoing from the radio.

“This song does seem out of place, doesn’t it?” She remarked.

…O children, lift up your voice, lift up your voice…

She held both his hands, and took a step backward. She started to sway her shoulders back and forth in time with the music.

…O children, rejoice, rejoice…

She cocked her head at Harry, who reluctantly joined in. They held each other’s hands, moving in an awkward little dance. It reminded him a bit of the bumbling fourth-year students that he watched at the Yule Ball so long ago during his first year at Hogwarts. Harry didn’t dance, no one ever taught him, and he certainly had no experience or occasion to practice.

Hermione didn’t seem to mind. She lifted one of his hands up, and spun him.

…Hey little train, we’re jumping on, the train that goes to the Kingdom

We’re happy, Ma, we’re having fun, and the train ain’t even left the station…

He laughed, silently, as they waltzed around the room, sometimes falling completely off-beat with the music which had started to pick up in tempo a bit. He felt guilty, though. This was time he could be spending working, but he was wasting it on frivolities. Hermione seemed to sense this shift in Harry’s emotions, and pulled him closer.

…Hey, little train, wait for me, I once was blind but now I see

Have you left a seat for me? Is that such a stretch of the imagination…

He couldn’t abandon his quest to save the world. But then again, wasn’t she part of that world? The enormity of it all, of the path that lay before him and the path that he had already walked down, seemed to crash in on him all at once.

What was he going to do? He thought back to the ancient times, remembering one of their arguments.

“I understand why you did what you did today,” Hermione said. “But I want you to promise that from now on, you’ll ask me first, always, even if you can come up with a reason why you shouldn’t.”

There was a pause that stretched, and Hermione could feel her heart sinking.

“Hermione -” Harry started to say.

“Why? ” The frustration burst out into her voice. “Why is it so awful? All you have to do is ask!”

He did the only thing he could think to do, and buried his head in her shoulder and began to cry, softly. They weren’t tears of woe or self-pity. They were the angry, hot tears of resolve. He felt Hermione’s hand on the top his head, patting his hair gently. He was a soldier in the war. An important soldier, but a soldier nonetheless. And no soldier can fight on the front lines twenty-four hours a day.

…Hey little train, wait for me, I was held in chains but now I’m free

I’m hanging in there, don’t you see, in this process of elimination…

He gave in, temporarily surrendered himself to this brief moment of respite. He knew, in his heart of hearts, that he would never give up the battle, that taking one break to have one silly dance would not be the end of the world, and that, it might, in fact, make the world better in its own special way.

…Hey little train, we’re jumping on, the train that goes to the Kingdom

We’re happy, Ma, we’re having fun, it’s beyond my wildest expectation…

They continued to shuffle back and forth to the music, their heads on each other’s shoulders. They held each other as the music and began to slowly fade away. The tears were gone.

…Hey little train, we’re jumping on, the train that goes to the Kingdom

We’re happy, Ma, we’re having fun, and the train ain’t even left the station…

The music faded out, and Harry and Hermione separated, looking at each other, so much unsaid, so much that did not need to be said. He closed his eyes. He thought back to the promise he made, so long ago…

“I don’t think you understand at all! ” Hermione said sharply. “You said we’d be partners, Harry!”

That stopped him, she could see it stop him.

“How about this?” Harry said at last. “I’ll promise to ask you first before I do anything that could be interpreted as meddling in your affairs. Only you’ve got to promise me to be reasonable, Hermione. I mean really, genuinely, stop and think for twenty seconds first, treat it as a real choice..”

“I shouldn’t have to make promises,” she said, “just to be consulted about my own life.” She turned from Harry and began walking toward the Ravenclaw tower, not looking at him. “But I’ll think about it, anyway.”

How could he keep that promise? The risk, no matter how slight, of her saying “No”, was unacceptable. Well, no, that’s wasn’t quite true. He was going to follow through with the plan, regardless. So why even bother soliciting her opinion if he had no plans of taking it into account?  That was just a cruel form of self-deception; going through the motions of friendship with nothing real behind it.

Maybe the Professor really was right, that Harry was simply playing the role of someone who had friends. His head still hurt from thinking about it. Was he considering telling her because he was truly Hermione’s friend, or simply because he was playing the role? Was asking that question in the first place indicative that he had her best interests at heart? Or was that just precisely what someone who was playing the role would do when confronted with the truth?  That kind of thinking was a self-destructive spiral; once you begin doubting your own volition, there’s no end to the questions.

Those questions had served him well in the past, but this was reality, or at least, it was about to be, and at some point, action had to be taken, decisions had to made. He was bound by a Vow to–

He stopped for a moment. He had considered it. He had truly considered it. He was weighing the value.  The very fact that he was even allowed to consider the question was significant: Somewhere in the deepest recesses of his mind, he knew beyond reasonable doubt, that it was safe, that telling Hermione was the right thing to do. He didn’t need to consider the levels upon levels, he didn’t need to question his own volition, he had a built-in barometer of his own internal continuity, free from cognitive biases.

He smiled. Even at the end of it all, he still found a way to cheat.

“Hermione, I… Uh… Thank you for that. I feel better. I really do.”

Hermione smiled. “I know, Harry.” She leaned forward and planted a kiss on his forehead. “That’s what friends are for. Don’t you ever forget that.”

Harry heard hurried footsteps from down the hall as Hermione turned to leave. As she opened the door–

“Hermione,” two voices spoke at once.  Harry’s own, and a voice from down the hall. Was that… Draco?

Hermione paused, her veins frozen. At one point, she had thought this moment might come, that she would have to choose between the two of them. But that was ridiculous, the stuff of cheap dime novels. Two boys happening to fall for the same girl was unrealistic although not implausible. But two boys choosing to confess their feelings at the exact same moment at the exact same place?

She had once told Harry that sometimes, life was, in fact, like a play. But most of the time, it wasn’t.

Harry must have seen her apprehension and the slight stiffening of her posture, because he began to laugh. It was a nice, pleasant sound, free from the burden of responsibility. For once, there was no deliberation on his part, the course of action was so straightforward, so clear for him. The situation really was quite comical, when viewed from the outside. He could see why she was nervous, and as amusing as it was, Harry was quite sure that Hermione did not find it so. “Go to him. What I have to say… it’s not about that,” he had to purse his lips  to prevent himself from grinning.

Hermione visibly relaxed, and now she was the one grinning. “I.. um.. Okay. I’ll be back in a minute.”

“Sure thing. It can wait. Believe me.”

“Hermione…” said Harry. “I’ve been watching you and thinking, since the day you said you were going to be a hero. You’ve got the courage. You’ll fight for what’s right, even in the face of enemies that would scare other people away. You’ve certainly got the raw intelligence for it, and you’re probably a better person inside than I am…”

It was convenient that Draco was there. It was fitting. From the beginning, and now at the end, they were The Three, and they were equals. There were no disposable lieutenants, no trusted confidantes. It was just Harry, Draco, and Hermione. And so, Harry waited patiently for his friends to arrive
\simpleline

\DatePlace{Somewhere above Russia\\
December 25, 1999}

High above them,  six hundred kilometers high, so that its field of view encompassed the whole planet, the Mirror hung in the exosphere. The anchors were gone, save for two: the Mirror itself, and the Line, which was in the process of passing out of this world.  Everything that ever was and everything that ever will be in the universe had led to this moment. This moment that must come to pass because it already has. All worlds had narrowed to two, and from those two all worlds would be born.

As it did so, the Mirror was completing its final task, rebuilding the world according to the designs of its master. It acted more efficiently than the most elite Obliviators could ever imagine was possible, with not a single iota of effort being wasted. Memories were rewritten as self-consistently as possible so as to require the least amount of intrusion, physical space was only recreated when absolutely necessary.

It was tasked not only with erasing all memories of the taint of Magic, but also fixing the world beyond the point of certitude onto the path of the Scorpion and the Archer. Lives were altered, backstories created and destroyed, stories written and rewritten.

When the last tales were spun, there was one final thing to do. When the Line of Merlin could bear the strain no longer, it glowed white, and began to fray apart at the edges. It folded in upon itself, distorting the very fabric of reality as it did so. In the final moments of its life, the Line flitted through some dimension that only exists in the minds of addled physics professors, and emerged to the place Beyond Time.

And with that, Magic was gone.
\simpleline
\DatePlace{Somewhere above Russia\\
December 25, 1999}

I’ll be home for Christmas
You can plan on me
Please have snow and mistletoe
And presents on the tree
Christmas Eve will find me
Where the lovelight gleams
I’ll be home for Christmas
If only in my dreams

Six hundred kilometers above the Earth, suspended in the exosphere, Commander Brown blinked several times as he was roused from his sleep by the sound of the radio from Mission Control. He picked up the radio transmitter.  “Merry Christmas to all of you down there,” replied Brown. “And Hubble will be home for Christmas ’cause today we’re going to set her free.”

That afternoon, as the robotic arm was about to release the Hubble back into orbit, Commander Brown inexplicably thought of the Mirror, and how a flaw the fraction of the width of a human hair spelled the difference between sight and blindness across the span of millions of light years. He thought of the Hubble Deep Field and how miniscule he was compared to it. Not just him, but the entirety of Earth and all that had come before him and likely would come after him.

He thought of mankind’s destiny, and whether they would ever reach the stars.

