\chapter{The Walrus Was Paul}

“From whence hath this man these things? and what wisdom is this which is given unto him, that even such mighty works are wrought by his hands? Is not this the carpenter, the son of Mary, the brother of James, and Joses, and of Juda, and Simon? and are not his sisters here with us? And they were offended at him. But Jesus said unto them, A prophet is not without honour, but in his own country, and among his own kin, and in his own house. And he could there do no mighty work, save that he laid his hands upon a few sick folk, and healed them. And he marvelled because of their unbelief.”

Mark 6:1-6

\simpleline

TISIPHONE: You’re beginning backwards!

MEGAERA: Aye, the first thing in the visit is to say:

ALECTO: How do you do, and shake hands, then state your name and business.

THE THREE (TOGETHER): That’s manners!

ERIN: Really? Well, my name is Erin, and I’m following the woman in the green dress…

TISIPHONE: No, no, no.

MEGAERA: You can’t go yet.

ALECTO: No, the visit has just started.

ERIN: I’m very sorry.

TISIPHONE: Would you like to play hide and seek?

MEGAERA: Or, button-button, who’s got the button?

ALECTO: So much time, and so little to do.

TISIPHONE: Wait a minute.

MEGAERA: Strike that.

ALECTO: Reverse it.

ERIN: No, thank you.

THE THREE (TOGETHER): If you stay long enough, we might have a battle!

ERIN: That’s very kind of you, but I really must be going.

THE THREE (TOGETHER): Why?

ERIN: Because I’m following the woman in the green dress!

THE THREE (TOGETHER): Why?

ERIN: Well… I’m curious to know where she is going.

TISIPHONE: Oh… She’s curious…

MEGAERA: The three brothers were curious, too, weren’t they?

ALECTO: Aye, and you remember what happened to them…

THE THREE (TOGETHER): Poor things!

ERIN: Why, what happened to them?

TISIPHONE: Oh, you wouldn’t be interested.

MEGAERA: No, no, not one bit.

ALECTO: Not interested at all.

ERIN: But I am!

TISIPHONE: Oh, no, you’re in much too much of a hurry!

MEGAERA: Yes, much too much of a hurry to listen to silly fairy tales.

ALECTO: Yes, yes, for where is fancy bred? In the heart, or in the head?

ERIN: Well, I suppose I could stay a bit longer…

THE THREE (TOGETHER): You could?! Well…

– “The Last Days of Exses O’Bruinan,” by S. Leigh, as staged in the 1979 London production.
\simpleline
\DatePlace{Merrick’s Tavern
Sontag
1229, C.E.}
The sun was shining on the snow, shining with all its might. It did its very best to make the billows smooth and bright, and this was odd because it was the middle of the night.

So, this is what it’s like to be dead, is it?

It’s cold. So cold and dark. Just a moment ago, Eloise Mintumble was standing in the sun outside Ilvermorny Castle with the prototype that Jeremiah Croaker had built. This one was different; it was not subject to the terms of Croaker’s original invention. Of course, it was commonly know amongst the Unspeakables that Croaker’s Law had a built-in safeguard. “Five hours”, because, of course, the world would push the limits. But they knew that the true limit was of the Time-Turner was six hours: inexplicably, inevitably, unchangably, six hours.

And yet, this new device worked off of a different principle entirely. Only a handful of Unspeakables and those few nameless, ageless wizards and witches of eldritch power knew that Time Turners did not turn back time at all. They did, in fact, work on the same principle as much more rudimentary objects such as Comed-Tea. They did not interact with the past, so to speak, but rather, they predicted the future with a remarkable degree of fidelity. Once you can do that, the rest is fairly trivial: check the mind to confirm the desired outcome, run a few iterative consistency checks, gin up some false memories of the “original” timeline, and you have a reasonably good facsimile of controlled time travel.

Eloise recalled once hearing an old legend, the tale of three brothers from the 13th century who once plunged so deeply into the secrets of the universe that they stumbled upon the hiding place of Father Time himself and woke him from his slumber. He did not care for this intrusion, and wishing to be will rid of these three intruders, offered them gifts in exchange for them leaving him be. The oldest brother, the most powerful of the three, sought to be the master of the Present, and so demanded the very Line of time itself. Father Time obliged, removing a hand from his own clock, whittling it down into a thin, stone rod, and presented it to the first brother. It is said that upon his first use of the Line, he was so overwhelmed with the power that he was erased from the very world-line itself, banished to a singular world of his own creation, of which he had sole dominion.

The middle brother was a troubled man, and wished to become master of the Past in order to right past wrongs. Father Time nodded, and took the face of his clock, and spun it thricely in his hand until it shrunk to the size of a small golden amulet, which he presented to the second brother. He bade him to spin the Time-Turner, allowing him to travel backward upon the skein of time. It is said that when the second brother did so, he was met with a resounding chorus of every sentient being in the multiverse shouting at him, “NO!” This was not what he wanted, nor what he expected, and out of fear of repeating the errors of Atlantis, he ended his own life, and thus forever lived in the past.

The youngest brother, and possibly the wisest, knew that the present was what you made of it, and the past was the past for a reason. He asked only for the ability to see into the future, and have its lessons guide his actions. Father Time looked on, quizzically, but obliged the request, nonetheless. He removed the triangular cap from atop his head, and the third brother saw that it contained with a frothy, effulgent green liquid that constantly refilled itself. He took a long draught of the potion, and upon seeing what the future held in store for him, spewed the liquid from his lips in one of the most spectacular spit-takes in modern history.

Of course, the veracity of this tale of the three brothers and their Timely Hallows was in serious question, given that it was propagated by none other than the inventor of Comed-Tea himself, who was known to be both an inveterate liar and a singularly skilled showman.

No, this creation with something much deeper and something much more powerful than a parlor trick. Mintumble and Croaker had long been partners at the Department of Mysteries, and they knew they were onto something when old Hank Armitage, the librarian at Ilvermorny School of Witchcraft and Wizardy, had sent them an urgent owl. He had been an informant for the Department of Mysteries for ages, and it seemed that he had stumbled upon a particularly dark secret when investigating the private library of the late Professor Whately, who had taught Ancient Lore at Ilvermorny since before any of them were born.

Professor Whately’s daughter was a constant source of scandal, particularly when she gave birth to twins despite no apparent father. Many of the old magical families still considered twins to be taboo, and there was a disturbing trend of the youngest twins within these families disappearing or dying under highly suspect circumstances, and the youngest Whately twin was no exception. This wound up being a bit of a mistake, as it quickly became apparent that the surviving twin, young Credence, was a squib. Professor Whately, who was never prone to displays of compassion, shipped young Credence off to live with some awful Nomaj family in New York when his daughter died.

What Hank Armitage had discovered though, was that the youngest twin did not die at all, he was alive and “well”, if you could call it that. He was a deformed and ostracized boy, and more importantly, showed all the signs of being an Obscurial. Armitage had nicked an ancient grimoire from Professor Whately’s collection, and saw the true reason why Old Whately was grooming his grandson’s Obscurus.

Together, Croaker, Mintumble and Armitage travelled to Wilbraham and managed to exorcise the Obscurus from the boy, who died shortly thereafter, but they were unable to initially contain it. The elemental force rampaged through the town, killing several Nomaj families and law officers, and it was only by the slimmest of margins and barest of chance that the three of them managed to contain the Obscurus and keep the incident hushed up from the MACUSA.

Using the dark ritual from the grimoire, they managed to harness and hold the Obscurus, and took it to Ilvermorny in order to create a True Time-Turner. The device itself was an amulet, similar to a Time-Turner, but the central feature was an eight-pointed star, whose points faced inward, binding the Obscurus. A circle encompassed the star, and a square further encompassed the circle, touching the north, south, east, and west quadrants. Finally, the outer ring of the amulet encircled the square, the four corners of the square joined to the rim with the finest of gilt.

Eloise volunteered to be the first one to use the device. According to the grimoire from which they devised its creation, it seemed that one simply had to hold the proper timeframe in one’s mind while spinning the amulet, which would take care of the rest.

And so she did. And it did not work, because Eloise Mintumble was now dead. Or at least, she thought she was dead, until she heard the voices. Two men talking… no. Was it three? Two of them had gruff voices, similar enough to where she thought they were one. And the third, he spoke softly and with great care. She did not understand their words, they were in some unfamiliar, arcane-sounding dialect of English.

No, she was not dead, just buried. Buried in snow. She stood up and roughly shook the billows of snow from her shoulders. She saw them now, silhouetted in the distance against the light of the tavern.

No, this wasn’t right.

Something about this didn’t make sense. None of it made sense. Or, rather, it made too much sense. Her world, for lack of a better world, was insane. There was no method to the madness. Somehow, she sensed that the fabric of this universe she had enteres was too… rational. Too… correct, for it to be hers. She was out of place, and out of time. She didn’t belong here. Why was she here?

She stumbled forward, into the light, and the three men stopped talking and stared at her. “Please, help me. I’m a traveler. I’m lost.” They stared at her blanking, and they responded in that curious dialect she couldn’t make sense of.

She knew who these three men were. How, she wasn’t sure, but she knew beyond every possible shadow of every possible doubt that these men were the Peverell brothers, and that it was vastly, terrifyingly important that she be here at this very moment, at this very place.

And that’s when she felt it. The enormous wrongness of everything began to weigh upon her, and an impulse emerged, something unavoidable, begging for release. It was like a sneeze, or an orgasm, or a sudden bout of nausea, but more intense, more demanding. She began convulsing as she tried to fight the urge, and the three men shifted cautiously, one even drew his wand. But she could bear it no longer.

She opened her mouth, and began to speak in a voice that was not hers.
\simpleline
\DatePlace{Earlier that evening}
“I always knew your brother was a whoopsie.”

The stink of ale was heavy on Osgurd’s breath. Antioch grunted in response and glanced over at his brother Cadmus, who was chatting, quite uninterested, with Brunhilda Rosmerta.

“I mean, he’s got to be, right? To stare at them knockers and not feel a thing? I’ve half a mind to go over there and bury me face in ’em, the way she’s puttin’ them out there like that.” Osgurd laughed uproariously at his own joke.

Indeed, Antioch and Cadmus Peverell had left their home in the Channel Islands to this strange Saxon land years before, due in no small part to Cadmus’ stolid resistance to showing any interest whatsoever in any of the members of the fairer sex in their home village. It seemed, however, that the Peverells’ quest was in vain. Sontag was ripe with eligible bachelorettes, and despite the fact that Antioch had taken one of them for his wife years earlier and bore three strapping young sons, Cadmus was still as single as ever.

“Not that your woman ent a catch, Oi, she rightfully is. I wouldn’t say no to having a go with ‘er, a bit of the ol’ in-out, in-out, if’n ya follow me. But her sister…” He stared longingly at Brunhilda, who happened to be the sister of Antioch’s wife, “Wot, I reckon she ent got the kinda downstairs mixup yer woman’s got, wot with three strong lads crawlin’ out of ‘er.” He gave a raucous laugh and jabbed an elbow into Antioch’s side.

“Watch it, Osgurd,” Antioch growled.

“Oi, feller, I’m only having a laugh. You know I’m not one for sloppy seconds, anyway. I like my meat fresh.” He gave Antioch a mighty slap on the back. Antioch was a huge man, by all accounts, but Osgurd was bigger. People jokingly called them the ‘odd couple’, a Saxon and a Norman who were best of friends, despite fighting like cats and dogs. On more than one occasion, they had laid waste to Merrick’s Tavern during one of their many scraps. The owner never seemed to mind; Antioch and Osgood never used wands in their brawls, and so the damage was easily fixable.

Perhaps more importantly, the other patrons viewed it as a constant source of entertainment. Drinks flowed faster and more merrily when the two of them were arguing, and once words gave way to fists, bets would fly as furiously as the blows. Tom Merrick, the barkeep and owner, would always keep track of who had drank more, so he was pretty good at predicting who would emerge on top.
Cadmus’ lack of interest in any sort of romantic dalliance was apparently a sensitive topic for Antioch, and as such, Osgurd took great pleasure in prodding him anytime they were both into the cups. Currently, Cadmus was blatantly ignoring Brunhilda and instead was chattering excitedly with the tall, lanky stranger that they had seen at the tavern several times in the past. Currently, the stranger was shaking his head, clearly trying to explain something.

“That’s not how eternity works.”

“Yes, it is! Over an infinite period of time, anything is possible, everything can and everything will happen. Even if we fail, someone else will succeed, it’s inevitable.”

The stranger sighed. “Possibility does not imply reality.”

“Not here, not now, but over a long enough time span? It–”

“No. Look.” The stranger carved a small line into the bar top, and placed his triangular-shaped cup next to it. “This is us.” He then gestured to the line. “This is Death.” He then gestured beyond the line. “And this, this is the other side of Death that you wish to reach, that we all wish to reach, no?”

Cadmus nodded, skeptically. “Go on.”

“Now, with every choice, we can either take one step towards that goal, or one step back. To decide, we should flip a coin.” He pulled out a small, bronze, circular coin from his bag. He showed the two sides: “If it lands on the ram, we take a step towards our goal. If it lands on the goat, we take a step back.” He flipped the coin, and it landed on the Goat, and the stranger slid the glass backward along the bar. He flipped the coin again, and again it showed the Goat. He slid the glass further back. “Now imagine that happening again, and again.”

Cadmus narrowed his eyes, “What of it?”

“Somewhere in your vast infinity, in the endless space of possibility, lies a world where every choice is the wrong one, where every coin lands on the wrong side, and we progress backward, backward, ever backward. Somewhere in the infinite, there is a world where we never reach the other side of death.”

Cadmus shook his head. “That is one possibility out of infinite. The probability may as well be zero.”

“Just one possibility?” He slid the glass back to the line. “Say we take a step backward. Then we take another step backward. But then, we take a step forward.” He slid the glass back and forth to demonstrate. “Now, say we take a step backward again. And another. And another. And another.” He shoved the glass so that it slid across the bar and clattered against the wall. “That makes two possibilities out of the infinite.” With a gesture, the glass flew back into his hand, and he repeated the demonstration, but with a slight variation. “That makes three…”

The levity had left Cadmus’ voice. His eyes darted back and forth between the line, the triangular cup, and the circular coin. “But–”

“No, don’t speak. Your mind is attempting to reject an unpleasant but true conclusion. Speaking right now would only cause you to try to reject it further. Just think, and listen. Even if there truly was only one possibility of failure, it would still be worth devoting everything in your life to avert it. But, that is not so. We are not here.” He gestured to the glass against the line. “We are in the middle days of the world, and magic only wanes further. We are farther away from the line than you could possibly imagine. And there are far more wrong choices to make than right ones.”

Cadmus shook his head. His mind was spinning through arguments and rebuttals, but he could find no purchase. His whole life, he and his brother had lived with a pleasant sort of optimism, knowing in his heart of hearts that someday, even if they failed, someone else would succeed in their stead. Even if it wasn’t him, somewhere in the infinite, there lay the path to salvation. And in one inebriated conversation, that optimism had been shattered.

“So then what… what do we do?”

“We have to make our own path.”

Cadmus nodded. “Yes. That we do.”

At this, Brunhilda, who had barely been following the conversation in the first place, stood up with a huff. She sauntered over to the other side of the bar where Antioch and Osgurd were exchanging bawdy stories.

“How goes it?” Antioch asked.

“Bah! If I didn’t know better, Antioch, I’d say your brother doesn’t know arse from quim!” Brunhilda spat.

At this, Osgurd roared with laughter. He slapped a huge, meaty hand upon the table, which made the glasses rattle. “HAAAAAA! HOOOOOOOO! DOESN’T KNOW ARSE FROM QUIM! HAAAAAAAAAAAAAAAAHHH!” He was doubled over, his head resting on the table, as he continued to laugh obnoxiously.

“Shut it.”

“Look at ’em two! Which one do you think is the quim? I mean, I’d say the tall one, he doesn’t look wot much of a manly sort, but I reckon yer brother would just break ’em like a twig!”

Antioch said nothing, gritting teeth and gripping his cup with such force that it cracked beneath his hands.

“I mean, there’s wot a sight I wouldn’t want a picture of, if’n the roles were reversed. That tall chap, he’d have ter have a right Bubotuber tween his legs to make in there. After all, yer brother’s got some meaty chops on him.” Osgurd continued to roar with laughter at his own jokes, until he was unceremoniously quited by Antioch backhanding him with the remnant of his ruined mug. The force of the impressive blow knocked Osgurd off his chair and back several feet.

Immediately, the tavern lept into action. The musicians, who had lazily been playing some wandering ballad, started to play a raucous tune more suited to fisticuffs. Brunhilda gasped and scampered away quickly, and other men began clearing away tables and chairs to give them room to brawl. Bets were being shouted, and when one man yelled, “A galleon on Antioch!”, Tom quietly raised his hand from behind the bar to take the bet.

“Why, you honorless whoreson! You’re more of a nancy than your brother!” Osgurd shouted, then picked up the chair that had fallen nearby and flung it across the room towards Antioch who raised a massive forearm to block the projectile. It shattered, sending splinters of wood ricocheting across the room. Osgurd charged forward with a howl, and Antioch tried to sidestep but was several drinks into the cups, and wasn’t able to deflect the full blow. He caught Osgurd’s shoulder straight to his gut, and was launched backward up onto the bar. Immediately, Osgurd began slamming heavy fists into Antioch’s chest. “Sucker punch me, will ya?”

Antioch flailed his arms wildly, trying to find something to grab with which to right is balance, but found nothing. So instead, he lashed out with his foot, sending a mighty kick into Osgurd’s hip, who chuffed from the blow, giving Antioch just enough time to roll sideways away, and then somersault backwards, crashing behind the bar. They both stood up, glaring at each other, separated by the slab of solid wood.

Antioch struck first, leaping over the bar with surprising agility for someone of his size and inebriation. He landed atop Osgurd, and the two men tumbled backwards and rolled around on the floor. The other patrons started whooping and laughing as the two were wrestling. Osgurd eventually got on top of Antioch and hooked his arm around his neck. Antioch waved against the chokehold, but then stood up with a mighty stifled grunt, lifting Osgurd with him, and stumbled backwards, slamming his full weight against Osgurd and the wall. It knocked the breath out of Osgurd, who listened his grip momentarily, allowing Antioch to suck in some much needed air.

Osgurd recovered quickly though, and aimed a sharp kick at the back of Antioch’s knee, causing him to buckle and fall back into the chokehold. He quickly dragged Antioch backwards, preventing him from finding any sort of solid ground with his feet, and dragged him closer and closer to the door. Antioch’s face shook, and it turned purple against the strain of Osgurd’s arm. Already his movements were becoming languid and weak. With a mighty heave, Osgurd hooked his arms underneath Antioch’s shoulders, spun him around, and hurled him out of the door of the tavern where he tumbled unceremoniously down two or three steps before landing in a pile of snow outside.

“See ya tomorrow, you cheeky ol’ bastard.” Osgurd shouted through a pant. “And work on yer grappling, ya big nancy.” He slammed the door shut, and Antioch could hear the cheers and applause of the patrons in the bar, along with Osgurd’s raunchily leading the tavern in a bawdy chant: “Arse from quim! Arse from quim! Arse from quim!”

Antioch looked up from the ground, wiping the blood from his mouth, and saw that Cadmus and the stranger were already outside. Cadmus knelt.

“I’m sorry, brother. I wish… I never meant to embarass you.”

Antioch stood up and roughly grabbed Cadmus’ shoulders. “No. Don’t. Don’t apologize, never apologize. You are who you are. You are my brother, and nothing else. And nothing comes between that. Nothing comes between us. You hear me?”

Cadmus nodded weakly, and started to speak, but had to swallow back a lump in his throat. “I think… I think I should introduce you. Ignotus, this is my brother, Antioch Peverell. Antioch, this is my… This is my friend, Ignotus Hand.”

Ignotus extended his hand. “Pleased to meet you, Antioch. It seems that we share a common goal, and there is much that I would like to discuss with you. As I understand it, you’re particularly skilled in the area of wandwork, having studied under Madame Ollivander herself–”

They were interrupted by a shambling figure that approached them. It was a woman, and she was dazed, confused. She was wearing a very curious green dress, not at all like the fashion of the time. It had the quality and craftmanship of a noble garment, but none of the ostentatiousness or decoration. It was plain, but surprisingly well made. Further, although she was clearly middle-aged, her body showed none of the signs of such. Most women were either wiry and unfed, or rather voluptuous and well-fed. She was neither, she was slim, but not gaunt. Her back was not arched and stooped from decades of work. And, Antioch noted that her breasts were not withered and drooped from years of feeding.

She looked lost, and scared. When she approach them, she shouted something at them in some unintelligible tongue. It was clearly some dialect of English, but it was unknown to them. They stared blankly at each other. Their hands, which were stuffed in their robes to keep them from the cold, instinctively gripped there wands.

When she began convulsing, Antioch withdrew his wand openly. Cadmus shifted his feet into a defensive position. And Ignotus crossed his arms and examined her curiously. She began retching, like a cat trying to cough up a hairball, and moments before Antioch could cast a curse to contain her, she began to speak in a voice that was not hers.

“Þregen béon Pefearles suna and þrie hira tól þissum Déað béo gewunen.”

The wind gave a mighty howl, she shuddered, and her form dispersed into nothingness, like mist in the morning.

\simpleline

\DatePlace{Swift River Valley, Massachusetts
January, 1938}

Merlin looked out over the valley. The sky was remarkably clear for the early hour, so from this vantage point, he could see “The Two Towers”. Ilvermorny Castle, about 60 miles to the west on Mount Greylock, and the Salem Witches’ Institute, which rested on Sentinel Hill, about 20 miles to the south.

Salem predated its more famous competitor by several centuries, and specialized in Ritual Magic. Few remember its more ancient name, which served to honor the Misqat tribe who formed the school centuries before. Back then it was little more than a stone circle and a curious altar on a small island in the middle of the Swift River. The land itself seemed to swell in response to the power that coursed through the place, and Sentinel Hill was coaxed from the ground over the years.

The eastern line of Merlin’s will ran through the Berkshire mountain range, and cut sharply across the heart of central Massachusetts, before eventually terminating in Boston Harbor. The point where he stood was the future site of the Russell Institute, the newest American bastion of magical knowledge.

The final steps of his plan were coming to fruition. The gears fit together so seamlessly. The Wilbraham Incident had galvanized the Scourers, who had emerged from their decades of hiding. The pressure on the Westphalians was enormous. Exposure simply could not be risked. And when it seemed that matters could not get worse for them, Grindelwald began cooperating with the European muggle dictatorship. Non-interventionism was simply not an option.

The Scourers had disposed of the last of the Old Ones; The Gate had been closed. The Westphalians and their No-Maj counterparts had entered the global theater and toppled Grindelwald and the Third Reich. The Eastern Ley was significantly weakened. And, perhaps most importantly, one more step of the Prophecy was fulfilled.

Born to those that have thrice defied him…

Three schools, formed in defiance of the true Dark Lord.

He smiled, despite himself.

