\chapter{Something to Protect: Bellatrix Black}

\DatePlace{August, 1962
London}

Cygnus Black was not a man who cried.

It was simply not in the Black family nature to reveal signs of weakness. And emotion is for the weak. Thus, Cygnus Black did not so much as weep, even when his firstborn daughter was readying herself for the Hogwarts’ Express for the first time.

“Daddy?”

His daughter looked up at him with heavy-lidded eyes, glittering with an innocent, good-natured curiosity.

“Yes, Bella?”

“What if I AM put into Gryffindor?”

“And what would be wrong with that?”

Bella paused for a moment to think. “It’s the house of the foolish. It’s not a house for the clever, or the cunning. It’s not Slytherin. What if I’m not good enough to get in to Slytherin?”

Cygnus kneeled down and put a large hand on Bella’s frizzy mop of hair. “Bella. Dear Bella. Gryffindor is also the house of the brave, the house of the strong. Two of the best men I’ve known were–”

“Cygnus! What is that ridiculous nonsense you’re filling her head with?”

Druella Black had overheard that one small bit of their conversation, and glowered at them both.

“Druella,” he whispered in a sidebar, “She’s worried. What you have me say to her?”

She loudly directed her next comment towards Bellatrix, “I would have you say that she should see to it that she gets sorted into Slytherin, or else both of her parents will be quite disappointed in her.” She turned her head as she caught the eye of someone in the crowd, waving them over.

Cygnus took this moment to speak directly to Bella. “Dear Bella, you will do well wherever you are sorted. And I want you to know that the Sorting Hat does take your choice into account. That’s not to say that’s the only thing it considers. But I will be proud of you, and will love you, regardless of the choice you make.”

He gave her a quick peck on the cheek, stood up, straightened himself, and pat her on the head. “Now, what you’ll want to do is walk straight at the wall between platforms nine and ten. Best to do it at a bit of a run if you’re nervous.”

Later, as Cygnus watched the train pull away, his heart swelled with emotion. But Cygnus Black was not a man who cried.
\simpleline

\DatePlace{July, 1963\\
Coventry}

Bella’s 13th birthday party was held at the sprawling Rosier Estate, where she had spent her youth outside of Hogwarts. Although it was deeded to her Uncle Gilles, the current scion of the Rosier family, Cygnus and Druella Black had made it their home. For her part, Bella was surprised when Uncle Gilles decided to attend the party: he had been coming up with flimsy excuses to avoid Black family gatherings for as long as she could remember.

As the night drew on, Bella noticed Uncle Gilles’ eyes growing glassy; he did seem to be drinking quite a large amount of her dad’s firewhiskey. Daddy really favored that particular vintage, and, although they were quite well off, it was still very expensive. That must have been why Bella kept catching him glaring at Uncle Gilles surreptitiously throughout the evening.

As the festivities drew on, Bella opened several fabulously expensive, lavishly wrapped presents. A new pair of cauldrons, a gilded set of Wizard’s Chess from Andromeda, a beautiful sapphire telescope from Cissy (although, neither of her sisters were present at the party; it was tradition that only those who had come of age could attend). After she unwrapped the last of them, Uncle Gilles strode behind her, leaned over, and whispered.

“You haven’t opened Uncle Gilles’ present, Bella.”

“Oh! I didn’t? I don’t think I saw it!”

Gilles chortled. He was a large man, with ruddy cheeks, bushy eyebrows, and stubbly fingers. Currently, those stubbly fingers were resting on Bella’s shoulders. “How foolish of me. I must have left it in my chambers. Bella, why don’t you come with me, and help me find it?”

At this, Cygnus stood up and coughed loudly. “Gilles, that’s quite alright. Why don’t I help you with that? We wouldn’t want to keep Bella from the festivities.”

Druella shot him an angry glance. “Cygnus, sit down. You’re being rude to our guest.”

Gilles said nothing, and simply smiled warmly at Druella. Cygnus shook. “I… No. I will not have this. Not in my house.”

At this, Gilles laughed, humorless and mocking.

There was a beat of silence, then Druella spoke. “Cygnus. Dear. Need I remind you that this is the ancestral home of the Rosiers, not the Blacks? So it is, in fact, MY home. Now sit down. I do believe you are offending my brother.”

Cygnus did not sit.

“Sit. Down.”

He closed his eyes, and slowly sunk into his chair, his teeth gritting. Bella was, well, confused. It wasn’t that big of a deal, Uncle Gilles just forgot to bring the present out. Daddy must have just been upset that Uncle drank all of the firewhiskey.

As she followed Uncle Gilles down the hall, Cygnus turned away. He couldn’t watch. And he would not cry. Even when he heard the muffled shouts and clipped sobs coming from the chambers, he did not cry.
\simpleline

\DatePlace{May, 1966\\
Coventry}

“Greetings, Uncle Gilles.” Bella intoned, icily.

“Bellatrix Black, you will greet your superiors with a smile, not with a scowl.” Druella warned.

“Greetings, Uncle Gilles!” She repeated, her voice dripping with saccharine sweetness.

Druella’s hand flew back, and Bella instinctively flinched.

“Greetings, Uncle Gilles…” Bella curtsied politely.

“Greetings, little Bella,” he replied, and he kneeled to cup her cheek in his hand. He lightly brushed her neck with his pinky.

Uncle Gilles stood and surveyed the house. He walked over to the sitting area, eyes locked on the bottle of firewhiskey that daddy had always favored. “I’m pleased to see that you still have some of the 1899, Cygnus. The vintage is truly delightful. Care for a glass, good man?”

“Gilles, it’s barely even noon…” Cygnus shifted, uncomfortably.

“Ha! Nonsense. Don’t be silly. Who is going to judge us?” He filled his tumbler about an inch from the top with liquor, and dipped two plump fingers into the glass. After swirling them around for a moment, he placed them lovingly in his mouth, tasting the firewhiskey with a wet, sucking noise. He let out an exaggerated moan. “Simply delightful.”

He stretched out his hand and waved his two fingers underneath Cygnus’ nose. “Come on now lad, give it a whiff.” He lifted his fingers up a bit, wafting the smell upwards, and Cygnus tilted his head back to avoid physical contact.

Uncle Gilles extended his remaining fingers, and with his open palm, gave Cygnus a hard yet good natured slap, and laughed uproariously. “There’s a lad!” Gilles took a loud slurp from the glass, and stared at Cygnus. “Curious, isn’t it, that some things actually taste better the older they get?”

At this, Uncle Gilles whipped around and smiled broadly. “And this must be little Cissy!”

“Narcissa,” Bella corrected. Druella shot her a warning glare. “Allow me to introduce Narcissa. Narcissa Black.”

“And how old are you, little Cissy?”

“I’m eleven sir. Pleased to meet you.” Narcissa giggled a bit.

“Pleased to meet you, darling.” Uncle Gilles ran his thumb across her cheek and she giggled even more. He was so silly. His round features and rosy cheeks reminded her of those kindly garden gnomes from the stories father used to tell her.

“And I hear another one is about to have a birthday soon… Her 13th, no?” Gilles inquired.

Druella turned away in disgust. “Andromeda will not be joining us for the summer. She has decided to spend her days in less… Desirable company.”

“She’s dating a Muggle,” Bella provided. Beneath the perfunctory tone of disgust, a perceptive listener may have noted a hint of triumph and challenge.

Uncle Gilles choked quietly on his firewhiskey. “Disgusting.” He made a face, worked his mouth a bit, and spit the remaining firewhiskey onto the plush carpet of the sitting room. “A Muggle, Cygnus? Truly?” Cygnus gave a slow sad shake of his head.

“Well, I suppose I shan’t be returning again this summer. I never much cared for the taste of mud.”
\simpleline

\DatePlace{June, 1968\\
Coventry}

It was Narcissa Black’s 13th birthday party, and Bellatrix had just graduated from Hogwarts. She was speaking pleasantly with other members of her family and extended family who had showed up for the twin festivities.

“–and I was thinking of picking up work at Burgin and Burke’s while I–

“A Rosier-Black, a common shopkeep?” Aunt Matilda scoffed.

“No, no, nothing of the sort. Their newest purchasing director, he has made some very interesting advances in the field of ritual magic, and–”

As Bellatrix spoke, a flicker of recognition glint across Aunt Matilda’s eyes. “Oh yes, I actually do recall that. I’ll have you know, I actually went to school with him. A good boy, a nice Slytherin. I’ll have you know, I fancied that boy once,” she cackled lasciviously. “Not as handsome now, though, sadly.” She lowered her voice conspiratorially, “I hear he took a curse to the face in Albania. Which reminds me, my husband I were just vacationing in the forests of–”

Bellatrix nodded vacantly. She was not listening, she was too busy staring across the room. She could pick up indistinct bits of the conversation. The words were missing, but the intent was crystal clear.

“But Cissy, you haven’t opened Uncle Gilles’ present.”

Narcissa cocked her head, looking around the dining room. “Oh! I didn’t see it! Where is it?”

Uncle Gilles chuckled. “Silly me! I must have left it in my chambers. It is a bit heavy, though… Do you think you could help me lift–”

He stopped mid sentence at the sound. Clambering footsteps, broken glass, a high-pitched shriek:

“NOT MY SISTER, YOU SON OF A BITCH!!!”

Bella had closed the distance between the two of them in the span of a moment, and she flung herself protectively in front of Cissy. With one hand, she pushed Cissy backward, and with the other, she lashed out across Uncle Gilles’ face.

She was still holding the shards of her broken wine glass.

The jagged edges of the crystal cut deep crimson ridges across Uncle Gilles’ ruddy cheeks. Blood gushed out in angry rivulets as he stumbled backward, crashing into the delicate glass coffee table. He lost his footing, and fell fully over onto the table, the glass giving away underneath with a terrific crash.

Druella stood up, her face ruddy with anger. “Bellatrix Black, what do you–”

“EXPELLIARMUS! SILENCIO!”

Bella flourished her wand, and shadowy black cords shot out, wrapping like tendrils around Druella’s feet and Uncle Gilles’ torso. With a swift motion, she cracked her hand and the cords whipped up, suspending the two mid-air.

It was Judgement Day. Reckoning. Vengeance. There was no one to stop her. No one that could keep her from taking what was hers, no one to keep her from protecting–

“PETRIFICUS TOTALIS!”

Bella’s body stiffened abruptly. The cords winked out of existence instantaneously, unceremoniously dropping both Druella and Uncle Gilles to the ground.

Cygnus Black stood, shaking, his wand out, his eyes filled with tears.

“I’m sorry, Gilles. She didn’t know what she was doing, she’s just–”

Uncle Gilles spoke as he stood up, the wounds already healing with the wordless gesture of his wand. “I’ve seen enough, Cygnus. One daughter who fornicates with Muggles, and another who would dare attack a pureblood superior? I had my reservations when my sister married a Black, but it’s disappointing to see them come true.”

“Gilles, please.”

“You can forget about my support on the Roanoke matter. And Druella: this man is no longer welcome in my house. I expect him to leave, immediately. Druella, you may stay if you wish. I think there is much business that you and I have to discuss.”

Druella nodded, and turned angrily towards Bellatrix, but she was already gone, as was Narcissa.

Bella had apparated them both to the hill, their hill. It was already dark, and they could see the stars through the clearing. She held her sister tightly, openly weeping. “Cissy, I may be going away for awhile. But you go back home. Go back to Hogwarts. I’ll make sure to write, I’ll make sure to visit.” She pressed something into Narcissa’s hand, a small blue sculpture carved of brilliant sapphire. It was a dolphin. Bella’s dolphin.

“Bella, I don’t understand.”

“You will, Cissy. You will.”

And with that, Bella apparated away, leaving Narcissa alone, staring up at the stars.
\simpleline

\DatePlace{December, 1975\\
Wiltshire}

It pleased her to know that Uncle Gilles never came to another Black family birthday celebration. If she had only done one thing in her life, that was enough. She protected Cissy. If she was safe, that was all that mattered. Eventually, she forgave Father. But the relationship was never the same. How could it be? She wasn’t Daddy’s dear Bella anymore. She was Bellatrix.

It also pleased her when she received the owl informing her of mother’s untimely death (although she lived long enough to scorch Andromeda off the family tree). Yes, Andromeda had run off with a Muggle. But she too was safe, in her own way.

But, it pleased her most of all,to be with her family and friends to witness the marriage of her Cissy. Malfoy Manor was resplendent and glorious, with the sun setting elegantly behind the Declaration of Intent. Now, Cissy truly was protected. She carried the protection of the Lord Malfoy. And soon enough, she would carry his children. And oh, how Cissy wanted children.

Some of Bella’s most wonderful memories as a child were of laying on the ground in the foothills outside the sprawling Rosier Estate. Due to the various enchantments surrounding the property, the night sky was always preternaturally dark. Cissy and Bella would stare up at the sky for hours, talking about the stars, telling stories about the constellations and thinking ahead into the future.

They talked about their future families and children. They would name them children after the constellations, to remind them of their destiny in the stars. Cissy always wanted a big family. She’d start with a boy and a girl. Draco would be the oldest, the greatest: king of the serpents. And Lyra, she represented the love story of Orpheus and Eurydice. Bella could appreciate that. If any harm ever came to Cissy, she too would travel to the depths of Hell and challenge the Lord of the Underworld himself to make things right.

For her part, Bella only wanted one child. A little girl who she would call Delphini. The dolphin, Bella had once told Cissy, is one of the most intelligent, most social animals. Oh, how Bella loved animals. She was protective, maternal. And one day, she would have that daughter of her own to protect and nurture. But until that day came, she would see to it that Cissy was safe.

Now, she was. Cissy would have her family. Bella looked up through her heavy lidded eyes, which sparkled like twin stars. She smiled lovingly at Cissy, who smiled lovingly back at her, and she gave the young Lord Malfoy an approving nod.

All was well.
\simpleline

\DatePlace{
June, 1980\\
Malfoy Manor}

It was dark times, truly dark times. One Dark Lord fell decades before, and another had risen in his place, more terrible and more powerful than any before him. One who saw the Malfoys as an enemy, and therefore saw Cissy as an enemy. A foe that even Bella, with her newfound power and lore, could not protect Cissy from. Bella needed allies, someone worthy of leading an army against the rising tide of Albus Dumbledore.

She found one.

There was something inscrutable about him. He was insane, yes, and powerful beyond measure. But something was off, and she noted a tiny hint of confusion. He spouted ridiculous ideologies, saying openly the kinds of hateful rhetoric that was typically exchanged behind closed doors within the ivory towers of privilege. Bella knew what it was like to speak those words aloud, and knew what it was like to not truly believe them. And she saw that quality in him.

But why? It was not even a means to an end. His power would have been sufficient to cow the noble families into submission. His cunning would have been sufficient to outmaneuver even the most seasoned Wizengamot veterans. The lore he possessed was sufficient to entice even the most erudite of scholars.

He could have easily won over the nobility. And when you win over the nobility, you win over the undesirables. He did not need to appeal to the Carrows of the world. And yet, he did. And so Bella needed to understand, to comprehend. If he was to be the new leader, their new ruler, she needed to know what type of ruler he would grow to becomes. Even a tyrant would be preferable, so long as Cissy was safe. Bella needed to understand.

But those were long term concerns. In the short-term, she needed protection. War was raging. And yet, in the middle of the darkness there was light. She stood beside Cissy’s bed, holding a small, frail baby boy, with piercing eyes and the thinnest wisps of platinum blonde hair. There was light in the world. And she would fight to protect that.
\simpleline

\DatePlace{
September, 1980\\
Wiltshire}

He’s dead. Albus silly, bully billy, bobbing Albus, silly silly silly silly silly Dumbledore, so silly and wily, why? Why why why did you take her, why why why why why why, now you are dead, dead by little Bella, deary Bella, silly Bella isn’t silly anymore, Cissy. Sweet Cissy and little Lyra, all burnt up. Burnt through, murdered. Burned up and burnt through and crisped up like little flakes of burning burning burning burning burning burning burning burning every last one of you will burn like phoenixes and I will burn you until you die and I will burn you when you are reborn and burn you burn you burn you when you wake up again, you took away sweet Cissy and little Lyra, burn burn burn burn burn burn burn–

The crackling power of Bella’s manic intensity filled the air outside Malfoy manor. She felt the very moment that the sapphire statue of a dolphin that she had given Cissy so many years before was consumed by the magical fire. Immediately, she apparated outside the grounds of Malfoy Manor, and she tore past the wards and jinxes, forcing her body into Mistform and bouncing off the ground in order to go faster.

When she arrived, it was too late. Dumbledore was gone, and so was Cissy. Lucius stood outside with several of the servants and a few members of the family who had been staying the night. He held little Draco in his arms. His face was white, his eyes sullen, the shock of it all rendering him dead to the world.

Once she gathered her bearings, she directed the mist of her body upwards, through the oppressive heat and licking flames, into bedroom of the Lord and Lady Malfoy. If there was even the remotest hint of a chance, she would do anything, give everything.

There was not.

She arrived in time only to see the last bits of ruined flesh bubble and crack, melting away from Cissy’s face. Although her bonds had long since burned away, her position suggested she had been tied to the bed. There were no eyes left to look into, no final shared gaze. Just a flaming, grinning skull, staring lifelessly back at her.

Bella’s scream was one of unending pain, as if all sorrow, loss, grief and rage in the world had condensed into a single point which was then stretched into a sound. With a terrifying crack of power and a whooshing thump, the temperature in the room dropped by about 150 degrees, covering everything in a chill of ice and frost. The heat was gone, but the scream continued.

She didn’t notice when another sound joined the scream: a hiss. That hiss. That cruel, terrible, baleful hiss that masqueraded as laughter. It echoed across the grounds of Malfoy Manor, unmistakable in its source. The laughter penetrated her mind, devoid of any hint of positive emotion. The laughter was a deliberate mockery of the very notion of happiness.

Beneath the laughter were the pops of various wizards and witches apparating. Still screaming, Bella looked up, and saw the Dark Mark burning bright green in the night sky. It was bright, oppressive, and it blocked out the other pinpricks of light. She could not see Draco, she could not see Lyra, she could not see Delphini. She could see nothing, and could feel only rage.

The Death Eaters were arriving, one by one, in response to their masters’ call. Lord Voldemort continued his insane, shrieking laughter, and compelled his dear Bella to return to the ground, where she slumped forward, fists on the ground, body wracking with sobs.

When they had all arrived, the Dark Lord spoke: “Dumbledore is finally learning to play the game as it should be played. He has grown up, and we now finally have a foe worthy of Lord Voldemort’s attention! Today, the battle has truly begun.

“You look somber, my servants. This is a cause for celebration! The game is afoot, and for that, you should be happy. For that, I shall reward you for your loyalty. For that…” His lips curled upward in a cruel smile, “we shall have a Dark Revel!”

He gestured with his skeleton-fingers towards the prostrate form of Bellatrix. She heard nothing. She did not hear the hushed, shocked silence. She did not hear the awkward cheers and forced shouts of celebration. And she did not feel any of what was to come. Her world was pain, and her world was rage, and there was no room for anything else.

She thought only of Orpheus and Eurydice, and his descent into descent into Hell, courting the Dark Lord himself for a chance to rescue his love from the clutches of Death. Bellatrix would not make the mistakes of Orpheus; she would not look back, she would not question His whim. If this was what he demanded of her, she would submit to it. If it was His desire to drive her insane, she would gladly descend into madness. If he wanted an all-powerful, fanatically devoted zealot, she would oblige.

Cissy’s little Draco would grow to abhor her, they all would, but it did not matter. One day, they would come to forgive her. One day, they would have someone to protect of their own, and they would understand.
\simpleline

\DatePlace{June, 1981\\
Sontag}

“HA HAHA HAHAHA HAHA!”

The cruel high-pitched laughter echo through the ruins of Sontag.

“The silly stupid stinking Scottish slut has a sissy for herself!”

It was too late to run. The anti-apparition wards had already been complete. No time to think. Physical escape was the only real option. If they could just get beyond the bounds of the wards. But the city was walled, there was only one exit point and it was sure to be guarded.

Well, it wasn’t the first time that Minerva and Moira McGonagall were going to go have to fight their way out of a sticky situation.

Of course, Bellatrix Black was far more than just a sticky situation. She remembered teaching the girl, she remembered her skill, and she remembered her soft, sad smile, and her quiet, reserved manner. She wondered what the Dark Lord had done to break her so completely.

”Come out, you old hag! Pull the snakes of of yer’ quim and fight us like a true lady!” Moira shouted, angrily.

“I cannot say I approve of my sisters choice of language, but I agree with the sentiment. Enough with the games. You came to fight, so fight you shall have, Ms. Black!”

“HA HAHAHAHAHAHAHAHAHAHHHAAHA”

The laughter rang out from behind them now, and they both whipped around. Bellatrix Black, in the flesh, not 10 meters away.

“Quim, Quim, Qualabim, Rastaban, let’s finish them!” Bellatrix sang.

“With pleasure.”

Rastaban LeStrange’s low, guttural voice rumbled from where Minerva and Moira were just looking, a few moments before they spun to face Bellatrix. Moira turned slowly, keeping her back against Minerva’s, as they both stood with their wands drawn.

The ground was flat, there was no cover to be had or high ground to be exploited. Two against two, nowhere to run, and nowhere to hide. This was a duel of pure power and skill. You devote exactly as much energy towards constructing a defense as is necessary, and pour the rest into your attack. An infinity of split-second decisions must be made, and any one of them could prove to be the crucial determiner of the fight.

Every shield has its weak point, and every shield can only tolerate so much abuse before its structure is compromised. Do you attack the weak point, spending more time and energy on precision and aim? Do you simply attack with pure brute force, sacrificing efficiency for speed and attention? If it’s your shield, do you take the time to craft false weak points to draw attacks elsewhere, or do you just reinforce the structure as much as you can? Or do you not even bother with shields, and rely on physical prowess to avoid curses?

Bellatrix was, at first, a vision of pure offensive power. She fired curse after curse, putting no effort whatsoever into the creation of any shield. The intensity of the onslaught forced Minerva into a defensive position. Her first shield was hastily assembled, and inefficient. She lost time, and had to make it up. Not seconds into the fight and she was already backpedaling. Not a chance to even fire a counter curse.

Bellatrix pressed the advantage. Sensing the lack of counterattack, she took her focus away from enhancing her physical maneuvers and poured everything into the ensemble of curses. Minerva threw up a Prismatic Wall, to give herself about a second and a half to think. No shields. Too fast, no point curse. No bystanders, use AOE. Limber, can duck or leap versus Line. Need Field. Mental math, look at feet. Bota Lunga, minimal lateral movement. Concentrated Field, 3 meters, Diffuse Field, 10 meters.

A ten foot wide burst of flame shot from Minerva’s wand, quickly followed by a cloud of needles three times the size. There was nowhere for Bellatrix to dodge, she could only counter or shield. Minerva prepared for both. She prepared a brute force volley of multiple weak physical attacks; it was a minimal expenditure of magic, and it would not do much if it actually landed, but it was enough to severely weaken most shields.

At the same time, she loosed an ice blast, in the event that Bellatrix opted for an elemental counter to the fire: ice trumps water trumps fire. Finally, Minerva prepared a single concentrated lance, in case Bellatrix tried a purely magical hard counter. Such a counter would need to be an applied area of magic, which would be easily penetrated by a directed burst.

Bellatrix indeed used the elemental counter, and her wall of water was quickly frozen by Minerva’s blast of ice. But Bellatrix had anticipated this, and directed a flow of magic into the wall of ice to lend it a measure of permanency. The now-physical barrier blocked the volley of blows intended to weaken a magical shield, and it trivially absorbed the impact of the lance. Bellatrix had the initiative now, and used it to withdraw her magic from the wall and turn it inward, rupturing it from the inside out and send an explosion of knife-sharp ice crystals towards the McGonagall sisters.

Minerva sensed the impending destruction, and also sensed an opportunity. Redirecting or blocking the crystals would not be difficult. But instead, she twisted her wand and summoned a vortex of wind, allowing the crystals to simply bypass them and continue their path. A path which happened to contain Rastaban LeStrange, who was ferociously engaged in his fight with Moira.

If Minerva and Bellatrix’s duel was a chess match, Moira and Rastaban’s was a fistfight. There was no elegance, no levels upon levels of moves, counters, counter-counters, contingencies or gambits. It was a knock-down, drag-out battle of who could out-magic the other. The simply fired curse after curse into each other, both opting for the pure brute-force approach. They were swapping shield-and-curse combinations ruthlessly, and one of them would eventually break.

Rastaban’s shield had been dropped by one of Moira’s curses, but he was already in the middle of loosing a curse of his own. As the magic began to flow from his wand, he saw the burst of ice-daggers flying towards him. He hastily attempted to assemble a barrier, but it was shattered by the hex that Moira had fired the moment she noticed the opening.

The shards pierced his skin, ripping chunks of a flesh away and crumpling him into a heap. It was over for him. A quick stunner from Moira, and it was over. She spared a brief moment to perform an Abjuration ritual; one of the links of the fine platinum chain in her pouch disappeared into nothingness. Massive chains, firmly rooted in the ground, sprung forth from the aether and bound Rastaban.

Bellatrix cackled. “SPECTACULAR, SPECTACULAR!”

There was a brief détente, as they all gauged what the next move was to be. Bellatrix was still cackling. Moira whispered, “She’s as mad a shit-house rat…”

“Mad or no, she could still turn you into a pile of blubbering jelly faster than you can say ‘Death Eater’.” Minerva cautioned.

“Sounds preferable than hearing another lecture from you.” Moira smirked, as they both readied themselves.

“MUSICAL LITTLE MINERVA AND MOIRA, MISERABLE MOUCHES! Time to fly, little flies!”

Rather than wait, Moira took the first action, and fired a standard blade volley at Bellatrix. Minerva backed her up with a trio of non-lethal area of effect jinxes with the intent of hobbling Bellatrix’s ability to respond effectively to Moira’s ceaseless attacks.

“SO EXCITING!” Bellatrix cackled. She cast her hand out, and rather than any sort of deadly curse or counterattack, a massive whirlwind of daffodils shot out, like some arcane blizzard of flower petals.

A distraction?

The flowers billowed around them, but they could still see her form so they continued the attack. But at the moment the blows would have struck, Bellatrix dissolved into viscous black smoke, and flickered backwards and then up. She continued to cackle as the flowers continued to rain down from nowhere. And then, the music.

Music?

A familiar tune, from an unknown source, bawdy and uplifting. Another distraction?

“ELEPHANTS, ARABIANS!”

Minerva tried to trace the position of the black smoke with her wand and fire Halting Hexes, but they could find no purchase. The black smoke landed, and Bellatrix instantiated once more. She grinned, baring her teeth, waving her wand. But there was no attack. Just more flowers, and more music.

“INDIANS AND COURTESEANS!”

“What is she blubbering about?” Moira whispered through the side of her mouth.

Minerva was barely paying attention to her sister, she was trying to focus on firing her curses. But as soon as she let out another round, Bellatrix flickered back into the thick black mist, and erratically bounced around the field once more.

“ACROBATS AND JUGGLING BEARS!”

The music was growing louder and louder, and the rain of flowers was getting too thick to see through. They could see Bellatrix in the distance, waving her wand like a conductor, kicking her legs up in time with the music. She wasn’t fighting back. It was almost like she was… Stalling? But what —

Oh no.

“Moira, construct a shield, now!” Minerva shouted, her voice barely registering now over the blaring horns and drums.

“Wha–”

Dear Bella….

No. That hiss.

Dear Bella… Take what we came here for, and depart. I will kill the spares.

No, no, no.

Minerva and Moira McGonagall were going to die.

The music cut out abruptly. Whatever eldritch wind was powering the tornado of flowers had ceased, and they began to drift silently to the ground. Bellatrix was nowhere to be seen.

He was coming. He was here.

She was going to die. And in that cold moment of clarity, she also realized the monumental mistake she had made earlier. It was so obvious, now. Anti-apparition jinxes were always exponentially wider than they were tall. Immediately, she thrust her wand into the air.

“EXPECTO PATRONUM!”

A bolt of white light shot upward. It only took a few meters, and then the form of her Patronus was able to escape.

Why, why didn’t she just think? She should have called for help from the very beginning. Once again, she was too busy playing a role, the plucky duo of sisters who complemented each other perfectly and could fight their way through anything. But where there is smoke, there is fire, and she should have known that the presence of Bellatrix Black most likely meant the presence of Lord Voldemort.

And no one could fight their way through him. Except for maybe…

POP

Alastor Moody appeared directly overhead, and immediately sped downward on his broom, assembling shields and fields and traps and weapons, even as he dismounted. His wand hand continued to cast every manner of protective spell, and his free hand was manipulating the landscape to provide cover, obstacles, and an advantageous position. No one except Dumbledore could ever hope to take on Voldemort in a fair fight.

But Alastor Moody never fought in a fair fight in his life.

“I’ve alerted Dumbledore. He’s bound by a Time Turner currently but he has…” The Eye of Vance whirled in his head, as he took a brief moment to check Albus’ status. “Seven minutes. We just need to hold him off for seven minutes.”

“AND IN THE END SHOULD SOMEONE DIE?” Bellatrix shrieked from somewhere in the distance.

“Quiet, Bella.”

And there he stood. Terrible, powerful, glorious.

It began.

If Moira’s duel was a fistfight, and Minerva’s was a chess match, then the duel between Alastor Moody and Lord Voldemort was… There was no comparison. It was like watching a gunfight where the combatants were shooting each others’ bullets out of midair.

It was an exercise in horrifically brutal efficiency. Shields were raised on a millisecond by millisecond basis, using no more magic than absolutely necessary. And they were dismantled just as swiftly, analyzed for their weak points and ruthlessly dispatched.

The physical element was equally impressive. There were no unnecessary flourishes or wasted movements. Just pure reaction time and power, traded back and forth. Minerva replenished Alastor’s magic with her own, bolstered his shields, and subtly manipulated the territory to their advantage. Moira, who was not as accomplished at battlefield control, desperately fired curse after curse.

Voldemort was still winning. But they weren’t expecting to win. They were doing what Bellatrix had done. They were stalling until their own Champion could arrive. Seven minutes. That’s all they needed.

Somewhere in the distance, they heard Bellatrix shout in glee. “MY LORD! I HAVE IT!”

From the corner of her eye, Minerva could see Bellatrix in her Mistform, hurtling towards them. The mist hurtled past Moira, who deftly dodged, and towards Lord Voldemort. She instantiated, grinning maliciously.

“Time to fly, dear Bella.”

And in an instant, they both were gone.

A beat passed. Minerva stood, wide-eyed, in shock. She had just faced Lord Voldemort and lived to tell the tale. They had all faced Lord Voldemort and lived to tell the tale.

Alastor took no time for such frivolities. He was already layering the entire area with dark detectors, protection spells, and shields. Moody gave a wolfish grin. “A few more minutes and we would have had that snaky bastard. Almost.”

“I’ll tell you the same thing I tell my students, Alastor: ‘Almost’ only counts in Divination and Gobstones.”

She paused, expectantly. That was odd. Moira usually never passed up an opportunity to quip. Minerva glanced over at her.

Minerva’s eyes widened.

Moira was hunched over in pain. She was bleeding out. Fast, too fast.

“Alastor. ALASTOR!” Minerva called. It was unnecessary; he was already rushing over. Minerva was casting as many healing charms as she could think of, and she held her sister tightly. She continued to work her magic, but spared a moment to glare at Moody expectantly, who was still casting defensive spells around their perimeter.

“Damnit, woman. I’m an Auror, not a healer. And this doesn’t look good…”

“Have you no Healer’s Kit? One would think, constant vigilance would dictate–”

“Minerva, for the types of wounds my men suffer on the job, a Healer’s Kit would do about as good as pumpkin juice. Just stem the bleeding. Three more minutes until Albus is here, and he’s sure to bring an army of healers.”

Moira coughed, and a light mist of blood sprayed from her mouth, and trickled down the corner of her cheek. She spoke, weakly. “Why didn’t YOU bring a Healer’s Kit, Minerva?”

Minerva froze, until she saw the small hint of a smile on Moira’s face. “I…” Minerva had been fighting the war for long enough to know how this was going to end. But she needed to be strong. She needed to quip. “I… I assumed that your unflappable sense of self-importance would be enough to protect you from any harm the Dark Lord might have thrown at you.”

“I AM important… You should have been more prepared…” Despite the pain, Moira grinned. Moody was respectfully giving them their distance. Minerva choked out a sob, but still smiled, which prompted Moira to laugh, softly. Minerva laughed too, as best as she could.

Laughter. Cold, dark, hissing laughter, mingled with a mad, manic cackle. That horrible laughter, that mockery, was Voldemort and Bellatrix’s parting gift, and it reverberated throughout the ruins of Sontag. They would not even allow her one final laugh to share with her sister, they took even that from her.

The laughter ceased only when Moira McGonagall’s eyes closed for the last time.
\simpleline

\DatePlace{May, 1999\\
Hogwarts}

There was no hope. Cissy was ashamed of what Bella had become. But the shame, it was just an act. It had to be. And, if the Dark Lord were to rise again, Cissy could stop the act, remove the mask. Cissy and Bella could be sisters again. Cissy didn’t need Bella’s protection anymore. A new Lord Malfoy protected her, who was in turn protected by the dark reflection of the Dark Lord, who was in turn protected by the true Dark Lord. There was hope.

Until today.

That man, that ancient man, had burned into her mind and she saw the truth, the horrifying, final, inexorable truth. The Dark Lord was gone. The mask would stay on forever. Cissy and Bella were no more. There was nothing left. Nothing to strive for. Nothing left but combat.

She felt no pleasure, or pain, or anything as she dueled with the boy. She fought without thinking. What was the point? She wore the mask, because why remove it? The mask protected her. The manic, mad smile. The cruel, nonsensical taunts that were as much a part of her combat technique as her curses. The singsong voice, the high pitched laugh, the insane ramblings, the horrible, soul-shredding curses. They protected her.

But the boy, he smashed mercilessly against her mask. With attack after attack, he was the waves and she was being battered upon the rocks. Battered, battered, battered through all of her protection. The mask cracked.

She was afraid.

And in one brief, tragic moment of clarity, she realized something terrible. She did not want to die. It didn’t have to be this way. Although she chose her path, the path of death, many years before, there was no law of the universe stating she had to continue down the path she had lay for herself. She could stop at any time, turn around, and walk back into the light. Back to Cissy.

As she desperately ducked the hundredth attack, and she shrieked with a voice full of fear, “Stop!”

And like a wrathful god, Neville Longbottom, a thousand feet tall and burning with brimstone, roared in return, “That’s what they said to you!  Avada Kedavra!”
