\chapter{Will We Die, Just a Little?}

All of the following is true. It is not, however, necessarily useful.

Magic is Real; that is to say, Magic is theoretically possible, and is therefore a subset of reality. As such, there are no ends that Magic can achieve which cannot be achieved without Magic; that is to say, Magic is not strictly necessary.

The “language” of Magic, like first-order logic, is primitive, basic, and mind-numbingly obtuse at any reasonable level of complexity. So it should be no surprise that one of the most basic discoveries in Functional Magic Theory is that Magic is non-recursive. That is to say, Magic cannot cast Magic.

However, most Functional Magical Theorists have not read Gödel, Escher, Bach.

It is possible (although complicated) to cast a spell which references itself. Therefore, it is possible to write a spell which references Magic as a whole. Therefore, it is possible to write a spell which recreates Magic as a whole. And because any effect that Magic is capable of causing can be duplicated without Magic, it is possible to recreate Magic without the use of Magic.
\simpleline

“Am I to be impressed?”

Harry had learned the subtleties of the synthesized voice of Lord Voldemort, and at this particular point it conveyed weariness. “You have succeeded at creating a physical embodiment of a tautology.”

“Professor, I don’t think you understand the implications.”

“How often will you forget that I am not, unlike your fellow companions, a wholesale idiot? Of course I understand the implications. And if you would permit yourself to see those implications through to their endpoint, you too would be unimpressed. This was always your weakness, boy: you grow impatient after the first few levels, and are too easily satisfied with your oversimplified explanations. But with every problem, there are levels upon levels upon levels that must be considered.”

Harry rolled his eyes. “So how do you know when to stop? You’re right of course, but that doesn’t tell me anything useful either. There are infinite levels to any problem.”

If Lord Voldemort’s box had a face, it would be smirking. “When you are one level higher than everyone else.”

“That’s quite clever.”

“Yes, well, that is why we are in our respective prisons. I know you, boy. I know that you have grown, and I know that you truly believe that you play the game at a sufficiently high level to win, and in some ways you have. In other ways, you have not. I am you. I know how we think. I know how I thought at your age. You have anticipated my blaseness, and yet you tell me anyway.

“Clearly you have thought through the first few levels of our interaction, so it would please me if we did not waste time by going through the motions. You are not so eager for praise as you were years ago; you would not simply tell me for the sake of having someone to tell, which means that there is some trump card, some hidden bit of lore that, in your opinion, changes the state of the game. What is it?”

“Sorry Professor. There’s no lore, no trump card, no hidden knowledge or artifacts.” Harry paused. “You could say it’s something of a riddle.”

There was another pause, this one even briefer. “You have found the second Box.”

Harry grinned. “Not found. Recreated.”

Lord Voldemort measured his words carefully. “I confess that I am still no expert in the trite practice of being nice, so I did not anticipate this. Of course, you would not truly release me. You have created the second Box of Orden, and within it placed a small, unbroachable, inescapable world that is free from Magic, and within that placed one of my Horcruxes.

“You have created a crude, basic facsimile of Magic within this world, sufficient to allow me access to my Horcrux. Because I have sensed no avenue of release, clearly you have not activated the reconstruction of Magic, which means you are waiting for the proper moment to unveil it. Much like myself, you always had a taste for the dramatic.

“I suppose, Mr. Potter, that you were hoping that the moment of dawning comprehension would follow your grand gesture, not precede it. I apologize for not playing the role you were expecting.”

Harry couldn’t keep himself from grinning as he, in response, snapped his fingers. “I expected you would expect that. Levels and levels, Professor. I knew that you would figure out what I had done quickly enough, and from there it would be fairly trivial to determine exactly when I would allow you access to the second Box. So the only way to beat you at this little game of who could outlevel the other was to completely take myself out of the equation, so I brought in my secret weapon: Luna Lovegood, the Platonic ideal of pure randomness. I had Luna write a number on a piece of paper, which I have only just now opened.” He paused briefly to read the number, and then continued. “And after this many seconds, I will ‘flip the switch’.”

“You must be almost as bored as I am, and we all must amuse ourselves in our own way. I would ask why you do me this favor, but I assume you intend to ‘rehabilitate’ me. It would not be in my best interest to discourage you from thinking I am rehabilitatable, so I shall not.”

Several minutes passed, in silence. Then, Lord Voldemort felt it.

“Ah.”
\simpleline

Tom Riddle examined his new prison. It had been eight years since he had inhabited a corporeal body. He recognized this as the body of his youth, free from the modifications made necessary by his role as Voldemort. He was in a small study. There were no doors or windows. There were, however, bookcases. Every wall a bookcase, every bookcase stacked two layers deep with books. On the desk were two objects of note. Firstly, a pair of boxes which he recognized from his conversations with Harry as a computer. Secondly, a wand. His wand.

Despite knowing that he would have placed no traps or wards upon the wand, Tom was still cautious. He channeled a small flow of “Magic” through the wand. It felt different. Synthetic. Like a rubber glove. It would take some getting used to, but it was real, and it was functional.

He cast his mind out, exploring the infinite that lay beyond physical barriers. There was only one true pathway that led away from this room. And it led to the other Box, a fuzzy morass of seething organic matter, all teeth and burrs and clouds and wisps of fat.

He cast his mind further, exploring the infinite that lie beyond the infinite. He saw all the possible pathways, all possible Boxes, all possible mistakes, all possible moments of weakness. He strode further out into nothing, passing by the most minute of possibilities, the coincidences and the bizarre. He strode further yet, into the deep nothing. Every so often he would encounter the barest of threads, the most impossibly impossible circumstances: atoms spontaneously degenerating in just the right ways to create just the right effects at just the right times. He briefly pondered the lives created and lost upon these distant threads, and then pondered no more.

He strode further yet.

The threads were limitless, Tom knew. Permutations could be stacked on top of permutations, and refactored in with the new results, ad infinitum. At a certain point, however, the threads grew faint enough and infrequent enough that they were formally indistinguishable from the nothing.

He stayed at this moment beyond Time, and pondered. He then strode further yet.

He felt the exact moment when he emerged on the other side of Eternity, and after another infinity, he was back where he started: The single black thread of Time that stretched from the beginning of Tom Riddle to the End of All Things.

In an instant, he opened his eyes and snapped back to his reality, the only Reality that mattered. The reality that he and all things were Bound to.
\simpleline

“Ah.”

Lord Voldemort’s box flickered with a brief shudder of red energy. He could sense that he was gone for less than an instant.

“I have not had much occasion in my life to say this, even more so now given my current predicament. But, I thank you, Harry Potter.”

Harry smiled, a true smile of grace. But it was only a moment before his trademark wry grin returned, “But it’s not completely altruistic.”

“There’s no such thing, boy. Of course I understand your intent. Time flows differently there. It loops back upon itself. I was gone for an eternity. I returned in the fraction of an instant. Thus, you intend to put me to work. I am to create something, the nature of which you have not told me, which means that you will not tell me. I suppose somewhere on those shelves is a book designed to teach me to use that computer.”

“Correct. I am giving you a chance at your heart’s desire, to create what you have desperately wanted more than anything in the world.”

Another brief pause. Another brief flicker. “Someone intelligent to talk to.”

In that instant, Tom Riddle was gone again.
\simpleline

Harry would have felt bad, offering up such blatantly false hope. But it was a victimless crime; in fact, it actually neatly tidied up a number of open problems. First and foremost, he was now free to permanently close the true Box of Orden, which he did as soon as he was certain the Professor was safely inside the replacement. From a utilitarian perspective, Harry needed to ensure that the Professor be occupied, kept interested, lest he start to make trouble in his restlessness. And from a humanitarian perspective, Harry wanted to ensure that the Professor was happy.

In theory, a thousand monkeys hammering away at typewriters for an infinitely long period of time would eventually recreate the entire works of Shakespeare. And in theory, a singularly brilliant Dark Lord hammering away at a keyboard for an infinite period of time would eventually create a fully functional, friendly artificial general intelligence.

But the world didn’t work like that. In an infinitely long possibility space, there also exists a reference frame in which those same monkeys hammer away for an arbitrarily long length of time, functionally infinite, without ever recreating Shakespeare; there exists a reference frame in which the Alpha never reaches the Omega.

There was a period of time in which Harry had thought, perhaps even hoped, that the answer was as trivial as some sort of grand computer simulation, that some Atlantean server in some distant corner of the universe was responsible for the world in which he lived. But it didn’t make sense, because there was no answer to the fundamental question: Why?

Why “Wingardium Leviosa”? Why Grindelwald? Why Voldemort? Why Walpurgisnacht, why Gotterdammerung? If you possessed the capacity for perfection, why would you deign to create an entire universe of flawed, imperfect people, still subject to the same laws of pain and death and hate and emptiness?

Harry had crashed into Chesterton’s Fence often enough. If something was deliberately designed, and yet still entirely nonsensical, typically there was some underlying sense, some hidden piece of the puzzle that needed to be uncovered.

But fortunately, Harry had from now until the End of Time to discover that piece of the puzzle. Until then, there was work to be done.
