\chapter{Saturn Ascends}

“Naught shall avail him that he should not fall, fall shamed, an intolerable fall. For he himself against himself prepares a foe, a portent irresistible, devising fire to outflash the lightning-fire, and might sound the thunder to outroar, and shattering old Neptune’s trident spear; that oceanic plague which shake the earth. Yes, stricken by this evil, Jove shall learn what difference lies between a king and slave.”

Prometheus Bound
Aeschylus
\simpleline
\DatePlace{Alderney\\
August 1, 1899, C.E.}

“Please, Master Flamel, please!”

Dumbledore held the broken body of Ariana in his arms. He was a handsome young man, barely come of age, and surrounded by the aura of prophecy so blindingly bright that even the least sensitive of minor seers would have noticed. “She is still alive, I feel it! Give her a taste of the Elixir. Please! You’ll have my undying loyalty. Everything I can ever give you. Anything. Everything. It’s yours!”

Nicholas Flamel raised his hand for silence. “Mister Dumbledore, I understand your pain. But–”

“Gellert is right. She is a Gateway. And he has already discovered great lore, he could harness her… Even that would be better than death. I could deliver him to you. I know where he will be going next. He seeks the Hallows, he knows where one of them is, I could tell you…”

Flamel scrutinized him for a brief moment, considering. It was possible that the young man in front of him, even in his grief, could be blatantly fishing for information. But it was unlikely. No, it would be cruel to give him false hope. “I find it unlikely that Mykew Gregorovitch will part lightly with the Elder Wand, assuming it is not simply a clever lie designed to drum up business. Mister Dumbledore, you must understand that the Elixir of Life cannot be doled out lightly nor at the whim–”

“WHIM? She’s DYING! Mrs. Flamel, please, talk some sense into him!”

Perenelle stood at the window, for she couldn’t bear to face the conversation.

Mom, Dad, please. Please. Do something. You’re healers. She’s breathing now, look she’s breathing now. The water is gone, now do something. Do something!

“Look at her face. You can see it, she knows this is the right thing to do. You can see it! Why are you letting my sister die?”

“Mister Dumbledore, need I remind you that you are a guest in our house?”

“This is a house of fools! A house of tyrants! You could change the world with what you have, and yet you hoard it. You stand there imperiously watching my sister die, how can you live with yourself? You have the riches of nations,” he gestured to the pots filled with bubbling lead and gold. “And yet you do nothing. You have eternal life! And what have you done with it? What have you–”

“Silence. Speak no more. For you speak of things of which you know nothing. Now, you will listen to me.” Nicholas Flamel’s hand darted out and touched Dumbledore’s shoulder faster than he could have ever hoped to react. “Egeustimentis.”
\simpleline
Dumbledore existed as slightly more than a fraction of consciousness within his own mind. It was laid bare before him: an automaton of levers, gears, bubbles, slicks, and whorls, and among them all, a scene coalesced. His sister and himself. His sister, young, beautiful, glowing. Himself, old, with half-moon spectacles and a ridiculous hat that looked like nothing more than a squashed mushroom.

They were in Godric’s Hollow. The cemetery. Albus was kneeling to lay flowers at a grave that he knew without looking was the grave of his brother Aberforth. He paused for a moment. Someone, in terrible cruelty, had left a wreath of flowers that had been deliberately arranged to resemble a sack of Galleons. One hundred thousand Galleons, to be specific. He did not understand why that number came into his mind, or why the act was of such monstrous evil.

As he wept, the scene shifted. Albus was gone, and it was now Ariana who held the flowers. There were two graves, side by side. Albus and Aberforth. Ariana stood, still young and beautiful, still glowing. The only imperfection was in her eyes; they were stained with tears, but more importantly, they carried an immense weight of sadness and torture and loneliness.

In those eyes, there were husbands and friends. There were children and students. There were lovers and enemies. They came into her life, and they left as quickly as a mayfly. All those that she had ever loved and all those that she ever could love were gone, and yet, an entire world of people for whose sake she must exist. It was a pain and weight beyond mere tears: it was a fundamental part of her being. She was tortured.

The fraction of consciousness that belonged to Albus resisted this. “Love will always find a way. There are always people to love, people to give meaning to the world. You and Perenelle have loved each other for centuries.”

Flamel’s response came, not as a voice, but as words that instantiated directly into Albus’ mind: “We are companions, yes. But even at our young age, our love has grown cold. Six hundred years is a long time, Mister Dumbledore. I confess that often I find myself longing for my… next great adventure.”

At this, the scene shifted once more.

They stood outside of Time. It was bright, clean, pristine, like the Platonic ideal of King’s Cross Station. Albus was there with Ariana and Aberforth, with Kendra and Percival, with a long unbroken chain of Dumbledores that stretched from now until deep into the past. Ariana was surrounded by all those she had ever loved, all those that she ever would love. Her body was young, restored, and perfect, but more importantly, so too was her soul.

A train pulled in through the tunnel, and Albus could see clearly that Nicholas Flamel was the conductor. He was busy turning gears, flipping switches, making minor adjustments here and there to the motive power that was Albus’ mind.Finally, with a warm, kind smile, Master Flamel pulled a lever. A gust of steam billowed from the train’s whistle, and a wave a great peace washed over Dumbledore.

“You are young, Mister Dumbledore, so you do not understand the curse of age. Although I cannot help your sister in the way you request, I am giving you the strength so that you may do so. You can ask me to keep her bound to this senseless, broken world. You can demand that she fight your battles for you, subject her to the cruelty and capriciousness of life. Or you can allow her to travel Beyond.”

Albus watched as Ariana smiled, peacefully. She looked so happy, so right. It would be a terrible thing, to force her from this place. She looked at him, expectantly. He did not need to embrace her, their souls were as one in this place; the love and compassion he felt coursed through her as well. After the briefest moment, he nodded, and she smiled.

As she stepped onto the train, the ethereal figures of all those before him dissipated into nothingness, leaving him alone at the platform. The place around him began to fade as he emerged into the world once more.
\simpleline

Dumbledore stood, knee deep in the calm ocean waters outside the cottage of the Flamel family. He held Ariana’s body, and he had no tears. Although Ariana was gone, for now, she was not gone forever. It was sad, terribly sad, that she would miss out on this brief flicker of a moment of this infinitesimal facet of the universe. But she would persist. They all would. Sooner or later, he would venture into eternity and they would be together, forever.

The waves washed over him, lapping gently at his waist. The ocean called to him, The voice of Neptune gently whispering, “Let go, let go, let go…”

And he did.
\simpleline
“I envy him, in a way, Nell.”

Meldh’s voice broke the silence. Perenelle was still fighting back the tears. The entire proceeding hit her in the gut on a visceral level. Of course, Meldh was right. The ethics of mind manipulation were questionable at best, even if the manipulation was subtle and ultimately beneficial. And things weren’t as pretty and clichéd as a pure white train station that took you “beyond”. But ultimately, the conclusion to which he had led the Dumbledore boy was correct.

She had seen enough of magic. Horcruxes. The Bone of the Father. The Ritual of the Starfire. The True Cross. All of these pointed to one single truth: No one was actually gone.

How could anyone who considered themselves rational doubt this? Both she and Meldh had died! And yet, they were still here. The rituals were complex, and they were enormously costly, but that was just an optimization problem. The information was there. What made up the entirety of a person’s being, whatever that may be, existed in some form, beyond the death of their physical body.

She had some theories which she never got around to testing, many of them involved Time, and many more involved the absurdly solipsistic and anthropocentric nature of Magic itself. Right now, it didn’t really matter one way or the other. What mattered is that it was possible. Time was no longer her enemy, as it was in her youth when every wasted minute was a tragedy. She was no longer filled with that rage.

A very small part of her looked back in regret on those days when she had been called Æsahættr, a name which meant “God-Killer”. She was young, so young, and yet, even then, she had accomplished so much. So much more than that ridiculous nihilist from whom she took the Stone. Boredom was so absurdly bourgeoisie that even now it still made her sick.

But even he, her, it, was not gone.

But pain… Pain still hurt. Even though Death was not the end, it was still bad. These moments, these centuries that would likely stretch into millennia, they were still lost forever. She felt the pain of knowing that, if and when she was to see her family again, they would but children to her. And pain… Pain was still bad. Nell was still a healer at heart and wanted to spare people that pain. She still remembered–

please, Master Payens, please. I’ve heard the rumors. I know you know people, I know what people say about the Cross,” she gestured violently at the plain-looking wooden cross adorning the nave of the temple.

“And what can you offer me in exchange for such a gift,” spoke the man, who once was tall, proud, and fit, and was now overweight and sallow.

“Everything I have, and more. Anything. everything! Just please, please. Help.”

“Everything you have?” Hugues de Payens laughed, mockingly. “Your family are healers, are they not? Not exactly a wealthy profession. If I grant you this favor, rumor shall spread. I know not how you found me, but I do not relish the thought of being interrupted thrice daily by intrepid adventurers carrying mostly-dead bodies in their arms. You have nothing you can offer me.”

“DONT MOCK ME!” Perenelle screamed, the desperation apparent in her voice as she could feel her hold over her magic slipping. The only thing keeping her sister’s lungs from being liquified from the inside out by de-transfigured water and muck was that thin thread of magic which was being stretched farther and farther beyond its limits with each glib remark.

“Oh? Or what?”

“I… I…”

“I know you, child. I have seen your personality before, in so many others. You see a problem in the world, and you burn with righteous rage. You hate the world for not fixing the problem, and you take the responsibility upon yourself, which you think justifies your impudence and rashness. Mark my words, child: it’s easy enough to ask big questions and make big plans. But to follow them through? What have you done with your short life besides angrily make demands of someone greater than yourself?”

She was already turning to leave. This was useless. Just another jaded power-hoarder. Damn him, damn his entire Order, damn his Knights, damn his Cross. God damn every last one of them. She would tear the world apart. She would rip apart the gates of Heaven, tear apart the very foundation of Christendom to pull her sister back
\doubleline

\DatePlace{Borley Rectory\\
February 27, 1939, C.E.}

“Idiot. Drunk idiot. What in God’s name were you thinking?” Cadmus shouted.

Antioch looked shell-shocked. He stared, wide-eyed at the corpse of Osgurd, while tottering up and down on his heels. Now that the motive power was gone from the body, it looked so frail. The wand in Antioch’s hand still throbbed with the glory of battle, short-lived as it was, and demanded further action: clean, erase, alter. Escape with no trace.

It was unnecessary to take further action, as Ignotus had already stunned Merrick and the few remaining patrons and was dutifully working on altering their memories. He acted efficiently, but not quickly. His tall, lanky frame did not age as well as the two true Peverells, who were still large, relatively healthy men, despite being of such advanced age.

Once satisfied, Ignotus began casting scrambler charms, warping the flux of magic such that no one would be able to make heads or tails of what kinds of spells were cast here, or by which wand.

“It… that wasn’t me. I can’t control it. It’s not me…” Antioch muttered to himself. Cadmus gripped him by the shoulders and jostled him.

“Pull yourself together. You did a terrible thing, but you’re still my brother. We need to get you out of here.”

“It wasn’t me…”

Cadmus huffed in frustration and removed his wedding band from his finger. Embedded in it was a brilliant black stone, and upon that was engraved the mark of a triangle, a circle, and a line. He hurried to turn it over in his hand thrice and cast his mind beyond.

Death Bursts were like beacons of light to any witch or wizard exploring the darkness of Time or the vastness of Space: individual pinpricks of white hot fire, burning desperately against the inexorable void. An inexperienced user is practically blinded by sheer multitude of them, and Cadmus rarely had occasion to practice.

Fortunately, however, Osgurd’s death was as recent as it was unexpected, so it shined hotter, angrier, more fervent than the rest. Cadmus willed the shapeless light into the form of Man, took its hand, and stepped back into their world.

“I told ya.”

Antioch snapped his head up, staring dumbly at the white mist that had coalesced. It was Osgurd, idealized. Young, big, virile, powerful. Nothing at all like the empty, ruined corpse that was currently in the process of being transfigured into a riding crop. The mist eventually gave way to a diffuse, soft light, which continued to speak.

“I told ya that wand was trouble. ‘Wands of elder, never prosper’, wot mum always told us. Yer lucky ya didn’t pull this stunt five years ago, or Catherine would have had yer hide. Oi! Catherine!” He turned and called, and obligingly from a place beyond places, another form began to condense from the air.

Somehow, despite having no discernible features, the light still managed to convey the expression of reproachfulness. It had a woman’s voice, which Antioch recognized as Osgurd’s late wife. “Ya finally went and did it. I knew one of yer would be the end of the other, always bouncing around and carrying on like you do. I always wot said, if it weren’t the drink, it’d be the fists, didn’t I?”

“Aye, ya did.” Osgurd nodded.

“Not fists.” Antioch spoke. “Not fists. Wands. This wand.” He thrust his weapon into the air.

“You went an’ did Osgurd in with a wand? Yer a better man than that, Antioch, what made…” The voice trailed off for a moment. “Osgurd, what’d you say to Antie that made him go off and pull out ‘is wand? You din’t wot make fun of his mancy fruit of a brother, did ya?”

At this, Cadmus coughed loudly, and she paused for a moment. “Not that there’s a thing wrong with that, mind you. You’ll have wot’ them clergy talk about sin and whatnot but, have a looksaround ya, we’re here, ent we? Don’t seem like no ‘eaven or Hell, just seems like more of the same!”

Of course, it was more of the same. Of course, they were quipping. Antioch’s life was one prolonged quip, punctuated by rare moments of sincerity. Although Cadmus operated the Stone, the Spirits were powered by Antioch’s memory, so it was only a matter of time before the conversation turned somber.

As if on cue, Osgurd turned towards Antioch. “I’ve wot’ eard them things you’ve all been talkin’ about, wot’ you three. Yeh want to end death. An’ it looks like yeh have, in a way, an’ I always knew ya would. But we both know, you an’ me, that this ‘ent really real. If’n ya want me back, yeh’ll need to work harder, and yeh’ll need to get out of this place. Now.”

Antioch stood. Cadmus nodded at Ignotus, who released his hold on the scrambler charms, and the tavern again bustled to life. It was a cheap trick, using the Spirit Stone in such a fashion, but there was so little time left to learn its full potential. It was only years before that they had completed their Hallows. He thought back to the–

–He opened his eyes. ‘Hugues de Payens’, as he had called himself, was tired. He wanted to go home, he wanted so desperately to be with his brother, and his husband, reunited once more. Soon. So soon. His wet, bulbous eyes watched as the Hungarians ransacked the place. As the minutes passed, their anger became more visible. The plain wooden cross on the wall seemed to mock them as they searched in vain. He did not move from his armchair when he finally spoke.

“Keresitek ember akit a villám megjelölt és ő kioltja majd a csillagokat.”

The commander of the Záh Kardja stopped. His subordinate looked at him, warily. “A kövér ember túl sokat tud . Meg kell ölni őt,” but the commander shook his head.

“Azt, hogy könnyen kitalálja , öreg. Mondja el, hogyan működik az Igazi Kereszt, és akkor lehet élni.”

Hugues laughed. It was an undignified, wheezing laugh, wet with rheum and phlegm. They were here to finish that girl’s work, what she had started in Sontag. He stood up, prompting the death squad to raise their blade-wands. He dismissively waved his hand and walked to his desk. He closed his eyes, and let his Magic flow into the room. A small metal plate materialized on the table. As it did, the wooden cross transmuted into cold, chilling iron.

Soon, Ignotus. Soon.

He reminded himself that, despite different methods, they all fought on the same side against the same enemy. He walked over to the commander and presented him with the plate. For a moment, he looked into the man’s eyes.

“Láttam az előrejelzések is. Most van itt az ideje . Vedd ezt , és vele együtt legyőzni az utolsó ellenség.”

The commander was young, perhaps in his thirties, with eyes that had seen far too many atrocities, won far too many Pyrrhic victories. He understood, though, and he nodded, taking the tablet. As soon as he claimed it, Hugues whirled around, whipped his wand from his robes, pointed the wand at his own chest and screamed: “AVADA KEDAVRA!”
\simpleline

“These words,” said Nicholas Flamel, “Are not called the Words of Power and Madness lightly.”

“Legend says they have been lost. But this is not the first time you have surprised me with hidden lore,” Dumbledore examined the words in the Pensieve with keen interest.

“Ah, but they are lost. They exist not in my mind, nor in the mind of any other. I could not recall them even if I wanted to. Nor could you. Go ahead, try to tell me the words you just heard spoke. Try anything you can to recall them.”

Dumbledore opened his mouth to speak, but could not. Faint echoes of the words swirled around in his head but there was nothing concrete for him to grasp. He understood the abstraction but couldn’t complete the metaphor. Interesting. He entered the Pensieve, listened to the incantation, and hastily wrote down a snippet of the words as they came to him.

…enim nidnah eltti lruo ytupmar ehtd nataog ehtl laf eht noitan igami erup nrets nedli ugdnazt narc nesor…

He had seen such a trick before, and just like with the Mirror, he saw the words, heard the words, but still, nothing. There was no comprehension. “Power and Madness, indeed, Master Flamel.”

“They are the Words of the First Enchanter. As with everything, there are levels upon levels of meaning to them. Legend has it that their true power was as an incantation that would lift the shackles of the Interdict. And yet, the Interdict has ensured that such knowledge could never pass from anything but one living mind to another. You will be using the words their meanest of purposes: a mere passcode to Merlin’s web of prophecy.”

“So I shall speak Merlin’s words in the heart of Merlin’s tower while holding Merlin’s line bequeathed to me by Merlin’s successors in order to access the knowledge that has been hoarded by Merlin’s web… It seems to me that you possess quite a great deal of knowledge and lore that once belonged to the Prince of Enchanters,” Dumbledore smiled with a twinkle, and yet there was a strange tone to his voice, a hint of warning. “Take caution, my old friends. I know that we have had words about your non-intervention in the past. A great deal of lives and pain could have been spared if you were to directly intercede on my behalf. And not just with this matter of mine, but with others, and with other heroes who have come before me.

“But I know you are no cowards, and I know you both to be good, decent people, and that you truly believe one death is too many and one minute wasted is one minute too long. You would not suffer such losses or make such sacrifices lightly, if not for the greater good, a higher cause, a deeper plan… A hidden hand, guiding things, if you will.”

“Choose your words carefully, Albus,” Nicholas spoke.

Perenelle held her hand up. “Peace, Nicholas, peace. Let our guest continue his speculation.” Inwardly, she rolled her eyes. Why did people expect her to talk like that, to say things like ‘Peace’?

“It is not my intent to speculate, only to observe. You have done me and my many great favors over the years, in exchange for lore that most would consider paltry in comparison to the magnitude of the aid. I am truly in your debt. However, you are not accustomed to fighting your battles directly or dealing in overly complex plots. You are not used to being, as they say, ‘in the trenches’, and I know all too well how it can be much easier to see a pattern from the outside but not the inside. So I will offer the following advice:

“When there are Three, there is always a leader, a trusted confidante, and a disposable lieutenant. I have come to know and love the both of you and it would trouble me greatly if any harm came to either of you. So please, for your own sake and not mine, know that with which you deal. And take caution.”

“Your words are well-intentioned. A lesser person may be inclined to take offense at your presumption, but we are no fools. You do know a great deal more about plotting than either of us, and it’s been centuries since I’ve personally slain a Dark Lord,” Perenelle spoke, softly, and turned to look at Nicholas. She wondered if that was too obvious? She was not very good at all this mystical, pretending-to-be-wise business.

Meldh could sense her apprehension, and he stepped in. “Indeed, Nell, indeed. Albus, this is one task in which you cannot fail. You must listen to the prophecies, and you must truly comprehend them. The world hangs in such precarious balance. The path to salvation is but a single thread that must pass through the eye of a single needle in a rainstorm. There is more than one Dark Lord that you will be defeating in the coming years. Beware εσχατος εχθρος, Albus.”
\simpleline

\DatePlace{The Department of Mysteries\\
Westminster, London\\
August 11, 1979, C.E.}

…THE ONE WITH THE POWER TO DEFEAT THE DARK LORD–
…STONE IN THE WINDOW MUST BE DESTROYED AGAINST THE ANVI–
…NEW RISE AT THE SOLSTICE IN THE AGE OF THE GOAT–
…CHOICE FOR ONE MUST BE MADE FOR THE TE–
…TEAR APART THE VERY STARS IN HEAV–
…STARS SHALL COME BY THE ONE MARKED BY LIGHTNI–
…SOLSTICE AND NONE WILL COME AFTE–
…THE DE-ARMED SERVANT SHALL BE FOUND WHEN SHE COME–
…REX QUANDAM, REXQUE FUTUR–
…ONLY BY THIS PATH SHALL THE CRUX SUCCEE–
…THE CHOICE TO FOLLOW THE PHOENIX OR SOLVE THE RIDDL–
…LIGHT SHALL PLANT A SEED IN THE DARKNE–
…IN A TIME OF GREAT STRIFE WHEN ALL WORLDS NARROW TO–
…DOWN ON THE SERPENTS’ CROWN THE STONE SHAL–

The words crashed in Dumbledore’s mind, an unceasing battery of waves breaking against the walls of his sanity. And yet, despite their fractured dissonance, when put together, they sang a song of such beauty, order, and righteousness that he could not deny the path he must walk.

He saw that all prophecy was true, and all prophecy had levels upon levels upon levels upon levels. The layers of meaning forked, and forked again, and bound back upon themselves. There was the Crux, he was the Crux, so was the boy, so was his mentor, so was his enemy, so was the boy’s enemy. And there was The Enemy, the Dark Lord, not just Grindelwald, not just Voldemort, but the One True Dark Lord, the enemy who had menaced all beings since the dawn of time. He Who Went By Many Names:

Mot. Thanatos. Yambe Akka. Shaitan. Death. εσχατος εχθρος.

It went by many names and came in many forms, and they were all warriors in this final battle. Even his love, even Gellert was a warrior, in his own misguided way. Dumbledore would fight as well. He would not fight against the Death of the Body, for he knew that those before him had already conquered that foe. He looked forward to the day when he would reunite with Aberforth and Ariana and all those who had come before him. He would not fight against the Death of the World, for another even greater warrior would soon rise to wear that mantle. He would not fight against the Death of the Spirit, for man had risen to great heights without his aid, and he would not fight against the Death of Knowledge, for that battle was fought on a daily basis.

No, Dumbledore would spend his last days fighting against the Death of Love. Hate had no place in Paradise, and an eternity without love would be nothing so more than Hell. As he stood in the ruined chambers of the Hall of Prophecy, he was filled with an intense love, a love for all of life and all people and all things, and he knew that for their sakes that not another minute was to be wasted in his task.

He began.
\simpleline

\DatePlace{Alderney\\
August 30, 1991, C.E.}

“It’s time, Meldh.”

Meldh paced restlessly back and forth in the cottage. The report was as clear as day: The Parselmouth who wears the Crown of the Serpents could locate the Stone, infallibly, and they were in grave danger. The evidence was so thorough, so overwhelming, so convincing that it simply had to be true.

Which meant, of course, that it was a bold-faced lie.

After a time, Meldh spoke. “The banished father has returned, and he has laid for us this new Path. We must follow it, and we must make it seem as though we are acting according to his design. It must be convincing, both to the Riddle boy and to Albus.

“One of us must go to Hogwarts. The Mirror cannot leave its grounds, we cannot risk that. We must visit in person, and we must maintain the ruse,” Perenelle was packing their things as Meldh was speaking, “Once the Stone is gone, we must be seen to age and wither and eventually die. Nicholas and Perenelle Flamel will be no more.”

Perenelle stood and faced him. He was tired. And he always spoke in that ridiculous, affected tone when he was tired like he was a character in a play. Really, they both were tired. She had been fighting for centuries. He had been fighting for centuries longer. But it was all coming to a head now. The final battle would come soon and the conduit would soon be destroyed, for good.

She stared at the eyes of her companion. She had a deep love for this man. There was, of course, no physical love. The difference in age was far too great, even now. He was Meldh would have called their love Philia, but he always was a bit ceremonious and used big, fancy words when everyday terms would suffice. After all, he called himself “Meldh”, which was just silly, in her opinion. There wasn’t anything wrong with Heraclius. To Nell, Meldh was simply her friend. And she loved him. It would pain her to be away from him after they had spent so much time together as Nicholas and Perenelle Flamel.

But one day, pain would be a thing of the past. Just a childish thing that humanity had outgrown, like Death and War and everything else. But until then, she had work to do.

