\chapter{The Day After Tomorrow}

\DatePlace{London\\
December 26, 1999}

Where have all the good men gone
and where are all the Gods?
Where’s the streetwise Hercules to fight the rising odds?
Isn’t there a white knight upon a fiery steed?
Late at night, I toss and I turn and I dream of what I need…

“I need a hero!” Natalie Kyros belted at the top of her lungs while drumming the beat on the steering wheel of her car. An enormous, older man with a walrus mustache glared at her from the next car over and yelled something indistinct which could not be heard over the music.

As she drove, she played idly with the small silver cross that hung around her neck, secured with a leather thong that looked quite ancient. She had worn it for as long as she could remember, which was odd because she didn’t even really believe in God in the first place. It gave her a distant sense of comfort, though. It reminded her of someone, somehow, something precious that was lost to her, but she could never quite put her finger on it.

It took longer than usual to find parking that day, given that someone had parked in her usual spot. She hurried past the rows of offices, placed her things down at her desk and grabbed her teacup, an delicate, fussy golden little thing that she held an unnatural fondness for.

As she waited for the kettle in the break room, she noticed that one of the offices that was typically empty had its lights on. She poked her head in, and watched as a tall man with Asiatic features unpacked his things from a box. His hair was cropped short, but still retained a bit of curl, and he looked up at Natalie just as she realized she was gawking.

Well, he was handsome! She couldn’t be blamed for staring. “New here?”

“Yeah. Research and Development. Cell phones, radio waves… boring stuff, really. You?”

Her eyes lit up a bit. “That’s my department! I mean, not my department like it’s mine, but that’s where I work. Natalie Kyros.” She held out her hand.

“Constantine Atreides. A pleasure.” He smiled at her.

“The pleasure is mine.” She realized that sounded much smoother in her head than it came out. She decided to quickly shift the focus of the conversation. “That’s an… interesting sculpture you’ve got there,” she remarked, pointing to a ceramic statue of a frog sitting on top of a chicken egg.

“Yeah, I found it in an old store a few years back in my hometown. Small little place in Greece. You from there, too?”

“What?”

“Are you Greek, too? Your last name,” he offered awkwardly.

“Oh! I thought you meant… nevermind. Yeah. Moved here a while back though.” As she spoke, she twirled her teacup around on her finger.

“That’s a cute teacup you have there.”

She laughed, but then stopped – “Ah, damnit. The kettle’s boiling! Well, it was nice to meet you! I’m sure all see you around, Gus.”

“Yeah… no one calls me that,” he called after her as she disappeared around the corner.

“Well, I do now!’
\simpleline

Michael and Petunia Verres sipped their tea in silence. The holidays were always the hardest. Ever since they lost their son almost eight years ago, the holidays did little except remind them of what once was.

They had tried to start over, build a family anew, but things never seemed to work out, and it was difficult at times to not blame the other. If only Michael spent less time at work, if only Petunia spent less time stressing over the little things, maybe things would be different.
\simpleline

“All right, Weseltons! Let’s all sit down!” Martha Weselton tried her best to shout over the din of her seven adult children who had all made it home for Christmas for the first time in who-knows-how-long.

Frank and Jerry, the twins, were giving Reggie grief about the dismal performance of Coventry City so far this season. “Not a single home win this year, mate,” Frank said, somberly.

“It’s not looking good.” Jerry confirmed.

“Well… at least we’re beating Watford!”

“Ha! ‘At least we’re beating Watford’, he says!” Frank mocked.

“Our great-aunt Tessie would have a sporting chance of beating Watford.” Jerry nodded.

From across the room, the sing-song voice of Ben’s wife, Flora, called out to the door. “‘Zat wouldn’t be Nicky, would it?”

Frank and Jerry jumped up and stumbled over themselves to greet him.

“I’m sorry to have kept you waiting, but my walk has become rather sillier recently,” Nicky quoted.

“How are your parents, then? Still at St. Michaels?” Paul asked courteously.

Frank and Jerry both murmured “Prat…” underneath their breath as Nicky replied. “Yeah. Still at St. Michaels.”

“I SAID, ALL RIGHT WESELTONS, LET’S ALL SIT DOWN!” Martha shouted at the top of her lungs, and all noise ceased immediately. She had spent what felt like half a decade preparing this meal, and she wasn’t about to let it get cold.
\simpleline

In a quiet corner of a quiet restaurant, Cid Gillory and Nicholas Nickleby sipped wine from glasses filled from an oversized bottle.

“This all still feels like a dream, Cid.”

“Well, here’s to never waking up then.”

They clinked glasses, and smiled.
\simpleline

Janus Tucker rolled over in bed. He had slept in for the first time in, he couldn’t remember how long. He still wasn’t completely convinced that this wasn’t all just a fantastic dream.

So he decided to double check.

He ran his fingers through the thick, chestnut curls of his companion in the bed next to him. Kayla Rahl sleepily looked up at him. “Good morning, Janus,” she said and smiled.

Janus was tall, with sharp features and platinum blonde hair. Even in a state of undress, he still managed to look aristocratic. “You’re still here.”

“Of course I’m still here, where would I go?”

“I… I’m not sure. When I woke up this morning, I had this strange feeling, like I had lost something that was precious.” He wasn’t quite sure what had come over him. “I’m… I’m just glad you’re still here.”

She said nothing in return, and instead just smiled radiantly at him. He couldn’t help but think she looked like a Goddess, stretched decadently across the sheets of his exorbitantly expensive bed.

“We better get dressed and ready. I doubt John will allow a moment’s rest, even the day after Christmas.” As he spoke, he was already pulling on a fresh dress shirt and buttoning it up. “Do you think he’ll be surprised?”

“Oh, I think he’s known this was going to happen long before we did. And even if he didn’t, you know that he’d just say that he did.”

Janus smiled at that. “Clever little bastard.”

Kayla nodded. “Clever little bastard, indeed.”
\simpleline

\DatePlace{The John Snow Center for Medicine}

John Merlin waited dramatically at his desk, his back facing the entrance to his office. Someone was knocking at the door. He was deliberately waiting. The rapping grew more insistent.

“Enter,” he spoke.

The door opened, and Kayla walked inside with Janus close behind. “That’s a rather rude way to greet your guests, don’t you think?” she said.

John spun around in his office chair, grinning. “Hello, lovebirds.” His disheveled black hair fell across  his green eyes which held a teasing, yet good-natured expression.

Kayla elbowed Janus, “Told you!”

Janus rolled his eyes. “So what’s on the agenda for today?”

“Oh, the same thing we do every day. Try to save the world.”
