\chapter{Infernal Galop}

\DatePlace{Almost There\\
27999 AD}

Harry scratched idly at the walls of the spacecraft, staring intently at the Professor. He didn’t have much time.

“What does it all add up to?”

The Professor replied immediately. “Can’t you guess?”

“Are you addressing me?” Harry fired back.

“Is there anyone else?”

“Who?”

“How would I know?”

“Why do you ask?”

“Are you serious?”

Harry cocked his head. “Was that rhetoric?”

The Professor rolled his eyes, and spoke in curt condescension. “No.”

Harry clapped his hands together with glee.  “Statement.  Two all.  Game point.”

Muttering under his breath, the Professor resumed the game. “What’s the matter with you today?”

“When?”

“What?”

“Are you deaf?”

“Am I dead?”

“Yes or no?”

“Is there a choice?”

“Is there a God?”

The Professor’s eyes narrowed. “Foul. No non-sequiturs. Three-two. One game all.”

Harry quickly launched into the next round, hoping to catch his foe off-guard. “What’s your name?”

“What’s yours?”

“You firs–”

Harry stopped himself, but it was too late. The Professor interjected: “Statement.  One – Love.”

Time to try again, perhaps a different angle. “What’s your name when you’re at home?”

“What’s yours?”

“When I’m at home?”

“Is it different at home?”

“What home?”

“Haven’t you got one?”

“Why do you ask?”

“What are you driving at?”

“What… is… your… name?”

The Professor held up a hand. “Repetition.  Two – Love.  Match point.”

“Who do you think you are?”

It was the Professor’s turn to clap. “Rhetoric.  Game and match!”

“Damnit.”

“Yes, damnit indeed. Even after all this time, I’m still one level above you.” He ran his fingers through his hair. His body, which Harry had allowed him, was biologically perfect, as if someone took Tom Riddle at age 40, allowed the eyes to reflect 25,000 years worth of experience, give or take a few millennia, and gave him the fitness level of an 18-year old.

“We’re almost there, you know. You can feel us going faster, perceptually,” Harry observed.

“Yes, that was always an open question, wasn’t it? What does it feel like? I am certainly eager to learn something new.”

Outside the windows, the stars began to stretch slightly, rather than simply passing by.

“It’s strange. Abstractly, it seems like such an enormously long amount of time. I mean, think about how much happened and how much changed between my first year of Hogwarts, and the day we set foot onto this craft, how much I learned, how much you learned in that time. We’ve surpassed that by several orders of magnitude. You’d think we’d be gods by this point.”

“No, you thought we’d be gods. My expectations, on the other hand, were tempered by my own time in exile.”

“Oh yeah. I forgot about that. I forget about a lot, now that I think about it.”

“Have you forgotten about them?”

Harry looked up, and spoke with firm resolution. “Never.”

“Even though you know full well what you intend to do to them, and to yourself?”

Harry pressed his face against the window, and watched as the universe began to reorient itself as they flung headlong into the void. “It’s not like they’re dying. They’re just… changing. They’ll still be the same people, just…” Harry fumbled, dumbly for a word. “Different. Kind of like what I did to you when I conquered you for the first time.”

The Professor sighed, “Yes, yes, you never fail to miss an opportunity to remind me of that. But it is different. My memories were merely locked away. This would be a Sacrifice, and furthermore, we are seeing to it that the only means of restoring a Sacrifice is utterly obliterated.”

“Yes, but what enforces the rules of a Sacrifice?”

The Professor considered this for a moment. “Yes, I see your point. But, to continue that logic, this suggests that everything we are about to do is in vain, because it could all happen again.”

Harry grinned. “Yes, and that’s quite the point. Again, and again, and again.”

Most of the time, their planning went unspoken. If you looked back, they had spent the overwhelming majority of their perceptual lifespans sharing the same set of rather limited experiences, being confined to a small spacecraft for most of them. As a result, their thought patterns tended to be quite similar. When they felt the need to speak, it was typically to shine light on a more esoteric aspect of the plan, or weigh the benefits of two different courses of action. Even though either one could likely independently deduce the other’s thought processes, time wasted was still time wasted, regardless of how much time you had.

“Almost there, now.”

The universe was fully curved by this point. On one side was the entirety of Everything, and on the other side was Nothing.

A thought occurred to the Professor. “Mr. Potter, would you care for some token gesture of comfort? A hand on the shoulder, or something along those lines?” Even now, The Professor had difficulty concealing the begrudged tone of his voice.

“Yes, I would, actually,” Harry held out his hand, expectantly, “See how good it feels to be nice?”

The Professor sighed dramatically, and grasped Harry’s hand. Together, hand-in-hand, they watched as they passed the event horizon. The Universe was now falling away from them as they descended further into nothingness. Paradoxically, it was not blackness that they experienced. The point of light of the universe that grew further and further away also grew progressively brighter as they fell toward and away from the horizon.

As they hurtled towards that point of infinite brightness, Harry took the opportunity to point out that all of this would have been fundamentally impossible without Magic to help cheat things along.

“I suppose you should enjoy it while it lasts.” He lifted his hand, which was still clasping Harry’s, slightly. “And this, too.”

In complete defiance of Actual Physics, they reached the point they had intended, the Singularity, the center of the black hole at the center of our galaxy. Instead of being pulled apart with the force of a trillion trillion suns, they were simply engulfed by whiteness. Their spacecraft had incinerated a long time ago, perhaps infinitely long ago, but as expected, they still had the supplies they needed. Also as expected, their guest was waiting for them, curiously examining his surroundings.

Albus Dumbledore somehow looked both younger and older. His wrinkles were gone, his glasses were gone, his hair was auburn instead of gray, and yet he still managed to convey a sense of great age. Despite the fact that Harry had now lived hundreds of times longer than Dumbledore, he still could not help feeling like a child in the presence of his old Headmaster.

Dumbledore tensed, startled, when he turned and saw Tom Riddle.

“He cannot hurt you.” He spun around. Harry James Potter-Evans-Verres was walking towards him, sprightly and upright, wearing sweeping robes over a Muggle suit.  “Prophecy has proven true. I have come to rescue you, Headmaster.”

“Harry. You have… You have aged. How long has it been?”

“Oh, about 25,000 years, objectively. Subjectively? Well, for you, it’s been but a few seconds, has it not?”

“It has, but I am trapped outside of Time. I would fear for you, but you are The Crux, the Once and Future King. You do not carry the look of sadness about you, which lightens my heart greatly. Dare I ask if you have succeeded? Did you tear apart the very stars in heaven to save its people?”

“Ah… Well…. Not quite.” Harry tittered on his feet a bit, “In fact, we’re not really out of the woods just yet.”

“I confess, I do not understand. But then again, that is more than fair turnabout. Would you do an old man the honor of explaining what I must do?”

“You’re going to destroy the world.” Harry offered. Dumbledore raised an eyebrow, but Harry continued. “Right now, back on Earth, a different Earth, a gentleman who goes by the name of John Merlin thinks that he is about to save the world. You are going to ensure that he does not. In fact, you are going to ensure that he destroys the world.”

Dumbledore nodded pleasantly, as if indulging an over-enthusiastic student’s explanations of Quidditch tactics. “Mmm, quite interesting. The same Merlin, I’m sure, of lore? Merlin of the Line, First of Atlantis?”

“Yes. Him, Headmaster. The Fall of Atlantis created our world, the world of Magic, and that world cannot be allowed to persist.”

“That sounds counterproductive, does it not?” he asked innocently, without any hint of insolence or challenge.

Harry had expected this resistance. “Yes, it does. And I struggled with it myself, believe me. But I can explain it to you, and I will give you as much time as you need so that you can understand, and are satisfied.”

“I don’t think that’s necessary, Harry. I believe I grasp the broad strokes,” Dumbledore spoke casually, his light tone in complete contrast to the gravity of the situation.

Harry was nonplussed. “I.. um. Okay?”

“Magic isn’t real.”

Harry nodded in satisfaction. Dumbledore understood that much. This was good, it would skip a large chunk of the explanation.

The Headmaster continued. “It’s as clear, plain, and obvious to anyone who bothers to consider the problem for longer than a few moments. Like the logic of a dream, Magic ‘just works’, does it not? In all other things natural, this is not the case. I have studied some of your physics, Harry, and I am quite fond of that Richard Feynman fellow. I have read enough to know that the true nature of reality is strange, bizarre, obtuse, and most importantly, operates based on principles that are in no way reflective of our expectations.

“Magic, on the other hand, is strange, bizarre, obtuse, but most importantly, operates precisely how we would expect it to. It does not seem likely to me that we as humans would have grown into this by accident. Thus, there is but one conclusion we can come to.”

Harry’s brow furrowed. “We are in agreement, so far, Headmaster… But, I notice that I am confused. My conception of you is, well, forgive me for saying this, but I had never known you to be very scientifically-minded. In fact, I seem to recall you being quite dismissive of our Muggle arts.”

“Indeed, Harry. But Death approaches, and it is the sort of Death that even I would flee, screaming from. Not the death of the body, which I, as an old man, though not as old as you are now, had grown to accept, and you had chastised me for not a few short months ago.”

Harry had to mentally dissect that sentence to extract any meaning from it, and as he was doing so, Dumbledore continued. “No, I refer to the death of the soul. All souls. The horrible Nothingness at the end of everything. You know the end of which I speak.”

Harry’s eyes were growing wide. He didn’t think Wizards knew or cared about such unimportant things as, oh, Heat Death.

“Magic is famous for its opaqueness and requires little understanding, only skill. As long as the great minds of the world rely on Magic as a crutch, they will be paralyzed, crippled, limited and Bound, powerless to prevent the ever-encroaching darkness which not only will consume their world, but all worlds.

“Magic can give us neither truth nor knowledge. It gives us nothing more or less than the deepest and most desperate desires of our hearts, and it does not do, Harry, to dwell on dreams and forget to live.”

Harry was dumbfounded. The Professor watched, amused, at his speechless protege, and Dumbledore let the silence hang heavy in the air for a few moments before he cheerfully offered, “Does that sound about right?”

“It.. Yes, it does. How…” Harry started.

“How do I know this? My boy, I am still the Wise Old Man in your story, and it is the job of the Wise Old Man to surprise you in ways that you least expect. But enough about me. I want to hear from you. I want to hear why you have not despaired at this inevitable fate, why you have not resigned yourself to blackness, why you travelled to the end of time with nothing but hope to guide you.”

Harry took a deep breath. He had been preparing for what seemed like an eternity for this. “Because, Headmaster, until the day that the last sentient being in this universe, in any universe, snuffs out of existence, there is still hope. As long as there exists someone, anyone who loves life enough to fight for it, they fight on behalf of all beings, human or otherwise, dead or alive.

“If I should die in that fight, it would be sad, yes. But it would not be the end, because someone, anyone would still fight to reclaim me from the depths of the void. I know that this is true because it is precisely what I would do. Preventing death is insufficient. I would not stop fighting until I could reverse death, until I restored every sentient being that ever lived a life that was taken from them.

“As long as there are those who think as I do, who believe as strongly in the value of Life as I do, there will always be those who will fight on behalf of those who have fallen before them. As long as there are those who will fight against the darkness, there is hope. As I told you once before, Headmaster, there is light in the world, and it is us.”

Dumbledore smiled, a tear in his eye. “I used to wonder what would become of you. I am proud to have lived to see it.” He removed a delicate handkerchief from the pocket of his robes. “But look at me, I’m getting sentimental when we should be discussing your plan. Tell me more, my dear Harry.”

It was a rather unceremonious end to Harry’s speech. In some dim part of his mind, he had expected something more. An applause, perhaps? At least he had earned a tear at the corner of his former Headmaster’s eye. “So, um… where were we?”

“I believe you were telling me that I would have to help this ‘Merlin’ in his quest to mistakenly destroy the world.”

“Ah, yes. So. Umm. After that, you’ll be able to harness the power of the cataclysm to escape from the forces keeping you here at the End of Time. You must travel to the moment that you hand the Stone over to Professor Quirrell, and you must sabotage it before you allow him to take ownership of it.”

Dumbledore raised an eyebrow, but Harry couldn’t help but feel it seemed rather perfunctory. “Sabotage? Sounds titillating. And then what shall I do?”

Harry was becoming unnerved by Dumbledore’s cavalier attitude. “Then you, well, you need to let him trap you again.”

“Mmm hmm, and then?”

“And then you will be forced back here, to the End of Time.”

Dumbledore was nodding pleasantly again. “Oh dear. And what misadventures can I expect to follow?”

Harry spoke haltingly, the realization slowly dawning on him. “And then you talk to us… Damn it!  You already knew all of this. You already knew all of this was going to happen. Because you’ve done it all before.”

Dumbledore did not reply, he simply folded his hands behind his back and beamed.

“So you already know that you’re…”

“I’ll spare you from having to say it, my boy. Yes, I know.”

Harry trod delicately, “How, um… how many times have you done this so far?”

“The answer is that I do not know. I stopped counting around one hundred and seven.”

At this, the Professor, who was busy reading a book on a bench nearby, laughed.

“Well… In that case, we have a final pair of gifts to give you, that I suspect you will greatly need.” Harry removed from his robes a thin stone rod, “The Line of Merlin Unbroken.” Harry handed the Headmaster the wand with reverence.

Tom Riddle stood up from the bench, put down his book, and strode forward. “And, Headmaster, my old enemy and future friend, I also have a gift for you.” He produced a thick glass bottle filled with viscous black ichor, and handed it to Dumbledore.

“Headmaster,” Harry spoke, “You need to understand something. You have a choice at this moment. All worlds, ultimately, have narrowed down to this one choice. Although I am, as you say, the Crux, you still must make this choice of your own volition. You would be sacrificing your Life, and your Time. Truly.”

“Harry. You know my views on this matter. I have already sacrificed my Life and my Time for your sake, for the sake of the world. Besides, you are the Boy Who Lived. I’m sure you’ll find a way to rescue me again.” He smiled with a twinkle in his eye. “Now, how do I leave this place?”

“Oh yes,” Harry smiled at him. “We are in King’s Cross, are we not? I think that if you decided to move on, you would be able to… Let’s say.. Board a train.”

“And where would it take me?”

“Beyond.” said Harry simply.

Silence again.

“Goodbye, Headmaster. And thank you, truly.”

“Do not pity the dead, Harry James Potter-Evans-Verres. Pity those who live without love.”

And with that, he boarded a train, and disappeared into the tunnel. His world was all worlds. His world was fire. His world was void. His world was formless nothing. His world was stagnant death. He focused all his being onto the two worlds that mattered. In one, the star burned, rendering the world insane, its very soul raging with white plasma that rendered such abstract notions as space and time irrelevant in the face of the heat.

He looked across the span of eons into the other world, wherein the Boy Who Lived was dead.

He had all of eternity to rehearse the ritual, and yet, he still felt the slightest bit of nervousness. He began, using the Line of Merlin to harness the magic of all worlds into this one final act. He was Dumbledore, destroyer of worlds, creator of life. Everything that ever was and everything that ever will be in the universe had led him to this moment. This moment that must come to pass because it already has.

All worlds had narrowed to two, and from those two all worlds would be born. When the Line of Merlin could bear the strain no longer, it glowed white, and began to fray apart at the edges. Dumbledore could feel the eyes of prophecy in the heavens upon him, about to be torn apart by the ritual of Harry’s creation. The Headmaster connected the nodes in his mind, and it was done.

Sagitarrius A* collapsed in less than a second. It folded in upon itself, and distorting the very fabric of reality as it did so. In the final moments of its life, the Headmaster flitted through some dimension that only exists in the minds of addled physics professors, and emerged to the place Beyond Time, where he was connected by the power of the ritual.

In the world he left behind, a galaxy was born. A galaxy where the balance of the world was held in place by a single thread of time, a universe where the only means by which the Crux could succeed was to seek the path of the Scorpion and the Archer. The fires of prophecy would burn with the white light of truth; they had come to be because they had come to be.

He entered a world that was already born, a world where the balance of the world was held in place by a single thread of time that had, until now, been snipped. It was at this very moment that he emerged. He was outside the Mirror. No, he was inside? It was a curious sensation, experiencing time backwards. He took a brief moment to consider the runes that had once been incomprehensible to him. He smiled.

Inside and outside the Mirror, the world was hazy, a confounded miasma of abstraction, like some sort of halfway lucid dream that someone had pressed the rewind button on. His brother took the stone from him. Not from him. From his shadowform. It was not him?  He was talking to his brother. But it wasn’t him. He was saying the war was over. They had won. That was true, no? It was Time. Time to stop holding on to the stone. Give away the stone. Yes.

You could change the past, you just had to think about it at the right time.

As he moved further backwards in time, he considered the tools of his craft that he still had upon his person. The Line of Merlin. The Stone of Permanence. The Elder Wand. A curious glass bottle.

A curious glass bottle of viscous black ichor.
\simpleline

Minutes later

“No,” said Albus Dumbledore. “No, no, NO! ”

Into the hand of the Albus Dumbledore flew from his sleeve his long, dark-grey wand, and in his other hand, as though from nowhere, appeared a short rod of dark stone.

Albus Dumbledore threw these both violently aside, just as the building sense of power rose to an unbearable peak, and then disappeared.

And then, there was nothing.

He lay facedown, listening to the silence. He was perfectly alone. Nobody else was there. A long time later, or maybe no time at all, it came to him that he must exist, must be more than disembodied thought, because he had a sense of touch, and the thing against which he lay existed too.

He sat up. His body appeared unscathed. He touched his face. He was not wearing glasses anymore. His beard was gone. As were the wrinkles.

Albus turned slowly on the spot, and his surroundings seemed to invent themselves before his eyes. A wide-open space, bright and clean. He was the only person there, except for–

He recoiled. Not out of shock, but simply because he knew that he had recoiled and he knew that he had to recoil at the sight of Tom Riddle sitting on a bench, idly reading a curiously thick book. Albus Dumbledore smiled to himself.


