\chapter{The Fault in Our Stars}

\DatePlace{Hogwarts\\
May 19, 1999}

It was time.

Having seen what he came to see, Merlin strode down the steps of the Astronomy Tower, feeling the intricacies of his Lines, the “Ley Lines”, as they directed him towards the familiar hallways on the Seventh floor.

Ah, yes.

The Room of Requirement was likely the most secure possible location within Hogwarts, but it was still insufficient. It, as with all things, ultimately bent to his Will. The walls separated, opening obligingly for him, and the Cup of Dawn stood flickering on the desk that lay within. It reminded him of his last visit to Hogwarts, roughly six hundred years ago, when he had claimed the girl who called herself Nell, and formed The Three.

Within moments, he was heading down the stairs, following the din of battle, looking for a Wizard, any Wizard, and the first he saw was a young man with dirty blonde hair and Gryffindor robes. Merlin commanded him silently, holding out the Goblet of Fire. Without words, he conveyed the intent of the contract between them:

I, Merlin of the Line, solemnly swear to bind your Will for the remainder of your days. The penalty if I should fail to do so or if I set you free will be the irrevocable destruction of the artifact of power responsible for enforcing this contract. 

“Do you agree?”

The wizard nodded, meekly.

“Then you are free to go.”

With that, Merlin dissipated into a white mist and took his leave of Hogwarts. As he faded to nothingness, The Cup of Dawn, the Holy Grail, the Goblet of Fire, the last remaining anchor of Yanotuk of the Cups, purged itself in a glorious conflagration, and its presence in the world of Magic was no more
\simpleline

\DatePlace{Nurmengard}

“Heh… heh…  You have come. You who are marked by lightning and who shall tear apart the stars,” the broken form of Gellert Grindelwald rasped. “I know what you seek. It will not work as you think it should; its true Master has passed from this world centuries ago.”

Merlin paid him no mind, and scanned the walls of the prison cell. “Hidden in plain sight, I see.” He took the unassuming wooden cross from the wall, and unfolded it. “But you are wrong, Mr. Grindelwald. Its true Master has simply yet to claim it.”

Grindelwald observed unflinchingly as the Cross expanded into unseen dimensions, a shape of limitless possibility and infinite connection, a shape with the potential to reach across Time and Space to ensure that life could be preserved. He was awed, but also bitter: he knew the ways of Dark Lords. Because he had been allowed to see this much, it either meant that either he or the beauty he was witnessing would soon be destroyed. He did not allow himself the luxury of Hope.

As if in response to the unanswered question, Merlin answered, “You will not die at my hand, Gellert Grindelwald.”

He forced out a chuckle. “I see. You play tricks with words, stranger. How then, shall I die this day?”

When Merlin was satisfied with the preparations, he turned to the former tyrant. “No tricks. You will live through the Transmigration, and perhaps if you are lucky, you will live long enough to have the opportunity to save the ones you love.”

Grindelwald’s eyes narrowed. “And what do you know of the ones I love?”

“Do you know of Gabriel’s Horn?”

Non-sequiturs. Of course, the stranger would not provide a straight answer. Why would he? Grindelwald had no choice but to play along. “With which the Archangel announces Judgement Day, no?”

“Yes, that too. But it is also, a shape, an impossible shape: a horn that holds a finite volume but has an infinite surface area. In truth, any impossible shape would have sufficed, but I felt the metaphor was quite apt.” A moment of silence passed as Merlin observed the Cross unfolding itself from all dimensions, withdrawing its influence. It was desperately trying to follow its master’s command, to form a shape that could not exist. It stretched, ever onward, ever upward, thinner and thinner, until after an indeterminate amount of time, the Cross simply ceased to exist; it had stretched far enough into the infinite as to be fundamentally, irrevocably inaccessible from this world or any world.

And with that, the last anchor of Neirkalatia of the Cross, once known as Natalie Kyros, and once known before that by an even more ancient name, had purged itself in a tangle of geometric impossibility, and its presence in the world of Magic was no more.
\simpleline
\DatePlace{Boston. New York. Mexico City. Sao Paolo. Lagos. Shanghai. Delhi. Moscow. Tokyo. London.}

City after city, Merlin arrived, summoning the remaining armies of the Unseelie, leading them as their Lord and master. The leji retracted their claws from the amygdala of their prey, the bundiwig halted their ceaseless devouring, the viscs unfolded their wings and swooped lazily down at his beck and call, and the gaunts let loose a low wail of anguish at a Sharpening cut short.

Their Master called and they must obey.

They followed him through the space in between space, until he had collected them all. It was time to go home.
\simpleline

\DatePlace{On the shores of the lake of teeth, where the black hills end, Tír inna n-Óc}

Unfettered by mere physical boundaries, the Unseelie celebrated the Gorging, blissfully unaware of their impending end. The many-toothed maw of the Lake opened itself, and Merlin stepped inside, traversing a staircase of compacted sinew, feces, and bone. Deeper he travelled, into the heart of Tír inna n-Óc, until he found the Sleeper himself, Nog-Nandh of the Flame, trapped in eternal nightmare, endlessly punishing himself.

With a simple exertion of Merlin’s will, a thought was burned indelibly into the mind of the sleeping titan, one which removed the leaden chains of guilt: “It was my fault.”

As Adnan Nejem slowly roused from his slumber, the world that he had created by sheer force of Will began to crumble around them; it was a world whose sole purpose was to inflict a punishment that was no longer necessary.

On the surface of Tír inna n-Óc, the hate-spires began to melt, and the oppressive yellow fog that had blanketed the landscape at this time of morning-night unrolled, allowing for clear sight across the horizon for the first time in millennia. The Unseelie which had gathered could now see, in full horror, the destruction of their home. The House of Fingers closed itself, taking with it vast chunks of landscape as it retracted into the arms of Nog-Nandh, who was stretching, rubbing his eyes.

The Archway on the Island of Woe crumbled to dust, and with it, the Lake of Teeth drained into the Unclean Maw, which opened for the last time as the Sleeper yawned. There was no escape for the Unseelie, who had taken refuge in the Amygdalan Temple. But as the last echoes of fear ebbed from the mind of Adnan Nejem, this too was no more.

The Sleeper awoke from his slumber. The horror-realm he had created, the last remaining anchor of Nog-Nandh of the Flame, purged itself in a fire of redemption, and its presence in the world of Magic was no more.

Tír inna n-Óc ceased to endure.
\simpleline

\DatePlace{The Tower\\
December 25, 1999}
It was almost time. Merlin was alone now, watching expectantly as the spider-like cracks spread across the surface of the Mirror. He felt the lines dissolve as wands began to break, as all of their arts ceased, and the blood of Atlantis failed. When the cracks reached the edge of the Mirror, it shattered with a noise that silenced the world, and the Transmigration began.
\simpleline

\DatePlace{A Dying World\\
Now, Then, Later}

The world was empty, except for Merlin, and a tiny spherical silver ship half a galaxy away.

The stars were beautiful. Redemption was at hand.

The world would die, this was true, but the world’s peoples would live on. After all, there can only be one king upon the chessboard. There can only be one piece whose value is beyond price.

For indeed, the fires of the soul are great and burn as bright as the stars: 100 billion stars in the galaxy. 100 billion lives created and lost.

As he sensed the craft draw closer and closer to the event horizon, he went about his work, one life at a time. There were too many to return all at once; the rebuilt world was not yet ready to support that. But a handful, a select few, he chose to rise again, moments before the Transmigration. The rest would be kept safe, shepherded through Time and history by the Line of Merlin Unbroken.

At the end of it all, there was one final star that was to be extinguished: Sagitarrius A*, the terminus of the Path of the Scorpion and Archer. Merlin observed Dumbledore arriving through the tunnel, as he observed all moments: the Fall of Atlantis, the Transmigration, and the Death of his World. Later. Then. Now.

He held out the Line for but an instant, a fractional moment in time as the star collapsed into a singularity and all the points became one.
\simpleline

\DatePlace{Albion\\
24,001 B.C.}

Merlin emerged on the back end of eternity, his Will nearly broken, his Life nearly lost. He desperately reached out backward across the span of Time, but he knew what the result would be. Nothing. What he created should have been Paradise. Instead, it was Hell. They were gone, all of them, and he had no one to blame but himself. No one was left to blame but himself.

He looked forward into the depths of Time, and what he saw horrified him further. So many were already dead at his hand, but there were to be more. Countless more. Billions more. With every day that passed, the Curse that now bound this world and all worlds would grow. New lives would be created, lives so unbelievably, horrifyingly, tragically short. There was nothing he could do to save them.

Not yet, at least.

He had looked through Time once more, and in that instant of calculation, he embraced all possible futures and saw only one. The world must be unbound. The world must be sacrificed for the sake of all other worlds. There was no other way. How could there be? This was his burden, and every moment wasted, a new tragedy was born.
